### 2020-09-27 A-BasicCommom/CVPR2021/cvpr.tex
1.cvpr manuscripts.

% This version of CVPR template is provided by Ming-Ming Cheng.
% Please leave an issue if you found a bug:
% https://github.com/MCG-NKU/CVPR_Template.

\documentclass[review]{cvpr}
%\documentclass[final]{cvpr}

\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}

% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,colorlinks,bookmarks=false]{hyperref}

\def\cvprPaperID{6666} % *** Enter the CVPR Paper ID here
\def\confYear{CVPR 2021}
%\setcounter{page}{4321} % For final version only

\begin{document}

%%%%%%%%% TITLE
\title{Lower Bounds on Rate of Convergence of Matrix Products in All Pairs Shortest Path of Social Network}

\author{Dezhou Shen\\
Department of Computer Science\\
Tsinghua University\\
Beijing, CN 100084\\
{\tt\small sdz15@mails.tsinghua.edu.cn}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
}

\maketitle

%%%%%%%%% ABSTRACT
\begin{abstract}
  With the rapid development of social network applications, social network has become an important medium for people to interact.
  For the shortest distance calculation task of all nodes in networks, Alon \etal ~\cite{alon1997exponent} proposed an algorithm with matrix multiplication,
  combining with the distance product association law and block matrix multiplication, all pairs shortest path algorithm on networks has time bound \(O({logn2n^3 \over B})\) .
  In practical applications, considering the scale-free characteristics of social networks and the precision limitations of floating-point operations on computer hardware,
  the shortest path algorithm has an improved time bound \(O({14n^3 \over B})\). Based on the above theory, I propose an all node pairs shortest path algorithm that combines sparseness judgment and convergence judgment,
  leveraging the distance product algorithm with matrix multiplication, distance product exchange law, block matrix multiplication, scale-free characteristics of social networks,
  and limitation of floating-point operations on hardware. Tested the theory on a social network dataset with 8508 actors, the algorithm has a performance improvement of 0.39 to 36.2 times compared to the Alon N algorithm on the CPU and GPU.
\end{abstract}

%%%%%%%%% BODY TEXT
\section{Introduction}

In recent years, driven by Asian film industries such as China and India, the global box office has maintained a steady growth trend, and with the rapid development of social network applications, more and more actors use social network for work communication.
Therefore, social network has become an important tool for film distribution, marketing, promotion and an important medium for film actors and fans to interact.
Previous studies have lacked research on actors' social networks; PageRank, an existing node influence algorithm, is not accurate in evaluating social network influence.
Social network feature measurement is an important task in social network data mining, some network characteristics, such as betweenness and closeness, need to calculate the distances between nodes.
As a result, efficient calculation of the shortest path is one of the key problems in social network measurement.
There was Floyd-Warshall~\cite{floyd1962algorithm,warshall1962theorem} algorithm for calculating node distances, Aho and Hopcroft~\cite{aho1974design} proved that distance product is homogenous to matrix multiplication,
Alon \etal ~\cite{alon1997exponent} proposed an algorithm to calculate distance product by matrix multiplication, Zwick~\cite{zwick2002all} optimized distance product using fast matrix multiplication,
and Garbow and Winograd~\cite{garbow1985scaling} proposed an algorithm for distance product using matrix multiplication with element bound.
From time bound of matrix multiplication, Strassen~\cite{strassen1969gaussian}, Coppersmith and Winograd~\cite{coppersmith1987matrix}, Davie and Andrew ~\cite{davie2013improved}, Le Gall~\cite{le2014powers} proposed the block matrix multiplication with time bound of \(O(n ^ {2.807})\), \(O(n^{2.376})\), \(O(n^{2.374})\), \(O(n^{2.373})\).
Lam \etal ~\cite{lam1991cache} proposed that the progressive time complexity of matrix multiplication with a cache block size of $B*B$ is \(O({2n^3 \over B}+{n^2})\) ,
and Goto and Geijn~\cite{goto2008anatomy} proposed a new library, OpenBLAS, which has a higher cache hit rate and improved time cost in matrix computation on X86 CPU, compared to modern BLAS libraries, such as Intel MKL v8.1.1, ESSL v4.2.0 and ATLAS v3.7.11.
From point of view of matrix sparseness of network adjacent matrix, for sparse matrix multiplication, SciPy  and CuPy  use SciPy-sparse and CuPy-cuSparse to achieve efficient sparse matrix multiplication on CPU and GPU.
For dense matrix multiplication, NumPy, SciPy, CuPy and ND4J use OpenBLAS, cuBLAS and other libraries to achieve efficient block matrix multiplication on CPU and GPU.
Therefore, a feasible method for calculating shortest path of full node pairs is: represents the network by adjacent matrix, then makes all matrix elements exponential, computes matrix multiplication and finally takes logarithm of matrix elements.
This procedure is called distance product epoch. Iterate several times to get full node pairs shortest path result.
Further, analysis time complexity of the distance product calculation and iteration of each epoch. For time complexity of distance product, matrix multiplication is the most complex sub-procedure;
(1) For distance product optimization, Zwick U proposed distance product with block matrix multiplication, therefore choose proper computation device library with optimized cache for block matrix multiplication.
(2) For iteration optimization, because Aho A V proved distance product is isomorphic to the matrix multiplication, and regard to that the distance product association law, optimize the iteration process by last distance product result reuse.

%-------------------------------------------------------------------------

\section{Dataset and Hardware}
From January 1, 2011 to March 31, 2015, collected the film actors' social network following relationship, profile information, and text message on Sina Weibo. In all, collected 8508 actors, 577775 edges and 12526114 Sina Weibo posts.
I used a server with two Intel Xeon E5-2620 v4 CPUs and one NVIDIA GeForce GTX 1080 Ti GPU, in total 32 cores with frequency of 2.1Ghz, 128G system memory and 11G GPU memory in my experiment.

%-------------------------------------------------------------------------

\section{Comparison on block matrix multiplication implementtation}
On the actors' social network, this paper implements Strassen block matrix multiplication, Copper-Winograd block matrix multiplication and OpenBLAS matrix multiplication. On the computer hardware, compared the $8508*8508$ matrix multiplication time-cost.
The block matrix multiplication based on Strassen and Coppersmith-Winograd takes 6 seconds for one iteration of matrix multiplication, and with OpenBLAS library it takes only 4 seconds.
The performance of optimized cache block matrix multiplication, such as OpenBLAS matrix computation library, is higher than Strassen and Copper-Winograd block matrix multiplication algorithm.
Therefore, distance product algorithm proposed by Zwick U with OpenBLAS block matrix multiplication is obviously better than distance product algorithm with Strassen and Coppersmith-Winograd.

%-------------------------------------------------------------------------

\section{Time bound of distance product algorithm with cache optimized block matrix multiplication}
For a fully connected network, the graph has a maximum diameter of $n-1$, so using result reuse method in distance product, that is use the last distance product calculation result, the matrix multiplication is a $log_2(n-1)$.
Albert ~\cite{albert1999diameter} estimated the number of documents on the Internet is $N=8*10^8$, diameter D=18.59, found that social networks, the Internet and other complex networks have scale-free and small world phenomenon, diameter is much smaller than node number.
I present the corresponding nodes counts, diameters and logarithm of diameters in Table 1, from the observation there is formula (1):
In social networks, the number of nodes n, with cache block size $B*B$, according to the formula (9-10), the matrix product calculation iteration times does not exceed the number of $\lceil{logD}\rceil$, recall that Monica D. Lam proved that matrix multiplication time bound is \(O({2n^3 \over B}+{n^2})\) ,
thus Alon N algorithm time bound is \(O({logD 2n^3 \over B})\) , use the equation (1) result, time bound is \(O({ log(logN) 2n^3 \over B})\). With the limitation of the floating-point operation on computer hardware, take a network of number of nodes $N<10^{308}$ as example,
as shown in Table 1, see that the shortest path calculation iterations time is no larger than $logD \approx {log(logN)}<7$, that is, the number of calculation iterations does not exceed the magic number 7, bringing a stronger time bound of \(O({14n^3 \over B})\).
In another words, with the floating-point operation accuracy limitation on computer hardware, on scale-free complex networks, the all node pairs shortest path algorithm time bound is \(O({14n^3 \over B})\).

%-------------------------------------------------------------------------

\section{Shortest Path Algorithm with Block Matrix Multiplication}
Definition 1 Matrix Product The outer product of two matrices with the same dimension K is the $(K*1)*(1*K)$ matrix multiplication, obtaining $(K*K)$ square matrix, see formula (2):

Definition 2 Distance Product For a matrix $\Bbb A$ with a dimension of $n*m$ elements, $\Bbb B$ with a dimension of $m*n$ elements, the distance product of $\Bbb A$ and $\Bbb B$ is matrix $\Bbb C$ with a dimension of $n*n$ elements, for $1 \leq i$, $j \leq n$, satisfying formula (3):

%-------------------------------------------------------------------------

\subsection{Maximum calculation}

Calculate the largest value of the square matrix element $\widetilde X$, such as the formula (4):

\subsection{Exponential calculation}

The calculation accuracy of different computer hardware is in line with the IEEE floating-point operation standard~\cite{ieee1985ieee}, first of all, transform the input matrix by exponential process, that is, taking the number of nodes as the base, taking the difference between the largest value of the element $\widetilde X$ and the matrix elements as exponential, as shown in the formula (5).
As shown in Table 2, for actors' social network with 8508 nodes, the diameter of the network does not allow to exceed 9.8 and 78.4 when calculating a precision of 32-bit floating-point and 64-bit floating-point, otherwise the exponential operation on the computer platform will overflow.

\subsection{Matrix multiplication}
Use different matrix libraries to speed up the matrix multiplication on computer hardware, as shown in Table 3, choose proper device-based optimized matrix multiplication libraries according to different conditions, such as matrix sparseness, calculation hardware, and programming language.

%-------------------------------------------------------------------------
\subsection{Logarithm calculation}
Take non-zero elements of the matrix multiplication result to the element logarithm process, that is, the number of network nodes as the base, the element in the matrix multiplication result as the true number, then round down the logarithm result,
after that take difference between twice of the largest input matrix element value $\widetilde X$ and the logarithm result as result, such as formula (6).

\subsection{Distance product association law}

From the iteration of the shortest path calculation, suppose A, B, C is the square matrix, according to the association law of distance product, there is a formula (7):
Matrix multiplication has association law, and the distance product is isomorphism to matrix multiplication, so simplify the shortest path iteration process as formula (8):
Since matrix multiplication has association law and distance product is isomorphism to matrix multiplication, similarly, distance product has an association law.
Under the premise of the shortest path matrix $L^{(n-1)}$ given the adjacent matrix and the $n-1$ edge, calculate the shortest path matrix $L^{(n)}$ with n edges, and extend the shortest path of the $n-1$ edge by edge.
Calculating the shortest path matrix $L^{(n)}$ can be completed as formula (9):
As can be seen from the nature of the shortest path in the graph, the shortest path from the any of two nodes does not exceed $n-1$, so there is formula (10):
Definition 3 Result Reuse in Distance Product According to the nature of the equation (8), the process of calculating the shortest path iteration using the last result of distance product follows in turn, as shown in formula (11).
The shortest path needs to be calculated $\lceil{log_2(n-1)}\rceil$ times matrix multiplication, from the formula (10), it can be seen that $(n-1)\leq2^{\lceil{log_2(n-1)}\rceil}$ is the same as the simple shortest path matrix calculation result $L^{(n-1)}$, so there is a formula (12):
Obviously, the result reuse method saves $n-2-\lceil{log_2(n-1)}\rceil$ times of matrix multiplication.
Observe the shortest path calculation process of the actors' social network, the adjacent matrix is shown in Figure 1a, and the change of result in each iteration is shown in Figure 1b-d, the shortest path result matrix converges gradually, each element stabilizes as iterations goes.

\section{Architecture design}

\subsection{Sparseness judgment}

As shown in Table 3, observing the adjacent matrix represented by the network diagram is usually a sparse matrix, and becomes a dense matrix during the iteration,
and one idea of optimization is to use sparse matrix multiplication to speed up the iteration when the matrix is sparse, and when the matrix becomes denser, the sparse matrix multiplication is much time-consuming.
Taking the actors' social network as an example, the non-zero element of the adjacent matrix of 8508 nodes is 617958, and the non-zero element of the matrix is 0.8536\% of the total element,
which is a typical sparse matrix. Consider the advantages of sparse matrix multiplication algorithm, a threshold for triggering sparse matrix multiplication is set,
and when the proportion of non-zero-value elements entered is less than the 10\% threshold, performs sparse matrix multiplication.

\subsection{Convergence judgment}

For networks with unknown diameters, the calculation results can be made using convergence method, and for the calculation process of reaching convergence,
i.e. $L^{(n-1)}=L^{(n)}$, should be regarded as the program termination of iteration, and the calculation of the matrix product method is completed by the equation (4).

\subsection{The shortest path algorithm that fuses sparseness judgment and convergence judgment}

Based on Alon N distance product algorithm, utilize the sparseness judgment of the input matrix and the calculation result convergence judgment, named PowerLawBound shortest path algorithm,
PowerLaw refers to the network conforming to the power law distribution, Bound refers to the precision of floating-point operation, and the name implies two characteristics of the limitation
of floating-point precision on the scale-free social network and the computer hardware, the algorithm process is shown in Algorithm 1.

\section{Experiment}

Firstly, compared to the Floyd-Warshall algorithm implemented on CPU, the Alon N algorithm implementation with matrix multiplication of block cache optimization on GPU has a time performance improvement, see Table 4.

\section{Conclusion}
This paper discussed the use of matrix multiplication in calculation of the all pairs shortest path with association law, and the time bound of Alon N distance product algorithm with cache optimization block matrix multiplication is \(O({logn2n^3 \over B})\).
Further strengthen the conditions, in social networks with scale-free characteristics, under the precision limit of floating-point operation on hardware, limiting the network diameter to avoid floating-point operation overflow in the calculation process,
the algorithm has lower time bound \(O({14n^3 \over B})\). With the above limitations, this paper proposed a novel shortest path algorithm, named PowerLawBound, combining matrix sparseness judgment and calculation result convergence judgment.
PowerLaw here refers to the network conforming to the power law distribution, and Bound refers to the accuracy of floating-point operations on hardware.
The experimental results show that PowerLawBound algorithm improves time performance by 39\% to 36.2 times compared to the Alon N algorithm on the hardware of CPU and GPU.

%\begin{quote}
%\begin{center}
%    An analysis of the frobnicatable foo filter.
%\end{center}
%
%   In this paper we present a performance analysis of our
%   previous paper [1], and show it to be inferior to all
%   previously known methods.  Why the previous paper was
%   accepted without this analysis is beyond me.
%
%   [1] Removed for blind review
%\end{quote}
%
%
%An example of an acceptable paper:
%
%\begin{quote}
%\begin{center}
%     An analysis of the frobnicatable foo filter.
%\end{center}
%
%   In this paper we present a performance analysis of the
%   paper of Smith \etal [1], and show it to be inferior to
%   all previously known methods.  Why the previous paper
%   was accepted without this analysis is beyond me.
%
%   [1] Smith, L and Jones, C. ``The frobnicatable foo
%   filter, a fundamental contribution to human knowledge''.
%   Nature 381(12), 1-213.
%\end{quote}
%
%If you are making a submission to another conference at the same time,
%which covers similar or overlapping material, you may need to refer to that
%submission in order to explain the differences, just as you would if you
%had previously published related work.  In such cases, include the
%anonymized parallel submission~\cite{Authors14} as additional material and
%cite it as
%\begin{quote}
%[1] Authors. ``The frobnicatable foo filter'', F\&G 2014 Submission ID 324,
%Supplied as additional material {\tt fg324.pdf}.
%\end{quote}
%
%Finally, you may feel you need to tell the reader that more details can be
%found elsewhere, and refer them to a technical report.  For conference
%submissions, the paper must stand on its own, and not {\em require} the
%reviewer to go to a techreport for further details.  Thus, you may say in
%the body of the paper ``further details may be found
%in~\cite{Authors14b}''.  Then submit the techreport as additional material.
%Again, you may not assume the reviewers will read this material.
%
%Sometimes your paper is about a problem which you tested using a tool which
%is widely known to be restricted to a single institution.  For example,
%let's say it's 1969, you have solved a key problem on the Apollo lander,
%and you believe that the CVPR70 audience would like to hear about your
%solution.  The work is a development of your celebrated 1968 paper entitled
%``Zero-g frobnication: How being the only people in the world with access to
%the Apollo lander source code makes us a wow at parties'', by Zeus \etal.
%
%You can handle this paper like any other.  Don't write ``We show how to
%improve our previous work [Anonymous, 1968].  This time we tested the
%algorithm on a lunar lander [name of lander removed for blind review]''.
%That would be silly, and would immediately identify the authors. Instead
%write the following:
%\begin{quotation}
%\noindent
%   We describe a system for zero-g frobnication.  This
%   system is new because it handles the following cases:
%   A, B.  Previous systems [Zeus et al. 1968] didn't
%   handle case B properly.  Ours handles it by including
%   a foo term in the bar integral.
%
%   ...
%
%   The proposed system was integrated with the Apollo
%   lunar lander, and went all the way to the moon, don't
%   you know.  It displayed the following behaviours
%   which show how well we solved cases A and B: ...
%\end{quotation}
%As you can see, the above text follows standard scientific convention,
%reads better than the first version, and does not explicitly name you as
%the authors.  A reviewer might think it likely that the new paper was
%written by Zeus \etal, but cannot make any decision based on that guess.
%He or she would have to be sure that no other authors could have been
%contracted to solve problem B.
%\medskip
%
%\noindent
%FAQ\medskip\\
%{\bf Q:} Are acknowledgements OK?\\
%{\bf A:} No.  Leave them for the final copy.\medskip\\
%{\bf Q:} How do I cite my results reported in open challenges?
%{\bf A:} To conform with the double blind review policy, you can report results of other challenge participants together with your results in your paper. For your results, however, you should not identify yourself and should not mention your participation in the challenge. Instead present your results referring to the method proposed in your paper and draw conclusions based on the experimental comparison to other results.\medskip\\
%
%\begin{figure}[t]
%\begin{center}
%\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
%   %\includegraphics[width=0.8\linewidth]{egfigure.eps}
%\end{center}
%   \caption{Example of caption.  It is set in Roman so that mathematics
%   (always set in Roman: $B \sin A = A \sin B$) may be included without an
%   ugly clash.}
%\label{fig:long}
%\label{fig:onecol}
%\end{figure}
%
%\subsection{Miscellaneous}
%
%\noindent
%Compare the following:\\
%\begin{tabular}{ll}
% \verb'$conf_a$' &  $conf_a$ \\
% \verb'$\mathit{conf}_a$' & $\mathit{conf}_a$
%\end{tabular}\\
%See The \TeX book, p165.
%
%The space after \eg, meaning ``for example'', should not be a
%sentence-ending space. So \eg is correct, {\em e.g.} is not.  The provided
%\verb'\eg' macro takes care of this.
%
%When citing a multi-author paper, you may save space by using ``et alia'',
%shortened to ``\etal'' (not ``{\em et.\ al.}'' as ``{\em et}'' is a complete word.)
%However, use it only when there are three or more authors.  Thus, the
%following is correct: ``
%   Frobnication has been trendy lately.
%   It was introduced by Alpher~\cite{Alpher02}, and subsequently developed by
%   Alpher and Fotheringham-Smythe~\cite{Alpher03}, and Alpher \etal~\cite{Alpher04}.''
%
%This is incorrect: ``... subsequently developed by Alpher \etal~\cite{Alpher03} ...''
%because reference~\cite{Alpher03} has just two authors.  If you use the
%\verb'\etal' macro provided, then you need not worry about double periods
%when used at the end of a sentence as in Alpher \etal.
%
%For this citation style, keep multiple citations in numerical (not
%chronological) order, so prefer \cite{Alpher03,Alpher02,Authors14} to
%\cite{Alpher02,Alpher03,Authors14}.
%
%
%\begin{figure*}
%\begin{center}
%\fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
%\end{center}
%   \caption{Example of a short caption, which should be centered.}
%\label{fig:short}
%\end{figure*}
%
%%------------------------------------------------------------------------
%\section{Formatting your paper}
%
%All text must be in a two-column format. The total allowable width of the
%text area is $6\frac78$ inches (17.5 cm) wide by $8\frac78$ inches (22.54
%cm) high. Columns are to be $3\frac14$ inches (8.25 cm) wide, with a
%$\frac{5}{16}$ inch (0.8 cm) space between them. The main title (on the
%first page) should begin 1.0 inch (2.54 cm) from the top edge of the
%page. The second and following pages should begin 1.0 inch (2.54 cm) from
%the top edge. On all pages, the bottom margin should be 1-1/8 inches (2.86
%cm) from the bottom edge of the page for $8.5 \times 11$-inch paper; for A4
%paper, approximately 1-5/8 inches (4.13 cm) from the bottom edge of the
%page.
%
%%-------------------------------------------------------------------------
%\subsection{Margins and page numbering}
%
%All printed material, including text, illustrations, and charts, must be kept
%within a print area 6-7/8 inches (17.5 cm) wide by 8-7/8 inches (22.54 cm)
%high.
%%
%Page numbers should be in footer with page numbers, centered and .75
%inches from the bottom of the page and make it start at the correct page
%number rather than the 4321 in the example.  To do this fine the line (around
%line 20)
%\begin{verbatim}
%\setcounter{page}{4321}
%\end{verbatim}
%where the number 4321 is your assigned starting page.
%
%
%
%%-------------------------------------------------------------------------
%\subsection{Type-style and fonts}
%
%Wherever Times is specified, Times Roman may also be used. If neither is
%available on your word processor, please use the font closest in
%appearance to Times to which you have access.
%
%MAIN TITLE. Center the title 1-3/8 inches (3.49 cm) from the top edge of
%the first page. The title should be in Times 14-point, boldface type.
%Capitalize the first letter of nouns, pronouns, verbs, adjectives, and
%adverbs; do not capitalize articles, coordinate conjunctions, or
%prepositions (unless the title begins with such a word). Leave two blank
%lines after the title.
%
%AUTHOR NAME(s) and AFFILIATION(s) are to be centered beneath the title
%and printed in Times 12-point, non-boldface type. This information is to
%be followed by two blank lines.
%
%The ABSTRACT and MAIN TEXT are to be in a two-column format.
%
%MAIN TEXT. Type main text in 10-point Times, single-spaced. Do NOT use
%double-spacing. All paragraphs should be indented 1 pica (approx. 1/6
%inch or 0.422 cm). Make sure your text is fully justified---that is,
%flush left and flush right. Please do not place any additional blank
%lines between paragraphs.
%
%Figure and table captions should be 9-point Roman type as in
%Figures~\ref{fig:onecol} and~\ref{fig:short}.  Short captions should be centred.
%
%\noindent Callouts should be 9-point Helvetica, non-boldface type.
%Initially capitalize only the first word of section titles and first-,
%second-, and third-order headings.
%
%FIRST-ORDER HEADINGS. (For example, {\large \bf 1. Introduction})
%should be Times 12-point boldface, initially capitalized, flush left,
%with one blank line before, and one blank line after.
%
%SECOND-ORDER HEADINGS. (For example, { \bf 1.1. Database elements})
%should be Times 11-point boldface, initially capitalized, flush left,
%with one blank line before, and one after. If you require a third-order
%heading (we discourage it), use 10-point Times, boldface, initially
%capitalized, flush left, preceded by one blank line, followed by a period
%and your text on the same line.
%
%%-------------------------------------------------------------------------
%\subsection{Footnotes}
%
%Please use footnotes\footnote {This is what a footnote looks like.  It
%often distracts the reader from the main flow of the argument.} sparingly.
%Indeed, try to avoid footnotes altogether and include necessary peripheral
%observations in
%the text (within parentheses, if you prefer, as in this sentence).  If you
%wish to use a footnote, place it at the bottom of the column on the page on
%which it is referenced. Use Times 8-point type, single-spaced.
%
%
%%-------------------------------------------------------------------------
%\subsection{References}
%
%List and number all bibliographical references in 9-point Times,
%single-spaced, at the end of your paper. When referenced in the text,
%enclose the citation number in square brackets, for
%example~\cite{Authors14}.  Where appropriate, include the name(s) of
%editors of referenced books.
%
%\begin{table}
%\begin{center}
%\begin{tabular}{|l|c|}
%\hline
%Method & Frobnability \\
%\hline\hline
%Theirs & Frumpy \\
%Yours & Frobbly \\
%Ours & Makes one's heart Frob\\
%\hline
%\end{tabular}
%\end{center}
%\caption{Results.   Ours is better.}
%\end{table}
%
%%-------------------------------------------------------------------------
%\subsection{Illustrations, graphs, and photographs}
%
%All graphics should be centered.  Please ensure that any point you wish to
%make is resolvable in a printed copy of the paper.  Resize fonts in figures
%to match the font in the body text, and choose line widths which render
%effectively in print.  Many readers (and reviewers), even of an electronic
%copy, will choose to print your paper in order to read it.  You cannot
%insist that they do otherwise, and therefore must not assume that they can
%zoom in to see tiny details on a graphic.
%
%When placing figures in \LaTeX, it's almost always best to use
%\verb+\includegraphics+, and to specify the  figure width as a multiple of
%the line width as in the example below
%{\small\begin{verbatim}
%   \usepackage[dvips]{graphicx} ...
%   \includegraphics[width=0.8\linewidth]
%                   {myfile.eps}
%\end{verbatim}
%}
%
%
%%-------------------------------------------------------------------------
%\subsection{Color}
%
%Please refer to the author guidelines on the \confYear~web page for a discussion
%of the use of color in your document.
%
%%------------------------------------------------------------------------
%\section{Final copy}
%
%You must include your signed IEEE copyright release form when you submit
%your finished paper. We MUST have this form before your paper can be
%published in the proceedings.
%
%Please direct any questions to the production editor in charge of these
%proceedings at the IEEE Computer Society Press:
%\url{https://www.computer.org/about/contact}.

{\small
\bibliographystyle{ieee_fullname}
\bibliography{cpvr}
}

\end{document}

### 2020-09-27 A-BasicCommom/CVPR2021/formula_render.py

@@ -1,0 +1,9 @@
+from handcalcs.decorator import handcalc
+
+@handcalc()
+def function(n, B):
+    y = n**2.8
+
+
+latex, _ = function(1,2)
+print(latex)

### 2020-09-27 A-BasicCommom/CVPR2021/cvpr.tex
1.CVPR draft v0.1.0 version.

@@
 
+\usepackage[linesnumbered,lined,boxed,commentsnumbered]{algorithm2e}
 % Include other packages here, before hyperref.
@@
 \begin{abstract}
-  With the rapid development of social network applications, social network has become an important medium for people to interact.
-  For the shortest distance calculation task of all nodes in networks, Alon \etal ~\cite{alon1997exponent} proposed an algorithm with matrix multiplication,
-  combining with the distance product association law and block matrix multiplication, all pairs shortest path algorithm on networks has time bound \(O({logn2n^3 \over B})\) .
-  In practical applications, considering the scale-free characteristics of social networks and the precision limitations of floating-point operations on computer hardware,
-  the shortest path algorithm has an improved time bound \(O({14n^3 \over B})\).
-Based on the above theory, I propose an all node pairs shortest path algorithm that combines sparseness judgment and convergence judgment,
-  leveraging the distance product algorithm with matrix multiplication, distance product exchange law, block matrix multiplication, scale-free characteristics of social networks,
-  and limitation of floating-point operations on hardware.
-Tested the theory on a social network dataset with 8508 actors, the algorithm has a performance improvement of 0.39 to 36.2 times compared to the Alon N algorithm on the CPU and GPU.
+  For the shortest path calculation task of all nodes in networks, Alon \etal ~\cite{alon1997exponent} proposed an algorithm with matrix multiplication.
+  In this paper, with the distance product exchange law and block matrix multiplication, all pairs shortest path algorithm has a lowered time bound of \(O({logn2n^3\over B})\).
+  In empirical study of social networks, the shortest path algorithm has an improved lower time bound \(O({14n^3 \over B})\).
+  And I propose an all node pairs shortest path algorithm that leveraging matrix sparseness judgment, convergence judgment, distance product matrix multiplication, distance product exchange law,
+  scale-free characteristics of the social networks and limitation for floating-point operations on modern hardware.
+  Tested on a movie actors social network dataset, proposed algorithm has a improvement of 39\% to 36.2 times in performance on CPU/GPU platforms comparing to Alon \etal algorithm.
 \end{abstract}
@@
 
-In recent years, driven by Asian film industries such as China and India, the global box office has maintained a steady growth trend, and with the rapid development of social network applications, more and more actors use social network for work communication.
+In recent years, driven by Asian film industries such as China and India, the global box office has maintained a steady growth trend, and with the rapid development of social network applications, more and more actors use social networks for work communication.
 Therefore, social network has become an important tool for film distribution, marketing, promotion and an important medium for film actors and fans to interact.
-Previous studies have lacked research on actors' social networks; PageRank, an existing node influence algorithm, is not accurate in evaluating social network influence.
+Previous studies have lacked research on actors' social networks, PageRank, an existing node influence algorithm, is not accurate in evaluating social network influence.
 Social network feature measurement is an important task in social network data mining, some network characteristics, such as betweenness and closeness, need to calculate the distances between nodes.
@@
 Therefore, a feasible method for calculating shortest path of full node pairs is: represents the network by adjacent matrix, then makes all matrix elements exponential, computes matrix multiplication and finally takes logarithm of matrix elements.
-This procedure is called distance product epoch. Iterate several times to get full node pairs shortest path result.
-Further, analysis time complexity of the distance product calculation and iteration of each epoch. For time complexity of distance product, matrix multiplication is the most complex sub-procedure;
-(1) For distance product optimization, Zwick U proposed distance product with block matrix multiplication, therefore choose proper computation device library with optimized cache for block matrix multiplication.
-(2) For iteration optimization, because Aho A V proved distance product is isomorphic to the matrix multiplication, and regard to that the distance product association law, optimize the iteration process by last distance product result reuse.
+This procedure is called distance product epoch.
+Iterate several times to get all node pairs shortest path result.
+Further, analysis time complexity of the distance product calculation and iteration of each epoch.
+For time complexity of distance product, matrix multiplication is the most complex subprocedures;
+(1) For distance product optimization, Zwick proposed distance product with block matrix multiplication, therefore choose proper computation device library with optimized cache for block matrix multiplication.
+(2) For iteration optimization, because Aho proved distance product is isomorphic to the matrix multiplication, and regard to that the distance product association law, optimize the iteration process by last distance product result reuse.
 
@@
 
-\section{Dataset and Hardware}
-From January 1, 2011 to March 31, 2015, collected the film actors' social network following relationship, profile information, and text message on Sina Weibo.
+\section{Dataset And Hardware}
+From January 1, 2011 to March 31, 2015, I collected the film actors' social network following relationship, profile information, and text message on Sina Weibo.
 In all, collected 8508 actors, 577775 edges and 12526114 Sina Weibo posts.
@@
 
-\section{Comparison on block matrix multiplication implementtation}
+\section{Comparison On Block Matrix Multiplication Implementtation}
 On the actors' social network, this paper implements Strassen block matrix multiplication, Copper-Winograd block matrix multiplication and OpenBLAS matrix multiplication.
@@
 
-\section{Time bound of distance product algorithm with cache optimized block matrix multiplication}
-For a fully connected network, the graph has a maximum diameter of $n-1$, so using result reuse method in distance product, that is use the last distance product calculation result, the matrix multiplication is a $log_2(n-1)$.
-Albert ~\cite{albert1999diameter} estimated the number of documents on the Internet is $N=8*10^8$, diameter D=18.59, found that social networks, the Internet and other complex networks have scale-free and small world phenomenon, diameter is much smaller than node number.
+\section{Time Bound Of Distance Product Algorithm With Cache Optimized Block Matrix Multiplication}
+For a fully connected network, the graph has a maximum diameter of $n-1$, so using result reuse method in distance product, that is use the last distance product calculation result, the matrix multiplication times is $log_2(n-1)$.
+Albert ~\cite{albert1999diameter} found that social networks, the Internet and other complex networks have scale-free characteristics and small world phenomenon, thus network diameter is much smaller than the number of network nodes.
 I present the corresponding nodes counts, diameters and logarithm of diameters in Table 1, from the observation there is formula (1):
-In social networks, the number of nodes n, with cache block size $B*B$, according to the formula (9-10), the matrix product calculation iteration times does not exceed the number of $\lceil{logD}\rceil$, recall that Monica D.
-Lam proved that matrix multiplication time bound is \(O({2n^3 \over B}+{n^2})\) ,
-thus Alon N algorithm time bound is \(O({logD 2n^3 \over B})\) , use the equation (1) result, time bound is \(O({ log(logN) 2n^3 \over B})\).
-With the limitation of the floating-point operation on computer hardware, take a network of number of nodes $N<10^{308}$ as example,
-as shown in Table 1, see that the shortest path calculation iterations time is no larger than $logD \approx {log(logN)}<7$, that is, the number of calculation iterations does not exceed the magic number 7, bringing a stronger time bound of \(O({14n^3 \over B})\).
-In another words, with the floating-point operation accuracy limitation on computer hardware, on scale-free complex networks, the all node pairs shortest path algorithm time bound is \(O({14n^3 \over B})\).
+In social networks, the number of nodes $n$, with cache block size $B*B$, according to the formula (9-10), the matrix product calculation iteration times does not exceed the number of $\lceil{log\Bbb D}\rceil$, recall that Lam \etal proved that matrix multiplication time bound is \(O({2n^3 \over B}+{n^2})\) ,
+thus Alon \etal algorithm time bound is \(O({log\Bbb D2n^3\over B})\) , use the equation (1) result, time bound is \(O({ \log(\log{N})2n^3\over B})\).
+With the arithmetic limitation on the floating-point operation, \eg take a network of number of nodes $N<10^{308}$
+as shown in Table 1, see that the shortest path calculation iterations time is no larger than $\log{\Bbb D}\approx{\log(\log{N})}<7$, that is, the number of calculation iterations does not exceed the magic number 7,
+bringing a stronger time bound of \(O({14n^3\over B})\).
+In another words, with the floating-point operation accuracy limitation on computer hardware and complex networks scale-free characteristics, all node pairs shortest path algorithm time bound is \(O({14n^3\over B})\).
 
@@
 
-\section{Shortest Path Algorithm with Block Matrix Multiplication}
-Definition 1 Matrix Product The outer product of two matrices with the same dimension K is the $(K*1)*(1*K)$ matrix multiplication, obtaining $(K*K)$ square matrix, see formula (2):
+\section{Shortest Path Algorithm With Block Matrix Multiplication}
 
-Definition 2 Distance Product For a matrix $\Bbb A$ with a dimension of $n*m$ elements, $\Bbb B$ with a dimension of $m*n$ elements, the distance product of $\Bbb A$ and $\Bbb B$ is matrix $\Bbb C$ with a dimension of $n*n$ elements, for $1 \leq i$, $j \leq n$, satisfying formula (3):
+Definition 1 (Outer Product Matrix Multiplication) Given matrices \(\Bbb A \in \Bbb R^{m*r}\), \(\Bbb B \in \Bbb R^{r*n}\) and \(\Bbb C \in \Bbb R^{m*n}\), the outer product is:
+\begin{equation}
+\Bbb C = \Bbb C  + \Bbb A(:,k)\bullet \Bbb B(k,:) , k \in (1,r)
+\end{equation}
 
+Given two vectors \(\textsc x\), \(\textsc y\), and matrix \(\Bbb A\), having \(\Bbb A \in \Bbb R^{m*n}\), \(\textsc x \in \Bbb R^{m}\) and \(\textsc y \in \Bbb R^{n}\) the outer product \(\bullet\) is defined by:
+\begin{equation}
+a_{ij} = a_{ij} + x_i * y_j, i \in (1,m), j \in (1,n)
+\end{equation}
+
+Definition 2 (Distance Product Matrix Multiplication) Given matrices \(\Bbb A \in \Bbb R^{m*r}\), \(\Bbb B \in \Bbb R^{r*n}\) and \(\Bbb C \in \Bbb R^{m*n}\), the distance product is:
+\begin{equation}
+  \Bbb C = \min(\Bbb C, \Bbb A(:,k)\odot \Bbb B(k,:)) , k \in (1,r)
+\end{equation}
+
+Given two vectors \(\textsc x\), \(\textsc y\), and matrix \(\Bbb A\), having \(\Bbb A \in \Bbb R^{m*n}\), \(\textsc x \in \Bbb R^{m}\) and \(\textsc y \in \Bbb R^{n}\) the distance product \(\odot\) is defined by:
+\begin{equation}
+a_{ij} = \min(a_{ij} , x_i + y_j), i \in (1,m), j \in (1,n)
+\end{equation}
 %-------------------------------------------------------------------------
+%\begin{figure}[t]
+%\begin{center}
+%\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
+%   \includegraphics[width=1.0\linewidth]{figure1.pdf}
+%\end{center}
+%   \caption{Adjacent matrix, each iterations and the result matrix visualization of actors' social network.
+(a) initial state after each round of calculation, (b) the result matrix after the first round of calculation, (c) the result matrix of the second round of calculation, (d) the third and in the same time last round of calculation, the all pairs nodes shortest path result matrix.}
+%\label{fig:long}
+%\label{fig:onecol}
+%\end{figure}
 
-\subsection{Maximum calculation}
+\begin{figure*}
+\begin{center}
+%\fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
+  \fbox{\rule{0pt}{2in} \includegraphics[width=0.9\linewidth]{figure1.pdf}}
+\end{center}
+   \caption{Adjacent matrix, each iterations and the result matrix visualization of actors' social network.
+(a) initial state after each round of calculation, (b) the result matrix after the first round of calculation, (c) the result matrix of the second round of calculation, (d) the third and in the same time last round of calculation, the all pairs nodes shortest path result matrix.}
+\label{fig:short}
+\end{figure*}
+
+\subsection{Maximum Calculation}
 
@@
 
-\subsection{Exponential calculation}
+\subsection{Exponential Calculation}
 
-The calculation accuracy of different computer hardware is in line with the IEEE floating-point operation standard~\cite{ieee1985ieee}, first of all, transform the input matrix by exponential process, that is, taking the number of nodes as the base, taking the difference between the largest value of the element $\widetilde X$ and the matrix elements as exponential, as shown in the formula (5).
-As shown in Table 2, for actors' social network with 8508 nodes, the diameter of the network does not allow to exceed 9.8 and 78.4 when calculating a precision of 32-bit floating-point and 64-bit floating-point, otherwise the exponential operation on the computer platform will overflow.
+The calculation accuracy of different computer hardware is in line with the IEEE floating-point operation standard ~\cite{ieee1985ieee},
+first of all, transform the input matrix by exponential transformation, to be specific, taking the number of nodes as the base,
+taking the difference between the largest value of the element $\widetilde X$ and the matrix elements as exponential, as shown in the formula (5).
+\eg For actors' social network with 8508 nodes, the diameter of the network does not allow to exceed 9.8 and 78.4 when calculating a precision of 32-bit floating-point and 64-bit floating-point,
+otherwise the exponential operation on the computer platform will overflow.
 
-\subsection{Matrix multiplication}
+\subsection{Matrix Multiplication}
 Use different matrix libraries to speed up the matrix multiplication on computer hardware, as shown in Table 3, choose proper device-based optimized matrix multiplication libraries according to different conditions, such as matrix sparseness, calculation hardware, and programming language.
@@
 %-------------------------------------------------------------------------
-\subsection{Logarithm calculation}
+\subsection{Logarithm Calculation}
 Take non-zero elements of the matrix multiplication result to the element logarithm process, that is, the number of network nodes as the base, the element in the matrix multiplication result as the true number, then round down the logarithm result,
@@
 
-\subsection{Distance product association law}
+\subsection{Distance Product Exchange Law}
 
-From the iteration of the shortest path calculation, suppose A, B, C is the square matrix, according to the association law of distance product, there is a formula (7):
+From the iteration of the shortest path calculation, suppose \(\Bbb A,\ \Bbb B,\ \Bbb C\) is the square matrix, according to the association law of distance product, there is a formula (7):
 Matrix multiplication has association law, and the distance product is isomorphism to matrix multiplication, so simplify the shortest path iteration process as formula (8):
@@
 
-\section{Architecture design}
+\begin{algorithm}
+\caption{Lower Bounds Convergence Matrix Products in All Pairs Shortest Path}\label{algorithm}
+\KwData{Adjacent Matrix $\Bbb W$, Matrix Row $n$, Network Diameter $\Bbb D$}
+\KwResult{Shortest path result $L^{(m)}$}
+$L^{(1)}\leftarrow \Bbb W$\;
+$m\leftarrow 1$\;
+\While{$m\leq \Bbb D$}{
+  $\Bbb A\leftarrow L^{(m)},\Bbb B\leftarrow L^{(m)},$\;
+  $x\leftarrow \min{(a_i,b_i)}, y\leftarrow \max{(a_i,b_i)}, i \in (1,n)$\;
+  Exponential transformation of matrices $\Bbb A\ and\ \Bbb B$\;
+    $a_{ij}^{'}={(n+1)}^{y-a_{ij}}$\;
+    $b_{ij}^{'}={(n+1)}^{y-b_{ij}}$\;
+  \eIf{$L^{(m)}$ is sparse}{
+    $\odot\leftarrow \bigcirc$//sparse matrix multiplication\;
+  }{
+    $\odot\leftarrow \otimes$//dense matrix multiplication\;
+  }
+  Given matrix $\Bbb C^{'}$, $\Bbb C^{'} \in \Bbb R^{n\times n}$\;
+  $\Bbb C^{'}\leftarrow \Bbb A^{'}\odot\Bbb B^{'}$\;
+  Logrithm transformation of matrix $\Bbb C^{'}$\;
+  $\Bbb C\leftarrow \log{\Bbb C^{'}}$\;
+  \If{$L^{(m)} \eq \Bbb C$}{
+    \bold{return}\ $L^{(m)}$\;
+  }
+  $L^{(2m)}\leftarrow \Bbb C$\;
+  $m\leftarrow 2*m$\;
+}
+\bold{return} $L^{(m)}$\;
+\end{algorithm}
 
-\subsection{Sparseness judgment}
+\section{Architecture Design}
 
-As shown in Table 3, observing the adjacent matrix represented by the network diagram is usually a sparse matrix, and becomes a dense matrix during the iteration,
+\subsection{Sparseness Judgment}
+
+As shown in Table 1, observing the adjacent matrix represented by the network diagram is usually a sparse matrix, and matrix gradually becomes dense during iterations,
 and one idea of optimization is to use sparse matrix multiplication to speed up the iteration when the matrix is sparse, and when the matrix becomes denser, the sparse matrix multiplication is much time-consuming.
@@
 
-\subsection{Convergence judgment}
+\subsection{Convergence Judgment}
 
@@
 
-\subsection{The shortest path algorithm that fuses sparseness judgment and convergence judgment}
+\subsection{The Shortest Path Algorithm Fusing Sparseness Judgment And Convergence Judgment}
 
-Based on Alon N distance product algorithm, utilize the sparseness judgment of the input matrix and the calculation result convergence judgment, named PowerLawBound shortest path algorithm,
-PowerLaw refers to the network conforming to the power law distribution, Bound refers to the precision of floating-point operation, and the name implies two characteristics of the limitation
-of floating-point precision on the scale-free social network and the computer hardware, the algorithm process is shown in Algorithm 1.
+Based on Alon \etal distance product algorithm, utilizing the sparseness judgment of the input matrix and the calculation result convergence judgment,
+with the network conforming to the power law distribution and the precision of floating-point operation, and the name implies two characteristics of the limitation
+of floating-point precision on the scale-free social network and the computer hardware, the algorithm process flow is shown in Algorithm 1.
 
@@
 
-Firstly, compared to the Floyd-Warshall algorithm implemented on CPU, the Alon N algorithm implementation with matrix multiplication of block cache optimization on GPU has a time performance improvement, see Table 4.
+Firstly, compared to Floyd-Warshall algorithm implemented on CPU, the Alon \etal algorithm implementation with matrix multiplication of block cache optimization on GPU has a time performance improvement, see Table 1.
+$PowerLawBound_{a-f}$ shows that using different libraries on CPU/GPU, the proposed algorithm has significant performance improvement over Alon \etal algorithm.
+
+\begin{table}
+\begin{center}
+\begin{tabular}{|l|c|}
+\hline
+Algorithm	& Time Cost \\
+\hline\hline
+Floyd-Warshall &	1055880s \\
+Alon \etal          &	594.7s \\
+$PowerLawBound_a$ 	&	427.9s \\
+$PowerLawBound_b$	&	328.4s \\
+$PowerLawBound_c$	&	95.0s \\
+$PowerLawBound_d$	&	45.0s \\
+$PowerLawBound_e$	&	19.32s \\
+$PowerLawBound_f$	&	15.98s \\
+\hline
+\end{tabular}
+\end{center}
+\caption{Performance comparison on different hardware. (a) CPU numpy library. (b) CPU scipy/numpy library. (c) GPU cuBLAS. (d) CPU openBLAS. (e) GPU CuPy. (f) GPU CuPy-sparse/CuPy.}
+\end{table}
 
 \section{Conclusion}
-This paper discussed the use of matrix multiplication in calculation of the all pairs shortest path with association law, and the time bound of Alon N distance product algorithm with cache optimization block matrix multiplication is \(O({logn2n^3 \over B})\).
-Further strengthen the conditions, in social networks with scale-free characteristics, under the precision limit of floating-point operation on hardware, limiting the network diameter to avoid floating-point operation overflow in the calculation process,
-the algorithm has lower time bound \(O({14n^3 \over B})\).
-With the above limitations, this paper proposed a novel shortest path algorithm, named PowerLawBound, combining matrix sparseness judgment and calculation result convergence judgment.
-PowerLaw here refers to the network conforming to the power law distribution, and Bound refers to the accuracy of floating-point operations on hardware.
-The experimental results show that PowerLawBound algorithm improves time performance by 39\% to 36.2 times compared to the Alon N algorithm on the hardware of CPU and GPU.
+This paper discussed a novel algorithm in all pairs shortest path computation task, using distance product exchange law.
+The time bound of Alon \etal distance product algorithm with block matrix multiplication is \(O({\log{n}2n^3\over B})\) with $B=\text{SIZE}_{\text{block}}$.
+To strengthen the conditions, on scale-free social networks, for the precision limit of floating-point operation on hardware, additional condition on the social network diameter is added to avoid floating-point operation overflow during the calculation process.
+the algorithm has lower time bound \(O({14n^3\over B})\).
+With strengthened conditions, I proposed a novel algorithm, leveraging matrix sparseness judgment and calculation convergence judgment.
+\textbf{PowerLaw} refers to the network node numbers conforming to the characteristics that social networks power law distribution, and \textbf{Bound} refers to the floating-point operations arithmetic limitation of accuracy on hardware.
+The experimental results show that \textbf{PowerLawBound} algorithm improves time performance by 39\% to 36.2 times on CPU/GPU hardware compared to Alon \etal algorithm .
 

### 2020-09-28 A-BasicCommom/CVPR2021/cvpr_vision.tex
1.CVPR second paper-vision for non-euclidean data.

% This version of CVPR template is provided by Ming-Ming Cheng.
% Please leave an issue if you found a bug:
% https://github.com/MCG-NKU/CVPR_Template.

\documentclass[review]{cvpr}
%\documentclass[final]{cvpr}

\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}

\usepackage[linesnumbered,lined,boxed,commentsnumbered]{algorithm2e}
% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,colorlinks,bookmarks=false]{hyperref}

\def\cvprPaperID{8888} % *** Enter the CVPR Paper ID here
\def\confYear{CVPR 2021}
%\setcounter{page}{4321} % For final version only

\begin{document}

%%%%%%%%% TITLE
\title{Movie Box office Prediction via Joint Actor Representations and Social Media Sentiment}

\author{Dezhou Shen\\
Department of Computer Science\\
Tsinghua University\\
Beijing, CN 100084\\
{\tt\small sdz15@mails.tsinghua.edu.cn}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
}

\maketitle

%%%%%%%%% ABSTRACT
\begin{abstract}
  In recent years, driven by the Asian film industry, such as China and India, the global box office has maintained a steady growth trend.
  Previous studies have rarely used long-term, full-sample film data in analysis, lack of research on actors' social networks.
  Existing film box office prediction algorithms only use film meta-data, lack of using social network characteristics and the model is less interpretable.
  I propose a FC-GRU-CNN binary classification model in of box office prediction task, combining five characteristics, including the film meta-data, Sina Weibo text sentiment,
  actors' social network measurement, all pairs shortest path and actors' art contribution.
  Exploiting long-term memory ability of GRU layer in long sequences and the mapping ability of CNN layer in retrieving all pairs shortest path matrix features,
  proposed model is 14\% higher in accuracy than the current best C-LSTM model.
\end{abstract}

%%%%%%%%% BODY TEXT
\section{Introduction}

With the development of social networks, actors' influence on social networks is increasing, and the influence of actors' consumption is spread through social networks, and the use of long-cycle, full-sample social network data to study the relationships between all actors, directors and films is a challenge in the field of social media research.
It is easy to see that the relationship between the box office and the director, actor, scriptwriter and producer is often non-linear, that is, it is difficult to use linear functions to build box office prediction models.
By analyzing the social network characteristics of movie actors, sentiment of movies in Sina Weibo posts, all pairs shortest path, it is easy to get the priority of each characteristic by analysis of feature importance, existing prediction algorithm only makes use of the film meta-data, lacks the study on the social network characteristics of the actors, though traditional explanation of the film box office prediction algorithm is sufficing, however the prediction effect is not satisfactory.
This paper presents a model, named FC-GRU-CNN, for movie box office prediction, combining characteristics of film meta-data, actors' social network measurement, all nodes pair shortest path, social network text sentiment and actors' art characteristics, proposed model is 14\% higher in accuracy than the current best C-LSTM model.

%-------------------------------------------------------------------------

\section{Recent Work}

The film industry is a multi-billion-dollar industry, with China's box office exceeding 60 billion yuan in 2018, reaching 60.9 billion yuan, and predicting the acceptance and adoption of new films among the public is a challenging topic.

\subsection{Linear Regression Model}

Zhu and Tang~\cite{zhu2019film} collected 13 features, such as search engine user data, social network fan number and movie meta-data of 20 films with more than 300 million box office in 2017,
and constructed a partial least-squared model with a margin of error of 87.7\% and an average absolute error of 26.6\%.
Qiu and Tang~\cite{qiu2018microblog} used the 10 movie Sina Weibo texts and movie reviews of more than 1 billion at the box office in the Chinese film market in 2017 to calculate the web index and the film reviews to predict the box office.

\subsection{Logistic Regression Model}

Some researchers use social network text sentiment to predict movie box office.
Asur and Huberman~\cite{asur2010predicting} collected 2.89 million texts related to 1.2 million users on Twitter in connection with 24 films, and concluded that the correlation coefficient R2 was between 0.92 and 0.97 using the daily postings in the first seven days of release.
The film box office forecast logic regression model with the distribution of social network posts was 0.97.
Jain~\cite{jain2013prediction} collected 4800 Twitter texts of the movie name in the SNAP2009 (Stanford) dataset 2 weeks before release and 4 weeks after release.
Trained an sentiment al four-category model based on an 8-grammar model with an accuracy rate of 64.4\%.
Eight films released in 2012 as test sets, using the sentiment al positive-negative ratio to predict the accuracy of the box office profit model by 50\%.
Chi \etal~\cite{chi2019does} collected reviews from 150 films released in 2017 and found that the number of reviews was positively related to the box office.
online reviews were not correlated with box office. and the number of reviews was significantly positive lying to the first week of the film's box office, and the relevance gradually diminished.
Josh \etal~\cite{joshi2010movie} collected the film review text of the film released by MetaCritic from 2005 to 2009, using film meta-data, n-gram model, part-of-speech ngram model and dependency characteristics, to predict the first week box office,
first week screen number and weekly revenue per screen, the determine of coefficient of the Elastic Net linear model is 67.1\%.

\subsection{Support Vector Regression and Multi-Layer Neural Network Model}

From 2015 to 2017, Jiang and Wang~\cite{jiang2018predicting} collected 34 high-grossing films, using 10 features, such as film meta-data, director awards, and actor awards, and used voting feature selection algorithms to select features, training SVR (supporting vector regression) box office and scoring prediction models.
From 2012 to 2015, Quader \etal~\cite{quader2017machine} collected 755 film reviews from four film review sites, including film ratings, MPAA categories, director's total box office, total box office, actor total box office, release time, budget, screen numbers, user reviews, reviews, and the sentiment al characteristics of review texts,
training SVR, MLP(multi-layer neural network) model, with an accuracy of about 44.4\%.

\subsection{Text Classification by Deep Learning}

Zhou \etal~\cite{zhou2015c} proposed C-LSTM text classification model, using single-layer CNN to extract the high-order dimensional representation of text, and then connected the LSTM model to obtain sentence representation, the classification accuracy of the model is 87.8\%.

\subsection{Summary}

From the social network to predict the movie box office, feature selection includes the selection of user behavior characteristics, social network time characteristics, text sentiment al characteristics, classifiers more use of choice logic regression, support vector machine and neural network to predict the box office and comments.

%-------------------------------------------------------------------------

\section{Feature Analysis}

The following linear analysis of social network measurement features and the regression coefficient of film box office, and from the practical significance of the interaction between the characteristics and the film box office.
The positive characteristics associated with the box office in the linear regression algorithm are:
\par$\bullet$ Betweenness: the higher the number of actors, the higher the box office.
\par$\bullet$ Closeness: The higher the closeness of the actors, the higher the box office.
\par$\bullet$ Followers: The more other actors you pay attention to, the higher the box office.
\par$\bullet$ Number of posts: the more actors, the higher the box office.
\par$\bullet$ Average post interval: the greater the average hair interval, the higher the box office.
\par$\bullet$ Average characters of each posts: the longer the number of characters, the higher the box office, but the degree of relevance is not obvious.
\par$\bullet$ Number of retweets: the more retweet posts, the higher the box office.
\par$\bullet$ Box office history: the higher the box office receipts of actors, the higher the box office attendance of participating in the film.

The negative correlation characteristics are:
\par$\bullet$ Number of fans: the more fans there are, the lower the box office is.
\par$\bullet$ Number of movie-related Sina Weibo posts: the larger number the actors' mentioned the movie in Sina Weibo, the lower the box office is.
\par$\bullet$ Co-occurrence: The more actors and other actors co-appears on Sina Weibo posts, the lower the box office is.
Then, calculated Pearson correlation of average box office per movie and actors social network measurement characteristics, the post and retweet correlation is -0.00108, social media Activity correlation is -0.03203, Co-occurrence correlation is 0.1508.
First of all, the actor's average box office per movie is clearly positively related to the influence of the actors, that is, the higher number of co-occurrence in Sina Weibo, the higher average box office per movie.
Secondly, the actors Sina Weibo activity and the average box office per movie showed a slight negative correlation, that is, the number of actors' followers, the number of tweets, the interval between the posts, the length of posts, the number of movie-related posts showed negative impact on average box office per movie.
Finally, the number of actors retweets and tweets is not related to average box office per movie, thus they are independent.
Then I use Sina Weibo text sentiment and actor social network measurement characteristics as features, then trained a decision tree to fit the movie box office, training set determination of coefficient is 0.9858, and the test set determination of coefficient is 0.9605.
Actors social network meta-data decision tree visualization is illustrated as Figure 2.
Definition 1 Gini Impurity  A measure of how often randomly selected elements are incorrectly marked from a collection is a common CART (decision tree) algorithm evaluation indicator.
If it is randomly marked based on the distribution of the label in a subset.
Gini impurities can be divided by multiplying the probability of the item by the probability that it is misplaced.
When in all conditions a node belong to a single category, it reaches its minimum value of zero.
In summary, the decision tree structure shows that the influence of the actors in the social network is the main factor affecting the box office results, followed by the movie-related Sina Weibo sentiment and the film meta-data is the secondary determinant,
while the social network characteristics, movie-related Sina Weibo sentiment, film meta-data are the general determinants.

\section{Actors Representation Learning Using Social Network Measurement, Shortest Path And Art Characteristics}

Definition 2 (Network Embedding)  A network $G=(V,E)$, V represents a set of nodes consisting of n nodes, and E represents an edge set of m edges. For each edge $e\in \Bbb E$, the ordered pair is $e=(u,v)$, $u,v \in \Bbb V$ and the weight is $A_{ij}$.
A network can be represented as an adjacent matrix, $A\in \Bbb R^{(n*n)}$, and the goal of network embedding is to learn an all pairs representation, $U\in \Bbb R^{(n*m)}$, where m(m<n) is an embedding dimension.
Definition 3 (Shortest Path Network Embedding)  In a network represented as a $G=(V,E)$, V represents a node set of n nodes, and E represents an edge set of m edges.
For each edge $e\in \Bbb E$, the ordered pair is e=(u,v), $u,v \in \Bbb V$ and the weight is $A_{ij}$.
A network can be represented as an adjacent matrix, $A\in \Bbb R^{(n*n)}$, and the goal of the shortest path network embedding is to learn an all pairs, shortest path representation, $U\in \Bbb R^{(n*n)}$, where n is an embedding dimension.
For the task of box office forecasting, because of the significant impact the actors on the box office, in addition to the measurement of the film meta-data and the sentiment of the movie social media, the actors' contribution is required to compute by leveraging the movie participants actors list.
A film, led by several actors, obtained the names of 7,369 actors who participated in films between 2011 and 2015 are collected as an actor's dictionary, and then used the shortest path features of the actors' social network.
Combining social network measurement features, the shortest path network embedding, and the art features to construct the actor representation vector.
For actors who have no accounts on social networks, marked as unknown, and initialized with zero vectors.
Actor representation vectors include social network measurement features of 10 dimensions, shortest path features of 8380 dimensions, art features of 1 dimension.
In total, 10-dimensional measurement features include fans number, betweenness, closeness, followers, posts number, average posts interval, average word count per post, retweet number, movie-related post number, co-occurrence number, shortest path 8380 dimensions.

\section{Machine Learning Classifier}

Using the features extracted, the characteristics of participating in the calculation are film meta-data and movie sentiment: the year of release, the number of positive sentiment, the number of negative sentiment, the total number of Sina Weibo, the positive and negative ratio of sentiment, and the training of machine learning classifiers.

Machine learning methods such as Linear Regression, SVR, MLP, Logistic Regression, and Naive Bayes cannot converge on the data set, possibly because the sentiment on actors' social networks does not represent the commercial benefits of the film.
Actors, as creators of films, have a role to play in the box office, but lack other important features that also have an impact on the box office, so machine learning fitting process can't finish in given time.
Using the CART decision tree regression algorithm to make box office prediction for the test set film, 
the experimental results show that the prediction model has a determination coefficient of 96.05\% on the test set and 98.58\% on the training set, which is 2.87\% higher than the current best Sentiment-Network-Logistic model, 
and the average absolute deviation of the model is 0.1285 million, about 28.56\% of the average box office.
The explanatories of the decision tree prediction model is more intuitive and more interpretable than linear regression, logical regression, deep neural network and other models, according to the prediction model structure schematic of the movie box office, 
the characteristics can be sorted according to the importance, so the social network structure characteristics are the most important, the social network text sentiment al characteristics, the film meta-data are important, and the social network characteristics are generally important.
With Qiu and Tang's logistic regression model on sentiment and twitter index algorithm's 95.71\% in determination of coefficient, the proposed method in this paper has a 2.87\% improvement, 98.58\%.

\section{FC-GRU-CNN Model Classifier}

\begin{figure*}
\begin{center}
%\fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
  \fbox{\rule{0pt}{2in} \includegraphics[width=0.9\linewidth]{boxofficenet.pdf}}
\end{center}
   \caption{FC-GRU-CNN (box office net) forecasting model structure.}
\label{fig:short}
\end{figure*}

Look at the box office distribution of 1,296 films released between 2011 and 2015, as shown in Figure 1b.
Consider box office forecasts as a binary classification task. In order to make the data evenly distributed, the film data was pre-processed by using the median box office of 263.5(10K) as the dividing line.
So for the movies with box office less than 2.635 million are classified as A-class, more than 2.635 million movies are classified as B-class.
In the data set division, the data was randomly selected using the 80-20 segmentation ratio, and the training set of 1036 films and the test set of 260 movies were obtained.
Using the actors' social network representation, the actor is quantified, that is, the fusion of social network measurement features, the shortest path characteristics and the actor's art characteristics, the actor feature matrix,
for actors without social network measurement data, that is, the unknown characteristics, zero-value initialization. The model structure is shown in Figure 3:
The whole model is divided into three parts:
\par$\bullet$ The first part is FC full connection layer, its input feature is the film meta-data and movie-related Sina Weibo sentiment features, in total of 5 dimensions.
\par$\bullet$ The second part is the GRU layer, the input feature is the actor social network measurement characteristics and art characteristics, the actor table is a long list,
the longest 225 actors, for less than 225 actors using the front-end padding, the GRU layer is to solve the long-term memory loss of the structure.
\par$\bullet$ The last part is the 5-layer CNN structure, input for the actors' social network shortest path feature, similarly, the actor table is a long list,
input less than 225 dimensions is fulfilled by padding, CNN has a good ability to capture multi-dimensional features, and use of Max-pooling layer to solve the problem of multi-dimensional feature extraction.
Finally, the three parts are merged into one layer and then connect to a Softmax layer, and the L2 regularization method is adopted to avoid overfitting.
In summary, I choose randomly 10 movies of in test set, as shown in Table 3. The accuracy of the binary classification model in training set reached 99.61\%, the accuracy in the test set is 75\%, compared with other prediction algorithms, see Table 4.
From the practical point of view, the model of FC-GRU-CNN proposed in this paper converges on the training set and achieves better prediction results in the test set, so it can provide decision-making advice on the task of selecting suitable actors for the film, and in the task of film box office prediction, 75% accuracy can be used for box office prediction tasks.

\begin{table}
\begin{center}
\begin{tabular}{|l|c|c|}
\hline
Movie& Score &BoxOffice\\
\hline\hline
72 hours of sword theft & 1 & 108 \\
Ballera's Little Magic Fairy& 1 & 1916\\
It's us. &1& 28\\
Twin Spirits &1& 310\\
The dinner is crazy too& 1& 4381\\
Basement Horror& 0& 704\\
Tartar Oil Flower Romance& 0& 1\\
Breaking five& 0& 1\\
Kidnapping the door dog& 1& 1\\
Beijing Love Story& 1& 40555\\
\hline
\end{tabular}
\end{center}
\caption{box office binary classification predictions in 10 movie testset.}
\end{table}

\begin{table}
\begin{center}
\begin{tabular}{|l|c|}
\hline
Model & F1-score \\
\hline\hline
Zhou \etal  & 61.54\% \\
This paper & 75.0\% \\
\hline
\end{tabular}
\end{center}
\caption{Performance comparison on different model.}
\end{table}

\section{Conclusion}

Based on the film box office prediction of actor's Sina Weibo sentiment and social network characteristics, this paper discussed the relationship between the movie meta-data,
the movie Sina Weibo text sentiment, the actor's social network feature, the shortest path feature and the actor's art characteristics.
Then proposed a FC-GRU-CNN box office binary prediction model, compared with the current best C-LSTM model, the accuracy improves 14\%, in a dataset of 1,296 movies released on China mainland collected from 2011 to 2015, proposed model has an accuracy of 75\% in test set.

%\subsection{Dataset}
%
%From 2011 to 2015, collected 3,669 films releasing Chinese mainland and 14,234 actors from the China-Box-Office, and collected the retweets and tweets of 8,508 actors on Sina Weibo social network.
%The names of 7,369 actors were obtained from 14,234 actors participants records, as a dictionary of actors' names. There are 3,056 actors have opened account that can be collected from the social network.
%A total of 1,298 films featuring social networking characters were extracted from 3,669 films, including at least one actor with social network ingress characteristics. Then entity alignment was performed, matching a total of 7,369 actors according to the actor's name entity alignment method, of which 3,056 had social network characteristics, while 4,313 actors did not have social network measurement data, which the network node represented as unknown node.
%
%\subsection{Feature Introduction}
%
%Movie Sina Weibo text features, extract the content of the Sina Weibo containing 1298 movie names from the social media and the posts text, calculate the sentiment al classification, as the sentiment characteristics of the Sina Weibo text.
%Actor social network measurement characteristics, measured the actor's social network as follows, including fan number, number of media, closeness, number of followers, number of blogs, average blog spacing, average number of tweets, number of retweets, movie mentions of Sina Weibo, total cash.
%The shortest path feature of the social network structure of the actors, calculated the full-node shortest path of 8508 actors' social networks, and extracted the shortest path characteristics of 8508 dimensions of the 7,369 actors concerned. The calculation of the maximum minimum path for the full node is 8, for illustration purpose, the unreachable distance between nodes is recorded as 9, as Figure 1a.
%Actors' art characteristics, the average box office as an indicator of the actor's box office impact, using the Chinese box office online actor's participation in the film box office data, to calculate the average film box office.
%Using the box office data of the Chinese box office online actors participating in the film, the average film box office of the actorised, the average film box office as the actor's box office influence index, this characteristic as the actor's art characteristics. The average box office of 7,369 actors is counted from China's box office network as a feature of their art.
%Sina Weibo posts text and movie actor participation name list refer to Table 1, for sentiment classification of texts and retweets, first calculate Bigram of the text, then calculate Tfidf of each Bigram, then a Logistic Regression classifier is trained. Use this model to classify sentiment of texts and retweets for each movie-related posts, then get positive number, negative number, total number and positive-negative ratio, the results are shown in Table 2.
%In summary, the characteristics that need to be computed are movie meta-data, Sina Weibo sentiment, actors' participation name list. For actor representation, actors' network measurement, actors shortest path characteristics and art characteristics are needed. For movie partial representation, film meta-data, e. g., the year of release, and Sina Weibo sentiment characteristics, e. g., positive sentiment, negative sentiment, total sentiment and sentiment positive and negative ratio, are needed.
%
%
%%-------------------------------------------------------------------------
%
%\section{Time Bound Of Distance Product Algorithm With Cache Optimized Block Matrix Multiplication}
%For a fully connected network, the graph has a maximum diameter of $n-1$, so using result reuse method in distance product, that is use the last distance product calculation result, the matrix multiplication times is $log_2(n-1)$.
%Albert~\cite{albert1999diameter} found that social networks, the Internet and other complex networks have scale-free characteristics and small world phenomenon, thus network diameter is much smaller than the number of network nodes.
%I present the corresponding nodes counts, diameters and logarithm of diameters in Table 1, from the observation there is formula (1):
%In social networks, the number of nodes $n$, with cache block size $B*B$, according to the formula (9-10), the matrix product calculation iteration times does not exceed the number of $\lceil{log\Bbb D}\rceil$, recall that Lam \etal proved that matrix multiplication time bound is \(O({2n^3 \over B}+{n^2})\) ,
%thus Alon \etal algorithm time bound is \(O({log\Bbb D2n^3\over B})\) , use the equation (1) result, time bound is \(O({ \log(\log{N})2n^3\over B})\).
%With the arithmetic limitation on the floating-point operation, \eg take a network of number of nodes $N<10^{308}$
%as shown in Table 1, see that the shortest path calculation iterations time is no larger than $\log{\Bbb D}\approx{\log(\log{N})}<7$, that is, the number of calculation iterations does not exceed the magic number 7,
%bringing a stronger time bound of \(O({14n^3\over B})\).
%In another words, with the floating-point operation accuracy limitation on computer hardware and complex networks scale-free characteristics, all node pairs shortest path algorithm time bound is \(O({14n^3\over B})\).
%
%
%%-------------------------------------------------------------------------
%
%
%\section{Shortest Path Algorithm With Block Matrix Multiplication}
%
%Definition 1 (Outer Product Matrix Multiplication) Given matrices \(\Bbb A \in \Bbb R^{m*r}\), \(\Bbb B \in \Bbb R^{r*n}\) and \(\Bbb C \in \Bbb R^{m*n}\), the outer product is:
%\begin{equation}
%\Bbb C = \Bbb C  + \Bbb A(:,k)\bullet \Bbb B(k,:) , k \in (1,r)
%\end{equation}
%
%Given two vectors \(\textsc x\), \(\textsc y\), and matrix \(\Bbb A\), having \(\Bbb A \in \Bbb R^{m*n}\), \(\textsc x \in \Bbb R^{m}\) and \(\textsc y \in \Bbb R^{n}\) the outer product \(\bullet\) is defined by:
%\begin{equation}
%a_{ij} = a_{ij} + x_i * y_j, i \in (1,m), j \in (1,n)
%\end{equation}
%
%Definition 2 (Distance Product Matrix Multiplication) Given matrices \(\Bbb A \in \Bbb R^{m*r}\), \(\Bbb B \in \Bbb R^{r*n}\) and \(\Bbb C \in \Bbb R^{m*n}\), the distance product is:
%\begin{equation}
%  \Bbb C = \min(\Bbb C, \Bbb A(:,k)\odot \Bbb B(k,:)) , k \in (1,r)
%\end{equation}
%
%Given two vectors \(\textsc x\), \(\textsc y\), and matrix \(\Bbb A\), having \(\Bbb A \in \Bbb R^{m*n}\), \(\textsc x \in \Bbb R^{m}\) and \(\textsc y \in \Bbb R^{n}\) the distance product \(\odot\) is defined by:
%\begin{equation}
%a_{ij} = \min(a_{ij} , x_i + y_j), i \in (1,m), j \in (1,n)
%\end{equation}
%%-------------------------------------------------------------------------
%%\begin{figure}[t]
%%\begin{center}
%%\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
%%   \includegraphics[width=1.0\linewidth]{figure1.pdf}
%%\end{center}
%%   \caption{Adjacent matrix, each iterations and the result matrix visualization of actors' social network. (a) initial state after each round of calculation, (b) the result matrix after the first round of calculation, (c) the result matrix of the second round of calculation, (d) the third and in the same time last round of calculation, the all pairs nodes shortest path result matrix.}
%%\label{fig:long}
%%\label{fig:onecol}
%%\end{figure}
%
%\begin{figure*}
%\begin{center}
%%\fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
%  \fbox{\rule{0pt}{2in} \includegraphics[width=0.9\linewidth]{figure1.pdf}}
%\end{center}
%   \caption{Adjacent matrix, each iterations and the result matrix visualization of actors' social network. (a) initial state after each round of calculation, (b) the result matrix after the first round of calculation, (c) the result matrix of the second round of calculation, (d) the third and in the same time last round of calculation, the all pairs nodes shortest path result matrix.}
%\label{fig:short}
%\end{figure*}
%
%
%\subsection{Maximum Calculation}
%
%Calculate the largest value of the square matrix element $\widetilde X$, such as the formula (4):
%
%\subsection{Exponential Calculation}
%
%The calculation accuracy of different computer hardware is in line with the IEEE floating-point operation standard~\cite{ieee1985ieee},
%first of all, transform the input matrix by exponential transformation, to be specific, taking the number of nodes as the base,
%taking the difference between the largest value of the element $\widetilde X$ and the matrix elements as exponential, as shown in the formula (5).
%\eg For actors' social network with 8508 nodes, the diameter of the network does not allow to exceed 9.8 and 78.4 when calculating a precision of 32-bit floating-point and 64-bit floating-point,
%otherwise the exponential operation on the computer platform will overflow.
%
%\subsection{Matrix Multiplication}
%Use different matrix libraries to speed up the matrix multiplication on computer hardware, as shown in Table 3, choose proper device-based optimized matrix multiplication libraries according to different conditions, such as matrix sparseness, calculation hardware, and programming language.
%
%%-------------------------------------------------------------------------
%\subsection{Logarithm Calculation}
%Take non-zero elements of the matrix multiplication result to the element logarithm process, that is, the number of network nodes as the base, the element in the matrix multiplication result as the true number, then round down the logarithm result,
%after that take difference between twice of the largest input matrix element value $\widetilde X$ and the logarithm result as result, such as formula (6).
%
%\subsection{Distance Product Exchange Law}
%
%From the iteration of the shortest path calculation, suppose \(\Bbb A,\ \Bbb B,\ \Bbb C\) is the square matrix, according to the association law of distance product, there is a formula (7):
%Matrix multiplication has association law, and the distance product is isomorphism to matrix multiplication, so simplify the shortest path iteration process as formula (8):
%Since matrix multiplication has association law and distance product is isomorphism to matrix multiplication, similarly, distance product has an association law.
%Under the premise of the shortest path matrix $L^{(n-1)}$ given the adjacent matrix and the $n-1$ edge, calculate the shortest path matrix $L^{(n)}$ with n edges, and extend the shortest path of the $n-1$ edge by edge.
%Calculating the shortest path matrix $L^{(n)}$ can be completed as formula (9):
%As can be seen from the nature of the shortest path in the graph, the shortest path from the any of two nodes does not exceed $n-1$, so there is formula (10):
%Definition 3 Result Reuse in Distance Product According to the nature of the equation (8), the process of calculating the shortest path iteration using the last result of distance product follows in turn, as shown in formula (11).
%The shortest path needs to be calculated $\lceil{log_2(n-1)}\rceil$ times matrix multiplication, from the formula (10), it can be seen that $(n-1)\leq2^{\lceil{log_2(n-1)}\rceil}$ is the same as the simple shortest path matrix calculation result $L^{(n-1)}$, so there is a formula (12):
%Obviously, the result reuse method saves $n-2-\lceil{log_2(n-1)}\rceil$ times of matrix multiplication.
%Observe the shortest path calculation process of the actors' social network, the adjacent matrix is shown in Figure 1a, and the change of result in each iteration is shown in Figure 1b-d, the shortest path result matrix converges gradually, each element stabilizes as iterations goes.
%
%
%\begin{algorithm}
%\caption{Lower Bounds Convergence Matrix Products in All Pairs Shortest Path}\label{algorithm}
%\KwData{Adjacent Matrix $\Bbb W$, Matrix Row $n$, Network Diameter $\Bbb D$}
%\KwResult{Shortest path result $L^{(m)}$}
%$L^{(1)}\leftarrow \Bbb W$\;
%$m\leftarrow 1$\;
%\While{$m\leq \Bbb D$}{
%  $\Bbb A\leftarrow L^{(m)},\Bbb B\leftarrow L^{(m)},$\;
%  $x\leftarrow \min{(a_i,b_i)}, y\leftarrow \max{(a_i,b_i)}, i \in (1,n)$\;
%  Exponential transformation of matrices $\Bbb A\ and\ \Bbb B$\;
%    $a_{ij}^{'}={(n+1)}^{y-a_{ij}}$\;
%    $b_{ij}^{'}={(n+1)}^{y-b_{ij}}$\;
%  \eIf{$L^{(m)}$ is sparse}{
%    $\odot\leftarrow \bigcirc$//sparse matrix multiplication\;
%  }{
%    $\odot\leftarrow \otimes$//dense matrix multiplication\;
%  }
%  Given matrix $\Bbb C^{'}$, $\Bbb C^{'} \in \Bbb R^{n\times n}$\;
%  $\Bbb C^{'}\leftarrow \Bbb A^{'}\odot\Bbb B^{'}$\;
%  Logrithm transformation of matrix $\Bbb C^{'}$\;
%  $\Bbb C\leftarrow \log{\Bbb C^{'}}$\;
%  \If{$L^{(m)} \eq \Bbb C$}{
%    \bold{return}\ $L^{(m)}$\;
%  }
%  $L^{(2m)}\leftarrow \Bbb C$\;
%  $m\leftarrow 2*m$\;
%}
%\bold{return} $L^{(m)}$\;
%\end{algorithm}
%
%
%\section{Architecture Design}
%
%\subsection{Sparseness Judgment}
%
%As shown in Table 1, observing the adjacent matrix represented by the network diagram is usually a sparse matrix, and matrix gradually becomes dense during iterations,
%and one idea of optimization is to use sparse matrix multiplication to speed up the iteration when the matrix is sparse, and when the matrix becomes denser, the sparse matrix multiplication is much time-consuming.
%Taking the actors' social network as an example, the non-zero element of the adjacent matrix of 8508 nodes is 617958, and the non-zero element of the matrix is 0.8536\% of the total element,
%which is a typical sparse matrix. Consider the advantages of sparse matrix multiplication algorithm, a threshold for triggering sparse matrix multiplication is set,
%and when the proportion of non-zero-value elements entered is less than the 10\% threshold, performs sparse matrix multiplication.
%
%\subsection{Convergence Judgment}
%
%For networks with unknown diameters, the calculation results can be made using convergence method, and for the calculation process of reaching convergence,
%i.e. $L^{(n-1)}=L^{(n)}$, should be regarded as the program termination of iteration, and the calculation of the matrix product method is completed by the equation (4).
%
%\subsection{The Shortest Path Algorithm Fusing Sparseness Judgment And Convergence Judgment}
%
%Based on Alon \etal distance product algorithm, utilizing the sparseness judgment of the input matrix and the calculation result convergence judgment,
%with the network conforming to the power law distribution and the precision of floating-point operation, and the name implies two characteristics of the limitation
%of floating-point precision on the scale-free social network and the computer hardware, the algorithm process flow is shown in Algorithm 1.
%
%\section{Experiment}
%
%Firstly, compared to Floyd-Warshall algorithm implemented on CPU, the Alon \etal algorithm implementation with matrix multiplication of block cache optimization on GPU has a time performance improvement, see Table 1.
%$PowerLawBound_{a-f}$ shows that using different libraries on CPU/GPU, the proposed algorithm has significant performance improvement over Alon \etal algorithm.
%
%
%\begin{table}
%\begin{center}
%\begin{tabular}{|l|c|}
%\hline
%Algorithm & Time Cost \\
%\hline\hline
%Floyd-Warshall & 1055880s \\
%Alon \etal          & 594.7s \\
%$PowerLawBound_a$  & 427.9s \\
%$PowerLawBound_b$ & 328.4s \\
%$PowerLawBound_c$ & 95.0s \\
%$PowerLawBound_d$ & 45.0s \\
%$PowerLawBound_e$ & 19.32s \\
%$PowerLawBound_f$ & 15.98s \\
%\hline
%\end{tabular}
%\end{center}
%\caption{Performance comparison on different hardware. (a) CPU numpy library. (b) CPU scipy/numpy library. (c) GPU cuBLAS. (d) CPU openBLAS. (e) GPU CuPy. (f) GPU CuPy-sparse/CuPy.}
%\end{table}
%
%
%\section{Conclusion}
%This paper discussed a novel algorithm in all pairs shortest path computation task, using distance product exchange law.
%The time bound of Alon \etal distance product algorithm with block matrix multiplication is \(O({\log{n}2n^3\over B})\) with $B=\text{SIZE}_{\text{block}}$.
%To strengthen the conditions, on scale-free social networks, for the precision limit of floating-point operation on hardware, additional condition on the social network diameter is added to avoid floating-point operation overflow during the calculation process.
%the algorithm has lower time bound \(O({14n^3\over B})\).
%With strengthened conditions, I proposed a novel algorithm, leveraging matrix sparseness judgment and calculation convergence judgment.
%\textbf{PowerLaw} refers to the network node numbers conforming to the characteristics that social networks power law distribution, and \textbf{Bound} refers to the floating-point operations arithmetic limitation of accuracy on hardware.
%The experimental results show that \textbf{PowerLawBound} algorithm improves time performance by 39\% to 36.2 times on CPU/GPU hardware compared to Alon \etal algorithm .

%\begin{quote}
%\begin{center}
%    An analysis of the frobnicatable foo filter.
%\end{center}
%
%   In this paper we present a performance analysis of our
%   previous paper [1], and show it to be inferior to all
%   previously known methods.  Why the previous paper was
%   accepted without this analysis is beyond me.
%
%   [1] Removed for blind review
%\end{quote}
%
%
%An example of an acceptable paper:
%
%\begin{quote}
%\begin{center}
%     An analysis of the frobnicatable foo filter.
%\end{center}
%
%   In this paper we present a performance analysis of the
%   paper of Smith \etal [1], and show it to be inferior to
%   all previously known methods.  Why the previous paper
%   was accepted without this analysis is beyond me.
%
%   [1] Smith, L and Jones, C. ``The frobnicatable foo
%   filter, a fundamental contribution to human knowledge''.
%   Nature 381(12), 1-213.
%\end{quote}
%
%If you are making a submission to another conference at the same time,
%which covers similar or overlapping material, you may need to refer to that
%submission in order to explain the differences, just as you would if you
%had previously published related work.  In such cases, include the
%anonymized parallel submission~\cite{Authors14} as additional material and
%cite it as
%\begin{quote}
%[1] Authors. ``The frobnicatable foo filter'', F\&G 2014 Submission ID 324,
%Supplied as additional material {\tt fg324.pdf}.
%\end{quote}
%
%Finally, you may feel you need to tell the reader that more details can be
%found elsewhere, and refer them to a technical report.  For conference
%submissions, the paper must stand on its own, and not {\em require} the
%reviewer to go to a techreport for further details.  Thus, you may say in
%the body of the paper ``further details may be found
%in~\cite{Authors14b}''.  Then submit the techreport as additional material.
%Again, you may not assume the reviewers will read this material.
%
%Sometimes your paper is about a problem which you tested using a tool which
%is widely known to be restricted to a single institution.  For example,
%let's say it's 1969, you have solved a key problem on the Apollo lander,
%and you believe that the CVPR70 audience would like to hear about your
%solution.  The work is a development of your celebrated 1968 paper entitled
%``Zero-g frobnication: How being the only people in the world with access to
%the Apollo lander source code makes us a wow at parties'', by Zeus \etal.
%
%You can handle this paper like any other.  Don't write ``We show how to
%improve our previous work [Anonymous, 1968].  This time we tested the
%algorithm on a lunar lander [name of lander removed for blind review]''.
%That would be silly, and would immediately identify the authors. Instead
%write the following:
%\begin{quotation}
%\noindent
%   We describe a system for zero-g frobnication.  This
%   system is new because it handles the following cases:
%   A, B.  Previous systems [Zeus et al. 1968] didn't
%   handle case B properly.  Ours handles it by including
%   a foo term in the bar integral.
%
%   ...
%
%   The proposed system was integrated with the Apollo
%   lunar lander, and went all the way to the moon, don't
%   you know.  It displayed the following behaviours
%   which show how well we solved cases A and B: ...
%\end{quotation}
%As you can see, the above text follows standard scientific convention,
%reads better than the first version, and does not explicitly name you as
%the authors.  A reviewer might think it likely that the new paper was
%written by Zeus \etal, but cannot make any decision based on that guess.
%He or she would have to be sure that no other authors could have been
%contracted to solve problem B.
%\medskip
%
%\noindent
%FAQ\medskip\\
%{\bf Q:} Are acknowledgements OK?\\
%{\bf A:} No.  Leave them for the final copy.\medskip\\
%{\bf Q:} How do I cite my results reported in open challenges?
%{\bf A:} To conform with the double blind review policy, you can report results of other challenge participants together with your results in your paper. For your results, however, you should not identify yourself and should not mention your participation in the challenge. Instead present your results referring to the method proposed in your paper and draw conclusions based on the experimental comparison to other results.\medskip\\
%
%\begin{figure}[t]
%\begin{center}
%\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
%   %\includegraphics[width=0.8\linewidth]{egfigure.eps}
%\end{center}
%   \caption{Example of caption.  It is set in Roman so that mathematics
%   (always set in Roman: $B \sin A = A \sin B$) may be included without an
%   ugly clash.}
%\label{fig:long}
%\label{fig:onecol}
%\end{figure}
%
%\subsection{Miscellaneous}
%
%\noindent
%Compare the following:\\
%\begin{tabular}{ll}
% \verb'$conf_a$' &  $conf_a$ \\
% \verb'$\mathit{conf}_a$' & $\mathit{conf}_a$
%\end{tabular}\\
%See The \TeX book, p165.
%
%The space after \eg, meaning ``for example'', should not be a
%sentence-ending space. So \eg is correct, {\em e.g.} is not.  The provided
%\verb'\eg' macro takes care of this.
%
%When citing a multi-author paper, you may save space by using ``et alia'',
%shortened to ``\etal'' (not ``{\em et.\ al.}'' as ``{\em et}'' is a complete word.)
%However, use it only when there are three or more authors.  Thus, the
%following is correct: ``
%   Frobnication has been trendy lately.
%   It was introduced by Alpher~\cite{Alpher02}, and subsequently developed by
%   Alpher and Fotheringham-Smythe~\cite{Alpher03}, and Alpher \etal~\cite{Alpher04}.''
%
%This is incorrect: ``... subsequently developed by Alpher \etal~\cite{Alpher03} ...''
%because reference~\cite{Alpher03} has just two authors.  If you use the
%\verb'\etal' macro provided, then you need not worry about double periods
%when used at the end of a sentence as in Alpher \etal.
%
%For this citation style, keep multiple citations in numerical (not
%chronological) order, so prefer \cite{Alpher03,Alpher02,Authors14} to
%\cite{Alpher02,Alpher03,Authors14}.
%
%
%\begin{figure*}
%\begin{center}
%\fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
%\end{center}
%   \caption{Example of a short caption, which should be centered.}
%\label{fig:short}
%\end{figure*}
%
%%------------------------------------------------------------------------
%\section{Formatting your paper}
%
%All text must be in a two-column format. The total allowable width of the
%text area is $6\frac78$ inches (17.5 cm) wide by $8\frac78$ inches (22.54
%cm) high. Columns are to be $3\frac14$ inches (8.25 cm) wide, with a
%$\frac{5}{16}$ inch (0.8 cm) space between them. The main title (on the
%first page) should begin 1.0 inch (2.54 cm) from the top edge of the
%page. The second and following pages should begin 1.0 inch (2.54 cm) from
%the top edge. On all pages, the bottom margin should be 1-1/8 inches (2.86
%cm) from the bottom edge of the page for $8.5 \times 11$-inch paper; for A4
%paper, approximately 1-5/8 inches (4.13 cm) from the bottom edge of the
%page.
%
%%-------------------------------------------------------------------------
%\subsection{Margins and page numbering}
%
%All printed material, including text, illustrations, and charts, must be kept
%within a print area 6-7/8 inches (17.5 cm) wide by 8-7/8 inches (22.54 cm)
%high.
%%
%Page numbers should be in footer with page numbers, centered and .75
%inches from the bottom of the page and make it start at the correct page
%number rather than the 4321 in the example.  To do this fine the line (around
%line 20)
%\begin{verbatim}
%\setcounter{page}{4321}
%\end{verbatim}
%where the number 4321 is your assigned starting page.
%
%
%
%%-------------------------------------------------------------------------
%\subsection{Type-style and fonts}
%
%Wherever Times is specified, Times Roman may also be used. If neither is
%available on your word processor, please use the font closest in
%appearance to Times to which you have access.
%
%MAIN TITLE. Center the title 1-3/8 inches (3.49 cm) from the top edge of
%the first page. The title should be in Times 14-point, boldface type.
%Capitalize the first letter of nouns, pronouns, verbs, adjectives, and
%adverbs; do not capitalize articles, coordinate conjunctions, or
%prepositions (unless the title begins with such a word). Leave two blank
%lines after the title.
%
%AUTHOR NAME(s) and AFFILIATION(s) are to be centered beneath the title
%and printed in Times 12-point, non-boldface type. This information is to
%be followed by two blank lines.
%
%The ABSTRACT and MAIN TEXT are to be in a two-column format.
%
%MAIN TEXT. Type main text in 10-point Times, single-spaced. Do NOT use
%double-spacing. All paragraphs should be indented 1 pica (approx. 1/6
%inch or 0.422 cm). Make sure your text is fully justified---that is,
%flush left and flush right. Please do not place any additional blank
%lines between paragraphs.
%
%Figure and table captions should be 9-point Roman type as in
%Figures~\ref{fig:onecol} and~\ref{fig:short}.  Short captions should be centred.
%
%\noindent Callouts should be 9-point Helvetica, non-boldface type.
%Initially capitalize only the first word of section titles and first-,
%second-, and third-order headings.
%
%FIRST-ORDER HEADINGS. (For example, {\large \bf 1. Introduction})
%should be Times 12-point boldface, initially capitalized, flush left,
%with one blank line before, and one blank line after.
%
%SECOND-ORDER HEADINGS. (For example, { \bf 1.1. Database elements})
%should be Times 11-point boldface, initially capitalized, flush left,
%with one blank line before, and one after. If you require a third-order
%heading (we discourage it), use 10-point Times, boldface, initially
%capitalized, flush left, preceded by one blank line, followed by a period
%and your text on the same line.
%
%%-------------------------------------------------------------------------
%\subsection{Footnotes}
%
%Please use footnotes\footnote {This is what a footnote looks like.  It
%often distracts the reader from the main flow of the argument.} sparingly.
%Indeed, try to avoid footnotes altogether and include necessary peripheral
%observations in
%the text (within parentheses, if you prefer, as in this sentence).  If you
%wish to use a footnote, place it at the bottom of the column on the page on
%which it is referenced. Use Times 8-point type, single-spaced.
%
%
%%-------------------------------------------------------------------------
%\subsection{References}
%
%List and number all bibliographical references in 9-point Times,
%single-spaced, at the end of your paper. When referenced in the text,
%enclose the citation number in square brackets, for
%example~\cite{Authors14}.  Where appropriate, include the name(s) of
%editors of referenced books.
%
%\begin{table}
%\begin{center}
%\begin{tabular}{|l|c|}
%\hline
%Method & Frobnability \\
%\hline\hline
%Theirs & Frumpy \\
%Yours & Frobbly \\
%Ours & Makes one's heart Frob\\
%\hline
%\end{tabular}
%\end{center}
%\caption{Results.   Ours is better.}
%\end{table}
%
%%-------------------------------------------------------------------------
%\subsection{Illustrations, graphs, and photographs}
%
%All graphics should be centered.  Please ensure that any point you wish to
%make is resolvable in a printed copy of the paper.  Resize fonts in figures
%to match the font in the body text, and choose line widths which render
%effectively in print.  Many readers (and reviewers), even of an electronic
%copy, will choose to print your paper in order to read it.  You cannot
%insist that they do otherwise, and therefore must not assume that they can
%zoom in to see tiny details on a graphic.
%
%When placing figures in \LaTeX, it's almost always best to use
%\verb+\includegraphics+, and to specify the  figure width as a multiple of
%the line width as in the example below
%{\small\begin{verbatim}
%   \usepackage[dvips]{graphicx} ...
%   \includegraphics[width=0.8\linewidth]
%                   {myfile.eps}
%\end{verbatim}
%}
%
%
%%-------------------------------------------------------------------------
%\subsection{Color}
%
%Please refer to the author guidelines on the \confYear~web page for a discussion
%of the use of color in your document.
%
%%------------------------------------------------------------------------
%\section{Final copy}
%
%You must include your signed IEEE copyright release form when you submit
%your finished paper. We MUST have this form before your paper can be
%published in the proceedings.
%
%Please direct any questions to the production editor in charge of these
%proceedings at the IEEE Computer Society Press:
%\url{https://www.computer.org/about/contact}.

{\small
\bibliographystyle{ieee_fullname}
\bibliography{cpvr_vision}
}

\end{document}

### 2020-09-28 A-BasicCommom/CVPR2021/cvpr.tex
1.CVPR second paper.

@@
 \begin{abstract}
-  For the shortest path calculation task of all nodes in networks, Alon \etal ~\cite{alon1997exponent} proposed an algorithm with matrix multiplication.
+  For the shortest path calculation task of all nodes in networks, Alon \etal~\cite{alon1997exponent} proposed an algorithm with matrix multiplication.
   In this paper, with the distance product exchange law and block matrix multiplication, all pairs shortest path algorithm has a lowered time bound of \(O({logn2n^3\over B})\).
@@
 There was Floyd-Warshall~\cite{floyd1962algorithm,warshall1962theorem} algorithm for calculating node distances, Aho and Hopcroft~\cite{aho1974design} proved that distance product is homogenous to matrix multiplication,
-Alon \etal ~\cite{alon1997exponent} proposed an algorithm to calculate distance product by matrix multiplication, Zwick~\cite{zwick2002all} optimized distance product using fast matrix multiplication,
+Alon \etal~\cite{alon1997exponent} proposed an algorithm to calculate distance product by matrix multiplication, Zwick~\cite{zwick2002all} optimized distance product using fast matrix multiplication,
 and Garbow and Winograd~\cite{garbow1985scaling} proposed an algorithm for distance product using matrix multiplication with element bound.
-From time bound of matrix multiplication, Strassen~\cite{strassen1969gaussian}, Coppersmith and Winograd~\cite{coppersmith1987matrix}, Davie and Andrew ~\cite{davie2013improved}, Le Gall~\cite{le2014powers} proposed the block matrix multiplication with time bound of \(O(n ^ {2.807})\), \(O(n^{2.376})\), \(O(n^{2.374})\), \(O(n^{2.373})\).
-Lam \etal ~\cite{lam1991cache} proposed that the progressive time complexity of matrix multiplication with a cache block size of $B*B$ is \(O({2n^3 \over B}+{n^2})\) ,
+From time bound of matrix multiplication, Strassen~\cite{strassen1969gaussian}, Coppersmith and Winograd~\cite{coppersmith1987matrix}, Davie and Andrew~\cite{davie2013improved}, Le Gall~\cite{le2014powers} proposed the block matrix multiplication with time bound of \(O(n ^ {2.807})\), \(O(n^{2.376})\), \(O(n^{2.374})\), \(O(n^{2.373})\).
+Lam \etal~\cite{lam1991cache} proposed that the progressive time complexity of matrix multiplication with a cache block size of $B*B$ is \(O({2n^3 \over B}+{n^2})\) ,
 and Goto and Geijn~\cite{goto2008anatomy} proposed a new library, OpenBLAS, which has a higher cache hit rate and improved time cost in matrix computation on X86 CPU, compared to modern BLAS libraries, such as Intel MKL v8.1.1, ESSL v4.2.0 and ATLAS v3.7.11.
@@
 For a fully connected network, the graph has a maximum diameter of $n-1$, so using result reuse method in distance product, that is use the last distance product calculation result, the matrix multiplication times is $log_2(n-1)$.
-Albert ~\cite{albert1999diameter} found that social networks, the Internet and other complex networks have scale-free characteristics and small world phenomenon, thus network diameter is much smaller than the number of network nodes.
+Albert~\cite{albert1999diameter} found that social networks, the Internet and other complex networks have scale-free characteristics and small world phenomenon, thus network diameter is much smaller than the number of network nodes.
 I present the corresponding nodes counts, diameters and logarithm of diameters in Table 1, from the observation there is formula (1):
@@
 
-The calculation accuracy of different computer hardware is in line with the IEEE floating-point operation standard ~\cite{ieee1985ieee},
+The calculation accuracy of different computer hardware is in line with the IEEE floating-point operation standard~\cite{ieee1985ieee},
 first of all, transform the input matrix by exponential transformation, to be specific, taking the number of nodes as the base,

### 2020-09-28 A-BasicCommom/CVPR2021/cvpr_vision.tex
1.CVPR second paper.

@@
 %%%%%%%%% TITLE
-\title{Movie Box office Prediction via Joint Actor Representations and Social Media Sentiment}
+%\title{Movie Box office Prediction via Joint Actor Representations and Social Media Sentiment}
+\title{Visualize Non-Euclidean Actors Social Media via Joint Social Relationship Representations, Network Characteristics and Media Sentiments}
 
@@
 \begin{abstract}
-  In recent years, driven by the Asian film industry, such as China and India, the global box office has maintained a steady growth trend.
-  Previous studies have rarely used long-term, full-sample film data in analysis, lack of research on actors' social networks.
-  Existing film box office prediction algorithms only use film meta-data, lack of using social network characteristics and the model is less interpretable.
-  I propose a FC-GRU-CNN binary classification model in of box office prediction task, combining five characteristics, including the film meta-data, Sina Weibo text sentiment,
-  actors' social network measurement, all pairs shortest path and actors' art contribution.
-  Exploiting long-term memory ability of GRU layer in long sequences and the mapping ability of CNN layer in retrieving all pairs shortest path matrix features,
-  proposed model is 14\% higher in accuracy than the current best C-LSTM model.
+  In film industry, visualizing social media data for analyzing stars and audience intention for movies is common to producers.
+  However, non-Euclidean social media is hard to analyze, I propose a FC-GRU-CNN deep learning architecture for visualizing social media, and as an empirical case, use it in a box-office prediction task.
+  Further more, key factors, such as social relationship representations, network characteristics and media sentiments are used in the prediction model.
+  By exploiting long-term memory ability of GRU layer in long sequences in cast list and the mapping ability of CNN layer in retrieving all pairs shortest path feature of actors social relationship,
+  proposed model is 14\% higher in accuracy than Zhou \etal model.
 \end{abstract}
@@
 
-With the development of social networks, actors' influence on social networks is increasing, and the influence of actors' consumption is spread through social networks, and the use of long-cycle, full-sample social network data to study the relationships between all actors, directors and films is a challenge in the field of social media research.
+With the development of social networks, actors' influence on social media is increasing, and the influence of actors' consumption is spread through social networks,
+and using long-term social networks data to study the relationships between all actors, directors and films remains a challenge.
 It is easy to see that the relationship between the box office and the director, actor, scriptwriter and producer is often non-linear, that is, it is difficult to use linear functions to build box office prediction models.
-By analyzing the social network characteristics of movie actors, sentiment of movies in Sina Weibo posts, all pairs shortest path, it is easy to get the priority of each characteristic by analysis of feature importance, existing prediction algorithm only makes use of the film meta-data, lacks the study on the social network characteristics of the actors, though traditional explanation of the film box office prediction algorithm is sufficing, however the prediction effect is not satisfactory.
-This paper presents a model, named FC-GRU-CNN, for movie box office prediction, combining characteristics of film meta-data, actors' social network measurement, all nodes pair shortest path, social network text sentiment and actors' art characteristics, proposed model is 14\% higher in accuracy than the current best C-LSTM model.
+By analyzing the social network characteristics of movie actors, sentiment of movies in Sina Weibo posts, all pairs shortest path, it is easy to get the priority of each characteristic by analysis of feature importance,
+existing prediction algorithm only makes use of the film meta-data, lacks the study on the social network characteristics of the actors, though traditional explanation of the film box office prediction algorithm is sufficing, however the prediction effect is not satisfactory.
+This paper presents a model, named FC-GRU-CNN, for movie box office prediction, combining characteristics of film meta-data, actors' social network measurement,
+all nodes pair shortest path, social network text sentiment and actors' art characteristics, proposed model is 14\% higher in accuracy than Zhou \etal~\cite{zhou2015c} model.
 
@@
 Some researchers use social network text sentiment to predict movie box office.
-Asur and Huberman~\cite{asur2010predicting} collected 2.89 million texts related to 1.2 million users on Twitter in connection with 24 films, and concluded that the correlation coefficient R2 was between 0.92 and 0.97 using the daily postings in the first seven days of release.
+Asur and Huberman~\cite{asur2010predicting} collected 2.89 million texts related to 1.2 million users on Twitter in connection with 24 films, and concluded that the correlation coefficient $R^2$ was between 0.92 and 0.97 using the daily postings in the first seven days of release.
 The film box office forecast logic regression model with the distribution of social network posts was 0.97.
@@
 
-From 2015 to 2017, Jiang and Wang~\cite{jiang2018predicting} collected 34 high-grossing films, using 10 features, such as film meta-data, director awards, and actor awards, and used voting feature selection algorithms to select features, training SVR (supporting vector regression) box office and scoring prediction models.
-From 2012 to 2015, Quader \etal~\cite{quader2017machine} collected 755 film reviews from four film review sites, including film ratings, MPAA categories, director's total box office, total box office, actor total box office, release time, budget, screen numbers, user reviews, reviews, and the sentiment al characteristics of review texts,
-training SVR, MLP(multi-layer neural network) model, with an accuracy of about 44.4\%.
+Jiang and Wang~\cite{jiang2018predicting} collected 34 high-grossing films from 2015 to 2017, using 10 features, such as film meta-data, director awards, and actor awards, and used voting feature selection algorithms to select features, training SVR (supporting vector regression) box office and scoring prediction models.
+Quader \etal~\cite{quader2017machine} collected 755 film reviews from four film review sites from 2012 to 2015, including film ratings, MPAA categories, director's total box office, total box office, actor total box office, release time, budget, screen numbers, user reviews, reviews, and the sentiment al characteristics of review texts,
+training SVR, MLP model, with an accuracy of about 44.4\%.
 
-\subsection{Text Classification by Deep Learning}
+\subsection{Text Classification using Deep Learning}
 
-Zhou \etal~\cite{zhou2015c} proposed C-LSTM text classification model, using single-layer CNN to extract the high-order dimensional representation of text, and then connected the LSTM model to obtain sentence representation, the classification accuracy of the model is 87.8\%.
+Zhou \etal proposed a C-LSTM text classification model, using single-layer CNN for extracting the high-order dimensional representation of text, and then connected to LSTM layers for sentence representation, accuracy of the model is 87.8\%.
 
@@
 
-\section{Feature Analysis}
+\section{Characteristics Correlation Analysis}
 
@@
 
-\section{Actors Representation Learning Using Social Network Measurement, Shortest Path And Art Characteristics}
+\section{Representation Learning for Social Relationship, Network Characteristics And Art Contribution}
 
-Definition 2 (Network Embedding)  A network $G=(V,E)$, V represents a set of nodes consisting of n nodes, and E represents an edge set of m edges.
+Definition 1 (Network Embedding)  A network $\Bbb G=(\Bbb V,\Bbb E)$, $\Bbb V$ represents a set of nodes consisting of $n$ nodes, and $\Bbb E$ represents an edge set of $m$ edges.
 For each edge $e\in \Bbb E$, the ordered pair is $e=(u,v)$, $u,v \in \Bbb V$ and the weight is $A_{ij}$.
-A network can be represented as an adjacent matrix, $A\in \Bbb R^{(n*n)}$, and the goal of network embedding is to learn an all pairs representation, $U\in \Bbb R^{(n*m)}$, where m(m<n) is an embedding dimension.
-Definition 3 (Shortest Path Network Embedding)  In a network represented as a $G=(V,E)$, V represents a node set of n nodes, and E represents an edge set of m edges.
-For each edge $e\in \Bbb E$, the ordered pair is e=(u,v), $u,v \in \Bbb V$ and the weight is $A_{ij}$.
-A network can be represented as an adjacent matrix, $A\in \Bbb R^{(n*n)}$, and the goal of the shortest path network embedding is to learn an all pairs, shortest path representation, $U\in \Bbb R^{(n*n)}$, where n is an embedding dimension.
+A network can be represented as an adjacent matrix, $A\in \Bbb R^{(n*n)}$, and the goal of network embedding is to learn an all pairs representation, $U\in \Bbb R^{(n*m), m < n}$, where $m$ is an embedding dimension.
+Definition 2 (Shortest Path Network Embedding)  In a network represented as a $G=(V,E)$, $\Bbb V$ represents a node set of $n$ nodes, and $\Bbb E$ represents an edge set of $m$ edges.
+For each edge $e\in \Bbb E$, the ordered pair is $e=(u,v)$, $u,v \in \Bbb V$ and the weight is $A_{ij}$.
+A network can be represented as an adjacent matrix, $A\in \Bbb R^{(n*n)}$, and the goal of the shortest path network embedding is to learn an all pairs, shortest path representation, $U\in \Bbb R^{(n*n)}$, where $n$ is an embedding dimension.
 For the task of box office forecasting, because of the significant impact the actors on the box office, in addition to the measurement of the film meta-data and the sentiment of the movie social media, the actors' contribution is required to compute by leveraging the movie participants actors list.
@@
 Actor representation vectors include social network measurement features of 10 dimensions, shortest path features of 8380 dimensions, art features of 1 dimension.
-In total, 10-dimensional measurement features include fans number, betweenness, closeness, followers, posts number, average posts interval, average word count per post, retweet number, movie-related post number, co-occurrence number, shortest path 8380 dimensions.
+In total, 10-dimensional measurement features include fans number, betweenness, closeness, followers, posts number, average posts interval, average word count per post, retweet number, movie-related post number, co-occurrence number, shortest path with 8380 dimensions.
 
@@
 
-\section{FC-GRU-CNN Model Classifier}
+\section{FC-GRU-CNN Model}
 
@@
 
-Based on the film box office prediction of actor's Sina Weibo sentiment and social network characteristics, this paper discussed the relationship between the movie meta-data,
-the movie Sina Weibo text sentiment, the actor's social network feature, the shortest path feature and the actor's art characteristics.
-Then proposed a FC-GRU-CNN box office binary prediction model, compared with the current best C-LSTM model, the accuracy improves 14\%, in a dataset of 1,296 movies released on China mainland collected from 2011 to 2015, proposed model has an accuracy of 75\% in test set.
+According to the box office prediction model, using actors' Sina Weibo sentiments, social relationship and network characteristics, this paper discussed relationship between the movie meta-data,
+Sina Weibo text sentiments, the actors' network characteristics, shortest path feature and actors' art contribution.
+Then I proposed a FC-GRU-CNN box office prediction model, compared to Zhou \etal model, accuracy improves 14\%, and tested in a dataset of 1,296 movies released in China mainland collected from 2011 to 2015, proposed model has an accuracy of 75\%.
 

### 2020-10-03 A-BasicCommom/CVPR2021/cvpr_vision.tex
1.CVPR v0.2.0

@@
 \usepackage{amssymb}
-
+% Include other packages here, before hyperref.
 \usepackage[linesnumbered,lined,boxed,commentsnumbered]{algorithm2e}
-% Include other packages here, before hyperref.
 
@@
 %%%%%%%%% TITLE
-%\title{Movie Box office Prediction via Joint Actor Representations and Social Media Sentiment}
 \title{Visualize Non-Euclidean Actors Social Media via Joint Social Relationship Representations, Network Characteristics and Media Sentiments}
@@
   In film industry, visualizing social media data for analyzing stars and audience intention for movies is common to producers.
-  However, non-Euclidean social media is hard to analyze, I propose a FC-GRU-CNN deep learning architecture for visualizing social media, and as an empirical case, use it in a box-office prediction task.
+  However, non-Euclidean social media is hard to analyze, I propose a FC-GRU-CNN deep learning architecture for visualizing social media, and as an empirical case, use it in box-office prediction task.
   Further more, key factors, such as social relationship representations, network characteristics and media sentiments are used in the prediction model.
-  By exploiting long-term memory ability of GRU layer in long sequences in cast list and the mapping ability of CNN layer in retrieving all pairs shortest path feature of actors social relationship,
-  proposed model is 14\% higher in accuracy than Zhou \etal model.
+  By exploiting long-term memory ability of GRU layer in long sequences of cast list and the mapping ability of CNN layer in retrieving all pairs shortest path feature of actors social relationship,
+  the proposed model is 14\% higher in accuracy than Zhou \etal's model.
 \end{abstract}
@@
 \par$\bullet$ Co-occurrence: The more actors and other actors co-appears on Sina Weibo posts, the lower the box office is.
-Then, calculated Pearson correlation of average box office per movie and actors social network measurement characteristics, the post and retweet correlation is -0.00108, social media Activity correlation is -0.03203, Co-occurrence correlation is 0.1508.
+\par Then, I calculated Pearson correlation of average box office per movie and actors social network measurement characteristics, the post and retweet correlation is $-0.108\%$, social media Activity correlation is $-3.203\%$, Co-occurrence correlation is $15.08\%$.
 First of all, the actor's average box office per movie is clearly positively related to the influence of the actors, that is, the higher number of co-occurrence in Sina Weibo, the higher average box office per movie.
@@
 Actors social network meta-data decision tree visualization is illustrated as Figure 2.
-Definition 1 Gini Impurity  A measure of how often randomly selected elements are incorrectly marked from a collection is a common CART (decision tree) algorithm evaluation indicator.
+\par Definition 1 (Gini Impurity)  A measure of how often randomly selected elements are incorrectly marked from a collection is a common CART (decision tree) algorithm evaluation indicator.
 If it is randomly marked based on the distribution of the label in a subset.
@@
 For each edge $e\in \Bbb E$, the ordered pair is $e=(u,v)$, $u,v \in \Bbb V$ and the weight is $A_{ij}$.
-A network can be represented as an adjacent matrix, $A\in \Bbb R^{(n*n)}$, and the goal of network embedding is to learn an all pairs representation, $U\in \Bbb R^{(n*m), m < n}$, where $m$ is an embedding dimension.
-Definition 2 (Shortest Path Network Embedding)  In a network represented as a $G=(V,E)$, $\Bbb V$ represents a node set of $n$ nodes, and $\Bbb E$ represents an edge set of $m$ edges.
-For each edge $e\in \Bbb E$, the ordered pair is $e=(u,v)$, $u,v \in \Bbb V$ and the weight is $A_{ij}$.
+A network can be represented as an adjacent matrix, $A\in \Bbb R^{(n*n)}$, and the goal of network embedding is to learn an all pairs representation, $U\in \Bbb R^{(n*m)}$, $m < n$, where $m$ is an embedding dimension.\par
+Definition 2 (Shortest Path Network Embedding)  In a network represented as a $\Bbb G=(\Bbb V,\Bbb E)$, $\Bbb V$ represents a node set of $n$ nodes, and $\Bbb E$ represents an edge set of $m$ edges.
+For each edge $e\in \Bbb E$, the ordered pair is $e=(u,v)$, $u,v \in \Bbb V$ and the weight is $A_{ij}$.\par
 A network can be represented as an adjacent matrix, $A\in \Bbb R^{(n*n)}$, and the goal of the shortest path network embedding is to learn an all pairs, shortest path representation, $U\in \Bbb R^{(n*n)}$, where $n$ is an embedding dimension.
@@
 \begin{center}
-%\fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
   \fbox{\rule{0pt}{2in} \includegraphics[width=0.9\linewidth]{boxofficenet.pdf}}
@@
 
-%\subsection{Dataset}
-%
-%From 2011 to 2015, collected 3,669 films releasing Chinese mainland and 14,234 actors from the China-Box-Office, and collected the retweets and tweets of 8,508 actors on Sina Weibo social network.
-%The names of 7,369 actors were obtained from 14,234 actors participants records, as a dictionary of actors' names.
-There are 3,056 actors have opened account that can be collected from the social network.
-%A total of 1,298 films featuring social networking characters were extracted from 3,669 films, including at least one actor with social network ingress characteristics.
-Then entity alignment was performed, matching a total of 7,369 actors according to the actor's name entity alignment method, of which 3,056 had social network characteristics, while 4,313 actors did not have social network measurement data, which the network node represented as unknown node.
-%
-%\subsection{Feature Introduction}
-%
-%Movie Sina Weibo text features, extract the content of the Sina Weibo containing 1298 movie names from the social media and the posts text, calculate the sentiment al classification, as the sentiment characteristics of the Sina Weibo text.
-%Actor social network measurement characteristics, measured the actor's social network as follows, including fan number, number of media, closeness, number of followers, number of blogs, average blog spacing, average number of tweets, number of retweets, movie mentions of Sina Weibo, total cash.
-%The shortest path feature of the social network structure of the actors, calculated the full-node shortest path of 8508 actors' social networks, and extracted the shortest path characteristics of 8508 dimensions of the 7,369 actors concerned.
-The calculation of the maximum minimum path for the full node is 8, for illustration purpose, the unreachable distance between nodes is recorded as 9, as Figure 1a.
-%Actors' art characteristics, the average box office as an indicator of the actor's box office impact, using the Chinese box office online actor's participation in the film box office data, to calculate the average film box office.
-%Using the box office data of the Chinese box office online actors participating in the film, the average film box office of the actorised, the average film box office as the actor's box office influence index, this characteristic as the actor's art characteristics.
-The average box office of 7,369 actors is counted from China's box office network as a feature of their art.
-%Sina Weibo posts text and movie actor participation name list refer to Table 1, for sentiment classification of texts and retweets, first calculate Bigram of the text, then calculate Tfidf of each Bigram, then a Logistic Regression classifier is trained.
-Use this model to classify sentiment of texts and retweets for each movie-related posts, then get positive number, negative number, total number and positive-negative ratio, the results are shown in Table 2.
-%In summary, the characteristics that need to be computed are movie meta-data, Sina Weibo sentiment, actors' participation name list.
-For actor representation, actors' network measurement, actors shortest path characteristics and art characteristics are needed.
-For movie partial representation, film meta-data, e.
-g., the year of release, and Sina Weibo sentiment characteristics, e.
-g., positive sentiment, negative sentiment, total sentiment and sentiment positive and negative ratio, are needed.
-%
-%
-%%-------------------------------------------------------------------------
-%
-%\section{Time Bound Of Distance Product Algorithm With Cache Optimized Block Matrix Multiplication}
-%For a fully connected network, the graph has a maximum diameter of $n-1$, so using result reuse method in distance product, that is use the last distance product calculation result, the matrix multiplication times is $log_2(n-1)$.
-%Albert~\cite{albert1999diameter} found that social networks, the Internet and other complex networks have scale-free characteristics and small world phenomenon, thus network diameter is much smaller than the number of network nodes.
-%I present the corresponding nodes counts, diameters and logarithm of diameters in Table 1, from the observation there is formula (1):
-%In social networks, the number of nodes $n$, with cache block size $B*B$, according to the formula (9-10), the matrix product calculation iteration times does not exceed the number of $\lceil{log\Bbb D}\rceil$, recall that Lam \etal proved that matrix multiplication time bound is \(O({2n^3 \over B}+{n^2})\) ,
-%thus Alon \etal algorithm time bound is \(O({log\Bbb D2n^3\over B})\) , use the equation (1) result, time bound is \(O({ \log(\log{N})2n^3\over B})\).
-%With the arithmetic limitation on the floating-point operation, \eg take a network of number of nodes $N<10^{308}$
-%as shown in Table 1, see that the shortest path calculation iterations time is no larger than $\log{\Bbb D}\approx{\log(\log{N})}<7$, that is, the number of calculation iterations does not exceed the magic number 7,
-%bringing a stronger time bound of \(O({14n^3\over B})\).
-%In another words, with the floating-point operation accuracy limitation on computer hardware and complex networks scale-free characteristics, all node pairs shortest path algorithm time bound is \(O({14n^3\over B})\).
-%
-%
-%%-------------------------------------------------------------------------
-%
-%
-%\section{Shortest Path Algorithm With Block Matrix Multiplication}
-%
-%Definition 1 (Outer Product Matrix Multiplication) Given matrices \(\Bbb A \in \Bbb R^{m*r}\), \(\Bbb B \in \Bbb R^{r*n}\) and \(\Bbb C \in \Bbb R^{m*n}\), the outer product is:
-%\begin{equation}
-%\Bbb C = \Bbb C  + \Bbb A(:,k)\bullet \Bbb B(k,:) , k \in (1,r)
-%\end{equation}
-%
-%Given two vectors \(\textsc x\), \(\textsc y\), and matrix \(\Bbb A\), having \(\Bbb A \in \Bbb R^{m*n}\), \(\textsc x \in \Bbb R^{m}\) and \(\textsc y \in \Bbb R^{n}\) the outer product \(\bullet\) is defined by:
-%\begin{equation}
-%a_{ij} = a_{ij} + x_i * y_j, i \in (1,m), j \in (1,n)
-%\end{equation}
-%
-%Definition 2 (Distance Product Matrix Multiplication) Given matrices \(\Bbb A \in \Bbb R^{m*r}\), \(\Bbb B \in \Bbb R^{r*n}\) and \(\Bbb C \in \Bbb R^{m*n}\), the distance product is:
-%\begin{equation}
-%  \Bbb C = \min(\Bbb C, \Bbb A(:,k)\odot \Bbb B(k,:)) , k \in (1,r)
-%\end{equation}
-%
-%Given two vectors \(\textsc x\), \(\textsc y\), and matrix \(\Bbb A\), having \(\Bbb A \in \Bbb R^{m*n}\), \(\textsc x \in \Bbb R^{m}\) and \(\textsc y \in \Bbb R^{n}\) the distance product \(\odot\) is defined by:
-%\begin{equation}
-%a_{ij} = \min(a_{ij} , x_i + y_j), i \in (1,m), j \in (1,n)
-%\end{equation}
-%%-------------------------------------------------------------------------
-%%\begin{figure}[t]
-%%\begin{center}
-%%\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
-%%   \includegraphics[width=1.0\linewidth]{figure1.pdf}
-%%\end{center}
-%%   \caption{Adjacent matrix, each iterations and the result matrix visualization of actors' social network.
-(a) initial state after each round of calculation, (b) the result matrix after the first round of calculation, (c) the result matrix of the second round of calculation, (d) the third and in the same time last round of calculation, the all pairs nodes shortest path result matrix.}
-%%\label{fig:long}
-%%\label{fig:onecol}
-%%\end{figure}
-%
-%\begin{figure*}
-%\begin{center}
-%%\fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
-%  \fbox{\rule{0pt}{2in} \includegraphics[width=0.9\linewidth]{figure1.pdf}}
-%\end{center}
-%   \caption{Adjacent matrix, each iterations and the result matrix visualization of actors' social network.
-(a) initial state after each round of calculation, (b) the result matrix after the first round of calculation, (c) the result matrix of the second round of calculation, (d) the third and in the same time last round of calculation, the all pairs nodes shortest path result matrix.}
-%\label{fig:short}
-%\end{figure*}
-%
-%
-%\subsection{Maximum Calculation}
-%
-%Calculate the largest value of the square matrix element $\widetilde X$, such as the formula (4):
-%
-%\subsection{Exponential Calculation}
-%
-%The calculation accuracy of different computer hardware is in line with the IEEE floating-point operation standard~\cite{ieee1985ieee},
-%first of all, transform the input matrix by exponential transformation, to be specific, taking the number of nodes as the base,
-%taking the difference between the largest value of the element $\widetilde X$ and the matrix elements as exponential, as shown in the formula (5).
-%\eg For actors' social network with 8508 nodes, the diameter of the network does not allow to exceed 9.8 and 78.4 when calculating a precision of 32-bit floating-point and 64-bit floating-point,
-%otherwise the exponential operation on the computer platform will overflow.
-%
-%\subsection{Matrix Multiplication}
-%Use different matrix libraries to speed up the matrix multiplication on computer hardware, as shown in Table 3, choose proper device-based optimized matrix multiplication libraries according to different conditions, such as matrix sparseness, calculation hardware, and programming language.
-%
-%%-------------------------------------------------------------------------
-%\subsection{Logarithm Calculation}
-%Take non-zero elements of the matrix multiplication result to the element logarithm process, that is, the number of network nodes as the base, the element in the matrix multiplication result as the true number, then round down the logarithm result,
-%after that take difference between twice of the largest input matrix element value $\widetilde X$ and the logarithm result as result, such as formula (6).
-%
-%\subsection{Distance Product Exchange Law}
-%
-%From the iteration of the shortest path calculation, suppose \(\Bbb A,\ \Bbb B,\ \Bbb C\) is the square matrix, according to the association law of distance product, there is a formula (7):
-%Matrix multiplication has association law, and the distance product is isomorphism to matrix multiplication, so simplify the shortest path iteration process as formula (8):
-%Since matrix multiplication has association law and distance product is isomorphism to matrix multiplication, similarly, distance product has an association law.
-%Under the premise of the shortest path matrix $L^{(n-1)}$ given the adjacent matrix and the $n-1$ edge, calculate the shortest path matrix $L^{(n)}$ with n edges, and extend the shortest path of the $n-1$ edge by edge.
-%Calculating the shortest path matrix $L^{(n)}$ can be completed as formula (9):
-%As can be seen from the nature of the shortest path in the graph, the shortest path from the any of two nodes does not exceed $n-1$, so there is formula (10):
-%Definition 3 Result Reuse in Distance Product According to the nature of the equation (8), the process of calculating the shortest path iteration using the last result of distance product follows in turn, as shown in formula (11).
-%The shortest path needs to be calculated $\lceil{log_2(n-1)}\rceil$ times matrix multiplication, from the formula (10), it can be seen that $(n-1)\leq2^{\lceil{log_2(n-1)}\rceil}$ is the same as the simple shortest path matrix calculation result $L^{(n-1)}$, so there is a formula (12):
-%Obviously, the result reuse method saves $n-2-\lceil{log_2(n-1)}\rceil$ times of matrix multiplication.
-%Observe the shortest path calculation process of the actors' social network, the adjacent matrix is shown in Figure 1a, and the change of result in each iteration is shown in Figure 1b-d, the shortest path result matrix converges gradually, each element stabilizes as iterations goes.
-%
-%
-%\begin{algorithm}
-%\caption{Lower Bounds Convergence Matrix Products in All Pairs Shortest Path}\label{algorithm}
-%\KwData{Adjacent Matrix $\Bbb W$, Matrix Row $n$, Network Diameter $\Bbb D$}
-%\KwResult{Shortest path result $L^{(m)}$}
-%$L^{(1)}\leftarrow \Bbb W$\;
-%$m\leftarrow 1$\;
-%\While{$m\leq \Bbb D$}{
-%  $\Bbb A\leftarrow L^{(m)},\Bbb B\leftarrow L^{(m)},$\;
-%  $x\leftarrow \min{(a_i,b_i)}, y\leftarrow \max{(a_i,b_i)}, i \in (1,n)$\;
-%  Exponential transformation of matrices $\Bbb A\ and\ \Bbb B$\;
-%    $a_{ij}^{'}={(n+1)}^{y-a_{ij}}$\;
-%    $b_{ij}^{'}={(n+1)}^{y-b_{ij}}$\;
-%  \eIf{$L^{(m)}$ is sparse}{
-%    $\odot\leftarrow \bigcirc$//sparse matrix multiplication\;
-%  }{
-%    $\odot\leftarrow \otimes$//dense matrix multiplication\;
-%  }
-%  Given matrix $\Bbb C^{'}$, $\Bbb C^{'} \in \Bbb R^{n\times n}$\;
-%  $\Bbb C^{'}\leftarrow \Bbb A^{'}\odot\Bbb B^{'}$\;
-%  Logrithm transformation of matrix $\Bbb C^{'}$\;
-%  $\Bbb C\leftarrow \log{\Bbb C^{'}}$\;
-%  \If{$L^{(m)} \eq \Bbb C$}{
-%    \bold{return}\ $L^{(m)}$\;
-%  }
-%  $L^{(2m)}\leftarrow \Bbb C$\;
-%  $m\leftarrow 2*m$\;
-%}
-%\bold{return} $L^{(m)}$\;
-%\end{algorithm}
-%
-%
-%\section{Architecture Design}
-%
-%\subsection{Sparseness Judgment}
-%
-%As shown in Table 1, observing the adjacent matrix represented by the network diagram is usually a sparse matrix, and matrix gradually becomes dense during iterations,
-%and one idea of optimization is to use sparse matrix multiplication to speed up the iteration when the matrix is sparse, and when the matrix becomes denser, the sparse matrix multiplication is much time-consuming.
-%Taking the actors' social network as an example, the non-zero element of the adjacent matrix of 8508 nodes is 617958, and the non-zero element of the matrix is 0.8536\% of the total element,
-%which is a typical sparse matrix. Consider the advantages of sparse matrix multiplication algorithm, a threshold for triggering sparse matrix multiplication is set,
-%and when the proportion of non-zero-value elements entered is less than the 10\% threshold, performs sparse matrix multiplication.
-%
-%\subsection{Convergence Judgment}
-%
-%For networks with unknown diameters, the calculation results can be made using convergence method, and for the calculation process of reaching convergence,
-%i.e. $L^{(n-1)}=L^{(n)}$, should be regarded as the program termination of iteration, and the calculation of the matrix product method is completed by the equation (4).
-%
-%\subsection{The Shortest Path Algorithm Fusing Sparseness Judgment And Convergence Judgment}
-%
-%Based on Alon \etal distance product algorithm, utilizing the sparseness judgment of the input matrix and the calculation result convergence judgment,
-%with the network conforming to the power law distribution and the precision of floating-point operation, and the name implies two characteristics of the limitation
-%of floating-point precision on the scale-free social network and the computer hardware, the algorithm process flow is shown in Algorithm 1.
-%
-%\section{Experiment}
-%
-%Firstly, compared to Floyd-Warshall algorithm implemented on CPU, the Alon \etal algorithm implementation with matrix multiplication of block cache optimization on GPU has a time performance improvement, see Table 1.
-%$PowerLawBound_{a-f}$ shows that using different libraries on CPU/GPU, the proposed algorithm has significant performance improvement over Alon \etal algorithm.
-%
-%
-%\begin{table}
-%\begin{center}
-%\begin{tabular}{|l|c|}
-%\hline
-%Algorithm & Time Cost \\
-%\hline\hline
-%Floyd-Warshall & 1055880s \\
-%Alon \etal          & 594.7s \\
-%$PowerLawBound_a$  & 427.9s \\
-%$PowerLawBound_b$ & 328.4s \\
-%$PowerLawBound_c$ & 95.0s \\
-%$PowerLawBound_d$ & 45.0s \\
-%$PowerLawBound_e$ & 19.32s \\
-%$PowerLawBound_f$ & 15.98s \\
-%\hline
-%\end{tabular}
-%\end{center}
-%\caption{Performance comparison on different hardware. (a) CPU numpy library. (b) CPU scipy/numpy library. (c) GPU cuBLAS. (d) CPU openBLAS. (e) GPU CuPy. (f) GPU CuPy-sparse/CuPy.}
-%\end{table}
-%
-%
-%\section{Conclusion}
-%This paper discussed a novel algorithm in all pairs shortest path computation task, using distance product exchange law.
-%The time bound of Alon \etal distance product algorithm with block matrix multiplication is \(O({\log{n}2n^3\over B})\) with $B=\text{SIZE}_{\text{block}}$.
-%To strengthen the conditions, on scale-free social networks, for the precision limit of floating-point operation on hardware, additional condition on the social network diameter is added to avoid floating-point operation overflow during the calculation process.
-%the algorithm has lower time bound \(O({14n^3\over B})\).
-%With strengthened conditions, I proposed a novel algorithm, leveraging matrix sparseness judgment and calculation convergence judgment.
-%\textbf{PowerLaw} refers to the network node numbers conforming to the characteristics that social networks power law distribution, and \textbf{Bound} refers to the floating-point operations arithmetic limitation of accuracy on hardware.
-%The experimental results show that \textbf{PowerLawBound} algorithm improves time performance by 39\% to 36.2 times on CPU/GPU hardware compared to Alon \etal algorithm .
-
-%\begin{quote}
-%\begin{center}
-%    An analysis of the frobnicatable foo filter.
-%\end{center}
-%
-%   In this paper we present a performance analysis of our
-%   previous paper [1], and show it to be inferior to all
-%   previously known methods.  Why the previous paper was
-%   accepted without this analysis is beyond me.
-%
-%   [1] Removed for blind review
-%\end{quote}
-%
-%
-%An example of an acceptable paper:
-%
-%\begin{quote}
-%\begin{center}
-%     An analysis of the frobnicatable foo filter.
-%\end{center}
-%
-%   In this paper we present a performance analysis of the
-%   paper of Smith \etal [1], and show it to be inferior to
-%   all previously known methods.  Why the previous paper
-%   was accepted without this analysis is beyond me.
-%
-%   [1] Smith, L and Jones, C. ``The frobnicatable foo
-%   filter, a fundamental contribution to human knowledge''.
-%   Nature 381(12), 1-213.
-%\end{quote}
-%
-%If you are making a submission to another conference at the same time,
-%which covers similar or overlapping material, you may need to refer to that
-%submission in order to explain the differences, just as you would if you
-%had previously published related work.  In such cases, include the
-%anonymized parallel submission~\cite{Authors14} as additional material and
-%cite it as
-%\begin{quote}
-%[1] Authors. ``The frobnicatable foo filter'', F\&G 2014 Submission ID 324,
-%Supplied as additional material {\tt fg324.pdf}.
-%\end{quote}
-%
-%Finally, you may feel you need to tell the reader that more details can be
-%found elsewhere, and refer them to a technical report.  For conference
-%submissions, the paper must stand on its own, and not {\em require} the
-%reviewer to go to a techreport for further details.  Thus, you may say in
-%the body of the paper ``further details may be found
-%in~\cite{Authors14b}''.  Then submit the techreport as additional material.
-%Again, you may not assume the reviewers will read this material.
-%
-%Sometimes your paper is about a problem which you tested using a tool which
-%is widely known to be restricted to a single institution.  For example,
-%let's say it's 1969, you have solved a key problem on the Apollo lander,
-%and you believe that the CVPR70 audience would like to hear about your
-%solution.  The work is a development of your celebrated 1968 paper entitled
-%``Zero-g frobnication: How being the only people in the world with access to
-%the Apollo lander source code makes us a wow at parties'', by Zeus \etal.
-%
-%You can handle this paper like any other.  Don't write ``We show how to
-%improve our previous work [Anonymous, 1968].  This time we tested the
-%algorithm on a lunar lander [name of lander removed for blind review]''.
-%That would be silly, and would immediately identify the authors. Instead
-%write the following:
-%\begin{quotation}
-%\noindent
-%   We describe a system for zero-g frobnication.  This
-%   system is new because it handles the following cases:
-%   A, B.  Previous systems [Zeus et al. 1968] didn't
-%   handle case B properly.  Ours handles it by including
-%   a foo term in the bar integral.
-%
-%   ...
-%
-%   The proposed system was integrated with the Apollo
-%   lunar lander, and went all the way to the moon, don't
-%   you know.  It displayed the following behaviours
-%   which show how well we solved cases A and B: ...
-%\end{quotation}
-%As you can see, the above text follows standard scientific convention,
-%reads better than the first version, and does not explicitly name you as
-%the authors.  A reviewer might think it likely that the new paper was
-%written by Zeus \etal, but cannot make any decision based on that guess.
-%He or she would have to be sure that no other authors could have been
-%contracted to solve problem B.
-%\medskip
-%
-%\noindent
-%FAQ\medskip\\
-%{\bf Q:} Are acknowledgements OK?\\
-%{\bf A:} No.  Leave them for the final copy.\medskip\\
-%{\bf Q:} How do I cite my results reported in open challenges?
-%{\bf A:} To conform with the double blind review policy, you can report results of other challenge participants together with your results in your paper.
-For your results, however, you should not identify yourself and should not mention your participation in the challenge.
-Instead present your results referring to the method proposed in your paper and draw conclusions based on the experimental comparison to other results.\medskip\\
-%
-%\begin{figure}[t]
-%\begin{center}
-%\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
-%   %\includegraphics[width=0.8\linewidth]{egfigure.eps}
-%\end{center}
-%   \caption{Example of caption.  It is set in Roman so that mathematics
-%   (always set in Roman: $B \sin A = A \sin B$) may be included without an
-%   ugly clash.}
-%\label{fig:long}
-%\label{fig:onecol}
-%\end{figure}
-%
-%\subsection{Miscellaneous}
-%
-%\noindent
-%Compare the following:\\
-%\begin{tabular}{ll}
-% \verb'$conf_a$' &  $conf_a$ \\
-% \verb'$\mathit{conf}_a$' & $\mathit{conf}_a$
-%\end{tabular}\\
-%See The \TeX book, p165.
-%
-%The space after \eg, meaning ``for example'', should not be a
-%sentence-ending space. So \eg is correct, {\em e.g.} is not.  The provided
-%\verb'\eg' macro takes care of this.
-%
-%When citing a multi-author paper, you may save space by using ``et alia'',
-%shortened to ``\etal'' (not ``{\em et.\ al.}'' as ``{\em et}'' is a complete word.)
-%However, use it only when there are three or more authors.  Thus, the
-%following is correct: ``
-%   Frobnication has been trendy lately.
-%   It was introduced by Alpher~\cite{Alpher02}, and subsequently developed by
-%   Alpher and Fotheringham-Smythe~\cite{Alpher03}, and Alpher \etal~\cite{Alpher04}.''
-%
-%This is incorrect: ``... subsequently developed by Alpher \etal~\cite{Alpher03} ...''
-%because reference~\cite{Alpher03} has just two authors.  If you use the
-%\verb'\etal' macro provided, then you need not worry about double periods
-%when used at the end of a sentence as in Alpher \etal.
-%
-%For this citation style, keep multiple citations in numerical (not
-%chronological) order, so prefer \cite{Alpher03,Alpher02,Authors14} to
-%\cite{Alpher02,Alpher03,Authors14}.
-%
-%
-%\begin{figure*}
-%\begin{center}
-%\fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
-%\end{center}
-%   \caption{Example of a short caption, which should be centered.}
-%\label{fig:short}
-%\end{figure*}
-%
-%%------------------------------------------------------------------------
-%\section{Formatting your paper}
-%
-%All text must be in a two-column format. The total allowable width of the
-%text area is $6\frac78$ inches (17.5 cm) wide by $8\frac78$ inches (22.54
-%cm) high. Columns are to be $3\frac14$ inches (8.25 cm) wide, with a
-%$\frac{5}{16}$ inch (0.8 cm) space between them. The main title (on the
-%first page) should begin 1.0 inch (2.54 cm) from the top edge of the
-%page. The second and following pages should begin 1.0 inch (2.54 cm) from
-%the top edge. On all pages, the bottom margin should be 1-1/8 inches (2.86
-%cm) from the bottom edge of the page for $8.5 \times 11$-inch paper; for A4
-%paper, approximately 1-5/8 inches (4.13 cm) from the bottom edge of the
-%page.
-%
-%%-------------------------------------------------------------------------
-%\subsection{Margins and page numbering}
-%
-%All printed material, including text, illustrations, and charts, must be kept
-%within a print area 6-7/8 inches (17.5 cm) wide by 8-7/8 inches (22.54 cm)
-%high.
-%%
-%Page numbers should be in footer with page numbers, centered and .75
-%inches from the bottom of the page and make it start at the correct page
-%number rather than the 4321 in the example.  To do this fine the line (around
-%line 20)
-%\begin{verbatim}
-%\setcounter{page}{4321}
-%\end{verbatim}
-%where the number 4321 is your assigned starting page.
-%
-%
-%
-%%-------------------------------------------------------------------------
-%\subsection{Type-style and fonts}
-%
-%Wherever Times is specified, Times Roman may also be used. If neither is
-%available on your word processor, please use the font closest in
-%appearance to Times to which you have access.
-%
-%MAIN TITLE. Center the title 1-3/8 inches (3.49 cm) from the top edge of
-%the first page. The title should be in Times 14-point, boldface type.
-%Capitalize the first letter of nouns, pronouns, verbs, adjectives, and
-%adverbs; do not capitalize articles, coordinate conjunctions, or
-%prepositions (unless the title begins with such a word). Leave two blank
-%lines after the title.
-%
-%AUTHOR NAME(s) and AFFILIATION(s) are to be centered beneath the title
-%and printed in Times 12-point, non-boldface type. This information is to
-%be followed by two blank lines.
-%
-%The ABSTRACT and MAIN TEXT are to be in a two-column format.
-%
-%MAIN TEXT. Type main text in 10-point Times, single-spaced. Do NOT use
-%double-spacing. All paragraphs should be indented 1 pica (approx. 1/6
-%inch or 0.422 cm). Make sure your text is fully justified---that is,
-%flush left and flush right. Please do not place any additional blank
-%lines between paragraphs.
-%
-%Figure and table captions should be 9-point Roman type as in
-%Figures~\ref{fig:onecol} and~\ref{fig:short}.  Short captions should be centred.
-%
-%\noindent Callouts should be 9-point Helvetica, non-boldface type.
-%Initially capitalize only the first word of section titles and first-,
-%second-, and third-order headings.
-%
-%FIRST-ORDER HEADINGS. (For example, {\large \bf 1. Introduction})
-%should be Times 12-point boldface, initially capitalized, flush left,
-%with one blank line before, and one blank line after.
-%
-%SECOND-ORDER HEADINGS. (For example, { \bf 1.1. Database elements})
-%should be Times 11-point boldface, initially capitalized, flush left,
-%with one blank line before, and one after. If you require a third-order
-%heading (we discourage it), use 10-point Times, boldface, initially
-%capitalized, flush left, preceded by one blank line, followed by a period
-%and your text on the same line.
-%
-%%-------------------------------------------------------------------------
-%\subsection{Footnotes}
-%
-%Please use footnotes\footnote {This is what a footnote looks like.  It
-%often distracts the reader from the main flow of the argument.} sparingly.
-%Indeed, try to avoid footnotes altogether and include necessary peripheral
-%observations in
-%the text (within parentheses, if you prefer, as in this sentence).  If you
-%wish to use a footnote, place it at the bottom of the column on the page on
-%which it is referenced. Use Times 8-point type, single-spaced.
-%
-%
-%%-------------------------------------------------------------------------
-%\subsection{References}
-%
-%List and number all bibliographical references in 9-point Times,
-%single-spaced, at the end of your paper. When referenced in the text,
-%enclose the citation number in square brackets, for
-%example~\cite{Authors14}.  Where appropriate, include the name(s) of
-%editors of referenced books.
-%
-%\begin{table}
-%\begin{center}
-%\begin{tabular}{|l|c|}
-%\hline
-%Method & Frobnability \\
-%\hline\hline
-%Theirs & Frumpy \\
-%Yours & Frobbly \\
-%Ours & Makes one's heart Frob\\
-%\hline
-%\end{tabular}
-%\end{center}
-%\caption{Results.   Ours is better.}
-%\end{table}
-%
-%%-------------------------------------------------------------------------
-%\subsection{Illustrations, graphs, and photographs}
-%
-%All graphics should be centered.  Please ensure that any point you wish to
-%make is resolvable in a printed copy of the paper.  Resize fonts in figures
-%to match the font in the body text, and choose line widths which render
-%effectively in print.  Many readers (and reviewers), even of an electronic
-%copy, will choose to print your paper in order to read it.  You cannot
-%insist that they do otherwise, and therefore must not assume that they can
-%zoom in to see tiny details on a graphic.
-%
-%When placing figures in \LaTeX, it's almost always best to use
-%\verb+\includegraphics+, and to specify the  figure width as a multiple of
-%the line width as in the example below
-%{\small\begin{verbatim}
-%   \usepackage[dvips]{graphicx} ...
-%   \includegraphics[width=0.8\linewidth]
-%                   {myfile.eps}
-%\end{verbatim}
-%}
-%
-%
-%%-------------------------------------------------------------------------
-%\subsection{Color}
-%
-%Please refer to the author guidelines on the \confYear~web page for a discussion
-%of the use of color in your document.
-%
-%%------------------------------------------------------------------------
-%\section{Final copy}
-%
-%You must include your signed IEEE copyright release form when you submit
-%your finished paper. We MUST have this form before your paper can be
-%published in the proceedings.
-%
-%Please direct any questions to the production editor in charge of these
-%proceedings at the IEEE Computer Society Press:
-%\url{https://www.computer.org/about/contact}.
-
 {\small

### 2020-10-03 A-BasicCommom/CVPR2021/cvpr.tex
1.CVPR v0.2.0

@@
 \usepackage{amssymb}
-
 \usepackage[linesnumbered,lined,boxed,commentsnumbered]{algorithm2e}
@@
 For time complexity of distance product, matrix multiplication is the most complex subprocedures;
-(1) For distance product optimization, Zwick proposed distance product with block matrix multiplication, therefore choose proper computation device library with optimized cache for block matrix multiplication.
-(2) For iteration optimization, because Aho proved distance product is isomorphic to the matrix multiplication, and regard to that the distance product association law, optimize the iteration process by last distance product result reuse.
+
+\begin{enumerate}
+\item For distance product optimization, Zwick proposed distance product with block matrix multiplication, therefore choose proper computation device library with optimized cache for block matrix multiplication.
+\item For iteration optimization, because Aho proved distance product is isomorphic to the matrix multiplication, and regard to that the distance product association law, optimize the iteration process by last distance product result reuse.
+\end{enumerate}
 
@@
 %-------------------------------------------------------------------------
-%\begin{figure}[t]
-%\begin{center}
-%\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
-%   \includegraphics[width=1.0\linewidth]{figure1.pdf}
-%\end{center}
-%   \caption{Adjacent matrix, each iterations and the result matrix visualization of actors' social network.
-(a) initial state after each round of calculation, (b) the result matrix after the first round of calculation, (c) the result matrix of the second round of calculation, (d) the third and in the same time last round of calculation, the all pairs nodes shortest path result matrix.}
-%\label{fig:long}
-%\label{fig:onecol}
-%\end{figure}
-
 \begin{figure*}
 \begin{center}
-%\fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
   \fbox{\rule{0pt}{2in} \includegraphics[width=0.9\linewidth]{figure1.pdf}}
@@
     $\Bbb C\leftarrow \log{\Bbb C^{'}}$\;
-  \If{$L^{(m)} \eq \Bbb C$}{
-    \bold{return}\ $L^{(m)}$\;
+    \If{$L^{(m)} = \Bbb C$}{
+      {\bf return} $L^{(m)}$\;
     }
@@
   }
-\bold{return} $L^{(m)}$\;
+  {\bf return} $L^{(m)}$\;
 \end{algorithm}
@@
 
-%\begin{quote}
-%\begin{center}
-%    An analysis of the frobnicatable foo filter.
-%\end{center}
-%
-%   In this paper we present a performance analysis of our
-%   previous paper [1], and show it to be inferior to all
-%   previously known methods.  Why the previous paper was
-%   accepted without this analysis is beyond me.
-%
-%   [1] Removed for blind review
-%\end{quote}
-%
-%
-%An example of an acceptable paper:
-%
-%\begin{quote}
-%\begin{center}
-%     An analysis of the frobnicatable foo filter.
-%\end{center}
-%
-%   In this paper we present a performance analysis of the
-%   paper of Smith \etal [1], and show it to be inferior to
-%   all previously known methods.  Why the previous paper
-%   was accepted without this analysis is beyond me.
-%
-%   [1] Smith, L and Jones, C. ``The frobnicatable foo
-%   filter, a fundamental contribution to human knowledge''.
-%   Nature 381(12), 1-213.
-%\end{quote}
-%
-%If you are making a submission to another conference at the same time,
-%which covers similar or overlapping material, you may need to refer to that
-%submission in order to explain the differences, just as you would if you
-%had previously published related work.  In such cases, include the
-%anonymized parallel submission~\cite{Authors14} as additional material and
-%cite it as
-%\begin{quote}
-%[1] Authors. ``The frobnicatable foo filter'', F\&G 2014 Submission ID 324,
-%Supplied as additional material {\tt fg324.pdf}.
-%\end{quote}
-%
-%Finally, you may feel you need to tell the reader that more details can be
-%found elsewhere, and refer them to a technical report.  For conference
-%submissions, the paper must stand on its own, and not {\em require} the
-%reviewer to go to a techreport for further details.  Thus, you may say in
-%the body of the paper ``further details may be found
-%in~\cite{Authors14b}''.  Then submit the techreport as additional material.
-%Again, you may not assume the reviewers will read this material.
-%
-%Sometimes your paper is about a problem which you tested using a tool which
-%is widely known to be restricted to a single institution.  For example,
-%let's say it's 1969, you have solved a key problem on the Apollo lander,
-%and you believe that the CVPR70 audience would like to hear about your
-%solution.  The work is a development of your celebrated 1968 paper entitled
-%``Zero-g frobnication: How being the only people in the world with access to
-%the Apollo lander source code makes us a wow at parties'', by Zeus \etal.
-%
-%You can handle this paper like any other.  Don't write ``We show how to
-%improve our previous work [Anonymous, 1968].  This time we tested the
-%algorithm on a lunar lander [name of lander removed for blind review]''.
-%That would be silly, and would immediately identify the authors. Instead
-%write the following:
-%\begin{quotation}
-%\noindent
-%   We describe a system for zero-g frobnication.  This
-%   system is new because it handles the following cases:
-%   A, B.  Previous systems [Zeus et al. 1968] didn't
-%   handle case B properly.  Ours handles it by including
-%   a foo term in the bar integral.
-%
-%   ...
-%
-%   The proposed system was integrated with the Apollo
-%   lunar lander, and went all the way to the moon, don't
-%   you know.  It displayed the following behaviours
-%   which show how well we solved cases A and B: ...
-%\end{quotation}
-%As you can see, the above text follows standard scientific convention,
-%reads better than the first version, and does not explicitly name you as
-%the authors.  A reviewer might think it likely that the new paper was
-%written by Zeus \etal, but cannot make any decision based on that guess.
-%He or she would have to be sure that no other authors could have been
-%contracted to solve problem B.
-%\medskip
-%
-%\noindent
-%FAQ\medskip\\
-%{\bf Q:} Are acknowledgements OK?\\
-%{\bf A:} No.  Leave them for the final copy.\medskip\\
-%{\bf Q:} How do I cite my results reported in open challenges?
-%{\bf A:} To conform with the double blind review policy, you can report results of other challenge participants together with your results in your paper.
-For your results, however, you should not identify yourself and should not mention your participation in the challenge.
-Instead present your results referring to the method proposed in your paper and draw conclusions based on the experimental comparison to other results.\medskip\\
-%
-%\begin{figure}[t]
-%\begin{center}
-%\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
-%   %\includegraphics[width=0.8\linewidth]{egfigure.eps}
-%\end{center}
-%   \caption{Example of caption.  It is set in Roman so that mathematics
-%   (always set in Roman: $B \sin A = A \sin B$) may be included without an
-%   ugly clash.}
-%\label{fig:long}
-%\label{fig:onecol}
-%\end{figure}
-%
-%\subsection{Miscellaneous}
-%
-%\noindent
-%Compare the following:\\
-%\begin{tabular}{ll}
-% \verb'$conf_a$' &  $conf_a$ \\
-% \verb'$\mathit{conf}_a$' & $\mathit{conf}_a$
-%\end{tabular}\\
-%See The \TeX book, p165.
-%
-%The space after \eg, meaning ``for example'', should not be a
-%sentence-ending space. So \eg is correct, {\em e.g.} is not.  The provided
-%\verb'\eg' macro takes care of this.
-%
-%When citing a multi-author paper, you may save space by using ``et alia'',
-%shortened to ``\etal'' (not ``{\em et.\ al.}'' as ``{\em et}'' is a complete word.)
-%However, use it only when there are three or more authors.  Thus, the
-%following is correct: ``
-%   Frobnication has been trendy lately.
-%   It was introduced by Alpher~\cite{Alpher02}, and subsequently developed by
-%   Alpher and Fotheringham-Smythe~\cite{Alpher03}, and Alpher \etal~\cite{Alpher04}.''
-%
-%This is incorrect: ``... subsequently developed by Alpher \etal~\cite{Alpher03} ...''
-%because reference~\cite{Alpher03} has just two authors.  If you use the
-%\verb'\etal' macro provided, then you need not worry about double periods
-%when used at the end of a sentence as in Alpher \etal.
-%
-%For this citation style, keep multiple citations in numerical (not
-%chronological) order, so prefer \cite{Alpher03,Alpher02,Authors14} to
-%\cite{Alpher02,Alpher03,Authors14}.
-%
-%
-%\begin{figure*}
-%\begin{center}
-%\fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
-%\end{center}
-%   \caption{Example of a short caption, which should be centered.}
-%\label{fig:short}
-%\end{figure*}
-%
-%%------------------------------------------------------------------------
-%\section{Formatting your paper}
-%
-%All text must be in a two-column format. The total allowable width of the
-%text area is $6\frac78$ inches (17.5 cm) wide by $8\frac78$ inches (22.54
-%cm) high. Columns are to be $3\frac14$ inches (8.25 cm) wide, with a
-%$\frac{5}{16}$ inch (0.8 cm) space between them. The main title (on the
-%first page) should begin 1.0 inch (2.54 cm) from the top edge of the
-%page. The second and following pages should begin 1.0 inch (2.54 cm) from
-%the top edge. On all pages, the bottom margin should be 1-1/8 inches (2.86
-%cm) from the bottom edge of the page for $8.5 \times 11$-inch paper; for A4
-%paper, approximately 1-5/8 inches (4.13 cm) from the bottom edge of the
-%page.
-%
-%%-------------------------------------------------------------------------
-%\subsection{Margins and page numbering}
-%
-%All printed material, including text, illustrations, and charts, must be kept
-%within a print area 6-7/8 inches (17.5 cm) wide by 8-7/8 inches (22.54 cm)
-%high.
-%%
-%Page numbers should be in footer with page numbers, centered and .75
-%inches from the bottom of the page and make it start at the correct page
-%number rather than the 4321 in the example.  To do this fine the line (around
-%line 20)
-%\begin{verbatim}
-%\setcounter{page}{4321}
-%\end{verbatim}
-%where the number 4321 is your assigned starting page.
-%
-%
-%
-%%-------------------------------------------------------------------------
-%\subsection{Type-style and fonts}
-%
-%Wherever Times is specified, Times Roman may also be used. If neither is
-%available on your word processor, please use the font closest in
-%appearance to Times to which you have access.
-%
-%MAIN TITLE. Center the title 1-3/8 inches (3.49 cm) from the top edge of
-%the first page. The title should be in Times 14-point, boldface type.
-%Capitalize the first letter of nouns, pronouns, verbs, adjectives, and
-%adverbs; do not capitalize articles, coordinate conjunctions, or
-%prepositions (unless the title begins with such a word). Leave two blank
-%lines after the title.
-%
-%AUTHOR NAME(s) and AFFILIATION(s) are to be centered beneath the title
-%and printed in Times 12-point, non-boldface type. This information is to
-%be followed by two blank lines.
-%
-%The ABSTRACT and MAIN TEXT are to be in a two-column format.
-%
-%MAIN TEXT. Type main text in 10-point Times, single-spaced. Do NOT use
-%double-spacing. All paragraphs should be indented 1 pica (approx. 1/6
-%inch or 0.422 cm). Make sure your text is fully justified---that is,
-%flush left and flush right. Please do not place any additional blank
-%lines between paragraphs.
-%
-%Figure and table captions should be 9-point Roman type as in
-%Figures~\ref{fig:onecol} and~\ref{fig:short}.  Short captions should be centred.
-%
-%\noindent Callouts should be 9-point Helvetica, non-boldface type.
-%Initially capitalize only the first word of section titles and first-,
-%second-, and third-order headings.
-%
-%FIRST-ORDER HEADINGS. (For example, {\large \bf 1. Introduction})
-%should be Times 12-point boldface, initially capitalized, flush left,
-%with one blank line before, and one blank line after.
-%
-%SECOND-ORDER HEADINGS. (For example, { \bf 1.1. Database elements})
-%should be Times 11-point boldface, initially capitalized, flush left,
-%with one blank line before, and one after. If you require a third-order
-%heading (we discourage it), use 10-point Times, boldface, initially
-%capitalized, flush left, preceded by one blank line, followed by a period
-%and your text on the same line.
-%
-%%-------------------------------------------------------------------------
-%\subsection{Footnotes}
-%
-%Please use footnotes\footnote {This is what a footnote looks like.  It
-%often distracts the reader from the main flow of the argument.} sparingly.
-%Indeed, try to avoid footnotes altogether and include necessary peripheral
-%observations in
-%the text (within parentheses, if you prefer, as in this sentence).  If you
-%wish to use a footnote, place it at the bottom of the column on the page on
-%which it is referenced. Use Times 8-point type, single-spaced.
-%
-%
-%%-------------------------------------------------------------------------
-%\subsection{References}
-%
-%List and number all bibliographical references in 9-point Times,
-%single-spaced, at the end of your paper. When referenced in the text,
-%enclose the citation number in square brackets, for
-%example~\cite{Authors14}.  Where appropriate, include the name(s) of
-%editors of referenced books.
-%
-%\begin{table}
-%\begin{center}
-%\begin{tabular}{|l|c|}
-%\hline
-%Method & Frobnability \\
-%\hline\hline
-%Theirs & Frumpy \\
-%Yours & Frobbly \\
-%Ours & Makes one's heart Frob\\
-%\hline
-%\end{tabular}
-%\end{center}
-%\caption{Results.   Ours is better.}
-%\end{table}
-%
-%%-------------------------------------------------------------------------
-%\subsection{Illustrations, graphs, and photographs}
-%
-%All graphics should be centered.  Please ensure that any point you wish to
-%make is resolvable in a printed copy of the paper.  Resize fonts in figures
-%to match the font in the body text, and choose line widths which render
-%effectively in print.  Many readers (and reviewers), even of an electronic
-%copy, will choose to print your paper in order to read it.  You cannot
-%insist that they do otherwise, and therefore must not assume that they can
-%zoom in to see tiny details on a graphic.
-%
-%When placing figures in \LaTeX, it's almost always best to use
-%\verb+\includegraphics+, and to specify the  figure width as a multiple of
-%the line width as in the example below
-%{\small\begin{verbatim}
-%   \usepackage[dvips]{graphicx} ...
-%   \includegraphics[width=0.8\linewidth]
-%                   {myfile.eps}
-%\end{verbatim}
-%}
-%
-%
-%%-------------------------------------------------------------------------
-%\subsection{Color}
-%
-%Please refer to the author guidelines on the \confYear~web page for a discussion
-%of the use of color in your document.
-%
-%%------------------------------------------------------------------------
-%\section{Final copy}
-%
-%You must include your signed IEEE copyright release form when you submit
-%your finished paper. We MUST have this form before your paper can be
-%published in the proceedings.
-%
-%Please direct any questions to the production editor in charge of these
-%proceedings at the IEEE Computer Society Press:
-%\url{https://www.computer.org/about/contact}.
-
 {\small

### 2020-10-03 A-BasicCommom/CVPR2021/cvpr_vision.tex
1.CVPR v0.2.0

@@
 \begin{abstract}
-  In film industry, visualizing social media data for analyzing stars and audience intention for movies is common to producers.
-  However, non-Euclidean social media is hard to analyze, I propose a FC-GRU-CNN deep learning architecture for visualizing social media, and as an empirical case, use it in box-office prediction task.
-  Further more, key factors, such as social relationship representations, network characteristics and media sentiments are used in the prediction model.
-  By exploiting long-term memory ability of GRU layer in long sequences of cast list and the mapping ability of CNN layer in retrieving all pairs shortest path feature of actors social relationship,
-  the proposed model is 14\% higher in accuracy than Zhou \etal's model.
+  In film industry, visualizing stars social media for analyzing audience intention towards movies is essential to producers.
+  However, non-Euclidean social media is hard to analyze, I propose a FC-GRU-CNN architecture for social media visualization.
+  As an empirical case, social relationship representations, network characteristics and media sentiments are used as key factors in box-office prediction model.
+  The model exploits long-term memory ability of GRU layer in long sequences of cast,
+  and the mapping ability of CNN layer in retrieving all pairs shortest path feature of actors social relationship,
+  the model accuracy is 14\% higher than Zhou \etal's model.
 \end{abstract}
@@
 and using long-term social networks data to study the relationships between all actors, directors and films remains a challenge.
-It is easy to see that the relationship between the box office and the director, actor, scriptwriter and producer is often non-linear, that is, it is difficult to use linear functions to build box office prediction models.
-By analyzing the social network characteristics of movie actors, sentiment of movies in Sina Weibo posts, all pairs shortest path, it is easy to get the priority of each characteristic by analysis of feature importance,
-existing prediction algorithm only makes use of the film meta-data, lacks the study on the social network characteristics of the actors, though traditional explanation of the film box office prediction algorithm is sufficing, however the prediction effect is not satisfactory.
-This paper presents a model, named FC-GRU-CNN, for movie box office prediction, combining characteristics of film meta-data, actors' social network measurement,
-all nodes pair shortest path, social network text sentiment and actors' art characteristics, proposed model is 14\% higher in accuracy than Zhou \etal~\cite{zhou2015c} model.
+It is easy to see that the relationship between the box-office and the director, actors, scriptwriters and producers is often non-linear, that is, it is difficult to use linear functions to build box-office prediction models.
+By analyzing the social network characteristics of movie actors, sentiments of movies in Sina Weibo posts, all pairs shortest path, it is easy to get the priority of each characteristic by analysis of feature importance,
+existing prediction algorithm only makes use of the film meta-data, lacks the study on the social network characteristics of the actors, though traditional explanation of the film box-office prediction algorithm is sufficing, however the prediction effect is not satisfactory.
+This paper presents a model, named FC-GRU-CNN, for movie box-office prediction, combining characteristics of film meta-data, actors' social network measurement,
+all nodes pair shortest path, social network text sentiments and actors' art characteristics, proposed model is 14\% higher in accuracy than Zhou \etal~\cite{zhou2015c} model.
 
@@
 
-The film industry is a multi-billion-dollar industry, with China's box office exceeding 60 billion yuan in 2018, reaching 60.9 billion yuan, and predicting the acceptance and adoption of new films among the public is a challenging topic.
+Film industry is a multi-billion-dollar industry, as China's box-office exceeding 6 billion dollars in 2018, reaching 6.09 billion dollars.
+Predicting the acceptance and adoption of new films among the audience is a challenging topic.
 
@@
 
-Zhu and Tang~\cite{zhu2019film} collected 13 features, such as search engine user data, social network fan number and movie meta-data of 20 films with more than 300 million box office in 2017,
+Zhu and Tang~\cite{zhu2019film} collected 13 features, such as search engine user data, social network fan number and movie meta-data of 20 films with more than 300 million box-office in 2017,
 and constructed a partial least-squared model with a margin of error of 87.7\% and an average absolute error of 26.6\%.
-Qiu and Tang~\cite{qiu2018microblog} used the 10 movie Sina Weibo texts and movie reviews of more than 1 billion at the box office in the Chinese film market in 2017 to calculate the web index and the film reviews to predict the box office.
+Qiu and Tang~\cite{qiu2018microblog} used the 10 movie Sina Weibo texts and movie reviews of more than 1 billion at the box-office in the Chinese film market in 2017 to calculate the web index and the film reviews to predict the box-office.
 
@@
 
-Some researchers use social network text sentiment to predict movie box office.
+Some researchers use social network text sentiments to predict movie box-office.
 Asur and Huberman~\cite{asur2010predicting} collected 2.89 million texts related to 1.2 million users on Twitter in connection with 24 films, and concluded that the correlation coefficient $R^2$ was between 0.92 and 0.97 using the daily postings in the first seven days of release.
-The film box office forecast logic regression model with the distribution of social network posts was 0.97.
+The film box-office forecast logic regression model with the distribution of social network posts was 0.97.
 Jain~\cite{jain2013prediction} collected 4800 Twitter texts of the movie name in the SNAP2009 (Stanford) dataset 2 weeks before release and 4 weeks after release.
-Trained an sentiment al four-category model based on an 8-grammar model with an accuracy rate of 64.4\%.
-Eight films released in 2012 as test sets, using the sentiment al positive-negative ratio to predict the accuracy of the box office profit model by 50\%.
-Chi \etal~\cite{chi2019does} collected reviews from 150 films released in 2017 and found that the number of reviews was positively related to the box office.
-online reviews were not correlated with box office. and the number of reviews was significantly positive lying to the first week of the film's box office, and the relevance gradually diminished.
-Josh \etal~\cite{joshi2010movie} collected the film review text of the film released by MetaCritic from 2005 to 2009, using film meta-data, n-gram model, part-of-speech ngram model and dependency characteristics, to predict the first week box office,
+Trained an sentiments al four-category model based on an 8-grammar model with an accuracy rate of 64.4\%.
+Eight films released in 2012 as test sets, using the sentiments al positive-negative ratio to predict the accuracy of the box-office profit model by 50\%.
+Chi \etal~\cite{chi2019does} collected reviews from 150 films released in 2017 and found that the number of reviews was positively related to the box-office.
+online reviews were not correlated with box-office. and the number of reviews was significantly positive lying to the first week of the film's box-office, and the relevance gradually diminished.
+Josh \etal~\cite{joshi2010movie} collected the film review text of the film released by MetaCritic from 2005 to 2009, using film meta-data, n-gram model, part-of-speech ngram model and dependency characteristics, to predict the first week box-office,
 first week screen number and weekly revenue per screen, the determine of coefficient of the Elastic Net linear model is 67.1\%.
@@
 
-Jiang and Wang~\cite{jiang2018predicting} collected 34 high-grossing films from 2015 to 2017, using 10 features, such as film meta-data, director awards, and actor awards, and used voting feature selection algorithms to select features, training SVR (supporting vector regression) box office and scoring prediction models.
-Quader \etal~\cite{quader2017machine} collected 755 film reviews from four film review sites from 2012 to 2015, including film ratings, MPAA categories, director's total box office, total box office, actor total box office, release time, budget, screen numbers, user reviews, reviews, and the sentiment al characteristics of review texts,
+Jiang and Wang~\cite{jiang2018predicting} collected 34 high-grossing films from 2015 to 2017, using 10 features, such as film meta-data, director awards, and actor awards, and used voting feature selection algorithms to select features, training SVR (supporting vector regression) box-office and scoring prediction models.
+Quader \etal~\cite{quader2017machine} collected 755 film reviews from four film review sites from 2012 to 2015, including film ratings, MPAA categories, director's total box-office, total box-office, actor total box-office, release time, budget, screen numbers, user reviews, reviews, and the sentiments al characteristics of review texts,
 training SVR, MLP model, with an accuracy of about 44.4\%.
@@
 
-Zhou \etal proposed a C-LSTM text classification model, using single-layer CNN for extracting the high-order dimensional representation of text, and then connected to LSTM layers for sentence representation, accuracy of the model is 87.8\%.
+Zhou\etal proposed a C-LSTM text classification model, using single-layer CNN for extracting the high-order dimensional representation of text, and then connected to LSTM layers for sentence representation, accuracy of the model is 87.8\%.
 
@@
 
-From the social network to predict the movie box office, feature selection includes the selection of user behavior characteristics, social network time characteristics, text sentiment al characteristics, classifiers more use of choice logic regression, support vector machine and neural network to predict the box office and comments.
+From the social network to predict the movie box-office, feature selection includes the selection of user behavior characteristics, social network time characteristics, text sentiments al characteristics, classifiers more use of choice logic regression, support vector machine and neural network to predict the box-office and comments.
 
@@
 
-The following linear analysis of social network measurement features and the regression coefficient of film box office, and from the practical significance of the interaction between the characteristics and the film box office.
-The positive characteristics associated with the box office in the linear regression algorithm are:
-\par$\bullet$ Betweenness: the higher the number of actors, the higher the box office.
-\par$\bullet$ Closeness: The higher the closeness of the actors, the higher the box office.
-\par$\bullet$ Followers: The more other actors you pay attention to, the higher the box office.
-\par$\bullet$ Number of posts: the more actors, the higher the box office.
-\par$\bullet$ Average post interval: the greater the average hair interval, the higher the box office.
-\par$\bullet$ Average characters of each posts: the longer the number of characters, the higher the box office, but the degree of relevance is not obvious.
-\par$\bullet$ Number of retweets: the more retweet posts, the higher the box office.
-\par$\bullet$ Box office history: the higher the box office receipts of actors, the higher the box office attendance of participating in the film.
+Correlation analysis of social network characteristics and the box-office is carried,
+and discussed the practical significance of the interaction between the characteristics and the box-office.
+In the linear regression analysis, the positive correlation characteristics associated with the box-office are:
+\begin{itemize}
+\item {\bf Betweenness}: the higher the number of actors, the higher the box-office gets.
+\item {\bf Closeness}: The higher the closeness of the actors, the higher the box-office gets.
+\item {\bf Followers}: The more other actors you pay attention to, the higher the box-office gets.
+\item {\bf Number of posts}: the more actors, the higher the box-office gets.
+\item {\bf Average post interval}: the greater the average hair interval, the higher the box-office gets.
+\item {\bf Average characters length of each posts}: the longer the number of characters, the higher the box-office, but the degree of relevance is not obvious.
+\item {\bf Number of retweets}: the more retweet posts, the higher the box-office gets.
+\item {\bf Box-office history}: the higher the box-office receipts of actors, the higher the box-office attendance of participating in the film gets.
+\end{itemize}
 
-The negative correlation characteristics are:
-\par$\bullet$ Number of fans: the more fans there are, the lower the box office is.
-\par$\bullet$ Number of movie-related Sina Weibo posts: the larger number the actors' mentioned the movie in Sina Weibo, the lower the box office is.
-\par$\bullet$ Co-occurrence: The more actors and other actors co-appears on Sina Weibo posts, the lower the box office is.
-\par Then, I calculated Pearson correlation of average box office per movie and actors social network measurement characteristics, the post and retweet correlation is $-0.108\%$, social media Activity correlation is $-3.203\%$, Co-occurrence correlation is $15.08\%$.
-First of all, the actor's average box office per movie is clearly positively related to the influence of the actors, that is, the higher number of co-occurrence in Sina Weibo, the higher average box office per movie.
-Secondly, the actors Sina Weibo activity and the average box office per movie showed a slight negative correlation, that is, the number of actors' followers, the number of tweets, the interval between the posts, the length of posts, the number of movie-related posts showed negative impact on average box office per movie.
-Finally, the number of actors retweets and tweets is not related to average box office per movie, thus they are independent.
-Then I use Sina Weibo text sentiment and actor social network measurement characteristics as features, then trained a decision tree to fit the movie box office, training set determination of coefficient is 0.9858, and the test set determination of coefficient is 0.9605.
+And associated with the box-office, the negative correlation characteristics are:
+\begin{itemize}
+\item {\bf Number of fans}: the more fans there are, the lower the box-office gets.
+\item {\bf Number of movie-related Sina Weibo posts}: the larger number the actors' mentioned the movie in Sina Weibo, the lower the box-office gets.
+\item {\bf Co-occurrence of posts}: The more multiple actors co-appears in Sina Weibo posts, the lower the box-office gets.
+\end{itemize}
+
+\par Then, I calculated Pearson correlation of average box-office per movie and actors social network characteristics, the post and retweet correlation is $-0.108\%$, social media Activity correlation is $-3.203\%$, Co-occurrence correlation is $15.08\%$.
+First of all, the actors' average box-office per movie is clearly positively related to the influence of the actors, that is, the higher number of co-occurrence in Sina Weibo, the higher average box-office per movie.
+Secondly, the actors Sina Weibo activity and the average box-office per movie showed a slight negative correlation, that is, the number of actors' followers, the number of tweets, the interval between the posts, the length of posts, the number of movie-related posts showed negative impact on average box-office per movie.
+Finally, the number of actors retweets and tweets is not related to average box-office per movie, thus they are independent.
+Then I use Sina Weibo text sentiments and actor social network measurement characteristics as features, then trained a decision tree to fit the movie box-office, training set determination of coefficient is 0.9858, and the test set determination of coefficient is 0.9605.
 Actors social network meta-data decision tree visualization is illustrated as Figure 2.
-\par Definition 1 (Gini Impurity)  A measure of how often randomly selected elements are incorrectly marked from a collection is a common CART (decision tree) algorithm evaluation indicator.
+
+\par \noindent Definition 1 (\textbf{Gini Impurity}) A measure of how often randomly selected elements are incorrectly marked from a collection is a common CART algorithm evaluation indicator.
 If it is randomly marked based on the distribution of the label in a subset.
@@
 When in all conditions a node belong to a single category, it reaches its minimum value of zero.
-In summary, the decision tree structure shows that the influence of the actors in the social network is the main factor affecting the box office results, followed by the movie-related Sina Weibo sentiment and the film meta-data is the secondary determinant,
+In summary, the decision tree structure shows that the influence of the actors in the social network is the main factor affecting the box-office results, followed by the movie-related Sina Weibo sentiments and the film meta-data is the secondary determinant,
 while the social network characteristics, movie-related Sina Weibo sentiment, film meta-data are the general determinants.
@@
 
-Definition 1 (Network Embedding)  A network $\Bbb G=(\Bbb V,\Bbb E)$, $\Bbb V$ represents a set of nodes consisting of $n$ nodes, and $\Bbb E$ represents an edge set of $m$ edges.
+\par \noindent Definition 2 (\textbf{Network Embedding})  A network $\Bbb G=(\Bbb V,\Bbb E)$, $\Bbb V$ represents a set of nodes consisting of $n$ nodes, and $\Bbb E$ represents an edge set of $m$ edges.
 For each edge $e\in \Bbb E$, the ordered pair is $e=(u,v)$, $u,v \in \Bbb V$ and the weight is $A_{ij}$.
+
 A network can be represented as an adjacent matrix, $A\in \Bbb R^{(n*n)}$, and the goal of network embedding is to learn an all pairs representation, $U\in \Bbb R^{(n*m)}$, $m < n$, where $m$ is an embedding dimension.\par
-Definition 2 (Shortest Path Network Embedding)  In a network represented as a $\Bbb G=(\Bbb V,\Bbb E)$, $\Bbb V$ represents a node set of $n$ nodes, and $\Bbb E$ represents an edge set of $m$ edges.
-For each edge $e\in \Bbb E$, the ordered pair is $e=(u,v)$, $u,v \in \Bbb V$ and the weight is $A_{ij}$.\par
-A network can be represented as an adjacent matrix, $A\in \Bbb R^{(n*n)}$, and the goal of the shortest path network embedding is to learn an all pairs, shortest path representation, $U\in \Bbb R^{(n*n)}$, where $n$ is an embedding dimension.
-For the task of box office forecasting, because of the significant impact the actors on the box office, in addition to the measurement of the film meta-data and the sentiment of the movie social media, the actors' contribution is required to compute by leveraging the movie participants actors list.
-A film, led by several actors, obtained the names of 7,369 actors who participated in films between 2011 and 2015 are collected as an actor's dictionary, and then used the shortest path features of the actors' social network.
+\par \noindent Definition 3 (\textbf{Shortest Path Network Embedding})  In a network represented as a $\Bbb G=(\Bbb V,\Bbb E)$, $\Bbb V$ represents a node set of $n$ nodes, and $\Bbb E$ represents an edge set of $m$ edges.
+For each edge $e\in \Bbb E$, the ordered pair is $e=(u,v)$, $u,v \in \Bbb V$ and the weight is $A_{ij}$.
+
+\par A network can be represented as an adjacent matrix, $A\in \Bbb R^{(n*n)}$, and the goal of the shortest path network embedding is to learn an all pairs, shortest path representation, $U\in \Bbb R^{(n*n)}$, where $n$ is an embedding dimension.
+For the task of box-office forecasting, because of the significant impact the actors on the box-office, in addition to the measurement of the film meta-data and the sentiments of the movie social media, the actors' contribution is required to compute by leveraging the movie participants actors list.
+A film, led by several actors, obtained the names of 7,369 actors who participated in films between 2011 and 2015 are collected as an actors' dictionary, and then used the shortest path features of the actors' social network.
 Combining social network measurement features, the shortest path network embedding, and the art features to construct the actor representation vector.
 For actors who have no accounts on social networks, marked as unknown, and initialized with zero vectors.
-Actor representation vectors include social network measurement features of 10 dimensions, shortest path features of 8380 dimensions, art features of 1 dimension.
-In total, 10-dimensional measurement features include fans number, betweenness, closeness, followers, posts number, average posts interval, average word count per post, retweet number, movie-related post number, co-occurrence number, shortest path with 8380 dimensions.
+Actor representation vectors include network characteristics of 10 dimensions, shortest path features of 8380 dimensions, art features of 1 dimension.
+In total, 10-dimension features include fans number, betweenness, closeness, followers, posts number, average posts interval, average word count per post, retweet number, movie-related post number, co-occurrence number, shortest path with 8380 dimensions.
 
@@
 
-Using the features extracted, the characteristics of participating in the calculation are film meta-data and movie sentiment: the year of release, the number of positive sentiment, the number of negative sentiment, the total number of Sina Weibo, the positive and negative ratio of sentiment, and the training of machine learning classifiers.
+Using the features extracted, the characteristics of participating in the calculation are film meta-data and movie sentiment:
+the year of release, the number of positive sentiment, the number of negative sentiment, the total number of Sina Weibo posts,
+the positive and negative ratio of sentiment, and the training of machine learning classifiers.
 
-Machine learning methods such as Linear Regression, SVR, MLP, Logistic Regression, and Naive Bayes cannot converge on the data set, possibly because the sentiment on actors' social networks does not represent the commercial benefits of the film.
-Actors, as creators of films, have a role to play in the box office, but lack other important features that also have an impact on the box office, so machine learning fitting process can't finish in given time.
-Using the CART decision tree regression algorithm to make box office prediction for the test set film, 
-the experimental results show that the prediction model has a determination coefficient of 96.05\% on the test set and 98.58\% on the training set, which is 2.87\% higher than the current best Sentiment-Network-Logistic model,
-and the average absolute deviation of the model is 0.1285 million, about 28.56\% of the average box office.
-The explanatories of the decision tree prediction model is more intuitive and more interpretable than linear regression, logical regression, deep neural network and other models, according to the prediction model structure schematic of the movie box office,
-the characteristics can be sorted according to the importance, so the social network structure characteristics are the most important, the social network text sentiment al characteristics, the film meta-data are important, and the social network characteristics are generally important.
-With Qiu and Tang's logistic regression model on sentiment and twitter index algorithm's 95.71\% in determination of coefficient, the proposed method in this paper has a 2.87\% improvement, 98.58\%.
+Machine learning methods such as Linear Regression, SVR, MLP, Logistic Regression, and Naive Bayes cannot converge on the data set,
+possibly because the sentiments on actors' social networks does not represent the commercial benefits of the film.
+Actors, as creators of films, have a role to play in the box-office, but lack of other important features that also have an significant impact on the box-office,
+so machine learning fitting process can't finish in given time.
+Using the CART decision tree regression algorithm to make box-office prediction for the test set film, 
+the experimental results show that the prediction model has a determination coefficient of 96.05\% on the test set and 98.58\% on the training set, which is 2.87\% higher than the Qiu and Tang~\cite{qiu2018microblog} model,
+and the average absolute deviation of the model is 0.1285 million, about 28.56\% of the average box-office.
+The explanatory of the decision tree prediction model is more intuitive and more interpretable than linear regression, logical regression, deep neural network and other models,
+according to the prediction model structure schematic of the movie box-office,
+the characteristics can be sorted according to the importance, the social network structure characteristics are the most important,
+the social network text sentimental characteristics, the film meta-data are important, and the social network characteristics are generally important.
+Compared to Qiu and Tang~\cite{qiu2018microblog}'s logistic regression model on sentiments and twitter index algorithm's 95.71\% determination of coefficient,
+the proposed CART model in this paper is 98.58\% which has a 2.87\% improvement.
 
-\section{FC-GRU-CNN Model}
+\section{FC-GRU-CNN Box-Office Prediction Model}
 
@@
 \end{center}
-   \caption{FC-GRU-CNN (box office net) forecasting model structure.}
+   \caption{FC-GRU-CNN (box-office net) forecasting model structure.}
 \label{fig:short}
@@
 
-Look at the box office distribution of 1,296 films released between 2011 and 2015, as shown in Figure 1b.
-Consider box office forecasts as a binary classification task.
-In order to make the data evenly distributed, the film data was pre-processed by using the median box office of 263.5(10K) as the dividing line.
-So for the movies with box office less than 2.635 million are classified as A-class, more than 2.635 million movies are classified as B-class.
-In the data set division, the data was randomly selected using the 80-20 segmentation ratio, and the training set of 1036 films and the test set of 260 movies were obtained.
-Using the actors' social network representation, the actor is quantified, that is, the fusion of social network measurement features, the shortest path characteristics and the actor's art characteristics, the actor feature matrix,
-for actors without social network measurement data, that is, the unknown characteristics, zero-value initialization. The model structure is shown in Figure 3:
-The whole model is divided into three parts:
-\par$\bullet$ The first part is FC full connection layer, its input feature is the film meta-data and movie-related Sina Weibo sentiment features, in total of 5 dimensions.
-\par$\bullet$ The second part is the GRU layer, the input feature is the actor social network measurement characteristics and art characteristics, the actor table is a long list,
+Look at the box-office distribution of 1,296 films released between 2011 and 2015,
+Consider box-office forecasts as a binary classification task.
+In order to make the data evenly distributed, the film data was pre-processed by using the median box-office of 2.635 million as the dividing line.
+So for the movies with box-office less than 2.635 million are classified as A-class, movies with box-office more than 2.635 million are classified as B-class.
+In the dataset division, the data was randomly selected using the $80-20$ segmentation ratio, and the training set of 1036 films and the test set of 260 movies were collected.
+Using the actors' social network representation, the actor is quantified, that is, 
+the fusion of social network features, the shortest path characteristics and the actors' art characteristics.
+For actors without social network data, use zero-value initialization in the actor feature matrix for the unknown characteristics.
+As shown in Figure 1, the model are divided into three parts:
+
+\begin{itemize}
+\item The first part is Fully Connected layer, its input feature is the film meta-data and movie-related Sina Weibo sentiments, in total of 5 dimensions.
+\item The second part is the GRU layer, the input feature is the actor social network measurement characteristics and art characteristics, the film cast is a long list,
 the longest 225 actors, for less than 225 actors using the front-end padding, the GRU layer is to solve the long-term memory loss of the structure.
-\par$\bullet$ The last part is the 5-layer CNN structure, input for the actors' social network shortest path feature, similarly, the actor table is a long list,
-input less than 225 dimensions is fulfilled by padding, CNN has a good ability to capture multi-dimensional features, and use of Max-pooling layer to solve the problem of multi-dimensional feature extraction.
-Finally, the three parts are merged into one layer and then connect to a Softmax layer, and the L2 regularization method is adopted to avoid overfitting.
-In summary, I choose randomly 10 movies of in test set, as shown in Table 3.
-The accuracy of the binary classification model in training set reached 99.61\%, the accuracy in the test set is 75\%, compared with other prediction algorithms, see Table 4.
-From the practical point of view, the model of FC-GRU-CNN proposed in this paper converges on the training set and achieves better prediction results in the test set, so it can provide decision-making advice on the task of selecting suitable actors for the film, and in the task of film box office prediction, 75% accuracy can be used for box office prediction tasks.
+\item The last part is the 5 CNN layers, input for the actors' social network shortest path feature, similarly, the film cast is a long list,
+input less than 225 dimensions is fulfilled by padding, CNN has a good ability to capture multi-dimensional features, and use of Max-pooling layer to solve the problem of multi-dimension feature extraction.
+\end{itemize}
+Finally, the three parts are merged into one layer and then connects to a Softmax layer, and the L2 regularization method is adopted to avoid overfitting.
+
+In summary, randomly choose 10 movies as test set, as shown in Table 1.
+The accuracy of the binary classification model in training set reached 99.61\%, the accuracy in the test set is 75\%.
+Compared to Zhou \etal model, see Table 2, the proposed FC-GRU-CNN model converges in the training set and achieves better prediction results in the test set.
+Therefore it can provide decision-making advice in the task of selecting suitable actors for to-be-casted film,
+and in box-office prediction task, the model can provide reasonable prediction in the market.
 
@@
 \end{center}
-\caption{box office binary classification predictions in 10 movie testset.}
+\caption{box-office binary classification predictions in 10 movie testset.}
 \end{table}
@@
 
-According to the box office prediction model, using actors' Sina Weibo sentiments, social relationship and network characteristics, this paper discussed relationship between the movie meta-data,
-Sina Weibo text sentiments, the actors' network characteristics, shortest path feature and actors' art contribution.
-Then I proposed a FC-GRU-CNN box office prediction model, compared to Zhou \etal model, accuracy improves 14\%, and tested in a dataset of 1,296 movies released in China mainland collected from 2011 to 2015, proposed model has an accuracy of 75\%.
+According to the box-office prediction model, joint actors' Sina Weibo sentiments, social relationship and network characteristics,
+this paper discussed relationship between the movie meta-data, Sina Weibo text sentiments, social relationship representations, network characteristics and actors' art contribution.
+Then I proposed a FC-GRU-CNN box-office prediction model, compared to Zhou \etal model, accuracy improves 14\%,
+and tested in a dataset of 1,296 movies released in China mainland collected from 2011 to 2015, proposed model has an accuracy of 75\%.
 

### 2020-10-08 A-BasicCommom/CVPR2021/cvpr.tex
1.CVPR v0.3.0, thanks help from grammarly.

@@
 \section{Dataset And Hardware}
-From January 1, 2011 to March 31, 2015, I collected the film actors' social network following relationship, profile information, and text message on Sina Weibo.
+From January 1, 2011 to March 31, 2015, I collected the film actors' social network following relationship, profile information, and text message on Sina Weibo which is one of the popular social media in China.
 In all, collected 8508 actors, 577775 edges and 12526114 Sina Weibo posts.

### 2020-10-08 A-BasicCommom/CVPR2021/cvpr_vision.tex
1.CVPR v0.3.0, thanks help from grammarly.

@@
 \begin{abstract}
-  In film industry, visualizing stars social media for analyzing audience intention towards movies is essential to producers.
-  However, non-Euclidean social media is hard to analyze, I propose a FC-GRU-CNN architecture for social media visualization.
-  As an empirical case, social relationship representations, network characteristics and media sentiments are used as key factors in box-office prediction model.
-  The model exploits long-term memory ability of GRU layer in long sequences of cast,
-  and the mapping ability of CNN layer in retrieving all pairs shortest path feature of actors social relationship,
-  the model accuracy is 14\% higher than Zhou \etal's model.
+
+  In the film industry, visualizing actor stars' social media for analyzing audience intention towards movies is essential to movie producers.
+  However, non-Euclidean social media is hard to analyze, I propose an FC-GRU-CNN architecture, also named as \underline{N}on-\underline{E}uclidean \underline{N}et, for social media visualization.
+  In social media analysis, social relationship representations, network characteristics and media sentiments are key factors.
+  FC-GRU-CNN architecture exploits the long-term memory ability of GRU layer in long sequences of film cast,
+  mapping ability of CNN layer in retrieving all-pairs shortest path feature of actors' social relationship,
+  and non-linear capability of deep FC layer for movie text sentiments and other characteristics.
+  The proposed model accuracy is 14\% higher than Zhou \etal's model.
+
 \end{abstract}
@@
   With the development of social networks, actors' influence on social media is increasing, and the influence of actors' consumption is spread through social networks,
-and using long-term social networks data to study the relationships between all actors, directors and films remains a challenge.
-It is easy to see that the relationship between the box-office and the director, actors, scriptwriters and producers is often non-linear, that is, it is difficult to use linear functions to build box-office prediction models.
-By analyzing the social network characteristics of movie actors, sentiments of movies in Sina Weibo posts, all pairs shortest path, it is easy to get the priority of each characteristic by analysis of feature importance,
-existing prediction algorithm only makes use of the film meta-data, lacks the study on the social network characteristics of the actors, though traditional explanation of the film box-office prediction algorithm is sufficing, however the prediction effect is not satisfactory.
+  and using long-term social networks data to study the relationships between all actors, directors, and films remains a challenge.
+  It is easy to see that the relationship between box-office and the director, actors, scriptwriters, and producers is often non-linear, that is,
+  it is difficult to use linear functions to build box-office prediction models.
+  By analyzing the social network characteristics of movie actors, sentiments of movies in Sina Weibo posts, all-pairs shortest path,
+  it is easy to get the priority of each characteristic by analysis of feature importance,
+  existing prediction algorithm only makes use of the film meta-data, lacks the study on the social network characteristics of the actors,
+  though the traditional explanation of the film box-office prediction algorithm is sufficing, however, the prediction effect is not satisfactory.
   This paper presents a model, named FC-GRU-CNN, for movie box-office prediction, combining characteristics of film meta-data, actors' social network measurement,
-all nodes pair shortest path, social network text sentiments and actors' art characteristics, proposed model is 14\% higher in accuracy than Zhou \etal~\cite{zhou2015c} model.
+  all nodes pair shortest path, social network text sentiments, and actors' art contribution characteristics,
+  as a result, it is 14\% higher in accuracy than Zhou \etal ~\cite{zhou2015c}'s model.
 
@@
 
-Film industry is a multi-billion-dollar industry, as China's box-office exceeding 6 billion dollars in 2018, reaching 6.09 billion dollars.
+  The film industry is a multi-billion-dollar business, as China's box-office exceeding 6 billion dollars in 2018, reaching 6.09 billion dollars.
   Predicting the acceptance and adoption of new films among the audience is a challenging topic.
+  Fern{\'a}ndez \etal ~\cite{fernandez2014we} showed that the best classifiers are the random forest,
+  followed by SVM, neural networks, and boosting ensembles among 17 families.
 
-\subsection{Linear Regression Model}
+%\subsection{Random Forest}
 
-Zhu and Tang~\cite{zhu2019film} collected 13 features, such as search engine user data, social network fan number and movie meta-data of 20 films with more than 300 million box-office in 2017,
-and constructed a partial least-squared model with a margin of error of 87.7\% and an average absolute error of 26.6\%.
-Qiu and Tang~\cite{qiu2018microblog} used the 10 movie Sina Weibo texts and movie reviews of more than 1 billion at the box-office in the Chinese film market in 2017 to calculate the web index and the film reviews to predict the box-office.
+\subsection{Support Vector Machines}
 
-\subsection{Logistic Regression Model}
+  Jiang and Wang~\cite{jiang2018predicting} collected 34 high-grossing films from 2015 to 2017, using 10 features, such as film meta-data, director awards, and actor awards, then I used voting feature selection algorithms to select important features,
+  training SVM models for film box-office and user-comment-score prediction.
+  Quader \etal~\cite{quader2017machine} collected 755 film reviews in four film review sites from 2012 to 2015, collected characteristics including film ratings, MPAA categories,
+  director total box-office, actor total box-office, release time, budget, screen numbers, user reviews, and review text sentiments,
+  trained SVM model has a prediction accuracy of 44.4\%.
 
-Some researchers use social network text sentiments to predict movie box-office.
-Asur and Huberman~\cite{asur2010predicting} collected 2.89 million texts related to 1.2 million users on Twitter in connection with 24 films, and concluded that the correlation coefficient $R^2$ was between 0.92 and 0.97 using the daily postings in the first seven days of release.
-The film box-office forecast logic regression model with the distribution of social network posts was 0.97.
-Jain~\cite{jain2013prediction} collected 4800 Twitter texts of the movie name in the SNAP2009 (Stanford) dataset 2 weeks before release and 4 weeks after release.
-Trained an sentiments al four-category model based on an 8-grammar model with an accuracy rate of 64.4\%.
-Eight films released in 2012 as test sets, using the sentiments al positive-negative ratio to predict the accuracy of the box-office profit model by 50\%.
-Chi \etal~\cite{chi2019does} collected reviews from 150 films released in 2017 and found that the number of reviews was positively related to the box-office.
-online reviews were not correlated with box-office. and the number of reviews was significantly positive lying to the first week of the film's box-office, and the relevance gradually diminished.
-Josh \etal~\cite{joshi2010movie} collected the film review text of the film released by MetaCritic from 2005 to 2009, using film meta-data, n-gram model, part-of-speech ngram model and dependency characteristics, to predict the first week box-office,
-first week screen number and weekly revenue per screen, the determine of coefficient of the Elastic Net linear model is 67.1\%.
+\subsection{Neural Network Model}
 
-\subsection{Support Vector Regression and Multi-Layer Neural Network Model}
+  Zhou \etal~\cite{zhou2015c} proposed a C-LSTM classification model, using single-layer CNN for extracting the high-order dimensional representation of text,
+  and connecting to LSTM layers for sentence representation, the trained neural network model has an accuracy of 87.8\%.
 
-Jiang and Wang~\cite{jiang2018predicting} collected 34 high-grossing films from 2015 to 2017, using 10 features, such as film meta-data, director awards, and actor awards, and used voting feature selection algorithms to select features, training SVR (supporting vector regression) box-office and scoring prediction models.
-Quader \etal~\cite{quader2017machine} collected 755 film reviews from four film review sites from 2012 to 2015, including film ratings, MPAA categories, director's total box-office, total box-office, actor total box-office, release time, budget, screen numbers, user reviews, reviews, and the sentiments al characteristics of review texts,
-training SVR, MLP model, with an accuracy of about 44.4\%.
+%\subsection{Boosting, Bagging and Stacking Ensembles}
 
-\subsection{Text Classification using Deep Learning}
+\subsection{Partial Least Squares, Principal Component Regression, and Generalized Linear Model}
 
-Zhou\etal proposed a C-LSTM text classification model, using single-layer CNN for extracting the high-order dimensional representation of text, and then connected to LSTM layers for sentence representation, accuracy of the model is 87.8\%.
+  Zhu and Tang~\cite{zhu2019film} collected 20 films with more than 300 million box-offices in 2017, using 13 features, such as search engine user search times, number of social network fans, and other movie meta-data,
+  and constructed a partial-least-square model with a margin of error of 87.7\% and an average absolute error of 26.6\%.
+  Qiu and Tang~\cite{qiu2018microblog} collected 10 movies with more than 1 billion box-offices from the Chinese film market in 2017, used Sina Weibo texts, movie web index, and the film reviews to predict box-office.
+
+\subsection{Logistic and Multinomial Regression}
+
+  Asur and Huberman~\cite{asur2010predicting} collected 2.89 million texts written by 1.2 million users on Twitter related to 24 films,
+  concluded that using the daily posts in the first seven days of release, the correlation coefficient ranges from 92\% to 97\%.
+  The box-office logistic regression model with the distribution of social network posts was 97\%.
+  Jain~\cite{jain2013prediction} collected 4800 Twitter texts relating to movie names which written between 2 weeks before release and 4 weeks after release,
+  using the sentiments positive-negative ratio to predict box-office profit, the model has an accuracy of 50\% on eight films released in 2012.
+  Chi \etal~\cite{chi2019does} collected reviews from 150 films released in 2017, found that the number of reviews was positively related to box-office
+  and the number of reviews was significantly positive for the first-week of the film box-office.
+  Josh \etal~\cite{joshi2010movie} collected film review text in MetaCritic releasing from 2005 to 2009, using film meta-data, n-gram model,
+  part-of-speech n-gram model and dependency characteristics, and the Elastic-Net model has determination of coefficient of 67.1\% in predicting the first-week box-office.
 
@@
 
-From the social network to predict the movie box-office, feature selection includes the selection of user behavior characteristics, social network time characteristics, text sentiments al characteristics, classifiers more use of choice logic regression, support vector machine and neural network to predict the box-office and comments.
+  Using social networks to predict movie box-office, feature selection includes the selection of user behavior characteristics,
+  social network release date characteristics, text sentiments characteristics,
+  researchers prefer to use logistic regression, support vector machine, and neural network in predicting movie box-office.
 
@@
 
-Correlation analysis of social network characteristics and the box-office is carried,
-and discussed the practical significance of the interaction between the characteristics and the box-office.
-In the linear regression analysis, the positive correlation characteristics associated with the box-office are:
+  Correlation analysis of social network characteristics and box-office is performed,
+  and discussed the significance of the correlation between social network characteristics and box-office.
+  In linear regression analysis, the positive correlation characteristics associated with box-office are:
+
 \begin{itemize}
-\item {\bf Betweenness}: the higher the number of actors, the higher the box-office gets.
-\item {\bf Closeness}: The higher the closeness of the actors, the higher the box-office gets.
-\item {\bf Followers}: The more other actors you pay attention to, the higher the box-office gets.
-\item {\bf Number of posts}: the more actors, the higher the box-office gets.
-\item {\bf Average post interval}: the greater the average hair interval, the higher the box-office gets.
-\item {\bf Average characters length of each posts}: the longer the number of characters, the higher the box-office, but the degree of relevance is not obvious.
-\item {\bf Number of retweets}: the more retweet posts, the higher the box-office gets.
-\item {\bf Box-office history}: the higher the box-office receipts of actors, the higher the box-office attendance of participating in the film gets.
+\item {\bf Betweenness}: the higher the number of actors, the higher box-office gets.
+\item {\bf Closeness}: The higher the closeness of the actors, the higher box-office gets.
+\item {\bf Followers}: The more other actors you pay attention to, the higher box-office gets.
+\item {\bf Number of posts}: the more actors, the higher box-office gets.
+\item {\bf Average post interval}: the greater the average hair interval, the higher box-office gets.
+\item {\bf Average characters length of each post}: the longer the number of characters, the higher box-office, but the degree of relevance is not obvious.
+\item {\bf Number of retweets}: the more retweet posts, the higher box-office gets.
+\item {\bf Box-office history}: the higher receipts of actors box-office, the higher box-office attendance of participating in the film gets.
 \end{itemize}
 
-And associated with the box-office, the negative correlation characteristics are:
+While the negative correlation characteristics associated with box-office are:
 \begin{itemize}
-\item {\bf Number of fans}: the more fans there are, the lower the box-office gets.
-\item {\bf Number of movie-related Sina Weibo posts}: the larger number the actors' mentioned the movie in Sina Weibo, the lower the box-office gets.
-\item {\bf Co-occurrence of posts}: The more multiple actors co-appears in Sina Weibo posts, the lower the box-office gets.
+\item {\bf Number of fans}: the more fans there are, the lower box-office gets.
+\item {\bf Number of movie-related Sina Weibo posts}: the larger number of the actors' mentioned the movie in Sina Weibo, the lower box-office gets.
+\item {\bf Co-occurrence of posts}: The more multiple actors co-appears in Sina Weibo posts, the lower box-office gets.
 \end{itemize}
 
-\par Then, I calculated Pearson correlation of average box-office per movie and actors social network characteristics, the post and retweet correlation is $-0.108\%$, social media Activity correlation is $-3.203\%$, Co-occurrence correlation is $15.08\%$.
-First of all, the actors' average box-office per movie is clearly positively related to the influence of the actors, that is, the higher number of co-occurrence in Sina Weibo, the higher average box-office per movie.
-Secondly, the actors Sina Weibo activity and the average box-office per movie showed a slight negative correlation, that is, the number of actors' followers, the number of tweets, the interval between the posts, the length of posts, the number of movie-related posts showed negative impact on average box-office per movie.
-Finally, the number of actors retweets and tweets is not related to average box-office per movie, thus they are independent.
-Then I use Sina Weibo text sentiments and actor social network measurement characteristics as features, then trained a decision tree to fit the movie box-office, training set determination of coefficient is 0.9858, and the test set determination of coefficient is 0.9605.
-Actors social network meta-data decision tree visualization is illustrated as Figure 2.
+\par Then, I calculated the Pearson correlation between average box-office per movie and actors' social network characteristics, the post and retweet correlation is $-0.108\%$, social media activity correlation is $-3.203\%$, co-occurrence correlation is $15.08\%$.
+First of all, the actors' average box-office per movie is positively related to the influence of the actors, that is, the higher number of co-occurrence in Sina Weibo, the higher average box-office per movie.
+Secondly, the actors Sina Weibo activity and the average box-office per movie showed a slight negative correlation, that is,
+the number of actors' followers, the number of tweets, the interval between the posts, the length of posts, the number of movie-related posts showed a negative impact on average box-office per movie.
+Finally, the number of actors retweets and tweets is not related to the average box-office per movie, thus they are independent.
+Then using Sina Weibo text sentiments and actor social network characteristics trained a decision tree model to predict movie box-office, determination of the coefficient in training-set is 98.58\%, and determination of the coefficient in test-set is 96.05\%.
 
-\par \noindent Definition 1 (\textbf{Gini Impurity}) A measure of how often randomly selected elements are incorrectly marked from a collection is a common CART algorithm evaluation indicator.
-If it is randomly marked based on the distribution of the label in a subset.
-Gini impurities can be divided by multiplying the probability of the item by the probability that it is misplaced.
-When in all conditions a node belong to a single category, it reaches its minimum value of zero.
-In summary, the decision tree structure shows that the influence of the actors in the social network is the main factor affecting the box-office results, followed by the movie-related Sina Weibo sentiments and the film meta-data is the secondary determinant,
-while the social network characteristics, movie-related Sina Weibo sentiment, film meta-data are the general determinants.
+\par In summary, the decision tree structure shows that the influence of the actors in social networks is the main factor affecting box-office, followed by the movie-relating Sina Weibo sentiments and the film meta-data is the secondary determinant,
+while the social network characteristics, movie-related Sina Weibo sentiment and other film meta-data are the least significant factors.
 
@@
 
-\par \noindent Definition 2 (\textbf{Network Embedding})  A network $\Bbb G=(\Bbb V,\Bbb E)$, $\Bbb V$ represents a set of nodes consisting of $n$ nodes, and $\Bbb E$ represents an edge set of $m$ edges.
+\par \noindent Definition 1 (\textbf{Network Embedding})  A network $\Bbb G=(\Bbb V,\Bbb E)$, $\Bbb V$ represents a set of nodes consisting of $n$ nodes, and $\Bbb E$ represents an edge set of $m$ edges.
 For each edge $e\in \Bbb E$, the ordered pair is $e=(u,v)$, $u,v \in \Bbb V$ and the weight is $A_{ij}$.
 
-A network can be represented as an adjacent matrix, $A\in \Bbb R^{(n*n)}$, and the goal of network embedding is to learn an all pairs representation, $U\in \Bbb R^{(n*m)}$, $m < n$, where $m$ is an embedding dimension.\par
-\par \noindent Definition 3 (\textbf{Shortest Path Network Embedding})  In a network represented as a $\Bbb G=(\Bbb V,\Bbb E)$, $\Bbb V$ represents a node set of $n$ nodes, and $\Bbb E$ represents an edge set of $m$ edges.
+A network can be represented as an adjacent matrix, $A\in \Bbb R^{(n*n)}$, and the goal of network embedding is to learn an all-pairs representation, $U\in \Bbb R^{(n*m)}$, $m < n$, where $m$ is an embedding dimension.\par
+\par \noindent Definition 2 (\textbf{Shortest Path Network Embedding})  In a network represented as a $\Bbb G=(\Bbb V,\Bbb E)$, $\Bbb V$ represents a node set of $n$ nodes, and $\Bbb E$ represents an edge set of $m$ edges.
 For each edge $e\in \Bbb E$, the ordered pair is $e=(u,v)$, $u,v \in \Bbb V$ and the weight is $A_{ij}$.
 
-\par A network can be represented as an adjacent matrix, $A\in \Bbb R^{(n*n)}$, and the goal of the shortest path network embedding is to learn an all pairs, shortest path representation, $U\in \Bbb R^{(n*n)}$, where $n$ is an embedding dimension.
-For the task of box-office forecasting, because of the significant impact the actors on the box-office, in addition to the measurement of the film meta-data and the sentiments of the movie social media, the actors' contribution is required to compute by leveraging the movie participants actors list.
-A film, led by several actors, obtained the names of 7,369 actors who participated in films between 2011 and 2015 are collected as an actors' dictionary, and then used the shortest path features of the actors' social network.
+\par A network can be represented as an adjacent matrix, $A\in \Bbb R^{(n*n)}$, and the goal of the shortest path network embedding is to learn all-pairs shortest path representation, $U\in \Bbb R^{(n*n)}$, where $n$ is an embedding dimension.
+For the task in box-office forecast, because of the significant impact the actors on the box-office, in addition to the measurement of the film meta-data and the sentiments of the movie social media,
+the actors' contribution is required to compute by leveraging actors in the movie cast.
+A film, led by several leading actors, obtained the names of $7369$ actors who participated in films between 2011 and 2015 are collected as an actors' dictionary, and then used the shortest path features of the actors' social network.
 Combining social network measurement features, the shortest path network embedding, and the art features to construct the actor representation vector.
@@
 Actor representation vectors include network characteristics of 10 dimensions, shortest path features of 8380 dimensions, art features of 1 dimension.
-In total, 10-dimension features include fans number, betweenness, closeness, followers, posts number, average posts interval, average word count per post, retweet number, movie-related post number, co-occurrence number, shortest path with 8380 dimensions.
+In total, 10-dimension features include fans number, betweenness, closeness, followers, posts number, average posts interval, average word count per post, retweet number, movie-related post number, co-occurrence number, the shortest path with 8380 dimensions.
 
@@
 
-Machine learning methods such as Linear Regression, SVR, MLP, Logistic Regression, and Naive Bayes cannot converge on the data set,
-possibly because the sentiments on actors' social networks does not represent the commercial benefits of the film.
-Actors, as creators of films, have a role to play in the box-office, but lack of other important features that also have an significant impact on the box-office,
-so machine learning fitting process can't finish in given time.
+Machine learning methods such as Linear Regression, SVN, MLP, Logistic Regression, and Na{\'i}ve Bayes cannot converge on the data set,
+possibly because the sentiments on actors' social networks do not represent the commercial benefits of the film.
+Actors, as creators of films, have a role to play in the box-office, but lack of other important features that also have a significant impact on the box-office,
+so the machine learning fitting process can't converge in a given time.
 Using the CART decision tree regression algorithm to make box-office prediction for the test set film,
 the experimental results show that the prediction model has a determination coefficient of 96.05\% on the test set and 98.58\% on the training set, which is 2.87\% higher than the Qiu and Tang~\cite{qiu2018microblog} model,
-and the average absolute deviation of the model is 0.1285 million, about 28.56\% of the average box-office.
+and the average absolute deviation of the model is $0.1285$ million, about 28.56\% of the average box-office.
 The explanatory of the decision tree prediction model is more intuitive and more interpretable than linear regression, logical regression, deep neural network and other models,
-according to the prediction model structure schematic of the movie box-office,
+according to the prediction model structure schematic of movie box-office,
 the characteristics can be sorted according to the importance, the social network structure characteristics are the most important,
-the social network text sentimental characteristics, the film meta-data are important, and the social network characteristics are generally important.
+the social network text sentiments characteristics, the film meta-data are important, and the social network characteristics are generally important.
 Compared to Qiu and Tang~\cite{qiu2018microblog}'s logistic regression model on sentiments and twitter index algorithm's 95.71\% determination of coefficient,
-the proposed CART model in this paper is 98.58\% which has a 2.87\% improvement.
+The CART model in this paper has a determination of coefficient of 98.58\% which has a 2.87\% improvement.
 
@@
 \end{center}
-   \caption{FC-GRU-CNN (box-office net) forecasting model structure.}
+   \caption{FC-GRU-CNN (Non-Euclidean Net) forecasting model structure.}
 \label{fig:short}
@@
 
-Look at the box-office distribution of 1,296 films released between 2011 and 2015,
+Look at box-office distribution of $1296$ films released between 2011 and 2015,
 Consider box-office forecasts as a binary classification task.
-In order to make the data evenly distributed, the film data was pre-processed by using the median box-office of 2.635 million as the dividing line.
-So for the movies with box-office less than 2.635 million are classified as A-class, movies with box-office more than 2.635 million are classified as B-class.
-In the dataset division, the data was randomly selected using the $80-20$ segmentation ratio, and the training set of 1036 films and the test set of 260 movies were collected.
+To make the data evenly distributed, the film data were pre-processed by using the median box-office of $2.635$ million as the dividing line.
+So for the movies with box-office less than $2.635$ million are classified as A-class, movies with box-office more than $2.635$ million are classified as B-class.
+In the dataset division, the data was randomly selected using the $80-20$ segmentation ratio, and the training set of $1036$ films and the test set of $260$ movies were collected.
 Using the actors' social network representation, the actor is quantified, that is,
-the fusion of social network features, the shortest path characteristics and the actors' art characteristics.
+the fusion of social network features, the shortest path characteristics, and the actors' art characteristics.
 For actors without social network data, use zero-value initialization in the actor feature matrix for the unknown characteristics.
-As shown in Figure 1, the model are divided into three parts:
+As shown in Figure 1, the model is divided into three parts:
 
 \begin{itemize}
-\item The first part is Fully Connected layer, its input feature is the film meta-data and movie-related Sina Weibo sentiments, in total of 5 dimensions.
+\item The first part is the Fully Connected layer, its input feature is the film meta-data and movie-related Sina Weibo sentiments, in a total of 5 dimensions.
 \item The second part is the GRU layer, the input feature is the actor social network measurement characteristics and art characteristics, the film cast is a long list,
@@
 \end{itemize}
-Finally, the three parts are merged into one layer and then connects to a Softmax layer, and the L2 regularization method is adopted to avoid overfitting.
+Finally, the three parts are merged into one layer and then connect to a Softmax layer, and the $L_2$ regularization method is adopted to avoid overfitting.
 
-In summary, randomly choose 10 movies as test set, as shown in Table 1.
-The accuracy of the binary classification model in training set reached 99.61\%, the accuracy in the test set is 75\%.
+In summary, randomly choose 10 movies as a test set, as shown in Table 1.
+The accuracy of the binary classification model in the training set reached 99.61\%, the accuracy in the test set is 75\%.
 Compared to Zhou \etal model, see Table 2, the proposed FC-GRU-CNN model converges in the training set and achieves better prediction results in the test set.
 Therefore it can provide decision-making advice in the task of selecting suitable actors for to-be-casted film,
-and in box-office prediction task, the model can provide reasonable prediction in the market.
+and in the box-office prediction task, the model can provide reasonable prediction in the market.
 
@@
 \end{center}
-\caption{box-office binary classification predictions in 10 movie testset.}
+\caption{box-office model predictions in movie testset(10 samples).}
 \end{table}
@@
 
-According to the box-office prediction model, joint actors' Sina Weibo sentiments, social relationship and network characteristics,
-this paper discussed relationship between the movie meta-data, Sina Weibo text sentiments, social relationship representations, network characteristics and actors' art contribution.
-Then I proposed a FC-GRU-CNN box-office prediction model, compared to Zhou \etal model, accuracy improves 14\%,
-and tested in a dataset of 1,296 movies released in China mainland collected from 2011 to 2015, proposed model has an accuracy of 75\%.
+According to the NEN(Non-Euclidean Net) box-office prediction model, this paper discussed the relationship between the movie meta-data, Sina Weibo text sentiments, social relationship representations, network characteristics, and actors' art contribution in detail.
+I proposed an FC-GRU-CNN box-office prediction model, and tested in a dataset of $1296$ movies released in China mainland from 2011 to 2015, compared to Zhou \etal's model, accuracy improves 14\%.
 
@@
 \bibliographystyle{ieee_fullname}
-\bibliography{cpvr_vision}
+\bibliography{cpvr_movienet}
 }

### 2020-10-09 A-BasicCommom/CVPR2021/cvpr.tex
1.CVPR v0.3.0, thanks help from grammarly and .

--- 2020-10-03 A-BasicCommom/CVPR2021/cvpr.tex
@@
 %%%%%%%%% TITLE
-\title{Lower Bounds on Rate of Convergence of Matrix Products in All Pairs Shortest Path of Social Network}
+\title{Lower Bounds on Rate of Convergence of Matrix Products in All-Pairs Shortest Path of Social Network}
 
@@
   For the shortest path calculation task of all nodes in networks, Alon \etal~\cite{alon1997exponent} proposed an algorithm with matrix multiplication.
-  In this paper, with the distance product exchange law and block matrix multiplication, all pairs shortest path algorithm has a lowered time bound of \(O({logn2n^3\over B})\).
-  In empirical study of social networks, the shortest path algorithm has an improved lower time bound \(O({14n^3 \over B})\).
-  And I propose an all node pairs shortest path algorithm that leveraging matrix sparseness judgment, convergence judgment, distance product matrix multiplication, distance product exchange law,
+  In this paper, with the distance product association law and block matrix multiplication, all-pairs shortest path algorithm has a lowered time-bound of \(O({logn2n^3\over B})\).
+  As an empirical study of social networks, the shortest path algorithm has an improved lower time-bound \(O({14n^3 \over B})\).
+  And I propose an all-pairs shortest path algorithm that leveraging matrix sparseness judgment, convergence judgment, distance product matrix multiplication, distance product association law,
   scale-free characteristics of the social networks and limitation for floating-point operations on modern hardware.
-  Tested on a movie actors social network dataset, proposed algorithm has a improvement of 39\% to 36.2 times in performance on CPU/GPU platforms comparing to Alon \etal algorithm.
+  Tested on movie actors' social network dataset, the proposed algorithm has an improvement of 39\% to 36.2 times in performance on CPU/GPU platforms comparing to Alon \etal algorithm.
 \end{abstract}
@@
 In recent years, driven by Asian film industries such as China and India, the global box office has maintained a steady growth trend, and with the rapid development of social network applications, more and more actors use social networks for work communication.
-Therefore, social network has become an important tool for film distribution, marketing, promotion and an important medium for film actors and fans to interact.
+Therefore, the social network has become an important tool for film distribution, marketing, promotion, and an important medium for film actors and fans to interact.
 Previous studies have lacked research on actors' social networks, PageRank, an existing node influence algorithm, is not accurate in evaluating social network influence.
@@
 and Garbow and Winograd~\cite{garbow1985scaling} proposed an algorithm for distance product using matrix multiplication with element bound.
-From time bound of matrix multiplication, Strassen~\cite{strassen1969gaussian}, Coppersmith and Winograd~\cite{coppersmith1987matrix}, Davie and Andrew~\cite{davie2013improved}, Le Gall~\cite{le2014powers} proposed the block matrix multiplication with time bound of \(O(n ^ {2.807})\), \(O(n^{2.376})\), \(O(n^{2.374})\), \(O(n^{2.373})\).
+From time-bound of matrix multiplication, Strassen~\cite{strassen1969gaussian}, Coppersmith and Winograd~\cite{coppersmith1987matrix}, Davie and Andrew~\cite{davie2013improved}, Le Gall~\cite{le2014powers} proposed the block matrix multiplication with time-bound of \(O(n ^ {2.807})\), \(O(n^{2.376})\), \(O(n^{2.374})\), \(O(n^{2.373})\).
 Lam \etal~\cite{lam1991cache} proposed that the progressive time complexity of matrix multiplication with a cache block size of $B*B$ is \(O({2n^3 \over B}+{n^2})\) ,
-and Goto and Geijn~\cite{goto2008anatomy} proposed a new library, OpenBLAS, which has a higher cache hit rate and improved time cost in matrix computation on X86 CPU, compared to modern BLAS libraries, such as Intel MKL v8.1.1, ESSL v4.2.0 and ATLAS v3.7.11.
+and Goto and Geijn~\cite{goto2008anatomy} proposed a new library, OpenBLAS, which has a higher cache hit rate and improved time cost in matrix computation on X86 CPU, compared to modern BLAS libraries, such as Intel MKL v8.1.1, ESSL v4.2.0, and ATLAS v3.7.11.
 From point of view of matrix sparseness of network adjacent matrix, for sparse matrix multiplication, SciPy and CuPy use SciPy-sparse and CuPy-cuSparse to achieve efficient sparse matrix multiplication on CPU and GPU.
-For dense matrix multiplication, NumPy, SciPy, CuPy and ND4J use OpenBLAS, cuBLAS and other libraries to achieve efficient block matrix multiplication on CPU and GPU.
-Therefore, a feasible method for calculating shortest path of full node pairs is: represents the network by adjacent matrix, then makes all matrix elements exponential, computes matrix multiplication and finally takes logarithm of matrix elements.
-This procedure is called distance product epoch.
+For dense matrix multiplication, NumPy, SciPy, CuPy, and ND4J use OpenBLAS, cuBLAS, and other libraries to achieve efficient block matrix multiplication on CPU and GPU.
+Therefore, a feasible method for calculating the shortest path of full node pairs is: represents the network by adjacent matrix, then makes all matrix elements exponential, computes matrix multiplication, and finally takes the logarithm of matrix elements.
+This procedure is called a distance product epoch.
 Iterate several times to get all node pairs shortest path result.
-Further, analysis time complexity of the distance product calculation and iteration of each epoch.
-For time complexity of distance product, matrix multiplication is the most complex subprocedures;
+Further, the analysis time complexity of the distance product calculation and iteration of each epoch.
+For time complexity of distance product, matrix multiplication is the most complex sub-procedures;
 
 \begin{enumerate}
-\item For distance product optimization, Zwick proposed distance product with block matrix multiplication, therefore choose proper computation device library with optimized cache for block matrix multiplication.
+\item For distance product optimization, Zwick proposed a distance product with block matrix multiplication, therefore choose proper computation device library with optimized cache for block matrix multiplication.
 \item For iteration optimization, because Aho proved distance product is isomorphic to the matrix multiplication, and regard to that the distance product association law, optimize the iteration process by last distance product result reuse.
@@
 \section{Dataset And Hardware}
-From January 1, 2011 to March 31, 2015, I collected the film actors' social network following relationship, profile information, and text message on Sina Weibo.
-In all, collected 8508 actors, 577775 edges and 12526114 Sina Weibo posts.
-I used a server with two Intel Xeon E5-2620 v4 CPUs and one NVIDIA GeForce GTX 1080 Ti GPU, in total 32 cores with frequency of 2.1Ghz, 128G system memory and 11G GPU memory in my experiment.
+From January 1, 2011, to March 31, 2015, I collected the film actors' social network following relationship, profile information, and text message on Sina Weibo which is one of the popular social media in China.
+In all, collected 8508 actors, 577775 edges, and 12526114 Sina Weibo posts.
+I used a server with two Intel Xeon E5-2620 v4 CPUs and one NVIDIA GeForce GTX 1080 Ti GPU, in total 32 cores with a frequency of 2.1Ghz, 128G system memory, and 11G GPU memory in my experiment.
 
@@
 \section{Comparison On Block Matrix Multiplication Implementtation}
-On the actors' social network, this paper implements Strassen block matrix multiplication, Copper-Winograd block matrix multiplication and OpenBLAS matrix multiplication.
+
+On the actors' social network, this paper implements Strassen block matrix multiplication, Copper-Winograd block matrix multiplication, and OpenBLAS matrix multiplication.
 On the computer hardware, compared the $8508*8508$ matrix multiplication time-cost.
-The block matrix multiplication based on Strassen and Coppersmith-Winograd takes 6 seconds for one iteration of matrix multiplication, and with OpenBLAS library it takes only 4 seconds.
-The performance of optimized cache block matrix multiplication, such as OpenBLAS matrix computation library, is higher than Strassen and Copper-Winograd block matrix multiplication algorithm.
-Therefore, distance product algorithm proposed by Zwick U with OpenBLAS block matrix multiplication is obviously better than distance product algorithm with Strassen and Coppersmith-Winograd.
+The block matrix multiplication based on Strassen and Coppersmith-Winograd takes 6 seconds for one iteration of matrix multiplication, and with the OpenBLAS library it takes only 4 seconds.
+The performance of optimized cache block matrix multiplication, such as the OpenBLAS matrix computation library, is higher than Strassen and Copper-Winograd block matrix multiplication algorithm.
+Therefore, the distance product algorithm proposed by Zwick U with OpenBLAS block matrix multiplication is better than the distance product algorithm with Strassen and Coppersmith-Winograd.
 
@@
 
-\section{Time Bound Of Distance Product Algorithm With Cache Optimized Block Matrix Multiplication}
-For a fully connected network, the graph has a maximum diameter of $n-1$, so using result reuse method in distance product, that is use the last distance product calculation result, the matrix multiplication times is $log_2(n-1)$.
-Albert~\cite{albert1999diameter} found that social networks, the Internet and other complex networks have scale-free characteristics and small world phenomenon, thus network diameter is much smaller than the number of network nodes.
-I present the corresponding nodes counts, diameters and logarithm of diameters in Table 1, from the observation there is formula (1):
-In social networks, the number of nodes $n$, with cache block size $B*B$, according to the formula (9-10), the matrix product calculation iteration times does not exceed the number of $\lceil{log\Bbb D}\rceil$, recall that Lam \etal proved that matrix multiplication time bound is \(O({2n^3 \over B}+{n^2})\) ,
-thus Alon \etal algorithm time bound is \(O({log\Bbb D2n^3\over B})\) , use the equation (1) result, time bound is \(O({ \log(\log{N})2n^3\over B})\).
-With the arithmetic limitation on the floating-point operation, \eg take a network of number of nodes $N<10^{308}$
-as shown in Table 1, see that the shortest path calculation iterations time is no larger than $\log{\Bbb D}\approx{\log(\log{N})}<7$, that is, the number of calculation iterations does not exceed the magic number 7,
-bringing a stronger time bound of \(O({14n^3\over B})\).
-In another words, with the floating-point operation accuracy limitation on computer hardware and complex networks scale-free characteristics, all node pairs shortest path algorithm time bound is \(O({14n^3\over B})\).
+\section{Time-Bound Of Distance Product Algorithm With Cache Optimized Block Matrix Multiplication}
+
+For a fully connected network, the graph has a maximum diameter of $n-1$, so using the result reuse method in distance product, that is use the last distance product calculation result, the matrix multiplication times are $log_2(n-1)$.
+Albert~\cite{albert1999diameter} found that social networks, the Internet, and other complex networks have scale-free characteristics and small-world phenomena, thus network diameter is much smaller than the number of network nodes.
+I present the corresponding nodes counts, diameters, and logarithm of diameters in Table 1, from the observation there is formula (1):
+In social networks, the number of nodes $n$, with cache block size $B*B$, according to the formula (9-10), the matrix product calculation iteration times does not exceed the number of $\lceil{log\Bbb D}\rceil$, recall that Lam \etal proved that matrix multiplication time-bound is \(O({2n^3 \over B}+{n^2})\),
+thus Alon \etal algorithm time-bound is \(O({log\Bbb D2n^3\over B})\), use the equation (1) result, time-bound is \(O({ \log(\log{N})2n^3\over B})\).
+With the arithmetic limitation on the floating-point operation, \eg take a network with nodes number of $N<10^{308}$
+as shown in Table 1, see that the shortest path calculation iterations time is no larger than $\log{\Bbb D}\approx{\log(\log{N})}<7$, that is, the number of calculation iterations does not exceed the magic number $7$,
+bringing a stronger time-bound of \(O({14n^3\over B})\).
+In other words, with the floating-point operation accuracy limitation on computer hardware and complex networks scale-free characteristics, all node pairs shortest path algorithm time-bound is \(O({14n^3\over B})\).
 
@@
    \caption{Adjacent matrix, each iterations and the result matrix visualization of actors' social network.
-(a) initial state after each round of calculation, (b) the result matrix after the first round of calculation, (c) the result matrix of the second round of calculation, (d) the third and in the same time last round of calculation, the all pairs nodes shortest path result matrix.}
+(a) initial state after each round of calculation, (b) the result matrix after the first round of calculation, (c) the result matrix of the second round of calculation, (d) the third and in the same time last round of calculation, the all-pairs nodes shortest path result matrix.}
 \label{fig:short}
@@
 taking the difference between the largest value of the element $\widetilde X$ and the matrix elements as exponential, as shown in the formula (5).
-\eg For actors' social network with 8508 nodes, the diameter of the network does not allow to exceed 9.8 and 78.4 when calculating a precision of 32-bit floating-point and 64-bit floating-point,
-otherwise the exponential operation on the computer platform will overflow.
+\eg For actors' social network with 8508 nodes, the diameter of the network does not allow to exceed 9.8 and 78.4 when calculating precision of 32-bit floating-point and 64-bit floating-point,
+otherwise, the exponential operation on the computer platform will overflow.
 
@@
 Take non-zero elements of the matrix multiplication result to the element logarithm process, that is, the number of network nodes as the base, the element in the matrix multiplication result as the true number, then round down the logarithm result,
-after that take difference between twice of the largest input matrix element value $\widetilde X$ and the logarithm result as result, such as formula (6).
+after that take difference between twice the largest input matrix element value $\widetilde X$ and the logarithm result as result, such as formula (6).
 
@@
 From the iteration of the shortest path calculation, suppose \(\Bbb A,\ \Bbb B,\ \Bbb C\) is the square matrix, according to the association law of distance product, there is a formula (7):
-Matrix multiplication has association law, and the distance product is isomorphism to matrix multiplication, so simplify the shortest path iteration process as formula (8):
-Since matrix multiplication has association law and distance product is isomorphism to matrix multiplication, similarly, distance product has an association law.
+Matrix multiplication has an association law, and the distance product is isomorphism to matrix multiplication, so simplify the shortest path iteration process as formula (8):
+Since matrix multiplication has an association law and distance product is isomorphism to matrix multiplication, similarly, distance product has an association law.
 Under the premise of the shortest path matrix $L^{(n-1)}$ given the adjacent matrix and the $n-1$ edge, calculate the shortest path matrix $L^{(n)}$ with n edges, and extend the shortest path of the $n-1$ edge by edge.
 Calculating the shortest path matrix $L^{(n)}$ can be completed as formula (9):
-As can be seen from the nature of the shortest path in the graph, the shortest path from the any of two nodes does not exceed $n-1$, so there is formula (10):
+As can be seen from the nature of the shortest path in the graph, the shortest path from any of two nodes does not exceed $n-1$, so there is formula (10):
 Definition 3 Result Reuse in Distance Product According to the nature of the equation (8), the process of calculating the shortest path iteration using the last result of distance product follows in turn, as shown in formula (11).
@@
 \begin{algorithm}
-\caption{Lower Bounds Convergence Matrix Products in All Pairs Shortest Path}\label{algorithm}
+\caption{Lower Bounds Convergence Matrix Products in All-Pairs Shortest Path}\label{algorithm}
 \KwData{Adjacent Matrix $\Bbb W$, Matrix Row $n$, Network Diameter $\Bbb D$}
-\KwResult{Shortest path result $L^{(m)}$}
+\KwResult{The shortest path result $L^{(m)}$}
   $L^{(1)}\leftarrow \Bbb W$\;
@@
     $x\leftarrow \min{(a_i,b_i)}, y\leftarrow \max{(a_i,b_i)}, i \in (1,n)$\;
-    Exponential transformation of matrices $\Bbb A\ and\ \Bbb B$\;
+    The exponential transformation of matrices $\Bbb A\ and\ \Bbb B$\;
       $a_{ij}^{'}={(n+1)}^{y-a_{ij}}$\;
@@
     }
-    Given matrix $\Bbb C^{'}$, $\Bbb C^{'} \in \Bbb R^{n\times n}$\;
+    Given matrices $\Bbb C^{'}$, $\Bbb C^{'} \in \Bbb R^{n\times n}$\;
     $\Bbb C^{'}\leftarrow \Bbb A^{'}\odot\Bbb B^{'}$\;
-    Logrithm transformation of matrix $\Bbb C^{'}$\;
+    The logrithm transformation of matrix $\Bbb C^{'}$\;
     $\Bbb C\leftarrow \log{\Bbb C^{'}}$\;
@@
 
-As shown in Table 1, observing the adjacent matrix represented by the network diagram is usually a sparse matrix, and matrix gradually becomes dense during iterations,
+As shown in Table 1, observing the adjacent matrix represented by the network diagram is usually a sparse matrix, and the matrix gradually becomes dense during iterations,
 and one idea of optimization is to use sparse matrix multiplication to speed up the iteration when the matrix is sparse, and when the matrix becomes denser, the sparse matrix multiplication is much time-consuming.
-Taking the actors' social network as an example, the non-zero element of the adjacent matrix of 8508 nodes is 617958, and the non-zero element of the matrix is 0.8536\% of the total element,
-which is a typical sparse matrix. Consider the advantages of sparse matrix multiplication algorithm, a threshold for triggering sparse matrix multiplication is set,
+Taking the actors' social network as an example, the non-zero elements of the adjacent matrix of 8508 nodes is 617958, and the percentage of non-zero elements in the matrix is 0.8536\%, which is a typical sparse matrix.
+Consider the advantages of sparse matrix multiplication algorithm, a threshold for triggering sparse matrix multiplication is set,
 and when the proportion of non-zero-value elements entered is less than the 10\% threshold, performs sparse matrix multiplication.
@@
 
-For networks with unknown diameters, the calculation results can be made using convergence method, and for the calculation process of reaching convergence,
+For networks with unknown diameters, the calculation results can be made using the convergence method, and for the calculation process of reaching convergence,
 i.e. $L^{(n-1)}=L^{(n)}$, should be regarded as the program termination of iteration, and the calculation of the matrix product method is completed by the equation (4).
@@
 Based on Alon \etal distance product algorithm, utilizing the sparseness judgment of the input matrix and the calculation result convergence judgment,
-with the network conforming to the power law distribution and the precision of floating-point operation, and the name implies two characteristics of the limitation
+with the network conforming to the power-law distribution and the precision of floating-point operation, and the name implies two characteristics of the limitation
 of floating-point precision on the scale-free social network and the computer hardware, the algorithm process flow is shown in Algorithm 1.
@@
 Firstly, compared to Floyd-Warshall algorithm implemented on CPU, the Alon \etal algorithm implementation with matrix multiplication of block cache optimization on GPU has a time performance improvement, see Table 1.
-$PowerLawBound_{a-f}$ shows that using different libraries on CPU/GPU, the proposed algorithm has significant performance improvement over Alon \etal algorithm.
+$Power-LawBound_{a-f}$ shows that using different libraries on CPU/GPU, the proposed algorithm has significant performance improvement over Alon \etal algorithm.
 
@@
 Alon \etal          &	594.7s \\
-$PowerLawBound_a$ 	&	427.9s \\
-$PowerLawBound_b$	&	328.4s \\
-$PowerLawBound_c$	&	95.0s \\
-$PowerLawBound_d$	&	45.0s \\
-$PowerLawBound_e$	&	19.32s \\
-$PowerLawBound_f$	&	15.98s \\
+$Power-LawBound_a$ 	&	427.9s \\
+$Power-LawBound_b$	&	328.4s \\
+$Power-LawBound_c$	&	95.0s \\
+$Power-LawBound_d$	&	45.0s \\
+$Power-LawBound_e$	&	19.32s \\
+$Power-LawBound_f$	&	15.98s \\
 \hline
@@
 \section{Conclusion}
-This paper discussed a novel algorithm in all pairs shortest path computation task, using distance product exchange law.
-The time bound of Alon \etal distance product algorithm with block matrix multiplication is \(O({\log{n}2n^3\over B})\) with $B=\text{SIZE}_{\text{block}}$.
+
+This paper discussed a novel algorithm in all-pairs shortest path computation tasks, using distance product association law.
+The time-bound of Alon \etal distance product algorithm with block matrix multiplication is \(O({\log{n}2n^3\over B})\) with $B=\text{SIZE}_{\text{block}}$.
 To strengthen the conditions, on scale-free social networks, for the precision limit of floating-point operation on hardware, additional condition on the social network diameter is added to avoid floating-point operation overflow during the calculation process.
-the algorithm has lower time bound \(O({14n^3\over B})\).
-With strengthened conditions, I proposed a novel algorithm, leveraging matrix sparseness judgment and calculation convergence judgment.
-\textbf{PowerLaw} refers to the network node numbers conforming to the characteristics that social networks power law distribution, and \textbf{Bound} refers to the floating-point operations arithmetic limitation of accuracy on hardware.
-The experimental results show that \textbf{PowerLawBound} algorithm improves time performance by 39\% to 36.2 times on CPU/GPU hardware compared to Alon \etal algorithm .
+the algorithm has lower time-bound \(O({14n^3\over B})\).
+With strengthened conditions, I proposed a novel algorithm, leveraging matrix sparseness judgment, and calculation convergence judgment.
+\textbf{Power-Law} refers to the network node numbers conforming to the characteristics that social networks power-law distribution, and \textbf{Bound} refers to the floating-point operations arithmetic limitation of accuracy on hardware.
+The experimental results show that \textbf{Power-LawBound} algorithm improves time performance by 39\% to 36.2 times on CPU/GPU hardware compared to Alon \etal algorithm.
 

### 2020-10-09 A-BasicCommom/CVPR2021/cvpr_vision.tex
1.CVPR v0.3.0, thanks help from grammarly and .

@@
   However, non-Euclidean social media is hard to analyze, I propose an FC-GRU-CNN architecture, also named as \underline{N}on-\underline{E}uclidean \underline{N}et, for social media visualization.
-  In social media analysis, social relationship representations, network characteristics and media sentiments are key factors.
+  On the analysis of social media , social relationship representations, network characteristics and media sentiments are key factors.
   FC-GRU-CNN architecture exploits the long-term memory ability of GRU layer in long sequences of film cast,
-  mapping ability of CNN layer in retrieving all-pairs shortest path feature of actors' social relationship,
+  the mapping ability of CNN layer in retrieving all-pairs shortest path feature of the actors' social relationship,
   and non-linear capability of deep FC layer for movie text sentiments and other characteristics.
@@
 
-  With the development of social networks, actors' influence on social media is increasing, and the influence of actors' consumption is spread through social networks,
-  and using long-term social networks data to study the relationships between all actors, directors, and films remains a challenge.
-  It is easy to see that the relationship between box-office and the director, actors, scriptwriters, and producers is often non-linear, that is,
+  With the development of social networks, actors' influence of social media is increasing, and the influence of actors' consumption spreads through social networks,
+  and using long-term social network data to study the relationships between all actors, directors, and films remains a challenge.
+  It is easy to see that the relationship between box-office and the director, actors, scriptwriters, and producers are often non-linear, that is,
   it is difficult to use linear functions to build box-office prediction models.
@@
   it is easy to get the priority of each characteristic by analysis of feature importance,
-  existing prediction algorithm only makes use of the film meta-data, lacks the study on the social network characteristics of the actors,
-  though the traditional explanation of the film box-office prediction algorithm is sufficing, however, the prediction effect is not satisfactory.
+  the existing prediction algorithm only makes use of the film meta-data, lacks the study on the social network characteristics of the actors,
+  though the traditional explanation of the film box-office prediction algorithm is sufficing, however, the prediction accuracy is not satisfactory.
   This paper presents a model, named FC-GRU-CNN, for movie box-office prediction, combining characteristics of film meta-data, actors' social network measurement,
-  all nodes pair shortest path, social network text sentiments, and actors' art contribution characteristics,
+  all-pairs shortest path, social network text sentiments, and actors' artisticcontribution characteristics,
   as a result, it is 14\% higher in accuracy than Zhou \etal ~\cite{zhou2015c}'s model.
@@
   director total box-office, actor total box-office, release time, budget, screen numbers, user reviews, and review text sentiments,
-  trained SVM model has a prediction accuracy of 44.4\%.
+  the trained SVM model has a prediction accuracy of 44.4\%.
 
@@
   Josh \etal~\cite{joshi2010movie} collected film review text in MetaCritic releasing from 2005 to 2009, using film meta-data, n-gram model,
-  part-of-speech n-gram model and dependency characteristics, and the Elastic-Net model has determination of coefficient of 67.1\% in predicting the first-week box-office.
+  part-of-speech n-gram model and dependency characteristics, and the Elastic-Net model has a determination of coefficient of 67.1\% in predicting the first-week box-office.
 
@@
 \item {\bf Number of retweets}: the more retweet posts, the higher box-office gets.
-\item {\bf Box-office history}: the higher receipts of actors box-office, the higher box-office attendance of participating in the film gets.
+\item {\bf Box-office history}: the higher average score of actors' box-office, the higher box-office attendance of participating in the film gets.
 \end{itemize}
@@
 Finally, the number of actors retweets and tweets is not related to the average box-office per movie, thus they are independent.
-Then using Sina Weibo text sentiments and actor social network characteristics trained a decision tree model to predict movie box-office, determination of the coefficient in training-set is 98.58\%, and determination of the coefficient in test-set is 96.05\%.
+Then, using Sina Weibo text sentiments and actor social network characteristics trained a decision tree model to predict movie box-office,
+determination of the coefficient in training-set is 98.58\%, and determination of the coefficient on the test-set is 96.05\%.
 
-\par In summary, the decision tree structure shows that the influence of the actors in social networks is the main factor affecting box-office, followed by the movie-relating Sina Weibo sentiments and the film meta-data is the secondary determinant,
+\par In summary, the decision tree structure shows that the influence of the actors in social networks is the main factor affecting box-office,
+followed by the movie-relating Sina Weibo sentiments and the film meta-data is the secondary determinant,
 while the social network characteristics, movie-related Sina Weibo sentiment and other film meta-data are the least significant factors.
 
-\section{Representation Learning for Social Relationship, Network Characteristics And Art Contribution}
+\section{Representation Learning for Social Relationship, Network Characteristics And artisticContribution}
 
@@
 For each edge $e\in \Bbb E$, the ordered pair is $e=(u,v)$, $u,v \in \Bbb V$ and the weight is $A_{ij}$.
+A network can be represented as an adjacent matrix, $A\in \Bbb R^{(n*n)}$, and the goal of network embedding is to learn an all-pairs representation, $U\in \Bbb R^{(n*m)}$, $m < n$, where $m$ is an embedding dimension.
 
-A network can be represented as an adjacent matrix, $A\in \Bbb R^{(n*n)}$, and the goal of network embedding is to learn an all-pairs representation, $U\in \Bbb R^{(n*m)}$, $m < n$, where $m$ is an embedding dimension.\par
 \par \noindent Definition 2 (\textbf{Shortest Path Network Embedding})  In a network represented as a $\Bbb G=(\Bbb V,\Bbb E)$, $\Bbb V$ represents a node set of $n$ nodes, and $\Bbb E$ represents an edge set of $m$ edges.
 For each edge $e\in \Bbb E$, the ordered pair is $e=(u,v)$, $u,v \in \Bbb V$ and the weight is $A_{ij}$.
+A network can be represented as an adjacent matrix, $A\in \Bbb R^{(n*n)}$, and the goal of the shortest path network embedding is to learn all-pairs shortest path representation, $U\in \Bbb R^{(n*n)}$, where $n$ is an embedding dimension.
 
-\par A network can be represented as an adjacent matrix, $A\in \Bbb R^{(n*n)}$, and the goal of the shortest path network embedding is to learn all-pairs shortest path representation, $U\in \Bbb R^{(n*n)}$, where $n$ is an embedding dimension.
-For the task in box-office forecast, because of the significant impact the actors on the box-office, in addition to the measurement of the film meta-data and the sentiments of the movie social media,
+\par For the task in box-office forecast, because of the significant impact the actors on the box-office, in addition to the measurement of the film meta-data and the sentiments of the movie social media,
 the actors' contribution is required to compute by leveraging actors in the movie cast.
 A film, led by several leading actors, obtained the names of $7369$ actors who participated in films between 2011 and 2015 are collected as an actors' dictionary, and then used the shortest path features of the actors' social network.
-Combining social network measurement features, the shortest path network embedding, and the art features to construct the actor representation vector.
+Combining social network measurement features, the shortest path network embedding, and the artisticfeatures to construct the actor representation vector.
 For actors who have no accounts on social networks, marked as unknown, and initialized with zero vectors.
-Actor representation vectors include network characteristics of 10 dimensions, shortest path features of 8380 dimensions, art features of 1 dimension.
-In total, 10-dimension features include fans number, betweenness, closeness, followers, posts number, average posts interval, average word count per post, retweet number, movie-related post number, co-occurrence number, the shortest path with 8380 dimensions.
+Actor representation vectors include network characteristics of 10 dimensions, shortest path features of 8380 dimensions, artisticfeatures of 1 dimension.
+In total, 10-dimension features include fans number, betweenness, closeness, followers, post number, average post interval, average word count per post, retweet number, movie-related post number, co-occurrence number, the shortest path with 8380 dimensions.
 
@@
 possibly because the sentiments on actors' social networks do not represent the commercial benefits of the film.
-Actors, as creators of films, have a role to play in the box-office, but lack of other important features that also have a significant impact on the box-office,
+Actors, as creators of films, have a role to play in the box-office, but lack of other important features that also has a significant impact on the box-office,
 so the machine learning fitting process can't converge in a given time.
-Using the CART decision tree regression algorithm to make box-office prediction for the test set film,
+Using the Cartisticdecision tree regression algorithm to make box-office prediction for the test set film,
 the experimental results show that the prediction model has a determination coefficient of 96.05\% on the test set and 98.58\% on the training set, which is 2.87\% higher than the Qiu and Tang~\cite{qiu2018microblog} model,
 and the average absolute deviation of the model is $0.1285$ million, about 28.56\% of the average box-office.
-The explanatory of the decision tree prediction model is more intuitive and more interpretable than linear regression, logical regression, deep neural network and other models,
+The explanation of the decision tree prediction model is more intuitive and more interpretable than linear regression, logical regression, deep neural network and other models,
 according to the prediction model structure schematic of movie box-office,
@@
 Compared to Qiu and Tang~\cite{qiu2018microblog}'s logistic regression model on sentiments and twitter index algorithm's 95.71\% determination of coefficient,
-The CART model in this paper has a determination of coefficient of 98.58\% which has a 2.87\% improvement.
+The Cartisticmodel in this paper has a determination of coefficient of 98.58\% which has a 2.87\% improvement.
 
@@
 
-Look at box-office distribution of $1296$ films released between 2011 and 2015,
+Look at the box-office distribution of $1296$ films released between 2011 and 2015,
 Consider box-office forecasts as a binary classification task.
 To make the data evenly distributed, the film data were pre-processed by using the median box-office of $2.635$ million as the dividing line.
-So for the movies with box-office less than $2.635$ million are classified as A-class, movies with box-office more than $2.635$ million are classified as B-class.
-In the dataset division, the data was randomly selected using the $80-20$ segmentation ratio, and the training set of $1036$ films and the test set of $260$ movies were collected.
+So for the movies with box-office, less than $2.635$ million are classified as A-class, movies with box-office more than $2.635$ million are classified as B-class.
+In the dataset division, the data were randomly selected using the $80-20$ segmentation ratio, and the training set of $1036$ films and the test set of $260$ movies were collected.
 Using the actors' social network representation, the actor is quantified, that is,
-the fusion of social network features, the shortest path characteristics, and the actors' art characteristics.
+the fusion of social network features, the shortest path characteristics, and the actors' artisticcharacteristics.
 For actors without social network data, use zero-value initialization in the actor feature matrix for the unknown characteristics.
@@
 \begin{itemize}
-\item The first part is the Fully Connected layer, its input feature is the film meta-data and movie-related Sina Weibo sentiments, in a total of 5 dimensions.
-\item The second part is the GRU layer, the input feature is the actor social network measurement characteristics and art characteristics, the film cast is a long list,
+\item The first partisticis the Fully Connected layer, its input feature is the film meta-data and movie-related Sina Weibo sentiments, in a total of 5 dimensions.
+\item The second partisticis the GRU layer, the input feature is the actor social network measurement characteristics and artisticcharacteristics, the film cast is a long list,
 the longest 225 actors, for less than 225 actors using the front-end padding, the GRU layer is to solve the long-term memory loss of the structure.
-\item The last part is the 5 CNN layers, input for the actors' social network shortest path feature, similarly, the film cast is a long list,
+\item The last partisticis the 5 CNN layers, input from the actors' social network shortest path feature, similarly, the film cast is a long list,
 input less than 225 dimensions is fulfilled by padding, CNN has a good ability to capture multi-dimensional features, and use of Max-pooling layer to solve the problem of multi-dimension feature extraction.
@@
 In summary, randomly choose 10 movies as a test set, as shown in Table 1.
-The accuracy of the binary classification model in the training set reached 99.61\%, the accuracy in the test set is 75\%.
-Compared to Zhou \etal model, see Table 2, the proposed FC-GRU-CNN model converges in the training set and achieves better prediction results in the test set.
-Therefore it can provide decision-making advice in the task of selecting suitable actors for to-be-casted film,
-and in the box-office prediction task, the model can provide reasonable prediction in the market.
+The accuracy of the binary classification model on the training set reached 99.61\%, the accuracy on the test set is 75\%.
+Compared to Zhou \etal model, see Table 2, the proposed FC-GRU-CNN model converges on the training set and achieves better prediction results on the test set.
+Therefore, it can provide decision-making advice in the task of selecting suitable actors for to-be-cast film,
+and in the box-office prediction task, the model can provide reasonable predictions in the market.
 
@@
 
-According to the NEN(Non-Euclidean Net) box-office prediction model, this paper discussed the relationship between the movie meta-data, Sina Weibo text sentiments, social relationship representations, network characteristics, and actors' art contribution in detail.
-I proposed an FC-GRU-CNN box-office prediction model, and tested in a dataset of $1296$ movies released in China mainland from 2011 to 2015, compared to Zhou \etal's model, accuracy improves 14\%.
+According to the NEN(Non-Euclidean Net) box-office prediction model, this paper discussed the relationship between the movie meta-data, Sina Weibo text sentiments, social relationship representations, network characteristics, and actors' artistic contribution in detail.
+I proposed an FC-GRU-CNN box-office prediction model, and tested on a dataset of $1296$ movies released in China mainland from 2011 to 2015, compared to Zhou \etal's model, accuracy improves 14\%.
 

### 2020-10-09 A-BasicCommom/CVPR2021/cvpr.tex
1.CVPR v0.3.0, thanks help from grammarly.

@@
   For the shortest path calculation task of all nodes in networks, Alon \etal~\cite{alon1997exponent} proposed an algorithm with matrix multiplication.
-  In this paper, with the distance product association law and block matrix multiplication, all-pairs shortest path algorithm has a lowered time-bound of \(O({logn2n^3\over B})\).
-  As an empirical study of social networks, the shortest path algorithm has an improved lower time-bound \(O({14n^3 \over B})\).
-  And I propose an all-pairs shortest path algorithm that leveraging matrix sparseness judgment, convergence judgment, distance product matrix multiplication, distance product association law,
-  scale-free characteristics of the social networks and limitation for floating-point operations on modern hardware.
-  Tested on movie actors' social network dataset, the proposed algorithm has an improvement of 39\% to 36.2 times in performance on CPU/GPU platforms comparing to Alon \etal algorithm.
+  In this paper, with the distance product association law and block matrix multiplication, all-pairs shortest path algorithm has a lowered time-bound of \(O(\log{n}2n^3)\).
+  I propose an all-pairs shortest path algorithm that leveraging matrix sparseness judgment, convergence judgment, distance product matrix multiplication, distance product association law,
+  scale-free characteristics of the social networks and limitation for floating-point operations on modern hardware, which has an improved lower time-bound \(O(14n^3)\).
+  As an empirical study of social networks, I tested on movie actors' social network dataset, the proposed algorithm has an improvement of 39\% to 36.2 times in performance on CPU/GPU platforms comparing to Alon \etal's algorithm.
 \end{abstract}
@@
 From time-bound of matrix multiplication, Strassen~\cite{strassen1969gaussian}, Coppersmith and Winograd~\cite{coppersmith1987matrix}, Davie and Andrew~\cite{davie2013improved}, Le Gall~\cite{le2014powers} proposed the block matrix multiplication with time-bound of \(O(n ^ {2.807})\), \(O(n^{2.376})\), \(O(n^{2.374})\), \(O(n^{2.373})\).
-Lam \etal~\cite{lam1991cache} proposed that the progressive time complexity of matrix multiplication with a cache block size of $B*B$ is \(O({2n^3 \over B}+{n^2})\) ,
+Lam \etal~\cite{lam1991cache} proposed that the progressive time complexity of matrix multiplication with a cache block size of $\Bbb B$ is \(O({2n^3 \over \Bbb B}+{n^2})\),
 and Goto and Geijn~\cite{goto2008anatomy} proposed a new library, OpenBLAS, which has a higher cache hit rate and improved time cost in matrix computation on X86 CPU, compared to modern BLAS libraries, such as Intel MKL v8.1.1, ESSL v4.2.0, and ATLAS v3.7.11.
@@
 This procedure is called a distance product epoch.
-Iterate several times to get all node pairs shortest path result.
+Iterate several times to get all-pairs shortest path result.
 Further, the analysis time complexity of the distance product calculation and iteration of each epoch.
@@
 The performance of optimized cache block matrix multiplication, such as the OpenBLAS matrix computation library, is higher than Strassen and Copper-Winograd block matrix multiplication algorithm.
-Therefore, the distance product algorithm proposed by Zwick U with OpenBLAS block matrix multiplication is better than the distance product algorithm with Strassen and Coppersmith-Winograd.
+Therefore, the distance product algorithm proposed by Zwick with OpenBLAS block matrix multiplication is better than the distance product algorithm with Strassen and Coppersmith-Winograd.
 
@@
 I present the corresponding nodes counts, diameters, and logarithm of diameters in Table 1, from the observation there is formula (1):
-In social networks, the number of nodes $n$, with cache block size $B*B$, according to the formula (9-10), the matrix product calculation iteration times does not exceed the number of $\lceil{log\Bbb D}\rceil$, recall that Lam \etal proved that matrix multiplication time-bound is \(O({2n^3 \over B}+{n^2})\),
-thus Alon \etal algorithm time-bound is \(O({log\Bbb D2n^3\over B})\), use the equation (1) result, time-bound is \(O({ \log(\log{N})2n^3\over B})\).
+In social networks, the number of nodes $n$, with cache block size $B*B$, according to the formula (9-10), the matrix product calculation iteration times does not exceed the number of $\lceil{\log{\Bbb D}}\rceil$, recall that Lam \etal proved that matrix multiplication time-bound is \(O({2n^3 \over \Bbb B}+{n^2})\),
+thus Alon \etal algorithm time-bound is \(O(\log{\Bbb D}2n^3\over \Bbb B)\) with cache block size of $\Bbb B$, use the equation (1) result, time-bound is \(O(\log(\log{N})2n^3\over \Bbb B)\).
 With the arithmetic limitation on the floating-point operation, \eg take a network with nodes number of $N<10^{308}$
-as shown in Table 1, see that the shortest path calculation iterations time is no larger than $\log{\Bbb D}\approx{\log(\log{N})}<7$, that is, the number of calculation iterations does not exceed the magic number $7$,
-bringing a stronger time-bound of \(O({14n^3\over B})\).
-In other words, with the floating-point operation accuracy limitation on computer hardware and complex networks scale-free characteristics, all node pairs shortest path algorithm time-bound is \(O({14n^3\over B})\).
+as shown in Table 1, see that the shortest path calculation iterations time is no larger than $\log{\Bbb D} \approx \log(\log{N})<7$, that is, the number of calculation iterations does not exceed the magic number $7$,
+bringing a stronger time-bound of \(O(14n^3\over \Bbb B)\).
+In other words, with the floating-point operation accuracy limitation on computer hardware and complex networks scale-free characteristics, all-pairs shortest path algorithm time-bound is \(O(14n^3\over \Bbb B)\), for $\Bbb B$ is a constant, thus, for simpler representation the time-bound is \(O(14n^3)\).
 
@@
 \hline\hline
-Floyd-Warshall &	1055880s \\
+Floyd-Warshall~\cite{floyd1962algorithm,warshall1962theorem}  &	1055880s \\
 Alon \etal          &	594.7s \\
@@
 This paper discussed a novel algorithm in all-pairs shortest path computation tasks, using distance product association law.
-The time-bound of Alon \etal distance product algorithm with block matrix multiplication is \(O({\log{n}2n^3\over B})\) with $B=\text{SIZE}_{\text{block}}$.
+The time-bound of Alon \etal distance product algorithm with block matrix multiplication is \(O({\log{n}2n^3\over \Bbb B})\).
 To strengthen the conditions, on scale-free social networks, for the precision limit of floating-point operation on hardware, additional condition on the social network diameter is added to avoid floating-point operation overflow during the calculation process.
-the algorithm has lower time-bound \(O({14n^3\over B})\).
+the algorithm has lower time-bound \(O({14n^3\over \Bbb B})\).
 With strengthened conditions, I proposed a novel algorithm, leveraging matrix sparseness judgment, and calculation convergence judgment.
 \textbf{Power-Law} refers to the network node numbers conforming to the characteristics that social networks power-law distribution, and \textbf{Bound} refers to the floating-point operations arithmetic limitation of accuracy on hardware.
-The experimental results show that \textbf{Power-LawBound} algorithm improves time performance by 39\% to 36.2 times on CPU/GPU hardware compared to Alon \etal algorithm.
+The experimental results show that \textbf{Power-LawBound} algorithm improves time performance by 39\% to 36.2 times on CPU/GPU hardware compared to Alon \etal's algorithm.
 

### 2020-10-12 A-BasicCommom/CVPR2021/cvpr_classification.tex
1.CVPR v0.4.0, add a new paper: image classification draft.

--- 2020-10-09 A-BasicCommom/CVPR2021/cvpr.tex
@@
 
-\def\cvprPaperID{6666} % *** Enter the CVPR Paper ID here
+\def\cvprPaperID{7777} % *** Enter the CVPR Paper ID here
 \def\confYear{CVPR 2021}
@@
 %%%%%%%%% TITLE
-\title{Lower Bounds on Rate of Convergence of Matrix Products in All-Pairs Shortest Path of Social Network}
+\title{Enhance Image Classification Performance Via Unsupervised Pre-trained Transformers Language Models}
 
@@
 \begin{abstract}
-  For the shortest path calculation task of all nodes in networks, Alon \etal~\cite{alon1997exponent} proposed an algorithm with matrix multiplication.
-  In this paper, with the distance product association law and block matrix multiplication, all-pairs shortest path algorithm has a lowered time-bound of \(O(\log{n}2n^3)\).
-  I propose an all-pairs shortest path algorithm that leveraging matrix sparseness judgment, convergence judgment, distance product matrix multiplication, distance product association law,
-  scale-free characteristics of the social networks and limitation for floating-point operations on modern hardware, which has an improved lower time-bound \(O(14n^3)\).
-  As an empirical study of social networks, I tested on movie actors' social network dataset, the proposed algorithm has an improvement of 39\% to 36.2 times in performance on CPU/GPU platforms comparing to Alon \etal's algorithm.
+
+  Image classification and categorization are essential for the capability of telling the difference between images for a machine.
+  As \underline{B}idirectional \underline{E}ncoder \underline{R}epresentations from \underline{T}ransformers became popular in many tasks of natural language processing recent years,
+  it is intuitive to use these pre-trained language models for enhancing the computer vision tasks, \eg image classification.
+  In this paper, by encoding image pixels using pre-trained transformers, then connect to a fully connected layer,
+  the classification model outperforms the Wide ResNet model and the linear-probe iGPT-L model,
+  and achieved an accuracy of $97.72\%$\~$99.60\%$ on the CIFAR-10 image set, and an accuracy of $98.27\%$\~ on the CIFAR-100 image set.
+
 \end{abstract}
@@
 
-In recent years, driven by Asian film industries such as China and India, the global box office has maintained a steady growth trend, and with the rapid development of social network applications, more and more actors use social networks for work communication.
-Therefore, the social network has become an important tool for film distribution, marketing, promotion, and an important medium for film actors and fans to interact.
-Previous studies have lacked research on actors' social networks, PageRank, an existing node influence algorithm, is not accurate in evaluating social network influence.
-Social network feature measurement is an important task in social network data mining, some network characteristics, such as betweenness and closeness, need to calculate the distances between nodes.
-As a result, efficient calculation of the shortest path is one of the key problems in social network measurement.
-There was Floyd-Warshall~\cite{floyd1962algorithm,warshall1962theorem} algorithm for calculating node distances, Aho and Hopcroft~\cite{aho1974design} proved that distance product is homogenous to matrix multiplication,
-Alon \etal~\cite{alon1997exponent} proposed an algorithm to calculate distance product by matrix multiplication, Zwick~\cite{zwick2002all} optimized distance product using fast matrix multiplication,
-and Garbow and Winograd~\cite{garbow1985scaling} proposed an algorithm for distance product using matrix multiplication with element bound.
-From time-bound of matrix multiplication, Strassen~\cite{strassen1969gaussian}, Coppersmith and Winograd~\cite{coppersmith1987matrix}, Davie and Andrew~\cite{davie2013improved}, Le Gall~\cite{le2014powers} proposed the block matrix multiplication with time-bound of \(O(n ^ {2.807})\), \(O(n^{2.376})\), \(O(n^{2.374})\), \(O(n^{2.373})\).
-Lam \etal~\cite{lam1991cache} proposed that the progressive time complexity of matrix multiplication with a cache block size of $\Bbb B$ is \(O({2n^3 \over \Bbb B}+{n^2})\),
-and Goto and Geijn~\cite{goto2008anatomy} proposed a new library, OpenBLAS, which has a higher cache hit rate and improved time cost in matrix computation on X86 CPU, compared to modern BLAS libraries, such as Intel MKL v8.1.1, ESSL v4.2.0, and ATLAS v3.7.11.
-From point of view of matrix sparseness of network adjacent matrix, for sparse matrix multiplication, SciPy and CuPy use SciPy-sparse and CuPy-cuSparse to achieve efficient sparse matrix multiplication on CPU and GPU.
-For dense matrix multiplication, NumPy, SciPy, CuPy, and ND4J use OpenBLAS, cuBLAS, and other libraries to achieve efficient block matrix multiplication on CPU and GPU.
-Therefore, a feasible method for calculating the shortest path of full node pairs is: represents the network by adjacent matrix, then makes all matrix elements exponential, computes matrix multiplication, and finally takes the logarithm of matrix elements.
-This procedure is called a distance product epoch.
-Iterate several times to get all-pairs shortest path result.
-Further, the analysis time complexity of the distance product calculation and iteration of each epoch.
-For time complexity of distance product, matrix multiplication is the most complex sub-procedures;
-
-\begin{enumerate}
-\item For distance product optimization, Zwick proposed a distance product with block matrix multiplication, therefore choose proper computation device library with optimized cache for block matrix multiplication.
-\item For iteration optimization, because Aho proved distance product is isomorphic to the matrix multiplication, and regard to that the distance product association law, optimize the iteration process by last distance product result reuse.
-\end{enumerate}
+  Unsupervised pre-training is important in modern research of deep learning.
+  Lee \etal~\cite{lee2009convolutional} used pre-training approaches
+  in Computer Vision tasks in 2009, and later from 2010 to 2016, Nair and Hinton~\cite{nair2010rectified} proved that the pre-training process is supplementary in the CV tasks,
+  thus, can be omitted in some cases.
+  However, it started to flourish in natural language processing domain since Mikolov \etal~\cite{mikolov2013distributed} had proposed Word2Vec.
+  Not long before Devin \etal~\cite{devlin2018bert}'s BERT language model dominates in most frequent used tasks in natural language processing,
+  which is close resemble of Vicent \etal~\cite{vincent2008extracting}'s Denoising Autoencoder model, which was initially designed for images.
+  Pre-training process become one of the most important procedures in deep learning.
 
@@
 
-\section{Dataset And Hardware}
-From January 1, 2011, to March 31, 2015, I collected the film actors' social network following relationship, profile information, and text message on Sina Weibo which is one of the popular social media in China.
-In all, collected 8508 actors, 577775 edges, and 12526114 Sina Weibo posts.
-I used a server with two Intel Xeon E5-2620 v4 CPUs and one NVIDIA GeForce GTX 1080 Ti GPU, in total 32 cores with a frequency of 2.1Ghz, 128G system memory, and 11G GPU memory in my experiment.
+\section{Recent Work}
+
+  Chen \etal~\cite{chen2020generative} trained image representation by sequence Transformers and tested on CIFAR-10 to show its outperforming to Wide-ResNet
+which inspired from unsupervised natural language representation learning.
+  Wang \etal~\cite{wang2019development} reviewed that convolutional neural networks had been proposed in 1960s, and had its implementation in 1980s,
+and until LeCun \etal~\cite{lecun1990handwritten}'s first experiment on handwritten digit recognition, CNN's great potential had been revealed.
+  In the 2010s, Krizhevsky \etal~\cite{krizhevsky2012imagenet} proposed the deep architecture, AlexNet, by concatenating multiple components of CNN layers.
+Several years later, a lot of variants of AlexNet had been proposed by researchers and the accuracy of ImageNet had been greatly improved, \eg ZFNet~\cite{zeiler2014visualizing}, VGG~\cite{simonyan2014very}, GoogLeNet~\cite{szegedy2015going}, ResNet~\cite{he2016deep},
+Wide-ResNet~\cite{zagoruyko2016wide}, ResNeXt~\cite{xie2017aggregated}, inception-ResNet-v2~\cite{szegedy2016inception}, DenseNet~\cite{huang2016deep}.
+  Lu and Weng~\cite{lu2007survey} concluded that for multi-source image classification task, additional information such as signatures, texture, context and ancillary data can be combined to achieve better performance.
+And it is difficult in handling the dichotomy between pixels and natural language texts in a single model.
+  Cui \etal~\cite{cui2019pre, cui2020revisiting} proposed several whole-word-masking pre-trained Chinese language models,
+which are improved versions of BERT~\cite{devlin2018bert} and RoBERTa~\cite{liu2019roberta} pre-trained language models, namely RBT3, RBTL3, and RoBERTa-wwm-ext-large.
+These models achieved better performance in Chinese machine reading comprehension and Chinese document classification tasks.
 
@@
 
-\section{Comparison On Block Matrix Multiplication Implementtation}
+\section{Image Classification via Pre-trained Transformers Language Models}
 
@@
 
-\section{Time-Bound Of Distance Product Algorithm With Cache Optimized Block Matrix Multiplication}
+\section{Pre-trained Transformers Language Models}
 
@@
 
-\section{Shortest Path Algorithm With Block Matrix Multiplication}
+\section{Image Classification Model}
 
-Definition 1 (Outer Product Matrix Multiplication) Given matrices \(\Bbb A \in \Bbb R^{m*r}\), \(\Bbb B \in \Bbb R^{r*n}\) and \(\Bbb C \in \Bbb R^{m*n}\), the outer product is:
-\begin{equation}
-\Bbb C = \Bbb C  + \Bbb A(:,k)\bullet \Bbb B(k,:) , k \in (1,r)
-\end{equation}
-
-Given two vectors \(\textsc x\), \(\textsc y\), and matrix \(\Bbb A\), having \(\Bbb A \in \Bbb R^{m*n}\), \(\textsc x \in \Bbb R^{m}\) and \(\textsc y \in \Bbb R^{n}\) the outer product \(\bullet\) is defined by:
-\begin{equation}
-a_{ij} = a_{ij} + x_i * y_j, i \in (1,m), j \in (1,n)
-\end{equation}
-
-Definition 2 (Distance Product Matrix Multiplication) Given matrices \(\Bbb A \in \Bbb R^{m*r}\), \(\Bbb B \in \Bbb R^{r*n}\) and \(\Bbb C \in \Bbb R^{m*n}\), the distance product is:
-\begin{equation}
-  \Bbb C = \min(\Bbb C, \Bbb A(:,k)\odot \Bbb B(k,:)) , k \in (1,r)
-\end{equation}
-
-Given two vectors \(\textsc x\), \(\textsc y\), and matrix \(\Bbb A\), having \(\Bbb A \in \Bbb R^{m*n}\), \(\textsc x \in \Bbb R^{m}\) and \(\textsc y \in \Bbb R^{n}\) the distance product \(\odot\) is defined by:
-\begin{equation}
-a_{ij} = \min(a_{ij} , x_i + y_j), i \in (1,m), j \in (1,n)
-\end{equation}
-%-------------------------------------------------------------------------
 \begin{figure*}
 \begin{center}
-  \fbox{\rule{0pt}{2in} \includegraphics[width=0.9\linewidth]{figure1.pdf}}
+  \fbox{\rule{0pt}{2in} \includegraphics[width=0.9\linewidth]{classification.pdf}}
 \end{center}
-   \caption{Adjacent matrix, each iterations and the result matrix visualization of actors' social network.
-(a) initial state after each round of calculation, (b) the result matrix after the first round of calculation, (c) the result matrix of the second round of calculation, (d) the third and in the same time last round of calculation, the all-pairs nodes shortest path result matrix.}
+   \caption{Concat, encoder, representation, and extraction layers for image classification task.}
 \label{fig:short}
 \end{figure*}
+
+%-------------------------------------------------------------------------
 
@@
 \bibliographystyle{ieee_fullname}
-\bibliography{cpvr}
+\bibliography{cpvr_classification}
 }

### 2020-10-12 A-BasicCommom/CVPR2021/cvpr_classification.tex
1.CVPR v0.3.0, thanks help from grammarly.

@@
   the classification model outperforms the Wide ResNet model and the linear-probe iGPT-L model,
-  and achieved an accuracy of $97.72\%$\~$99.60\%$ on the CIFAR-10 image set, and an accuracy of $98.27\%$\~ on the CIFAR-100 image set.
+  and achieved an accuracy of $97.72\%~99.60\%$ on the CIFAR-10 image set, and an accuracy of $98.27\%~98.95\%$ on the CIFAR-100 image set.
 
@@
 which are improved versions of BERT~\cite{devlin2018bert} and RoBERTa~\cite{liu2019roberta} pre-trained language models, namely RBT3, RBTL3, and RoBERTa-wwm-ext-large.
-These models achieved better performance in Chinese machine reading comprehension and Chinese document classification tasks.
+These models achieved better performance in Chinese machine reading comprehension, Chinese document classification and other downstream natural language tasks.
 
@@
 
-On the actors' social network, this paper implements Strassen block matrix multiplication, Copper-Winograd block matrix multiplication, and OpenBLAS matrix multiplication.
-On the computer hardware, compared the $8508*8508$ matrix multiplication time-cost.
-The block matrix multiplication based on Strassen and Coppersmith-Winograd takes 6 seconds for one iteration of matrix multiplication, and with the OpenBLAS library it takes only 4 seconds.
-The performance of optimized cache block matrix multiplication, such as the OpenBLAS matrix computation library, is higher than Strassen and Copper-Winograd block matrix multiplication algorithm.
-Therefore, the distance product algorithm proposed by Zwick with OpenBLAS block matrix multiplication is better than the distance product algorithm with Strassen and Coppersmith-Winograd.
+Three of the most popular approaches for image classification task are per-pixel, subpixel, and heterogeneous.
+Lu and Weng found that, for per-pixel approach, non-parametric classifiers, \eg neural networks, support vector machines and decision trees,
+are most well known algorithms for their performance and generalization advantages in late 1990s and 2000s.
+Fern{\'a}ndez \etal~\cite{fernandez2014we} compared different classifiers in small datasets, and they found that the random forest algorithm ranks first among the 179 classifiers.
 
 %-------------------------------------------------------------------------
+\section{Per-pixel Encoder}
 
-\section{Pre-trained Transformers Language Models}
+For the per-pixel image classification approach, for every RGB channel of pixel in a image,
+each pixel had its pixel-channel code, ranges from $0x00$ to $0xff$ for different colors.
+Thus, taking these pixels in a image is identical to ASCII characters in a document.
+Generality speaking, the performance of the pre-trained language models achieved in document classification task, can be transferred to image classification naturally.
 
-For a fully connected network, the graph has a maximum diameter of $n-1$, so using the result reuse method in distance product, that is use the last distance product calculation result, the matrix multiplication times are $log_2(n-1)$.
-Albert~\cite{albert1999diameter} found that social networks, the Internet, and other complex networks have scale-free characteristics and small-world phenomena, thus network diameter is much smaller than the number of network nodes.
-I present the corresponding nodes counts, diameters, and logarithm of diameters in Table 1, from the observation there is formula (1):
-In social networks, the number of nodes $n$, with cache block size $B*B$, according to the formula (9-10), the matrix product calculation iteration times does not exceed the number of $\lceil{\log{\Bbb D}}\rceil$, recall that Lam \etal proved that matrix multiplication time-bound is \(O({2n^3 \over \Bbb B}+{n^2})\),
-thus Alon \etal algorithm time-bound is \(O(\log{\Bbb D}2n^3\over \Bbb B)\) with cache block size of $\Bbb B$, use the equation (1) result, time-bound is \(O(\log(\log{N})2n^3\over \Bbb B)\).
-With the arithmetic limitation on the floating-point operation, \eg take a network with nodes number of $N<10^{308}$
-as shown in Table 1, see that the shortest path calculation iterations time is no larger than $\log{\Bbb D} \approx \log(\log{N})<7$, that is, the number of calculation iterations does not exceed the magic number $7$,
-bringing a stronger time-bound of \(O(14n^3\over \Bbb B)\).
-In other words, with the floating-point operation accuracy limitation on computer hardware and complex networks scale-free characteristics, all-pairs shortest path algorithm time-bound is \(O(14n^3\over \Bbb B)\), for $\Bbb B$ is a constant, thus, for simpler representation the time-bound is \(O(14n^3)\).
+\par Recall that Kim~\cite{kim2014convolutional} had proved that unsupervised pre-trained language model $word2vec$ and CNN outperformed many other machine learning algorithms,
+\eg support vector machines and conditional random field, in many dataset such as, movie reviews, Stanford sentiment treebank, and TREC question.
+Adhikari \etal~\cite{adhikari2019docbert} showed the BERT and BERT-large model had achieved higher accuracy in the Routers, IMDB, and Yelp dataset which classification ranges from 5 to 90.
+Cui \etal's pre-trained language model, namely RBT3, RBTL3, and RoBERTa-wwm-ext-large, had improved performances over many other machine learning algorithms.
+BERT and RoBERTa-wwm-ext-large models both achieved an f1-score of 97.8\% in the THUCNews dataset, which contains 65 thousands of news in 10 domains.
 
+\par I used RBTL3 and RoBERTa-wwm-ext-large pre-trained language model in two Chinese Judicial dataset, which have 2 and 4 main domains.
+The $Case-2$ dataset annotated civil and criminal cases, and the $Case-4$ dataset annotated by civil, criminal, intellectual property, and administrative cases.
+The $Case-2$ dataset has $19508$ training documents and $2000$ test documents, and the $Case-4$ dataset has $34789$ training documents and $2013$ test documents.
+
+\par From table-1, by combining pre-trained language model with fully connected layer as the document classification model,
+the test accuracy exceeds the other popular machine learning algorithms.
+Therefore, the pixel channels of image can be properly represented by these pre-trained language models.
+
+\begin{table}
+\begin{center}
+\begin{tabular}{|l|c|r|}
+\hline
+Language Model 	& Dataset & Accuracy \\
+\hline\hline
+RoBERTa-wwm-ext-large & Case-2	&	99.8\% \\
+RoBERTa-wwm-ext-large & Case-4	&	98.95\% \\
+RBTL3  & Case-4	&	96.35\% \\
+\hline
+\end{tabular}
+\end{center}
+\caption{Comparision of accuracy of the pre-trained language models on different dataset in the document classification task.}
+\end{table}
 %-------------------------------------------------------------------------
@@
 
+We design a simple classification models without too many layers, as Figure-1 shows.
+And use the CIFAR-10 and CIFAR-100 dataset as an example to show the architecture of the model.
+The model architecture has seven functional layers:
+\begin{itemize}
+\item {\bf Input layer}
+\item {\bf Concat layer}
+\item {\bf Trim layer}
+\item {\bf Encoder layer}
+\item {\bf Embedding layer}
+\item {\bf Feature Extraction layer}
+\item {\bf Output layer}
+\end{itemize}
+
+\par The CIFAR-10 dataset contains 60000 colour images with a resolution of 32x32 in 10 classes, and the CIFAR-100 dataset has 100 classes containing 600 images each.
+Encode the image by the sequence of RGB channel values, in the order of Red-channel, Green-channel, and Blue-channel,
+then encode other meta-data if provided, as a sequence of ASCII character.
+In the Concat layer, the pixel-channel value and meta data are concatenated, put a special token of $\textbf{[CLS]}$ at the start,
+and put a $\textbf{[SEP]}$ token between channel vules and meta values, put a special token of $\textbf{[SEP]}$ at the end.
+In the Trim layer, due to the limit on the max sequence of BERT language model, sequence larger than $512$ need to be trimmed before sending to BERT model.
+Keep the first 256 characters and last 256 characters of the concatenated sequence, trimmed result contrains the first 255 red-channel value,
+some blue-channel value, and all the meta value in common cases.
+In the Encoder layer and the Embedding layer, trimmed sequence of values are encoded by BERT-like models,
+and get the encoded representation of the token $\textbf{[CLS]}$ as the images' language model embeddings.
+In the Feature-Extraction layer, a combination of one dropout layer, one fully connected layer, and one softmax layer is used.
+In the Output layer, the classification label of the image is feed in the model.
+
 %-------------------------------------------------------------------------
 
-\subsection{Maximum Calculation}
+\section{Image Classification Model}
 
-Calculate the largest value of the square matrix element $\widetilde X$, such as the formula (4):
+\subsection{Experiments and Results}
 
-\subsection{Exponential Calculation}
-
-The calculation accuracy of different computer hardware is in line with the IEEE floating-point operation standard~\cite{ieee1985ieee},
-first of all, transform the input matrix by exponential transformation, to be specific, taking the number of nodes as the base,
-taking the difference between the largest value of the element $\widetilde X$ and the matrix elements as exponential, as shown in the formula (5).
-\eg For actors' social network with 8508 nodes, the diameter of the network does not allow to exceed 9.8 and 78.4 when calculating precision of 32-bit floating-point and 64-bit floating-point,
-otherwise, the exponential operation on the computer platform will overflow.
-
-\subsection{Matrix Multiplication}
-Use different matrix libraries to speed up the matrix multiplication on computer hardware, as shown in Table 3, choose proper device-based optimized matrix multiplication libraries according to different conditions, such as matrix sparseness, calculation hardware, and programming language.
-
-%-------------------------------------------------------------------------
-\subsection{Logarithm Calculation}
-Take non-zero elements of the matrix multiplication result to the element logarithm process, that is, the number of network nodes as the base, the element in the matrix multiplication result as the true number, then round down the logarithm result,
-after that take difference between twice the largest input matrix element value $\widetilde X$ and the logarithm result as result, such as formula (6).
-
-\subsection{Distance Product Exchange Law}
-
-From the iteration of the shortest path calculation, suppose \(\Bbb A,\ \Bbb B,\ \Bbb C\) is the square matrix, according to the association law of distance product, there is a formula (7):
-Matrix multiplication has an association law, and the distance product is isomorphism to matrix multiplication, so simplify the shortest path iteration process as formula (8):
-Since matrix multiplication has an association law and distance product is isomorphism to matrix multiplication, similarly, distance product has an association law.
-Under the premise of the shortest path matrix $L^{(n-1)}$ given the adjacent matrix and the $n-1$ edge, calculate the shortest path matrix $L^{(n)}$ with n edges, and extend the shortest path of the $n-1$ edge by edge.
-Calculating the shortest path matrix $L^{(n)}$ can be completed as formula (9):
-As can be seen from the nature of the shortest path in the graph, the shortest path from any of two nodes does not exceed $n-1$, so there is formula (10):
-Definition 3 Result Reuse in Distance Product According to the nature of the equation (8), the process of calculating the shortest path iteration using the last result of distance product follows in turn, as shown in formula (11).
-The shortest path needs to be calculated $\lceil{log_2(n-1)}\rceil$ times matrix multiplication, from the formula (10), it can be seen that $(n-1)\leq2^{\lceil{log_2(n-1)}\rceil}$ is the same as the simple shortest path matrix calculation result $L^{(n-1)}$, so there is a formula (12):
-Obviously, the result reuse method saves $n-2-\lceil{log_2(n-1)}\rceil$ times of matrix multiplication.
-Observe the shortest path calculation process of the actors' social network, the adjacent matrix is shown in Figure 1a, and the change of result in each iteration is shown in Figure 1b-d, the shortest path result matrix converges gradually, each element stabilizes as iterations goes.
-
-\begin{algorithm}
-\caption{Lower Bounds Convergence Matrix Products in All-Pairs Shortest Path}\label{algorithm}
-\KwData{Adjacent Matrix $\Bbb W$, Matrix Row $n$, Network Diameter $\Bbb D$}
-\KwResult{The shortest path result $L^{(m)}$}
-  $L^{(1)}\leftarrow \Bbb W$\;
-  $m\leftarrow 1$\;
-  \While{$m\leq \Bbb D$}{
-    $\Bbb A\leftarrow L^{(m)},\Bbb B\leftarrow L^{(m)},$\;
-    $x\leftarrow \min{(a_i,b_i)}, y\leftarrow \max{(a_i,b_i)}, i \in (1,n)$\;
-    The exponential transformation of matrices $\Bbb A\ and\ \Bbb B$\;
-      $a_{ij}^{'}={(n+1)}^{y-a_{ij}}$\;
-      $b_{ij}^{'}={(n+1)}^{y-b_{ij}}$\;
-    \eIf{$L^{(m)}$ is sparse}{
-      $\odot\leftarrow \bigcirc$//sparse matrix multiplication\;
-    }{
-      $\odot\leftarrow \otimes$//dense matrix multiplication\;
-    }
-    Given matrices $\Bbb C^{'}$, $\Bbb C^{'} \in \Bbb R^{n\times n}$\;
-    $\Bbb C^{'}\leftarrow \Bbb A^{'}\odot\Bbb B^{'}$\;
-    The logrithm transformation of matrix $\Bbb C^{'}$\;
-    $\Bbb C\leftarrow \log{\Bbb C^{'}}$\;
-    \If{$L^{(m)} = \Bbb C$}{
-      {\bf return} $L^{(m)}$\;
-    }
-    $L^{(2m)}\leftarrow \Bbb C$\;
-    $m\leftarrow 2*m$\;
-  }
-  {\bf return} $L^{(m)}$\;
-\end{algorithm}
-
-\section{Architecture Design}
-
-\subsection{Sparseness Judgment}
-
-As shown in Table 1, observing the adjacent matrix represented by the network diagram is usually a sparse matrix, and the matrix gradually becomes dense during iterations,
-and one idea of optimization is to use sparse matrix multiplication to speed up the iteration when the matrix is sparse, and when the matrix becomes denser, the sparse matrix multiplication is much time-consuming.
-Taking the actors' social network as an example, the non-zero elements of the adjacent matrix of 8508 nodes is 617958, and the percentage of non-zero elements in the matrix is 0.8536\%, which is a typical sparse matrix.
-Consider the advantages of sparse matrix multiplication algorithm, a threshold for triggering sparse matrix multiplication is set,
-and when the proportion of non-zero-value elements entered is less than the 10\% threshold, performs sparse matrix multiplication.
-
-\subsection{Convergence Judgment}
-
-For networks with unknown diameters, the calculation results can be made using the convergence method, and for the calculation process of reaching convergence,
-i.e. $L^{(n-1)}=L^{(n)}$, should be regarded as the program termination of iteration, and the calculation of the matrix product method is completed by the equation (4).
-
-\subsection{The Shortest Path Algorithm Fusing Sparseness Judgment And Convergence Judgment}
-
-Based on Alon \etal distance product algorithm, utilizing the sparseness judgment of the input matrix and the calculation result convergence judgment,
-with the network conforming to the power-law distribution and the precision of floating-point operation, and the name implies two characteristics of the limitation
-of floating-point precision on the scale-free social network and the computer hardware, the algorithm process flow is shown in Algorithm 1.
-
-\section{Experiment}
-
-Firstly, compared to Floyd-Warshall algorithm implemented on CPU, the Alon \etal algorithm implementation with matrix multiplication of block cache optimization on GPU has a time performance improvement, see Table 1.
-$Power-LawBound_{a-f}$ shows that using different libraries on CPU/GPU, the proposed algorithm has significant performance improvement over Alon \etal algorithm.
+Use the proposed model, and we tried different pre-trained language models to see the impact on classification accuracy.
+From the table-2, from line 2 and line 4, for the same size of dataset with larger classes, it need more epochs and training time for the classification model.
+From line 2 and line 3, for the same RoBERTa language model with different numbers of transformer layers, 24 layers of transformers had better accuracy than 3 layers,
+however, its training cost grows for the larger language model.
+From line 3 and line 5, for the same fine-tuned language model, classes number has some impact on the accuracy,
+the less classes the dataset has, the more accuracy the model can achieve.
 
@@
 \begin{center}
-\begin{tabular}{|l|c|}
+\begin{tabular}{|l|c|c|r|}
 \hline
-Algorithm	& Time Cost \\
+Language Model 	& Dataset & Epoch & Accuracy \\
 \hline\hline
-Floyd-Warshall~\cite{floyd1962algorithm,warshall1962theorem}  &	1055880s \\
-Alon \etal          &	594.7s \\
-$Power-LawBound_a$ 	&	427.9s \\
-$Power-LawBound_b$	&	328.4s \\
-$Power-LawBound_c$	&	95.0s \\
-$Power-LawBound_d$	&	45.0s \\
-$Power-LawBound_e$	&	19.32s \\
-$Power-LawBound_f$	&	15.98s \\
+RBT3   & CIFAR-10 & 1	&	84.89\% \\
+RBTL3  & CIFAR-10 & 1	&	97.72\% \\
+RoBERTa-wwm-ext-large  & CIFAR-10 & 6	&	99.60\% \\
+RBTL3  & CIFAR-100 & 6  & 	98.27\% \\
+RoBERTa-wwm-ext-large & CIFAR-100 & 16 &	98.95\% \\
 \hline
@@
 \end{center}
-\caption{Performance comparison on different hardware. (a) CPU numpy library. (b) CPU scipy/numpy library. (c) GPU cuBLAS. (d) CPU openBLAS. (e) GPU CuPy. (f) GPU CuPy-sparse/CuPy.}
+\caption{Comparision of accuracy of the pre-trained language models on the CIFAR-10 and CIFAR-100 datasets in the image classification task.}
 \end{table}
+
+\subsection{Discussion}
+
+ Compare to iGPT-L's accuracy of 96.3\% on the unaugmented CIFAR-10 dataset and 82.8\% on the CIFAR-100 dataset, our models has preferable better results.
+The reason that the model's outstanding performance lie in the large pre-trained data for BERT, on top of that fine-tuned by RoBERTa, and use extra language corpus of
+$5.4$ billions of tokens of wiki data and other resources.
+The transformers in the pre-trained language models use multiple layers for representing images, and maybe used in other Computer Vision task, \eg object detection, gesture prediction.
 
@@
 
-This paper discussed a novel algorithm in all-pairs shortest path computation tasks, using distance product association law.
-The time-bound of Alon \etal distance product algorithm with block matrix multiplication is \(O({\log{n}2n^3\over \Bbb B})\).
-To strengthen the conditions, on scale-free social networks, for the precision limit of floating-point operation on hardware, additional condition on the social network diameter is added to avoid floating-point operation overflow during the calculation process.
-the algorithm has lower time-bound \(O({14n^3\over \Bbb B})\).
-With strengthened conditions, I proposed a novel algorithm, leveraging matrix sparseness judgment, and calculation convergence judgment.
-\textbf{Power-Law} refers to the network node numbers conforming to the characteristics that social networks power-law distribution, and \textbf{Bound} refers to the floating-point operations arithmetic limitation of accuracy on hardware.
-The experimental results show that \textbf{Power-LawBound} algorithm improves time performance by 39\% to 36.2 times on CPU/GPU hardware compared to Alon \etal's algorithm.
+This paper proposed a novel idea by using pre-trained language models for images representation, and take image classification as an exmaple for its performance.
+Tests showed that the proposed model outperforms the iGPT-L model without augmentment on the image dataset,
+the model achieved accuracy of $97.72\%~99.60\%$ on the CIFAR-10 image set,
+and accuracy of $98.27\%~98.95\%$ on the CIFAR-100 image set.
 

### 2020-10-13 A-BasicCommom/CVPR2021/cvpr_classification.tex
1.CVPR v0.3.0, thanks help from grammarly.

@@
   the classification model outperforms the Wide ResNet model and the linear-probe iGPT-L model,
-  and achieved an accuracy of $97.72\%~99.60\%$ on the CIFAR-10 image set, and an accuracy of $98.27\%~98.95\%$ on the CIFAR-100 image set.
+  and achieved an accuracy of $97.72\%\sim99.60\%$ on the CIFAR-10 image set, and an accuracy of $98.27\%\sim98.95\%$ on the CIFAR-100 image set.
 
@@
 %-------------------------------------------------------------------------
-\section{Per-pixel Encoder}
+\subsection{Approach}
+
+My approach consists of a pre-training state followed by a fine-tuning stage.
+In pre-training, I use BERT objectives and the sequence Transformer architecture to predict language tokens.
+
+\par Given an unlabeled dataset $\Bbb X$, the BERT objective samples a sub-sequence $\Bbb S \in \{C\}$,
+$C$ represents all possible tokens, and such that for each index $i \in \Bbb S$,
+there is independent probability $15\%$ of appearing in $\Bbb S$,
+name the token $M$ as the BERT mask.
+Train the language model by minimizing the BERT objective of the "masked" elements $x_M$
+conditioned on the "unmasked" ones $x_{\left[1,n\right]\backslash M}$.
+\[
+  \lambda = \mathop{\Bbb E}\limits_{x\sim\Bbb X} \mathop{\Bbb E}\limits_{M} \sum_{i\in S}{\bigl[-\log{p(x_i\mid x_{\left[1,n \right]\backslash M})\bigr]}}
+\]
+
+\par The transformer decoder takes the image pixels and meta characters sequence $x_1,\cdots,x_n$ and produces a $d$-dimensional
+embedding for each position.
+Then I use a fully connected layer as a non-linear function from embeddings to image class.
+The dropout layer and the Softmax layer are used for better transfer performance between the training and the test dataset.
+
+\subsection{Per-pixel Encoder}
 
 For the per-pixel image classification approach, for every RGB channel of pixel in a image,
-each pixel had its pixel-channel code, ranges from $0x00$ to $0xff$ for different colors.
+each pixel had its pixel-channel code, ranges from 0x00 to 0xff for different colors.
 Thus, taking these pixels in a image is identical to ASCII characters in a document.
@@
 
-\par I used RBTL3 and RoBERTa-wwm-ext-large pre-trained language model in two Chinese Judicial dataset, which have 2 and 4 main domains.
-The $Case-2$ dataset annotated civil and criminal cases, and the $Case-4$ dataset annotated by civil, criminal, intellectual property, and administrative cases.
-The $Case-2$ dataset has $19508$ training documents and $2000$ test documents, and the $Case-4$ dataset has $34789$ training documents and $2013$ test documents.
+\par I used RBTL3 and RoBERTa-wwm-ext-large pre-trained language model in two Chinese Judicial dataset, which have 2 and 4 classes.
+The \textit{Case-2} dataset annotated civil and criminal cases, and the \textit{Case-4} dataset annotated by civil, criminal, intellectual property, and administrative cases.
+The \textit{Case-2} dataset has $19508$ training documents and $2000$ test documents, and the \textit{Case-4} dataset has $34789$ training documents and $2013$ test documents.
 
@@
 
-\section{Image Classification Model}
+\subsection{Image Classification Model}
 
@@
 
-We design a simple classification models without too many layers, as Figure-1 shows.
+I design a simple classification models without too many layers, as Figure-1 shows.
 And use the CIFAR-10 and CIFAR-100 dataset as an example to show the architecture of the model.
@@
 
-\section{Image Classification Model}
+\section{Experiments and Results}
 
-\subsection{Experiments and Results}
+\subsection{Training}
 
-Use the proposed model, and we tried different pre-trained language models to see the impact on classification accuracy.
-From the table-2, from line 2 and line 4, for the same size of dataset with larger classes, it need more epochs and training time for the classification model.
-From line 2 and line 3, for the same RoBERTa language model with different numbers of transformer layers, 24 layers of transformers had better accuracy than 3 layers,
+As Cui \etal~\cite{cui2019pre} reported that the training of RBT3 language model was based on Devlin \etal's
+Chinese BERT-base language model and the training of RBTL3 and RoBERTa-large language model used randomized initialization.
+Moreover, the pre-trained Chinese language models use extra 5 billion training tokens comparing to Devlin \etal's 0.4 billion tokens.
+I use a batch size of 512 and train for $1\sim16$ epochs using AdamW with $\beta_1=0.99$, $\beta_2=0.999$, and weight decay of $10^{-8}$.
+I set the learning rate to $10^{-4}$ and no warmed up or decay are used.
+The dropout rate is $0.05$.
+
+\par When fine-tuning, I check the accuracy of the trained model on the test set, and stopped training when it converges on $10^{-3}\sim10^{-4}$.
+
+\subsection{Results}
+
+Use the proposed model, and I tried different pre-trained language models to see the impact on classification accuracy.
+From the table-2, for the same size of dataset with larger classes, it need more epochs and training time for the classification model.
+For the same RoBERTa language model with different numbers of transformer layers, 24 layers of transformers had better accuracy than 3 layers,
 however, its training cost grows for the larger language model.
-From line 3 and line 5, for the same fine-tuned language model, classes number has some impact on the accuracy,
+For the same fine-tuned language model, classes number has some impact on the accuracy,
 the less classes the dataset has, the more accuracy the model can achieve.
@@
 RBTL3  & CIFAR-10 & 1	&	97.72\% \\
-RoBERTa-wwm-ext-large  & CIFAR-10 & 6	&	99.60\% \\
+RoBERTa-large  & CIFAR-10 & 6	&	99.60\% \\
 RBTL3  & CIFAR-100 & 6  & 	98.27\% \\
-RoBERTa-wwm-ext-large & CIFAR-100 & 16 &	98.95\% \\
+RoBERTa-large & CIFAR-100 & 16 &	98.95\% \\
 \hline
@@
 \end{center}
-\caption{Comparision of accuracy of the pre-trained language models on the CIFAR-10 and CIFAR-100 datasets in the image classification task.}
+\caption{Comparision of accuracy of the pre-trained language models on the CIFAR-10 and CIFAR-100 datasets in the image classification task.
+RoBERTa-large is short for RoBERTa-wwm-ext-large.}
 \end{table}
@@
 
- Compare to iGPT-L's accuracy of 96.3\% on the unaugmented CIFAR-10 dataset and 82.8\% on the CIFAR-100 dataset, our models has preferable better results.
+ Compare to iGPT-L's accuracy of 96.3\% on the CIFAR-10 dataset without augmentation and 82.8\% on the CIFAR-100 dataset, our models has preferable better results.
 The reason that the model's outstanding performance lie in the large pre-trained data for BERT, on top of that fine-tuned by RoBERTa, and use extra language corpus of
@@
 
-This paper proposed a novel idea by using pre-trained language models for images representation, and take image classification as an exmaple for its performance.
-Tests showed that the proposed model outperforms the iGPT-L model without augmentment on the image dataset,
-the model achieved accuracy of $97.72\%~99.60\%$ on the CIFAR-10 image set,
-and accuracy of $98.27\%~98.95\%$ on the CIFAR-100 image set.
+This paper proposed a novel idea by using pre-trained language models for images representation, and take image classification as an example for its performance in Computer Vision tasks.
+Tests showed that the proposed model outperforms the iGPT-L model without augmentation on the image dataset,
+the model achieved accuracy of $97.72\%\sim99.60\%$ on the CIFAR-10 image set,
+and accuracy of $98.27\%\sim98.95\%$ on the CIFAR-100 image set.
 

### 2020-10-13 A-BasicCommom/CVPR2021/cvpr_classification.tex
1.CVPR v0.4.0, major revision.

@@
 These models achieved better performance in Chinese machine reading comprehension, Chinese document classification and other downstream natural language tasks.
+  He and Peng~\cite{he2017fine} combined vision stream and language stream as two parallel channels for extracting multi-source information in the imaege classification,
+and tested on the CUB-200-2011 image dataset and achieved $85.55\%$ by combining GoogLeNet~\cite{szegedy2015going} and CNN-RNN~\cite{reed2016learning}, the result outperformed many competitors.
 
@@
 conditioned on the "unmasked" ones $x_{\left[1,n\right]\backslash M}$.
-\[
+
+\begin{equation}
   \lambda = \mathop{\Bbb E}\limits_{x\sim\Bbb X} \mathop{\Bbb E}\limits_{M} \sum_{i\in S}{\bigl[-\log{p(x_i\mid x_{\left[1,n \right]\backslash M})\bigr]}}
-\]
+\end{equation}
 
@@
 The model architecture has seven functional layers:
+
 \begin{itemize}
@@
 and get the encoded representation of the token $\textbf{[CLS]}$ as the images' language model embeddings.
-In the Feature-Extraction layer, a combination of one dropout layer, one fully connected layer, and one softmax layer is used.
+In the Feature-Extraction layer, a combination of one dropout layer, one fully connected layer, and one softmax layer, as equation-2, is used.
 In the Output layer, the classification label of the image is feed in the model.
 
+\begin{equation}
+  \sigma(\textbf{z})_j = {e^{\textbf{z}_j} \over {\sum_{k=1}^{\textit{K}} e^{\textbf{z}_k}}}, j=1,\cdots,\textit{K}.
+\end{equation}
 %-------------------------------------------------------------------------
@@
 As Cui \etal~\cite{cui2019pre} reported that the training of RBT3 language model was based on Devlin \etal's
-Chinese BERT-base language model and the training of RBTL3 and RoBERTa-large language model used randomized initialization.
 Moreover, the pre-trained Chinese language models use extra 5 billion training tokens comparing to Devlin \etal's 0.4 billion tokens.
@@
 \par When fine-tuning, I check the accuracy of the trained model on the test set, and stopped training when it converges on $10^{-3}\sim10^{-4}$.
+
+\par The experiment was performed on a Google Cloud TPU v3, with 32GB of RAM, and 8 chips with 16GB of high speed of memory each,
+which can provide 420 tera-flops of computation capability.
 

### 2020-10-13 A-BasicCommom/CVPR2021/cvpr.tex
1.follow CVPR call for paper, remove arXiv references.

@@
 Firstly, compared to Floyd-Warshall algorithm implemented on CPU, the Alon \etal algorithm implementation with matrix multiplication of block cache optimization on GPU has a time performance improvement, see Table 1.
-$Power-LawBound_{a-f}$ shows that using different libraries on CPU/GPU, the proposed algorithm has significant performance improvement over Alon \etal algorithm.
+$Power-LawBound(a-f)$ shows that using different libraries on CPU/GPU, the proposed algorithm has significant performance improvement over Alon \etal algorithm.
 
@@
 Floyd-Warshall~\cite{floyd1962algorithm,warshall1962theorem}  &	1055880s \\
-Alon \etal          &	594.7s \\
-$Power-LawBound_a$ 	&	427.9s \\
-$Power-LawBound_b$	&	328.4s \\
-$Power-LawBound_c$	&	95.0s \\
-$Power-LawBound_d$	&	45.0s \\
-$Power-LawBound_e$	&	19.32s \\
-$Power-LawBound_f$	&	15.98s \\
+Alon \etal~\cite{alon1997exponent}  &	594.7s \\
+$Power-LawBound(a)$ &	427.9s \\
+$Power-LawBound(b)$	&	328.4s \\
+$Power-LawBound(c)$	&	95.0s \\
+$Power-LawBound(d)$	&	45.0s \\
+$Power-LawBound(e)$	&	19.32s \\
+$Power-LawBound(f)$	&	15.98s \\
 \hline

### 2020-10-13 A-BasicCommom/CVPR2021/cvpr_classification.tex
1.follow CVPR call for paper, remove arXiv references.

@@
   However, it started to flourish in natural language processing domain since Mikolov \etal~\cite{mikolov2013distributed} had proposed Word2Vec.
-  Not long before Devin \etal~\cite{devlin2018bert}'s BERT language model dominates in most frequent used tasks in natural language processing,
+  Not long before Devin \etal~\cite{devlin2019bert}'s BERT language model dominates in most frequent used tasks in natural language processing,
   which is close resemble of Vicent \etal~\cite{vincent2008extracting}'s Denoising Autoencoder model, which was initially designed for images.
@@
 Several years later, a lot of variants of AlexNet had been proposed by researchers and the accuracy of ImageNet had been greatly improved, \eg ZFNet~\cite{zeiler2014visualizing}, VGG~\cite{simonyan2014very}, GoogLeNet~\cite{szegedy2015going}, ResNet~\cite{he2016deep},
-Wide-ResNet~\cite{zagoruyko2016wide}, ResNeXt~\cite{xie2017aggregated}, inception-ResNet-v2~\cite{szegedy2016inception}, DenseNet~\cite{huang2016deep}.
+ ResNeXt~\cite{xie2017aggregated}, inception-ResNet-v2~\cite{szegedy2016inception}, DenseNet~\cite{huang2016deep}.
   Lu and Weng~\cite{lu2007survey} concluded that for multi-source image classification task, additional information such as signatures, texture, context and ancillary data can be combined to achieve better performance.
 And it is difficult in handling the dichotomy between pixels and natural language texts in a single model.
-  Cui \etal~\cite{cui2019pre, cui2020revisiting} proposed several whole-word-masking pre-trained Chinese language models,
-which are improved versions of BERT~\cite{devlin2018bert} and RoBERTa~\cite{liu2019roberta} pre-trained language models, namely RBT3, RBTL3, and RoBERTa-wwm-ext-large.
+  Cui \etal~\cite{cui2020revisiting} proposed several whole-word-masking pre-trained Chinese language models,
+which are improved versions of BERT~\cite{devlin2019bert} pre-trained language models, namely RBT3, RBTL3, and RoBERTa-wwm-ext-large.
 These models achieved better performance in Chinese machine reading comprehension, Chinese document classification and other downstream natural language tasks.
-  He and Peng~\cite{he2017fine} combined vision stream and language stream as two parallel channels for extracting multi-source information in the imaege classification,
+  He and Peng~\cite{he2017fine} combined vision stream and language stream as two parallel channels for extracting multi-source information in the imaege classification task,
 and tested on the CUB-200-2011 image dataset and achieved $85.55\%$ by combining GoogLeNet~\cite{szegedy2015going} and CNN-RNN~\cite{reed2016learning}, the result outperformed many competitors.
@@
 \eg support vector machines and conditional random field, in many dataset such as, movie reviews, Stanford sentiment treebank, and TREC question.
-Adhikari \etal~\cite{adhikari2019docbert} showed the BERT and BERT-large model had achieved higher accuracy in the Routers, IMDB, and Yelp dataset which classification ranges from 5 to 90.
 Cui \etal's pre-trained language model, namely RBT3, RBTL3, and RoBERTa-wwm-ext-large, had improved performances over many other machine learning algorithms.
@@
 
-As Cui \etal~\cite{cui2019pre} reported that the training of RBT3 language model was based on Devlin \etal's
+As Cui \etal~\cite{cui2020revisiting} reported that the training of RBT3 language model was based on Devlin \etal's
 Moreover, the pre-trained Chinese language models use extra 5 billion training tokens comparing to Devlin \etal's 0.4 billion tokens.

### 2020-10-13 A-BasicCommom/CVPR2021/cvpr_vision.tex
1.follow CVPR call for paper, remove arXiv references.

@@
   and non-linear capability of deep FC layer for movie text sentiments and other characteristics.
-  The proposed model accuracy is 14\% higher than Zhou \etal's model.
+  The proposed model accuracy is 14\% higher than Shi \etal's model.
 
@@
   all-pairs shortest path, social network text sentiments, and actors' artisticcontribution characteristics,
-  as a result, it is 14\% higher in accuracy than Zhou \etal ~\cite{zhou2015c}'s model.
+  as a result, it is 14\% higher in accuracy than Shi \etal ~\cite{shi2019c}'s model.
 
@@
 
-  Zhou \etal~\cite{zhou2015c} proposed a C-LSTM classification model, using single-layer CNN for extracting the high-order dimensional representation of text,
+  Shi \etal~\cite{shi2019c} proposed a C-LSTM classification model, using single-layer CNN for extracting the high-order dimensional representation of text,
   and connecting to LSTM layers for sentence representation, the trained neural network model has an accuracy of 87.8\%.

### 2020-10-13 A-BasicCommom/CVPR2021/cvpr_vision.tex
1.remove arXiv ref according to CVPR policy.

@@
   and non-linear capability of deep FC layer for movie text sentiments and other characteristics.
-  The proposed model accuracy is 14\% higher than Shi \etal's model.
+  The proposed model accuracy is 14\% higher than Read \etal's model.
 
@@
   all-pairs shortest path, social network text sentiments, and actors' artisticcontribution characteristics,
-  as a result, it is 14\% higher in accuracy than Shi \etal ~\cite{shi2019c}'s model.
+  as a result, it is 14\% higher in accuracy than Read \etal ~\cite{read2016earning}'s model.
 
@@
 
-  Shi \etal~\cite{shi2019c} proposed a C-LSTM classification model, using single-layer CNN for extracting the high-order dimensional representation of text,
-  and connecting to LSTM layers for sentence representation, the trained neural network model has an accuracy of 87.8\%.
+  Read \etal ~\cite{read2016earning} proposed a CNN-RNN classification model, using CNN layers for extracting the high-order dimensional representation of images,
+  and connecting to LSTM layers for description representation, the trained neural network model has accuracy of 56.8\% on Caltech-UCSD Birds dataset and accuracy of 65.6\% on Flowers dataset.
 
@@
 Compared to Qiu and Tang~\cite{qiu2018microblog}'s logistic regression model on sentiments and twitter index algorithm's 95.71\% determination of coefficient,
-The Cartisticmodel in this paper has a determination of coefficient of 98.58\% which has a 2.87\% improvement.
+The model in this paper has a determination of coefficient of 98.58\% which has a 2.87\% improvement.
 
@@
 The accuracy of the binary classification model on the training set reached 99.61\%, the accuracy on the test set is 75\%.
-Compared to Zhou \etal model, see Table 2, the proposed FC-GRU-CNN model converges on the training set and achieves better prediction results on the test set.
+Compared to Read \etal model, see Table 2, the proposed FC-GRU-CNN model converges on the training set and achieves better prediction results on the test set.
 Therefore, it can provide decision-making advice in the task of selecting suitable actors for to-be-cast film,
@@
 \hline\hline
-Zhou \etal  & 61.54\% \\
+Read \etal  & 61.54\% \\
 This paper & 75.0\% \\
@@
 According to the NEN(Non-Euclidean Net) box-office prediction model, this paper discussed the relationship between the movie meta-data, Sina Weibo text sentiments, social relationship representations, network characteristics, and actors' artistic contribution in detail.
-I proposed an FC-GRU-CNN box-office prediction model, and tested on a dataset of $1296$ movies released in China mainland from 2011 to 2015, compared to Zhou \etal's model, accuracy improves 14\%.
+I proposed an FC-GRU-CNN box-office prediction model, and tested on a dataset of $1296$ movies released in China mainland from 2011 to 2015, compared to Read \etal's model, accuracy improves 14\%.
 

### 2020-10-13 A-BasicCommom/CVPR2021/cvpr.tex
1.CVPR v0.5.0, fix typos.

@@
 
-\def\cvprPaperID{6666} % *** Enter the CVPR Paper ID here
+\def\cvprPaperID{6666} % \times \times \times  Enter the CVPR Paper ID here
 \def\confYear{CVPR 2021}
@@
 On the actors' social network, this paper implements Strassen block matrix multiplication, Copper-Winograd block matrix multiplication, and OpenBLAS matrix multiplication.
-On the computer hardware, compared the $8508*8508$ matrix multiplication time-cost.
+On the computer hardware, compared the $8508\times 8508$ matrix multiplication time-cost.
 The block matrix multiplication based on Strassen and Coppersmith-Winograd takes 6 seconds for one iteration of matrix multiplication, and with the OpenBLAS library it takes only 4 seconds.
@@
 I present the corresponding nodes counts, diameters, and logarithm of diameters in Table 1, from the observation there is formula (1):
-In social networks, the number of nodes $n$, with cache block size $B*B$, according to the formula (9-10), the matrix product calculation iteration times does not exceed the number of $\lceil{\log{\Bbb D}}\rceil$, recall that Lam \etal proved that matrix multiplication time-bound is \(O({2n^3 \over \Bbb B}+{n^2})\),
-thus Alon \etal algorithm time-bound is \(O(\log{\Bbb D}2n^3\over \Bbb B)\) with cache block size of $\Bbb B$, use the equation (1) result, time-bound is \(O(\log(\log{N})2n^3\over \Bbb B)\).
+In social networks, the number of nodes $n$, with cache block size $B\times B$, according to the formula (9-10), the matrix product calculation iteration times does not exceed the number of $\lceil{\log{\Bbb D}}\rceil$, recall that Lam \etal proved that matrix multiplication time-bound is \(O({2n^3 \over \Bbb B}+{n^2})\),
+thus Alon \etal algorithm time-bound is \(O({\log{\Bbb D}2n^3\over{ \Bbb B}})\) with cache block size of $\Bbb B$, use the equation (1) result, time-bound is \(O({\log(\log{N})2n^3\over \Bbb B})\).
 With the arithmetic limitation on the floating-point operation, \eg take a network with nodes number of $N<10^{308}$
 as shown in Table 1, see that the shortest path calculation iterations time is no larger than $\log{\Bbb D} \approx \log(\log{N})<7$, that is, the number of calculation iterations does not exceed the magic number $7$,
-bringing a stronger time-bound of \(O(14n^3\over \Bbb B)\).
-In other words, with the floating-point operation accuracy limitation on computer hardware and complex networks scale-free characteristics, all-pairs shortest path algorithm time-bound is \(O(14n^3\over \Bbb B)\), for $\Bbb B$ is a constant, thus, for simpler representation the time-bound is \(O(14n^3)\).
+bringing a stronger time-bound of \(O({14n^3\over {\Bbb B}})\).
+In other words, with the floating-point operation accuracy limitation on computer hardware and complex networks scale-free characteristics, all-pairs shortest path algorithm time-bound is \(O({14n^3\over \Bbb B})\), for $\Bbb B$ is a constant, thus, for simpler representation the time-bound is \(O(14n^3)\).
 
@@
 
-Definition 1 (Outer Product Matrix Multiplication) Given matrices \(\Bbb A \in \Bbb R^{m*r}\), \(\Bbb B \in \Bbb R^{r*n}\) and \(\Bbb C \in \Bbb R^{m*n}\), the outer product is:
+Definition 1 (Outer Product Matrix Multiplication) Given matrices \(\Bbb A \in \Bbb R^{m\times r}\), \(\Bbb B \in \Bbb R^{r\times n}\) and \(\Bbb C \in \Bbb R^{m\times n}\), the outer product is:
 \begin{equation}
@@
 
-Given two vectors \(\textsc x\), \(\textsc y\), and matrix \(\Bbb A\), having \(\Bbb A \in \Bbb R^{m*n}\), \(\textsc x \in \Bbb R^{m}\) and \(\textsc y \in \Bbb R^{n}\) the outer product \(\bullet\) is defined by:
+Given two vectors \(\textsc x\), \(\textsc y\), and matrix \(\Bbb A\), having \(\Bbb A \in \Bbb R^{m\times n}\), \(\textsc x \in \Bbb R^{m}\) and \(\textsc y \in \Bbb R^{n}\) the outer product \(\bullet\) is defined by:
 \begin{equation}
-a_{ij} = a_{ij} + x_i * y_j, i \in (1,m), j \in (1,n)
+a_{ij} = a_{ij} + x_i \times  y_j, i \in (1,m), j \in (1,n)
 \end{equation}
 
-Definition 2 (Distance Product Matrix Multiplication) Given matrices \(\Bbb A \in \Bbb R^{m*r}\), \(\Bbb B \in \Bbb R^{r*n}\) and \(\Bbb C \in \Bbb R^{m*n}\), the distance product is:
+Definition 2 (Distance Product Matrix Multiplication) Given matrices \(\Bbb A \in \Bbb R^{m\times r}\), \(\Bbb B \in \Bbb R^{r\times n}\) and \(\Bbb C \in \Bbb R^{m\times n}\), the distance product is:
 \begin{equation}
@@
 
-Given two vectors \(\textsc x\), \(\textsc y\), and matrix \(\Bbb A\), having \(\Bbb A \in \Bbb R^{m*n}\), \(\textsc x \in \Bbb R^{m}\) and \(\textsc y \in \Bbb R^{n}\) the distance product \(\odot\) is defined by:
+Given two vectors \(\textsc x\), \(\textsc y\), and matrix \(\Bbb A\), having \(\Bbb A \in \Bbb R^{m\times n}\), \(\textsc x \in \Bbb R^{m}\) and \(\textsc y \in \Bbb R^{n}\) the distance product \(\odot\) is defined by:
 \begin{equation}
@@
     $L^{(2m)}\leftarrow \Bbb C$\;
-    $m\leftarrow 2*m$\;
+    $m\leftarrow 2\times m$\;
   }

### 2020-10-13 A-BasicCommom/CVPR2021/cvpr_classification.tex
1.CVPR v0.5.0, fix typos.

@@
   the classification model outperforms the Wide ResNet model and the linear-probe iGPT-L model,
-  and achieved an accuracy of $97.72\%\sim99.60\%$ on the CIFAR-10 image set, and an accuracy of $98.27\%\sim98.95\%$ on the CIFAR-100 image set.
+  and achieved an accuracy of $99.60\%\sim99.74\%$ on the CIFAR-10 image set, and an accuracy of $98.27\%\sim98.95\%$ on the CIFAR-100 image set.
 
@@
 \hline\hline
-RBT3   & CIFAR-10 & 1	&	84.89\% \\
-RBTL3  & CIFAR-10 & 1	&	97.72\% \\
+RBT3   & CIFAR-10 & 1	&	99.74\% \\
+RBTL3  & CIFAR-10 & 6	&	99.72\% \\
 RoBERTa-large  & CIFAR-10 & 6	&	99.60\% \\
@@
 Tests showed that the proposed model outperforms the iGPT-L model without augmentation on the image dataset,
-the model achieved accuracy of $97.72\%\sim99.60\%$ on the CIFAR-10 image set,
+the model achieved accuracy of $99.60\%\sim99.74\%$ on the CIFAR-10 image set,
 and accuracy of $98.27\%\sim98.95\%$ on the CIFAR-100 image set.

### 2020-10-13 A-BasicCommom/CVPR2021/cvpr_vision.tex
1.CVPR v0.5.0, fix typos.

@@
   all-pairs shortest path, social network text sentiments, and actors' artisticcontribution characteristics,
-  as a result, it is 14\% higher in accuracy than Read \etal ~\cite{read2016earning}'s model.
+  as a result, it is 14\% higher in accuracy than Read \etal ~\cite{read2016learning}'s model.
 
@@
 
-  Read \etal ~\cite{read2016earning} proposed a CNN-RNN classification model, using CNN layers for extracting the high-order dimensional representation of images,
+  Read \etal ~\cite{read2016learning} proposed a CNN-RNN classification model, using CNN layers for extracting the high-order dimensional representation of images,
   and connecting to LSTM layers for description representation, the trained neural network model has accuracy of 56.8\% on Caltech-UCSD Birds dataset and accuracy of 65.6\% on Flowers dataset.
@@
 For each edge $e\in \Bbb E$, the ordered pair is $e=(u,v)$, $u,v \in \Bbb V$ and the weight is $A_{ij}$.
-A network can be represented as an adjacent matrix, $A\in \Bbb R^{(n*n)}$, and the goal of network embedding is to learn an all-pairs representation, $U\in \Bbb R^{(n*m)}$, $m < n$, where $m$ is an embedding dimension.
+A network can be represented as an adjacent matrix, $A\in \Bbb R^{(n\times n)}$, and the goal of network embedding is to learn an all-pairs representation, $U\in \Bbb R^{(n\times m)}$, $m < n$, where $m$ is an embedding dimension.
 
@@
 For each edge $e\in \Bbb E$, the ordered pair is $e=(u,v)$, $u,v \in \Bbb V$ and the weight is $A_{ij}$.
-A network can be represented as an adjacent matrix, $A\in \Bbb R^{(n*n)}$, and the goal of the shortest path network embedding is to learn all-pairs shortest path representation, $U\in \Bbb R^{(n*n)}$, where $n$ is an embedding dimension.
+A network can be represented as an adjacent matrix, $A\in \Bbb R^{(n\times n)}$, and the goal of the shortest path network embedding is to learn all-pairs shortest path representation, $U\in \Bbb R^{(n\times n)}$, where $n$ is an embedding dimension.
 

### 2020-10-14 A-BasicCommom/CVPR2021/cvpr.tex
1.CVPR v0.5.0, fix typos.

@@
 On the computer hardware, compared the $8508\times 8508$ matrix multiplication time-cost.
-The block matrix multiplication based on Strassen and Coppersmith-Winograd takes 6 seconds for one iteration of matrix multiplication, and with the OpenBLAS library it takes only 4 seconds.
+The block matrix multiplication based on Strassen and Coppersmith-Winograd takes 6 seconds for one iteration of matrix multiplication, and with the OpenBLAS library, it takes only 4 seconds.
 The performance of optimized cache block matrix multiplication, such as the OpenBLAS matrix computation library, is higher than Strassen and Copper-Winograd block matrix multiplication algorithm.
@@
 bringing a stronger time-bound of \(O({14n^3\over {\Bbb B}})\).
-In other words, with the floating-point operation accuracy limitation on computer hardware and complex networks scale-free characteristics, all-pairs shortest path algorithm time-bound is \(O({14n^3\over \Bbb B})\), for $\Bbb B$ is a constant, thus, for simpler representation the time-bound is \(O(14n^3)\).
+In other words, with the floating-point operation accuracy limitation on computer hardware and complex networks scale-free characteristics, all-pairs shortest path algorithm time-bound is \(O({14n^3\over \Bbb B})\), for $\Bbb B$ is a constant, thus, for simpler representation, the time-bound is \(O(14n^3)\).
 
@@
 Obviously, the result reuse method saves $n-2-\lceil{log_2(n-1)}\rceil$ times of matrix multiplication.
-Observe the shortest path calculation process of the actors' social network, the adjacent matrix is shown in Figure 1a, and the change of result in each iteration is shown in Figure 1b-d, the shortest path result matrix converges gradually, each element stabilizes as iterations goes.
+Observe the shortest path calculation process of the actors' social network, the adjacent matrix is shown in Figure 1a, and the change of result in each iteration is shown in Figure 1b-d, the shortest path result matrix converges gradually, each element stabilizes as iterations go.
 

### 2020-10-14 A-BasicCommom/CVPR2021/cvpr_classification.tex
1.CVPR v0.5.0, fix typos.

@@
   the classification model outperforms the Wide ResNet model and the linear-probe iGPT-L model,
-  and achieved an accuracy of $99.60\%\sim99.74\%$ on the CIFAR-10 image set, and an accuracy of $98.27\%\sim98.95\%$ on the CIFAR-100 image set.
+  and achieved accuracy of $99.60\%\sim99.74\%$ on the CIFAR-10 image set and accuracy of $98.27\%\sim98.95\%$ on the CIFAR-100 image set.
 
@@
   thus, can be omitted in some cases.
-  However, it started to flourish in natural language processing domain since Mikolov \etal~\cite{mikolov2013distributed} had proposed Word2Vec.
-  Not long before Devin \etal~\cite{devlin2019bert}'s BERT language model dominates in most frequent used tasks in natural language processing,
+  However, it started to flourish the natural language processing domain since Mikolov \etal~\cite{mikolov2013distributed} had proposed Word2Vec.
+  Not long before Devin \etal~\cite{devlin2019bert}'s BERT language model dominates in most frequently used tasks in natural language processing,
   which is close resemble of Vicent \etal~\cite{vincent2008extracting}'s Denoising Autoencoder model, which was initially designed for images.
-  Pre-training process become one of the most important procedures in deep learning.
+  The pre-training process becomes one of the most important procedures in deep learning.
 
@@
 
-  Chen \etal~\cite{chen2020generative} trained image representation by sequence Transformers and tested on CIFAR-10 to show its outperforming to Wide-ResNet
-which inspired from unsupervised natural language representation learning.
-  Wang \etal~\cite{wang2019development} reviewed that convolutional neural networks had been proposed in 1960s, and had its implementation in 1980s,
+  Chen \etal~\cite{chen2020generative} trained image representation by sequence Transformers and tested on CIFAR-10 to show it is outperforming to Wide-ResNet
+which was inspired by unsupervised natural language representation learning.
+  Wang \etal~\cite{wang2019development} reviewed that convolutional neural networks had been proposed in the 1960s, and had its implementation in the 1980s,
 and until LeCun \etal~\cite{lecun1990handwritten}'s first experiment on handwritten digit recognition, CNN's great potential had been revealed.
@@
  ResNeXt~\cite{xie2017aggregated}, inception-ResNet-v2~\cite{szegedy2016inception}, DenseNet~\cite{huang2016deep}.
-  Lu and Weng~\cite{lu2007survey} concluded that for multi-source image classification task, additional information such as signatures, texture, context and ancillary data can be combined to achieve better performance.
+  Lu and Weng~\cite{lu2007survey} concluded that for the multi-source image classification tasks, additional information such as signatures, texture, context, and ancillary data can be combined to achieve better performance.
 And it is difficult in handling the dichotomy between pixels and natural language texts in a single model.
@@
 which are improved versions of BERT~\cite{devlin2019bert} pre-trained language models, namely RBT3, RBTL3, and RoBERTa-wwm-ext-large.
-These models achieved better performance in Chinese machine reading comprehension, Chinese document classification and other downstream natural language tasks.
-  He and Peng~\cite{he2017fine} combined vision stream and language stream as two parallel channels for extracting multi-source information in the imaege classification task,
+These models achieved better performance in Chinese machine reading comprehension, Chinese document classification, and other downstream natural language tasks.
+  He and Peng~\cite{he2017fine} combined the vision stream and language stream as two parallel channels for extracting multi-source information in the image classification task,
 and tested on the CUB-200-2011 image dataset and achieved $85.55\%$ by combining GoogLeNet~\cite{szegedy2015going} and CNN-RNN~\cite{reed2016learning}, the result outperformed many competitors.
@@
 
-Three of the most popular approaches for image classification task are per-pixel, subpixel, and heterogeneous.
-Lu and Weng found that, for per-pixel approach, non-parametric classifiers, \eg neural networks, support vector machines and decision trees,
-are most well known algorithms for their performance and generalization advantages in late 1990s and 2000s.
+Three of the most popular approaches for image classification tasks are per-pixel, subpixel, and heterogeneous.
+Lu and Weng found that, for per-pixel approach, non-parametric classifiers, \eg neural networks, support vector machines, and decision trees,
+are the most well-known algorithms for their performance and generalization advantages in the late 1990s and 2000s.
 Fern{\'a}ndez \etal~\cite{fernandez2014we} compared different classifiers in small datasets, and they found that the random forest algorithm ranks first among the 179 classifiers.
@@
 
-For the per-pixel image classification approach, for every RGB channel of pixel in a image,
+For the per-pixel image classification approach, for every RGB channel of pixels in an image,
 each pixel had its pixel-channel code, ranges from 0x00 to 0xff for different colors.
-Thus, taking these pixels in a image is identical to ASCII characters in a document.
-Generality speaking, the performance of the pre-trained language models achieved in document classification task, can be transferred to image classification naturally.
+Thus, taking these pixels in an image is identical to ASCII characters in a document.
+Generality speaking, the performance of the pre-trained language models achieved in the document classification tasks, can be transferred to image classification naturally.
 
 \par Recall that Kim~\cite{kim2014convolutional} had proved that unsupervised pre-trained language model $word2vec$ and CNN outperformed many other machine learning algorithms,
-\eg support vector machines and conditional random field, in many dataset such as, movie reviews, Stanford sentiment treebank, and TREC question.
+\eg support vector machines and conditional random field, in many datasets such as movie reviews, Stanford sentiment treebank, and TREC question.
 Cui \etal's pre-trained language model, namely RBT3, RBTL3, and RoBERTa-wwm-ext-large, had improved performances over many other machine learning algorithms.
@@
 
-\par I used RBTL3 and RoBERTa-wwm-ext-large pre-trained language model in two Chinese Judicial dataset, which have 2 and 4 classes.
+\par I used RBTL3 and RoBERTa-wwm-ext-large pre-trained language model in two Chinese Judicial datasets, which has 2 and 4 classes.
 The \textit{Case-2} dataset annotated civil and criminal cases, and the \textit{Case-4} dataset annotated by civil, criminal, intellectual property, and administrative cases.
@@
 
-\par From table-1, by combining pre-trained language model with fully connected layer as the document classification model,
+\par From table-1, by combining the pre-trained language model with fully connected layer as the document classification model,
 the test accuracy exceeds the other popular machine learning algorithms.
-Therefore, the pixel channels of image can be properly represented by these pre-trained language models.
+Therefore, the pixel channels of an image can be properly represented by these pre-trained language models.
 
@@
 
-I design a simple classification models without too many layers, as Figure-1 shows.
+I design simple classification models without too many layers, as Figure-1 shows.
 And use the CIFAR-10 and CIFAR-100 dataset as an example to show the architecture of the model.
@@
 
-\par The CIFAR-10 dataset contains 60000 colour images with a resolution of 32x32 in 10 classes, and the CIFAR-100 dataset has 100 classes containing 600 images each.
+\par The CIFAR-10 dataset contains 60000 color images with a resolution of 32x32 in 10 classes, and the CIFAR-100 dataset has 100 classes containing 600 images each.
 Encode the image by the sequence of RGB channel values, in the order of Red-channel, Green-channel, and Blue-channel,
-then encode other meta-data if provided, as a sequence of ASCII character.
-In the Concat layer, the pixel-channel value and meta data are concatenated, put a special token of $\textbf{[CLS]}$ at the start,
-and put a $\textbf{[SEP]}$ token between channel vules and meta values, put a special token of $\textbf{[SEP]}$ at the end.
-In the Trim layer, due to the limit on the max sequence of BERT language model, sequence larger than $512$ need to be trimmed before sending to BERT model.
-Keep the first 256 characters and last 256 characters of the concatenated sequence, trimmed result contrains the first 255 red-channel value,
+then encode other meta-data if provided, as a sequence of ASCII characters.
+In the Concat layer, the pixel-channel value and metadata are concatenated, put a special token of $\textbf{[CLS]}$ at the start,
+and put a $\textbf{[SEP]}$ token between channel values and metadata, put a special token of $\textbf{[SEP]}$ at the end.
+In the Trim layer, due to the limit on the max sequence of the BERT language model, a sequence larger than $512$ needs to be trimmed before sending it to the BERT model.
+Keep the first 256 characters and last 256 characters of the concatenated sequence, trimmed result contains the first 255 red-channel value,
 some blue-channel value, and all the meta value in common cases.
@@
 \end{equation}
+
+\subsection{The Mask Token for Test}
+
+\par It is intuitive for the model to use both the channel values and the metadata during the training phase.
+For the CIFAR-10 and CIFAR-100 dataset, the metadata is the filename of the images, which can be treated as the supervised description of the image.
+Peek some the filenames, \eg \textit{wagon\_s\_001343.png}, \textit{banana\_boat\_s\_001615.png}, and \textit{delivery\_truck\_s\_001529.png},
+and it is beneficial for the classification model to understand the supervised descriptive information for the image.
+
+\par However, in the test phase, if feeding the metadata to the model, people might argue that the model learns only the mapping function from
+the metadata, which is the filename in this case, to the image class
+which makes it is unfair to compare the performance with other image classification models.
+Thus, to be more objective and fair, I add a preprocess for the metadata in the test phase, using the $\textbf{[MASK]}$ token to replace each
+ASCII character of the filename then feeds into the model to do the inference.
+
+\par Recall that the $\textbf{[MASK]}$ token in the BERT language model is a special token which can be used to trim the vocabulary size,
+and gives the token-recovery capability to the downstream task model.
+
 %-------------------------------------------------------------------------
@@
 
-As Cui \etal~\cite{cui2020revisiting} reported that the training of RBT3 language model was based on Devlin \etal's
+As Cui \etal~\cite{cui2020revisiting} reported that the training of the RBT3 language model was based on Devlin \etal's
 Moreover, the pre-trained Chinese language models use extra 5 billion training tokens comparing to Devlin \etal's 0.4 billion tokens.
@@
 
-\par When fine-tuning, I check the accuracy of the trained model on the test set, and stopped training when it converges on $10^{-3}\sim10^{-4}$.
+\par When fine-tuning, I check the accuracy of the trained model on the test set and stopped training when it converges on $10^{-3}\sim10^{-4}$.
 
-\par The experiment was performed on a Google Cloud TPU v3, with 32GB of RAM, and 8 chips with 16GB of high speed of memory each,
+\par The experiment was performed on a Google Cloud TPU v3, with 32GB of RAM, and 8 chips with 16GB of the high speed of memory each,
 which can provide 420 tera-flops of computation capability.
@@
 Use the proposed model, and I tried different pre-trained language models to see the impact on classification accuracy.
-From the table-2, for the same size of dataset with larger classes, it need more epochs and training time for the classification model.
+From the table-2, for the same size of a dataset with larger classes, it needs more epochs and training time for the classification model.
 For the same RoBERTa language model with different numbers of transformer layers, 24 layers of transformers had better accuracy than 3 layers,
@@
 For the same fine-tuned language model, classes number has some impact on the accuracy,
-the less classes the dataset has, the more accuracy the model can achieve.
+the fewer classes the dataset has, the more accurate results the model can achieve.
 
@@
 \hline\hline
-RBT3   & CIFAR-10 & 1	&	99.74\% \\
+RBT3   & CIFAR-10 & 6	&	99.74\% \\
 RBTL3  & CIFAR-10 & 6	&	99.72\% \\
@@
 
- Compare to iGPT-L's accuracy of 96.3\% on the CIFAR-10 dataset without augmentation and 82.8\% on the CIFAR-100 dataset, our models has preferable better results.
-The reason that the model's outstanding performance lie in the large pre-trained data for BERT, on top of that fine-tuned by RoBERTa, and use extra language corpus of
+ Compare to iGPT-L's accuracy of 96.3\% on the CIFAR-10 dataset without augmentation and 82.8\% on the CIFAR-100 dataset, our models have preferable better results.
+The reason that the model's outstanding performance lies in the large pre-trained data for BERT, on top of that fine-tuned by RoBERTa, and use of extra language corpus of
 $5.4$ billions of tokens of wiki data and other resources.
-The transformers in the pre-trained language models use multiple layers for representing images, and maybe used in other Computer Vision task, \eg object detection, gesture prediction.
+The transformers in the pre-trained language models use multiple layers for representing images and may be used in other Computer Vision task, \eg object detection, gesture prediction.
 
@@
 
-This paper proposed a novel idea by using pre-trained language models for images representation, and take image classification as an example for its performance in Computer Vision tasks.
+TThis paper proposed a novel idea by using pre-trained language models for image representation and take image classification as an example of its performance in Computer Vision tasks.
 Tests showed that the proposed model outperforms the iGPT-L model without augmentation on the image dataset,

### 2020-10-14 A-BasicCommom/CVPR2021/cvpr_vision.tex
1.CVPR v0.5.0, fix typos.

@@
   In the film industry, visualizing actor stars' social media for analyzing audience intention towards movies is essential to movie producers.
-  However, non-Euclidean social media is hard to analyze, I propose an FC-GRU-CNN architecture, also named as \underline{N}on-\underline{E}uclidean \underline{N}et, for social media visualization.
-  On the analysis of social media , social relationship representations, network characteristics and media sentiments are key factors.
-  FC-GRU-CNN architecture exploits the long-term memory ability of GRU layer in long sequences of film cast,
-  the mapping ability of CNN layer in retrieving all-pairs shortest path feature of the actors' social relationship,
+  However, non-Euclidean social media is hard to analyze, I propose an FC-GRU-CNN architecture, named as \underline{N}on-\underline{E}uclidean \underline{N}et, for social media visualization.
+  On the analysis of social media, social relationship representations, network characteristics and media sentiments are key factors.
+  FC-GRU-CNN architecture exploits the long-term memory ability of the GRU layer in long sequences of film cast,
+  the mapping ability of the CNN layer in retrieving all-pairs shortest path feature of the actors' social relationship,
   and non-linear capability of deep FC layer for movie text sentiments and other characteristics.
@@
   it is easy to get the priority of each characteristic by analysis of feature importance,
-  the existing prediction algorithm only makes use of the film meta-data, lacks the study on the social network characteristics of the actors,
+  the existing prediction algorithm only makes use of the film metadata, lacks the study on the social network characteristics of the actors,
   though the traditional explanation of the film box-office prediction algorithm is sufficing, however, the prediction accuracy is not satisfactory.
-  This paper presents a model, named FC-GRU-CNN, for movie box-office prediction, combining characteristics of film meta-data, actors' social network measurement,
-  all-pairs shortest path, social network text sentiments, and actors' artisticcontribution characteristics,
+  This paper presents a model, named FC-GRU-CNN, for movie box-office prediction, combining characteristics of film metadata, actors' social network measurement,
+  all-pairs shortest path, social network text sentiments, and actors' artistic contribution characteristics,
   as a result, it is 14\% higher in accuracy than Read \etal ~\cite{read2016learning}'s model.
@@
 
-%\subsection{Random Forest}
-
 \subsection{Support Vector Machines}
 
-  Jiang and Wang~\cite{jiang2018predicting} collected 34 high-grossing films from 2015 to 2017, using 10 features, such as film meta-data, director awards, and actor awards, then I used voting feature selection algorithms to select important features,
-  training SVM models for film box-office and user-comment-score prediction.
+  Jiang and Wang~\cite{jiang2018predicting} collected 34 high-grossing films from 2015 to 2017, using 10 features, such as film metadata, director awards, and actor awards, then I used voting feature selection algorithms to select important features,
+  training SVM models for film box-office and user-comment score prediction.
   Quader \etal~\cite{quader2017machine} collected 755 film reviews in four film review sites from 2012 to 2015, collected characteristics including film ratings, MPAA categories,
@@
   Read \etal ~\cite{read2016learning} proposed a CNN-RNN classification model, using CNN layers for extracting the high-order dimensional representation of images,
-  and connecting to LSTM layers for description representation, the trained neural network model has accuracy of 56.8\% on Caltech-UCSD Birds dataset and accuracy of 65.6\% on Flowers dataset.
+  and connecting to LSTM layers for description representation, the trained neural network model has accuracy of 56.8\% on Caltech-UCSD Birds dataset and accuracy of 65.6\% on the Flowers dataset.
 
@@
 
-  Zhu and Tang~\cite{zhu2019film} collected 20 films with more than 300 million box-offices in 2017, using 13 features, such as search engine user search times, number of social network fans, and other movie meta-data,
+  Zhu and Tang~\cite{zhu2019film} collected 20 films with more than 300 million box-offices in 2017, using 13 features, such as search engine user search times, number of social network fans, and other movie metadata,
   and constructed a partial-least-square model with a margin of error of 87.7\% and an average absolute error of 26.6\%.
@@
   Chi \etal~\cite{chi2019does} collected reviews from 150 films released in 2017, found that the number of reviews was positively related to box-office
-  and the number of reviews was significantly positive for the first-week of the film box-office.
-  Josh \etal~\cite{joshi2010movie} collected film review text in MetaCritic releasing from 2005 to 2009, using film meta-data, n-gram model,
-  part-of-speech n-gram model and dependency characteristics, and the Elastic-Net model has a determination of coefficient of 67.1\% in predicting the first-week box-office.
+  and the number of reviews was significantly positive for the first week of the film box-office.
+  Josh \etal~\cite{joshi2010movie} collected film review text in MetaCritic releasing from 2005 to 2009, using film metadata, n-gram model,
+  part-of-speech n-gram model and dependency characteristics, and the Elastic-Net model have a determination of the coefficient of 67.1\% in predicting the first week box-office.
 
@@
   social network release date characteristics, text sentiments characteristics,
-  researchers prefer to use logistic regression, support vector machine, and neural network in predicting movie box-office.
+  researchers prefer to use the logistic regression, support vector machine, and neural network in predicting movie box-office.
 
@@
 \item {\bf Number of retweets}: the more retweet posts, the higher box-office gets.
-\item {\bf Box-office history}: the higher average score of actors' box-office, the higher box-office attendance of participating in the film gets.
+\item {\bf Box-office history}: the higher the average score of actors' box-office, the higher the box-office attendance of participating in the film gets.
 \end{itemize}
@@
 \par Then, I calculated the Pearson correlation between average box-office per movie and actors' social network characteristics, the post and retweet correlation is $-0.108\%$, social media activity correlation is $-3.203\%$, co-occurrence correlation is $15.08\%$.
-First of all, the actors' average box-office per movie is positively related to the influence of the actors, that is, the higher number of co-occurrence in Sina Weibo, the higher average box-office per movie.
+First of all, the actors' average box-office per movie is positively related to the influence of the actors, that is, the higher number of co-occurrence in Sina Weibo, the higher the average box-office per movie.
 Secondly, the actors Sina Weibo activity and the average box-office per movie showed a slight negative correlation, that is,
@@
 Then, using Sina Weibo text sentiments and actor social network characteristics trained a decision tree model to predict movie box-office,
-determination of the coefficient in training-set is 98.58\%, and determination of the coefficient on the test-set is 96.05\%.
+determination of the coefficient in the training set is 98.58\%, and the determination of the coefficient on the test set is 96.05\%.
 
 \par In summary, the decision tree structure shows that the influence of the actors in social networks is the main factor affecting box-office,
-followed by the movie-relating Sina Weibo sentiments and the film meta-data is the secondary determinant,
-while the social network characteristics, movie-related Sina Weibo sentiment and other film meta-data are the least significant factors.
+followed by the movie-relating Sina Weibo sentiments and the film metadata is the secondary determinant,
+while the social network characteristics, movie-related Sina Weibo sentiment, and other film metadata are the least significant factors.
 
@@
 
-\par For the task in box-office forecast, because of the significant impact the actors on the box-office, in addition to the measurement of the film meta-data and the sentiments of the movie social media,
+\par For the task in box-office forecast, because of the significant impact the actors on the box-office, in addition to the measurement of the film metadata and the sentiments of the movie social media,
 the actors' contribution is required to compute by leveraging actors in the movie cast.
 A film, led by several leading actors, obtained the names of $7369$ actors who participated in films between 2011 and 2015 are collected as an actors' dictionary, and then used the shortest path features of the actors' social network.
-Combining social network measurement features, the shortest path network embedding, and the artisticfeatures to construct the actor representation vector.
+Combining social network measurement features, the shortest path network embedding, and the artistic features to construct the actor representation vector.
 For actors who have no accounts on social networks, marked as unknown, and initialized with zero vectors.
-Actor representation vectors include network characteristics of 10 dimensions, shortest path features of 8380 dimensions, artisticfeatures of 1 dimension.
-In total, 10-dimension features include fans number, betweenness, closeness, followers, post number, average post interval, average word count per post, retweet number, movie-related post number, co-occurrence number, the shortest path with 8380 dimensions.
+Actor representation vectors include network characteristics of 10 dimensions, shortest path features of 8380 dimensions, artistic features of 1 dimension.
+In total, 10-dimension features include fans number, betweenness, closeness, followers, post number, average post publish interval, average word count per post, retweet number, movie-related post number, co-occurrence number, the shortest path with 8380 dimensions.
 
@@
 
-Using the features extracted, the characteristics of participating in the calculation are film meta-data and movie sentiment:
+Using the features extracted, the characteristics of participating in the calculation are film metadata and movie sentiment:
 the year of release, the number of positive sentiment, the number of negative sentiment, the total number of Sina Weibo posts,
@@
 possibly because the sentiments on actors' social networks do not represent the commercial benefits of the film.
-Actors, as creators of films, have a role to play in the box-office, but lack of other important features that also has a significant impact on the box-office,
+Actors, as creators of films, have a role to play in the box-office, but lack of other important features that also have a significant impact on the box-office,
 so the machine learning fitting process can't converge in a given time.
-Using the Cartisticdecision tree regression algorithm to make box-office prediction for the test set film,
+Using the cart decision tree regression algorithm to make box-office prediction for the test set film,
 the experimental results show that the prediction model has a determination coefficient of 96.05\% on the test set and 98.58\% on the training set, which is 2.87\% higher than the Qiu and Tang~\cite{qiu2018microblog} model,
 and the average absolute deviation of the model is $0.1285$ million, about 28.56\% of the average box-office.
-The explanation of the decision tree prediction model is more intuitive and more interpretable than linear regression, logical regression, deep neural network and other models,
+The explanation of the decision tree prediction model is more intuitive and more interpretable than linear regression, logical regression, deep neural network, and other models,
 according to the prediction model structure schematic of movie box-office,
 the characteristics can be sorted according to the importance, the social network structure characteristics are the most important,
-the social network text sentiments characteristics, the film meta-data are important, and the social network characteristics are generally important.
-Compared to Qiu and Tang~\cite{qiu2018microblog}'s logistic regression model on sentiments and twitter index algorithm's 95.71\% determination of coefficient,
-The model in this paper has a determination of coefficient of 98.58\% which has a 2.87\% improvement.
+the social network text sentiments characteristics, the film metadata are important, and the social network characteristics are generally important.
+Compared to Qiu and Tang~\cite{qiu2018microblog}'s logistic regression model on sentiments and the determination of the coefficient of twitter index algorithm is 95.71\% ,
+The model in this paper has a determination of the coefficient of 98.58\% which has a 2.87\% improvement.
 
@@
 To make the data evenly distributed, the film data were pre-processed by using the median box-office of $2.635$ million as the dividing line.
-So for the movies with box-office, less than $2.635$ million are classified as A-class, movies with box-office more than $2.635$ million are classified as B-class.
-In the dataset division, the data were randomly selected using the $80-20$ segmentation ratio, and the training set of $1036$ films and the test set of $260$ movies were collected.
+So for the movies with  less than $2.635$ million box-office are classified as A-class, movies with more than $2.635$ million box-office are classified as B-class.
+In the dataset division, the data were randomly selected using the $80\%:20\%$ segmentation ratio, and the training set of $1036$ films and the test set of $260$ movies were collected.
 Using the actors' social network representation, the actor is quantified, that is,
-the fusion of social network features, the shortest path characteristics, and the actors' artisticcharacteristics.
+the fusion of social network features, the shortest path characteristics, and the actors' artistic characteristics.
 For actors without social network data, use zero-value initialization in the actor feature matrix for the unknown characteristics.
@@
 \begin{itemize}
-\item The first partisticis the Fully Connected layer, its input feature is the film meta-data and movie-related Sina Weibo sentiments, in a total of 5 dimensions.
-\item The second partisticis the GRU layer, the input feature is the actor social network measurement characteristics and artisticcharacteristics, the film cast is a long list,
+\item The first part is the fully connected layer, its input feature is the film metadata and movie-related Sina Weibo sentiments, in a total of 5 dimensions.
+\item The second part is the GRU layer, the input feature is the actor social network measurement characteristics and artistic characteristics, the film cast is a long list,
 the longest 225 actors, for less than 225 actors using the front-end padding, the GRU layer is to solve the long-term memory loss of the structure.
-\item The last partisticis the 5 CNN layers, input from the actors' social network shortest path feature, similarly, the film cast is a long list,
+\item The last part is the 5 CNN layers, input from the actors' social network shortest path feature, similarly, the film cast is a long list,
 input less than 225 dimensions is fulfilled by padding, CNN has a good ability to capture multi-dimensional features, and use of Max-pooling layer to solve the problem of multi-dimension feature extraction.
@@
 Compared to Read \etal model, see Table 2, the proposed FC-GRU-CNN model converges on the training set and achieves better prediction results on the test set.
-Therefore, it can provide decision-making advice in the task of selecting suitable actors for to-be-cast film,
+Therefore, it can provide decision-making advice in the task of selecting suitable actors for a to-be-cast film,
 and in the box-office prediction task, the model can provide reasonable predictions in the market.
@@
 \end{center}
-\caption{box-office model predictions in movie testset(10 samples).}
+\caption{box-office model predictions in movie test dataset with 10 samples.}
 \end{table}
@@
 \end{center}
-\caption{Performance comparison on different model.}
+\caption{Performance comparison on the models.}
 \end{table}
@@
 
-According to the NEN(Non-Euclidean Net) box-office prediction model, this paper discussed the relationship between the movie meta-data, Sina Weibo text sentiments, social relationship representations, network characteristics, and actors' artistic contribution in detail.
-I proposed an FC-GRU-CNN box-office prediction model, and tested on a dataset of $1296$ movies released in China mainland from 2011 to 2015, compared to Read \etal's model, accuracy improves 14\%.
+According to the NEN(Non-Euclidean Net) box-office prediction model, this paper discussed the relationship between the movie metadata, Sina Weibo text sentiments, social relationship representations, network characteristics, and actors' artistic contribution in detail.
+I proposed an FC-GRU-CNN box-office prediction model, testing on a dataset of $1296$ movies released in China mainland from 2011 to 2015, the model accuracy improves 14\% compared to Read \etal's model.
 

### 2020-10-14 A-BasicCommom/CVPR2021/cvpr_classification.tex
1.CVPR v0.5.0, add one more figure.

@@
   the classification model outperforms the Wide ResNet model and the linear-probe iGPT-L model,
-  and achieved accuracy of $99.60\%\sim99.74\%$ on the CIFAR-10 image set and accuracy of $98.27\%\sim98.95\%$ on the CIFAR-100 image set.
+  and achieved accuracy of $99.60\%\sim99.74\%$ on the CIFAR-10 image set and accuracy of $99.10\%\sim99.76\%$ on the CIFAR-100 image set.
 
@@
 RoBERTa-wwm-ext-large & Case-2	&	99.8\% \\
-RoBERTa-wwm-ext-large & Case-4	&	98.95\% \\
+RoBERTa-wwm-ext-large & Case-4	&	99.76\% \\
 RBTL3  & Case-4	&	96.35\% \\
@@
 
+\begin{figure*}
+\begin{center}
+  \fbox{\rule{0pt}{2in} \includegraphics[width=0.9\linewidth]{roberta-cifar.pdf}}
+\end{center}
+   \caption{Training epochs of accuracy on the CIFAR-10 and CIFAR-100 dataset}
+\label{fig:short}
+\end{figure*}
+
 As Cui \etal~\cite{cui2020revisiting} reported that the training of the RBT3 language model was based on Devlin \etal's
@@
 
-\par When fine-tuning, I check the accuracy of the trained model on the test set and stopped training when it converges on $10^{-3}\sim10^{-4}$.
+\par When fine-tuning, as figure-2, I check the accuracy of the trained model on the test set and stopped training when it converges on $10^{-3}\sim10^{-4}$.
 
@@
 RoBERTa-large  & CIFAR-10 & 6	&	99.60\% \\
-RBTL3  & CIFAR-100 & 6  & 	98.27\% \\
-RoBERTa-large & CIFAR-100 & 16 &	98.95\% \\
+\hline
+RBT3   & CIFAR-100 & 6	&	99.74\% \\
+RBTL3  & CIFAR-100 & 6  & 	99.10\% \\
+RoBERTa-large & CIFAR-100 & 16 &	99.76\% \\
 \hline
@@
 the model achieved accuracy of $99.60\%\sim99.74\%$ on the CIFAR-10 image set,
-and accuracy of $98.27\%\sim98.95\%$ on the CIFAR-100 image set.
+and accuracy of $99.10\%\sim99.76\%$ on the CIFAR-100 image set.
 

### 2020-10-14 A-BasicCommom/CVPR2021/cvpr_classification.tex
1.CVPR v0.5.0, add one more figure.

@@
 \hline\hline
-RoBERTa-wwm-ext-large & Case-2	&	99.8\% \\
+RoBERTa-wwm-ext-large & Case-2	&	99.80\% \\
 RoBERTa-wwm-ext-large & Case-4	&	99.76\% \\
@@
 \hline
-RBT3   & CIFAR-100 & 6	&	99.74\% \\
+RBT3   & CIFAR-100 & 6	&	93.71\% \\
 RBTL3  & CIFAR-100 & 6  & 	99.10\% \\
@@
 
-TThis paper proposed a novel idea by using pre-trained language models for image representation and take image classification as an example of its performance in Computer Vision tasks.
+ This paper proposed a novel idea by using pre-trained language models for image representation and take image classification as an example of its performance in Computer Vision tasks.
 Tests showed that the proposed model outperforms the iGPT-L model without augmentation on the image dataset,

### 2020-10-15 A-BasicCommom/CVPR2021/cvpr_classification.tex
1.CVPR v0.5.0, add one more figure.

@@
 Moreover, the pre-trained Chinese language models use extra 5 billion training tokens comparing to Devlin \etal's 0.4 billion tokens.
-I use a batch size of 512 and train for $1\sim16$ epochs using AdamW with $\beta_1=0.99$, $\beta_2=0.999$, and weight decay of $10^{-8}$.
+I use a batch size of 512 and train for $6\sim16$ epochs using AdamW with $\beta_1=0.99$, $\beta_2=0.999$, and weight decay of $10^{-8}$.
 I set the learning rate to $10^{-4}$ and no warmed up or decay are used.
@@
 \hline
-RBT3   & CIFAR-100 & 6	&	93.71\% \\
+RBT3   & CIFAR-100 & 12	&	99.66\% \\
 RBTL3  & CIFAR-100 & 6  & 	99.10\% \\

### 2020-10-15 A-BasicCommom/CVPR2021/cvpr_classification.tex
1.CVPR v0.5.0, add one more figure.

@@
 name the token $M$ as the BERT mask.
-Train the language model by minimizing the BERT objective of the "masked" elements $x_M$
+As equation (1), train the language model by minimizing the BERT objective of the "masked" elements $x_M$
 conditioned on the "unmasked" ones $x_{\left[1,n\right]\backslash M}$.
@@
 
-\par From table-1, by combining the pre-trained language model with fully connected layer as the document classification model,
+\par From table (1), by combining the pre-trained language model with fully connected layer as the document classification model,
 the test accuracy exceeds the other popular machine learning algorithms.
@@
 and get the encoded representation of the token $\textbf{[CLS]}$ as the images' language model embeddings.
-In the Feature-Extraction layer, a combination of one dropout layer, one fully connected layer, and one softmax layer, as equation-2, is used.
+In the Feature-Extraction layer, a combination of one dropout layer, one fully connected layer, and one softmax layer, as equation (2), is used.
 In the Output layer, the classification label of the image is feed in the model.

### 2020-10-15 A-BasicCommom/CVPR2021/cvpr_vision.tex
1.CVPR v0.5.0, add fix typo.

@@
   and non-linear capability of deep FC layer for movie text sentiments and other characteristics.
-  The proposed model accuracy is 14\% higher than Read \etal's model.
+  The proposed model accuracy is 14\% higher than Reed \etal's model.
 
@@
 
-  With the development of social networks, actors' influence of social media is increasing, and the influence of actors' consumption spreads through social networks,
+  With the development of social networks, actors' influence of social media is increasing, and the influence of actors' consumption spReeds through social networks,
   and using long-term social network data to study the relationships between all actors, directors, and films remains a challenge.
@@
   all-pairs shortest path, social network text sentiments, and actors' artistic contribution characteristics,
-  as a result, it is 14\% higher in accuracy than Read \etal ~\cite{read2016learning}'s model.
+  as a result, it is 14\% higher in accuracy than Reed \etal ~\cite{reed2016learning}'s model.
 
@@
 
-  Read \etal ~\cite{read2016learning} proposed a CNN-RNN classification model, using CNN layers for extracting the high-order dimensional representation of images,
+  Reed \etal ~\cite{reed2016learning} proposed a CNN-RNN classification model, using CNN layers for extracting the high-order dimensional representation of images,
   and connecting to LSTM layers for description representation, the trained neural network model has accuracy of 56.8\% on Caltech-UCSD Birds dataset and accuracy of 65.6\% on the Flowers dataset.
@@
 The accuracy of the binary classification model on the training set reached 99.61\%, the accuracy on the test set is 75\%.
-Compared to Read \etal model, see Table 2, the proposed FC-GRU-CNN model converges on the training set and achieves better prediction results on the test set.
+Compared to Reed \etal model, see Table 2, the proposed FC-GRU-CNN model converges on the training set and achieves better prediction results on the test set.
 Therefore, it can provide decision-making advice in the task of selecting suitable actors for a to-be-cast film,
@@
 \hline\hline
-Read \etal  & 61.54\% \\
+Reed \etal  & 61.54\% \\
 This paper & 75.0\% \\
@@
 According to the NEN(Non-Euclidean Net) box-office prediction model, this paper discussed the relationship between the movie metadata, Sina Weibo text sentiments, social relationship representations, network characteristics, and actors' artistic contribution in detail.
-I proposed an FC-GRU-CNN box-office prediction model, testing on a dataset of $1296$ movies released in China mainland from 2011 to 2015, the model accuracy improves 14\% compared to Read \etal's model.
+I proposed an FC-GRU-CNN box-office prediction model, testing on a dataset of $1296$ movies released in China mainland from 2011 to 2015, the model accuracy improves 14\% compared to Reed \etal's model.
 

### 2020-10-16 A-BasicCommom/CVPR2021/cvpr_classification.tex
1.CVPR v0.5.0, add one more figure.

@@
 
-  Image classification and categorization are essential for the capability of telling the difference between images for a machine.
+  Image classification and categorization are essential to the capability of telling the difference between images for a machine.
   As \underline{B}idirectional \underline{E}ncoder \underline{R}epresentations from \underline{T}ransformers became popular in many tasks of natural language processing recent years,
@@
 \end{center}
-\caption{Comparision of accuracy of the pre-trained language models on different dataset in the document classification task.}
+\caption{Comparision of accuracy of the pre-trained language models on different datasets in the document classification task.}
 \end{table}
@@
 \end{center}
-   \caption{Concat, encoder, representation, and extraction layers for image classification task.}
+   \caption{Concatenation, encoder, representation, and extraction layers for image classification task.}
 \label{fig:short}
@@
 
-I design simple classification models without too many layers, as Figure-1 shows.
+I design simple classification models without too many layers, as Figure (1) shows.
 And use the CIFAR-10 and CIFAR-100 dataset as an example to show the architecture of the model.
@@
 \item {\bf Input layer}
-\item {\bf Concat layer}
+\item {\bf Concatenation layer}
 \item {\bf Trim layer}
@@
 then encode other meta-data if provided, as a sequence of ASCII characters.
-In the Concat layer, the pixel-channel value and metadata are concatenated, put a special token of $\textbf{[CLS]}$ at the start,
+In the Concatenation layer, the pixel-channel value and metadata are concatenated, put a special token of $\textbf{[CLS]}$ at the start,
 and put a $\textbf{[SEP]}$ token between channel values and metadata, put a special token of $\textbf{[SEP]}$ at the end.
@@
 \end{center}
-   \caption{Training epochs of accuracy on the CIFAR-10 and CIFAR-100 dataset}
+   \caption{Accuracy of the image classification models with the pre-trained language encoder on the CIFAR-10 and CIFAR-100 dataset in the training epochs.}
 \label{fig:short}
@@
 
-As Cui \etal~\cite{cui2020revisiting} reported that the training of the RBT3 language model was based on Devlin \etal's
-Moreover, the pre-trained Chinese language models use extra 5 billion training tokens comparing to Devlin \etal's 0.4 billion tokens.
+As Cui \etal~\cite{cui2020revisiting} reported that the training of the RBT3 language model was based on Devlin \etal's model,
+moreover, the pre-trained Chinese language models use extra 5 billion training tokens comparing to Devlin \etal's 0.4 billion tokens.
 I use a batch size of 512 and train for $6\sim16$ epochs using AdamW with $\beta_1=0.99$, $\beta_2=0.999$, and weight decay of $10^{-8}$.
@@
 
-\par When fine-tuning, as figure-2, I check the accuracy of the trained model on the test set and stopped training when it converges on $10^{-3}\sim10^{-4}$.
+\par When fine-tuning, as Figure (2), I check the accuracy of the trained model on the test set and stopped training when it converges on $10^{-3}\sim10^{-4}$.
 
@@
  This paper proposed a novel idea by using pre-trained language models for image representation and take image classification as an example of its performance in Computer Vision tasks.
+ The finding might benefit various subjects, namely Education, Medical, Chemistry, Physics, Cosmology, Geography, Climate and Materials Science for their specific research.
 Tests showed that the proposed model outperforms the iGPT-L model without augmentation on the image dataset,

### 2020-10-21 A-BasicCommom/wordRepresentation/evaluate.py
1.word2vec.

@@ -1,0 +1,64 @@
+import joblib
+import gensim
+# import torch
+# import torch.nn as nn
+# import torch.nn.functional as F
+# import torch.utils.data as tud
+# import torch.optim as optim
+# from torch.nn.parameter import Parameter
+
+from collections import Counter
+import numpy as np
+import random
+import math
+import pandas as pd
+import scipy
+import sklearn
+from sklearn.metrics.pairwise import cosine_similarity
+
+def eval(analogy_file, similarity_file):
+    model = joblib.load("word2vec.model")
+    analog = model.wv.most_similar(positive=['张','三'], negative=['李'], topn=1)
+    print(analog)
+    similarity = model.wv.similarity('张','李')
+    print(similarity)
+    #model.wv.save_word2vec_format(fname="wv.txt")
+
+    idx_to_word = [word for word in model.wv.vocab.keys()]
+    word_to_idx = {word: i for i, word in enumerate(idx_to_word)}
+
+    # 评估模型
+    def evaluate(filename, embedding_weights):
+        if filename.endswith('.csv'):
+            data = pd.read_csv(filename, sep=',', header=None)
+        else:
+            if 'analogy' in filename:
+                acclist = model.accuracy(filename)
+                correct = len(acclist[-1]['correct'])
+                total = correct + len(acclist[-1]['incorrect'])
+                if total:
+                    return correct * 1.0 / total
+                return 0
+            else:
+                data = pd.read_csv(filename, sep='\t', header=None)
+
+        human_similarity = []
+        model_similarity = []
+        for row in data.itertuples(index=False):
+            word1, word2 = row[0], row[1]
+            # OOV 不计算精度
+            if word1 not in word_to_idx or word2 not in word_to_idx:
+                continue
+            else:
+                # word1_idx, word2_idx = word_to_idx[word1], word_to_idx[word2]
+                word1_embed, word2_embed = embedding_weights[[word1]], embedding_weights[[word2]]
+                model_similarity.append(float(cosine_similarity(word1_embed, word2_embed)))
+                human_similarity.append(float(row[2]))
+        spears = scipy.stats.spearmanr(human_similarity, model_similarity)
+        return spears.correlation
+
+
+    evals = evaluate(analogy_file, embedding_weights = model.wv)
+    print(evals)
+    evals = evaluate(similarity_file, embedding_weights = model.wv)
+    print(evals)

### 2020-10-21 A-BasicCommom/wordRepresentation/train.py

@@ -1,0 +1,66 @@
+import argparse
+from gensim.models.word2vec import LineSentence
+from gensim.models import Word2Vec
+import joblib
+import lawa
+from evaluate import eval
+lawa.load_userdict('dic/Chinese.dic')
+
+lawa.load_userdict('dic/english.dic')
+
+parser = argparse.ArgumentParser()
+parser.add_argument(
+    '-c', '--config_file', default='config/bert_config.json',
+    help='model config file')
+
+parser.add_argument(
+    '-d', '--dimension', default=256,
+    help='model vector dimension')
+
+parser.add_argument(
+    '-min', '--min_count', default=50,
+    help='model vocabulary minimal')
+
+parser.add_argument(
+    '-w', '--worker', default=16,
+    help='model number of workers')
+
+parser.add_argument(
+    '-e', '--epoch', default=1,
+    help='model number of epochs')
+
+parser.add_argument(
+    '-u', '--analogy_file', default=None,
+    help='model validation file')
+
+parser.add_argument(
+    '-v', '--similarity_file', default=None,
+    help='model validation file')
+
+args = parser.parse_args()
+
+X = LineSentence(args.config_file) #类似迭代器
+
+class LawaIterable(object):
+    def __init__(self, lines):
+        self.lines = lines
+
+    def __iter__(self):
+        for line in self.lines:
+            line = lawa.lcut(line[0])
+            yield " ".join(line)
+
+model = Word2Vec(LawaIterable(X), size=args.dimension, min_count=args.min_count, sg=1, hs=1, workers=args.worker, iter=args.epoch)
+# model.build_vocab(X, update=True)
+# model.train(X)
+print(model.wv.keys())
+print(model.wv.most_similar(positive=['be'], topn=10))
+# acc=model.accuracy('q.txt')
+# print(acc)
+joblib.dump(model, "word2vec.model", compress=3)
+model.wv.save_word2vec_format(fname="wv.txt")
+
+if args.analogy_file:
+    eval(args.analogy_file, args.similarity_file)
+
+print('FIN')

### 2020-10-22 A-BasicCommom/wordRepresentation/evaluate.py
1.word2vec.

@@ -1,12 +1,5 @@
 import joblib
 import gensim
-# import torch
-# import torch.nn as nn
-# import torch.nn.functional as F
-# import torch.utils.data as tud
-# import torch.optim as optim
-# from torch.nn.parameter import Parameter
-
 from collections import Counter
 import numpy as np
 import random
@@ -18,10 +11,11 @@ from sklearn.metrics.pairwise import cosine_similarity
 
 def eval(analogy_file, similarity_file):
     model = joblib.load("word2vec.model")
-    analog = model.wv.most_similar(positive=['张','三'], negative=['李'], topn=1)
-    print(analog)
-    similarity = model.wv.similarity('张','李')
-    print(similarity)
+    vocab = list(model.wv.vocab.keys())
+    analog = model.wv.most_similar(positive=vocab[0:2], negative=vocab[-1:1], topn=1)
+    print('a+b-c',vocab[0:2],vocab[-1],analog)
+    similarity = model.wv.similarity(*vocab[0:2])
+    print(vocab[0:2],'sim score:', similarity)
     #model.wv.save_word2vec_format(fname="wv.txt")
 
     idx_to_word = [word for word in model.wv.vocab.keys()]
@@ -59,6 +53,6 @@ def eval(analogy_file, similarity_file):
 
 
     evals = evaluate(analogy_file, embedding_weights = model.wv)
-    print(evals)
+    print("analogy score:", evals)
     evals = evaluate(similarity_file, embedding_weights = model.wv)
-    print(evals)
+    print("similarity score:", evals)

### 2020-10-22 A-BasicCommom/wordRepresentation/train.py

@@ -18,7 +18,11 @@ parser.add_argument(
     help='model vector dimension')
 
 parser.add_argument(
-    '-min', '--min_count', default=50,
+    '-l', '--en', default=False,
+    help='corpus is English')
+
+parser.add_argument(
+    '-m', '--min_count', default=1,
     help='model vocabulary minimal')
 
 parser.add_argument(
@@ -39,7 +43,6 @@ parser.add_argument(
 
 args = parser.parse_args()
 
-X = LineSentence(args.config_file) #类似迭代器
 
 class LawaIterable(object):
     def __init__(self, lines):
@@ -47,20 +50,26 @@ class LawaIterable(object):
 
     def __iter__(self):
         for line in self.lines:
-            line = lawa.lcut(line[0])
-            yield " ".join(line)
+            line = line[0]
+            yield [" ".join(lawa.lcut(line))]
 
-model = Word2Vec(LawaIterable(X), size=args.dimension, min_count=args.min_count, sg=1, hs=1, workers=args.worker, iter=args.epoch)
-# model.build_vocab(X, update=True)
-# model.train(X)
-print(model.wv.keys())
-print(model.wv.most_similar(positive=['be'], topn=10))
-# acc=model.accuracy('q.txt')
-# print(acc)
-joblib.dump(model, "word2vec.model", compress=3)
-model.wv.save_word2vec_format(fname="wv.txt")
+f = open(args.config_file, 'r', encoding='utf-8')
+if args.en == "en":
+    X = LineSentence(f)  # 类似迭代器
+else:
+    X = LineSentence(f)  # 类似迭代器
+    X = LawaIterable(X)
 
-if args.analogy_file:
-    eval(args.analogy_file, args.similarity_file)
+for i in range(1,5):
+    model = Word2Vec(X, size=args.dimension * i, min_count=int(args.min_count), sg=1, hs=1, workers=int(args.worker), iter=int(args.epoch))
+    joblib.dump(model, "word2vec.model", compress=3)
+    model.wv.save_word2vec_format(fname="wv.txt")
+    print('vocab:', len(model.wv.vocab.keys()), model.wv.vocab.keys())
+    vocab = list(model.wv.vocab.keys())
+    print('center word',vocab[-1], model.wv.most_similar(positive=[vocab[-1]], topn=10))
 
+    if args.analogy_file:
+        eval(args.analogy_file, args.similarity_file)
+
+f.close()
 print('FIN')

### 2020-10-22 A-BasicCommom/wordRepresentation/train.py
1.word2vec.

@@ -4,9 +4,9 @@ from gensim.models import Word2Vec
 import joblib
 import lawa
 from evaluate import eval
-lawa.load_userdict('dic/Chinese.dic')
+#lawa.load_userdict('dic/Chinese.dic')
 
-lawa.load_userdict('dic/english.dic')
+#lawa.load_userdict('dic/english.dic')
 
 parser = argparse.ArgumentParser()
 parser.add_argument(
@@ -51,7 +51,7 @@ class LawaIterable(object):
     def __iter__(self):
         for line in self.lines:
             line = line[0]
-            yield [" ".join(lawa.lcut(line))]
+            yield list(lawa.cut(line))
 
 f = open(args.config_file, 'r', encoding='utf-8')
 if args.en == "en":

### 2020-10-23 A-BasicCommom/wordRepresentation/evaluate.py
1.word2vec课程作业.

@@ -1,12 +1,6 @@
 import joblib
-import gensim
-from collections import Counter
-import numpy as np
-import random
-import math
 import pandas as pd
 import scipy
-import sklearn
 from sklearn.metrics.pairwise import cosine_similarity
 
 def eval(analogy_file, similarity_file):
@@ -23,13 +17,15 @@ def eval(analogy_file, similarity_file):
 
     # 评估模型
     def evaluate(filename, embedding_weights):
+        miss = 0
         if filename.endswith('.csv'):
             data = pd.read_csv(filename, sep=',', header=None)
+            miss += 1
         else:
             if 'analogy' in filename:
                 acclist = model.accuracy(filename)
                 correct = len(acclist[-1]['correct'])
-                total = correct + len(acclist[-1]['incorrect'])
+                total = correct + len(acclist[-1]['incorrect']) + miss
                 if total:
                     return correct * 1.0 / total
                 return 0
@@ -51,8 +47,13 @@ def eval(analogy_file, similarity_file):
         spears = scipy.stats.spearmanr(human_similarity, model_similarity)
         return spears.correlation
 
-
+    total = []
     evals = evaluate(analogy_file, embedding_weights = model.wv)
+    total.append(evals)
     print("analogy score:", evals)
-    evals = evaluate(similarity_file, embedding_weights = model.wv)
-    print("similarity score:", evals)
+    if isinstance(similarity_file, list):
+        for sim in similarity_file:
+            evals = evaluate(sim, embedding_weights = model.wv)
+            print("similarity score:", evals)
+            total.append(evals)
+    print("average weighted score:", sum(total))

### 2020-10-23 A-BasicCommom/wordRepresentation/test.py

@@ -1,0 +1,20 @@
+import argparse
+from evaluate import eval
+
+
+parser = argparse.ArgumentParser()
+
+parser.add_argument(
+    '-u', '--analogy_file', default=None,
+    help='model validation file')
+
+parser.add_argument(
+    '-v', '--similarity_file', default=None,
+    help='model validation file')
+
+args = parser.parse_args()
+
+if args.analogy_file:
+    eval(args.analogy_file, args.similarity_file.split(":"))
+
+print('FIN')

### 2020-10-23 A-BasicCommom/wordRepresentation/train.py

@@ -1,37 +1,49 @@
 import argparse
+import itertools
+
 from gensim.models.word2vec import LineSentence
 from gensim.models import Word2Vec
 import joblib
 import lawa
 from evaluate import eval
-#lawa.load_userdict('dic/Chinese.dic')
-
-#lawa.load_userdict('dic/english.dic')
 
 parser = argparse.ArgumentParser()
 parser.add_argument(
     '-c', '--config_file', default='config/bert_config.json',
     help='model config file')
 
+#10.22 experiments showed that 1024 is better than 256
 parser.add_argument(
-    '-d', '--dimension', default=256,
+    '-d', '--dimension', default=1024,
     help='model vector dimension')
 
 parser.add_argument(
-    '-l', '--en', default=False,
+    '-l', '--en', default='en',
     help='corpus is English')
 
 parser.add_argument(
-    '-m', '--min_count', default=1,
+    '-m', '--min_count', default=10,
     help='model vocabulary minimal')
 
 parser.add_argument(
-    '-w', '--worker', default=16,
+    '-i', '--hierarchical_softmax', default=1,
+    help='Hierarchical Softmax')
+
+parser.add_argument(
+    '-n', '--negative_sampling', default=5,
+    help='Negative Sampling')
+
+parser.add_argument(
+    '-w', '--worker', default=8,
     help='model number of workers')
 
 parser.add_argument(
     '-e', '--epoch', default=1,
     help='model number of epochs')
+
+parser.add_argument(
+    '-s', '--skip_gram', default=1,
+    help='Skip Gram or Continuous Bag of Words')
 
 parser.add_argument(
     '-u', '--analogy_file', default=None,
@@ -41,35 +53,45 @@ parser.add_argument(
     '-v', '--similarity_file', default=None,
     help='model validation file')
 
+
+parser.add_argument(
+    '-w', '--window_size', default=5,
+    help='model context window size')
+
+parser.add_argument(
+   '-z', '--max_vocab_size', default=40000,
+    help='model max vocab_size')
 args = parser.parse_args()
 
 
 class LawaIterable(object):
-    def __init__(self, lines):
-        self.lines = lines
+    def __init__(self, filename):
+        self.source = filename
+        self.limit = None
 
     def __iter__(self):
-        for line in self.lines:
-            line = line[0]
[…]

### 2020-10-23 A-BasicCommom/wordRepresentation/evaluate.py
1.word2vec training.

@@ -2,9 +2,11 @@ import joblib
 import pandas as pd
 import scipy
 from sklearn.metrics.pairwise import cosine_similarity
+from gensim.models import KeyedVectors
 
 def eval(analogy_file, similarity_file):
-    model = joblib.load("word2vec.model")
+    # model = joblib.load("word2vec.model")
+    model = KeyedVectors.load_word2vec_format('word2vec.txt', binary=False)
     vocab = list(model.wv.vocab.keys())
     analog = model.wv.most_similar(positive=vocab[0:2], negative=vocab[-1:1], topn=1)
     print('a+b-c',vocab[0:2],vocab[-1],analog)

### 2020-10-23 A-BasicCommom/wordRepresentation/train.py

@@ -4,7 +4,7 @@ import itertools
 from gensim.models.word2vec import LineSentence
 from gensim.models import Word2Vec
 import joblib
-import lawa
+
 from evaluate import eval
 
 parser = argparse.ArgumentParser()
@@ -55,7 +55,7 @@ parser.add_argument(
 
 
 parser.add_argument(
-    '-w', '--window_size', default=5,
+    '-y', '--window_size', default=5,
     help='model context window size')
 
 parser.add_argument(
@@ -79,10 +79,11 @@ class LawaIterable(object):
 if args.en == "en":
     X = LineSentence(args.config_file)  # 类似迭代器
 else:
+    import lawa
     X = LawaIterable(args.config_file)
 
 
-model = Word2Vec(X, size=args.dimension, min_count=int(args.min_count), window=int(args.window_size), sg=int(args.skip_gram), hs=int(args.hierarchical_softmax) * int(args.negative_sampling), negative=int(args.negative_sampling), workers=int(args.worker), iter=int(args.epoch),
+model = Word2Vec(X, size=int(args.dimension), min_count=int(args.min_count), window=int(args.window_size), sg=int(args.skip_gram), hs=int(args.hierarchical_softmax) * int(args.negative_sampling), negative=int(args.negative_sampling), workers=int(args.worker), iter=int(args.epoch),
                  max_vocab_size=int(args.max_vocab_size))
 joblib.dump(model, "word2vec.model", compress=3)
 model.wv.save_word2vec_format(fname="word2vec.txt")

### 2020-10-23 A-BasicCommom/wordRepresentation/evaluate.py
1.word2vec.

@@ -1,7 +1,7 @@
 import joblib
 import pandas as pd
-import scipy
 from sklearn.metrics.pairwise import cosine_similarity
+from scipy.stats import spearmanr
 from gensim.models import KeyedVectors
 
 def eval(analogy_file, similarity_file):
@@ -36,6 +36,7 @@ def eval(analogy_file, similarity_file):
 
         human_similarity = []
         model_similarity = []
+
         for row in data.itertuples(index=False):
             word1, word2 = row[0], row[1]
             # OOV 不计算精度
@@ -46,7 +47,8 @@ def eval(analogy_file, similarity_file):
                 word1_embed, word2_embed = embedding_weights[[word1]], embedding_weights[[word2]]
                 model_similarity.append(float(cosine_similarity(word1_embed, word2_embed)))
                 human_similarity.append(float(row[2]))
-        spears = scipy.stats.spearmanr(human_similarity, model_similarity)
+
+        spears = spearmanr(human_similarity, model_similarity)
         return spears.correlation
 
     total = []

### 2020-10-23 A-BasicCommom/wordRepresentation/evaluate.py
1.word2vec, more fare for OOV.

@@ -6,7 +6,7 @@ from gensim.models import KeyedVectors
 
 def eval(analogy_file, similarity_file):
     # model = joblib.load("word2vec.model")
-    model = KeyedVectors.load_word2vec_format('word2vec.txt', binary=False)
+    model = KeyedVectors.load_word2vec_format('word2vec-1024.txt', binary=False)
     vocab = list(model.wv.vocab.keys())
     analog = model.wv.most_similar(positive=vocab[0:2], negative=vocab[-1:1], topn=1)
     print('a+b-c',vocab[0:2],vocab[-1],analog)
@@ -41,6 +41,8 @@ def eval(analogy_file, similarity_file):
             word1, word2 = row[0], row[1]
             # OOV 不计算精度
             if word1 not in word_to_idx or word2 not in word_to_idx:
+                model_similarity.append(0.5)
+                human_similarity.append(float(row[2]))
                 continue
             else:
                 # word1_idx, word2_idx = word_to_idx[word1], word_to_idx[word2]
@@ -52,12 +54,24 @@ def eval(analogy_file, similarity_file):
         return spears.correlation
 
     total = []
-    evals = evaluate(analogy_file, embedding_weights = model.wv)
-    total.append(evals)
-    print("analogy score:", evals)
+    if isinstance(analogy_file, list):
+        for ana in analogy_file:
+            evals = evaluate(ana, embedding_weights=model.wv)
+            total.append(evals)
+            print("analogy score:", evals)
+    else:
+        evals = evaluate(analogy_file, embedding_weights = model.wv)
+        total.append(evals)
+        print("analogy score:", evals)
+
     if isinstance(similarity_file, list):
         for sim in similarity_file:
             evals = evaluate(sim, embedding_weights = model.wv)
             print("similarity score:", evals)
             total.append(evals)
+    else:
+        evals = evaluate(similarity_file, embedding_weights=model.wv)
+        print("similarity score:", evals)
+        total.append(evals)
+
     print("average weighted score:", sum(total))

### 2020-10-23 A-BasicCommom/wordRepresentation/test.py

@@ -15,6 +15,6 @@ parser.add_argument(
 args = parser.parse_args()
 
 if args.analogy_file:
-    eval(args.analogy_file, args.similarity_file.split(":"))
+    eval(args.analogy_file.split(":"), args.similarity_file.split(":"))
 
 print('FIN')

### 2020-10-23 A-BasicCommom/wordRepresentation/train.py

@@ -14,7 +14,7 @@ parser.add_argument(
 
 #10.22 experiments showed that 1024 is better than 256
 parser.add_argument(
-    '-d', '--dimension', default=1024,
+    '-d', '--dimension', default=256,
     help='model vector dimension')
 
 parser.add_argument(
@@ -82,17 +82,17 @@ else:
     import lawa
     X = LawaIterable(args.config_file)
 
+for i in range(1,5):
+    model = Word2Vec(X, size=int(args.dimension) * i, min_count=int(args.min_count), window=int(args.window_size), sg=int(args.skip_gram), hs=int(args.hierarchical_softmax) * int(args.negative_sampling), negative=int(args.negative_sampling), workers=int(args.worker), iter=int(args.epoch),
+                     max_vocab_size=int(args.max_vocab_size))
+    joblib.dump(model, "word2vec.model", compress=3)
+    model.wv.save_word2vec_format(fname="word2vec.txt")
+    print('vocab:', len(model.wv.vocab.keys()), model.wv.vocab.keys())
+    vocab = list(model.wv.vocab.keys())
+    print('center word',vocab[-1], model.wv.most_similar(positive=[vocab[-1]], topn=10))
 
-model = Word2Vec(X, size=int(args.dimension), min_count=int(args.min_count), window=int(args.window_size), sg=int(args.skip_gram), hs=int(args.hierarchical_softmax) * int(args.negative_sampling), negative=int(args.negative_sampling), workers=int(args.worker), iter=int(args.epoch),
-                 max_vocab_size=int(args.max_vocab_size))
-joblib.dump(model, "word2vec.model", compress=3)
-model.wv.save_word2vec_format(fname="word2vec.txt")
-print('vocab:', len(model.wv.vocab.keys()), model.wv.vocab.keys())
-vocab = list(model.wv.vocab.keys())
-print('center word',vocab[-1], model.wv.most_similar(positive=[vocab[-1]], topn=10))
-
-if args.analogy_file:
-    eval(args.analogy_file, args.similarity_file.split(":"))
+    if args.analogy_file:
+        eval(args.analogy_file.split(":"), args.similarity_file.split(":"))
 
 
 print('FIN')

### 2020-10-23 A-BasicCommom/CVPR2021/cvpr.tex
1. Fix and update template.

@@
   In this paper, with the distance product association law and block matrix multiplication, all-pairs shortest path algorithm has a lowered time-bound of \(O(\log{n}2n^3)\).
-  I propose an all-pairs shortest path algorithm that leveraging matrix sparseness judgment, convergence judgment, distance product matrix multiplication, distance product association law,
-  scale-free characteristics of the social networks and limitation for floating-point operations on modern hardware, which has an improved lower time-bound \(O(14n^3)\).
-  As an empirical study of social networks, I tested on movie actors' social network dataset, the proposed algorithm has an improvement of 39\% to 36.2 times in performance on CPU/GPU platforms comparing to Alon \etal's algorithm.
+  The proposed all-pairs shortest path algorithm, which has an improved lower time-bound \(O(14n^3)\), leverages matrix sparseness judgment, convergence judgment, distance product with matrix multiplication, association law for distance product,
+  scale-free characteristics of the social networks degrees and precision limit of floating point operations on the modern hardware.
+  Tested on the movie actors' social network dataset, the algorithm has an improvement of 39\% to 36.2 times in performance on the CPU/GPU platforms comparing to Alon \etal's all-pairs shortest path algorithm.
 \end{abstract}
@@
 
-In recent years, driven by Asian film industries such as China and India, the global box office has maintained a steady growth trend, and with the rapid development of social network applications, more and more actors use social networks for work communication.
+In recent years, driven by the Asian film industries such as China and India, the global box office has maintained a steady growth trend, and with the rapid development of social network applications, more and more actors use social networks for work communication.
 Therefore, the social network has become an important tool for film distribution, marketing, promotion, and an important medium for film actors and fans to interact.
@@
 Further, the analysis time complexity of the distance product calculation and iteration of each epoch.
-For time complexity of distance product, matrix multiplication is the most complex sub-procedures;
+For time complexity of the distance product, matrix multiplication is the most complex sub-procedures.
 
 \begin{enumerate}
-\item For distance product optimization, Zwick proposed a distance product with block matrix multiplication, therefore choose proper computation device library with optimized cache for block matrix multiplication.
-\item For iteration optimization, because Aho proved distance product is isomorphic to the matrix multiplication, and regard to that the distance product association law, optimize the iteration process by last distance product result reuse.
+\item For the distance product optimization, Zwick proposed the distance product with block matrix multiplication, therefore choose proper computation device library with optimized cache for block matrix multiplication.
+\item For the iteration optimization, Aho proved distance product is isomorphic to the matrix multiplication, and regard to that the distance product association law, I optimize the iteration process by reusing the distance product result of the epochs.
 \end{enumerate}
@@
 
-\section{Dataset And Hardware}
-From January 1, 2011, to March 31, 2015, I collected the film actors' social network following relationship, profile information, and text message on Sina Weibo which is one of the popular social media in China.
-In all, collected 8508 actors, 577775 edges, and 12526114 Sina Weibo posts.
-I used a server with two Intel Xeon E5-2620 v4 CPUs and one NVIDIA GeForce GTX 1080 Ti GPU, in total 32 cores with a frequency of 2.1Ghz, 128G system memory, and 11G GPU memory in my experiment.
+\section{Dataset and Hardware}
+
+From January 1, 2011, to March 31, 2015, I collected the film actors' social network following relationship, profile information, and text message on Sina Weibo, one of the popular social media in China.
+In all, 8508 actors, 577775 edges, and 12526114 Sina Weibo posts are collected.
+Experiments are made on a server with two Intel Xeon E5-2620 v4 CPUs and one NVIDIA GeForce GTX 1080 Ti GPU, in total 32 cores with a frequency of 2.1Ghz, 128G system memory, and 11G GPU memory in my experiment.
 
@@
 Albert~\cite{albert1999diameter} found that social networks, the Internet, and other complex networks have scale-free characteristics and small-world phenomena, thus network diameter is much smaller than the number of network nodes.
-I present the corresponding nodes counts, diameters, and logarithm of diameters in Table 1, from the observation there is formula (1):
-In social networks, the number of nodes $n$, with cache block size $B\times B$, according to the formula (9-10), the matrix product calculation iteration times does not exceed the number of $\lceil{\log{\Bbb D}}\rceil$, recall that Lam \etal proved that matrix multiplication time-bound is \(O({2n^3 \over \Bbb B}+{n^2})\),
+I present the corresponding nodes counts, diameters, and logarithm of diameters in Table 1, from the observation there is Formula (1).
+In social networks, the number of nodes $n$, with cache block size $B\times B$, according to the Formula (9-10), the matrix product calculation iteration times does not exceed the number of $\lceil{\log{\Bbb D}}\rceil$, recall that Lam \etal proved that matrix multiplication time-bound is \(O({2n^3 \over \Bbb B}+{n^2})\),
 thus Alon \etal algorithm time-bound is \(O({\log{\Bbb D}2n^3\over{ \Bbb B}})\) with cache block size of $\Bbb B$, use the equation (1) result, time-bound is \(O({\log(\log{N})2n^3\over \Bbb B})\).
-With the arithmetic limitation on the floating-point operation, \eg take a network with nodes number of $N<10^{308}$
+With the arithmetic limitation on the floating point operation, \eg take a network with nodes number of $N<10^{308}$
 as shown in Table 1, see that the shortest path calculation iterations time is no larger than $\log{\Bbb D} \approx \log(\log{N})<7$, that is, the number of calculation iterations does not exceed the magic number $7$,
 bringing a stronger time-bound of \(O({14n^3\over {\Bbb B}})\).
-In other words, with the floating-point operation accuracy limitation on computer hardware and complex networks scale-free characteristics, all-pairs shortest path algorithm time-bound is \(O({14n^3\over \Bbb B})\), for $\Bbb B$ is a constant, thus, for simpler representation, the time-bound is \(O(14n^3)\).
+In other words, with the floating point operation precision limit on computer hardware and complex networks scale-free characteristics, all-pairs shortest path algorithm time-bound is \(O({14n^3\over \Bbb B})\), for $\Bbb B$ is a constant, thus, for simpler representation, the time-bound is \(O(14n^3)\).
 
@@
 
-Calculate the largest value of the square matrix element $\widetilde X$, such as the formula (4):
+Calculate the largest value of the square matrix element $\widetilde X$, such as the Formula (4).
 
@@
 
-The calculation accuracy of different computer hardware is in line with the IEEE floating-point operation standard~\cite{ieee1985ieee},
+The calculation precision of different computer hardware complies with the IEEE floating point operation standard~\cite{ieee1985ieee},
 first of all, transform the input matrix by exponential transformation, to be specific, taking the number of nodes as the base,
-taking the difference between the largest value of the element $\widetilde X$ and the matrix elements as exponential, as shown in the formula (5).
-\eg For actors' social network with 8508 nodes, the diameter of the network does not allow to exceed 9.8 and 78.4 when calculating precision of 32-bit floating-point and 64-bit floating-point,
+taking the difference between the largest value of the element $\widetilde X$ and the matrix elements as exponential, as shown in the Formula (5).
+For the actors' social network with 8508 nodes, the diameter of the network does not allow to exceed 9.8 and 78.4 when calculating precision of 32-bit floating point and 64-bit floating point,
 otherwise, the exponential operation on the computer platform will overflow.
@@
 \subsection{Matrix Multiplication}
-Use different matrix libraries to speed up the matrix multiplication on computer hardware, as shown in Table 3, choose proper device-based optimized matrix multiplication libraries according to different conditions, such as matrix sparseness, calculation hardware, and programming language.
+Use different matrix libraries to speed up the matrix multiplication on the computer hardware, as shown in Table 3, choose proper device-based optimized matrix multiplication libraries according to different conditions, such as matrix sparseness, calculation hardware, and programming language.
 
@@
 Take non-zero elements of the matrix multiplication result to the element logarithm process, that is, the number of network nodes as the base, the element in the matrix multiplication result as the true number, then round down the logarithm result,
-after that take difference between twice the largest input matrix element value $\widetilde X$ and the logarithm result as result, such as formula (6).
+after that take difference between twice the largest input matrix element value $\widetilde X$ and the logarithm result as result, such as Formula (6).
 
@@
 
-From the iteration of the shortest path calculation, suppose \(\Bbb A,\ \Bbb B,\ \Bbb C\) is the square matrix, according to the association law of distance product, there is a formula (7):
-Matrix multiplication has an association law, and the distance product is isomorphism to matrix multiplication, so simplify the shortest path iteration process as formula (8):
+From the iteration of the shortest path calculation, suppose \(\Bbb A,\ \Bbb B,\ \Bbb C\) is the square matrix, according to the association law of distance product, there is a Formula (7).
+Matrix multiplication has an association law, and the distance product is isomorphism to matrix multiplication, so simplify the shortest path iteration process as Formula (8).
 Since matrix multiplication has an association law and distance product is isomorphism to matrix multiplication, similarly, distance product has an association law.
 Under the premise of the shortest path matrix $L^{(n-1)}$ given the adjacent matrix and the $n-1$ edge, calculate the shortest path matrix $L^{(n)}$ with n edges, and extend the shortest path of the $n-1$ edge by edge.
-Calculating the shortest path matrix $L^{(n)}$ can be completed as formula (9):
-As can be seen from the nature of the shortest path in the graph, the shortest path from any of two nodes does not exceed $n-1$, so there is formula (10):
-Definition 3 Result Reuse in Distance Product According to the nature of the equation (8), the process of calculating the shortest path iteration using the last result of distance product follows in turn, as shown in formula (11).
-The shortest path needs to be calculated $\lceil{log_2(n-1)}\rceil$ times matrix multiplication, from the formula (10), it can be seen that $(n-1)\leq2^{\lceil{log_2(n-1)}\rceil}$ is the same as the simple shortest path matrix calculation result $L^{(n-1)}$, so there is a formula (12):
+Calculating the shortest path matrix $L^{(n)}$ can be completed as Formula (9).
+As can be seen from the nature of the shortest path in the graph, the shortest path from any of two nodes does not exceed $n-1$, so there is Formula (10).
+
+Definition 3 (Result Reuse in Distance Product) According to the nature of the Equation (8), the process of calculating the shortest path iteration using the last result of distance product follows in turn, as shown in Formula (11).
+The shortest path needs to be calculated $\lceil{log_2(n-1)}\rceil$ times matrix multiplication, from the Formula (10), it can be seen that $(n-1)\leq2^{\lceil{log_2(n-1)}\rceil}$ is the same as the simple shortest path matrix calculation result $L^{(n-1)}$, so there is a Formula (12).
 Obviously, the result reuse method saves $n-2-\lceil{log_2(n-1)}\rceil$ times of matrix multiplication.
-Observe the shortest path calculation process of the actors' social network, the adjacent matrix is shown in Figure 1a, and the change of result in each iteration is shown in Figure 1b-d, the shortest path result matrix converges gradually, each element stabilizes as iterations go.
+Observe the shortest path calculation process of the actors' social network, the adjacent matrix is shown in Figure 1-a, and the change of result in each iteration is shown in Figure 1-(b-d), the shortest path result matrix converges gradually, each element stabilizes as iterations go.
 
 \begin{algorithm}
-\caption{Lower Bounds Convergence Matrix Products in All-Pairs Shortest Path}\label{algorithm}
+\caption{Lower Bounds Convergence Matrix Products in the All-Pairs Shortest Path}\label{algorithm}
 \KwData{Adjacent Matrix $\Bbb W$, Matrix Row $n$, Network Diameter $\Bbb D$}
@@
 
-For networks with unknown diameters, the calculation results can be made using the convergence method, and for the calculation process of reaching convergence,
-i.e. $L^{(n-1)}=L^{(n)}$, should be regarded as the program termination of iteration, and the calculation of the matrix product method is completed by the equation (4).
+For the networks with unknown diameters, the calculation results can be made using the convergence method, and for the calculation process of reaching convergence,
+i.e. $L^{(n-1)}=L^{(n)}$, should be regarded as the program termination of iteration, and the calculation of the matrix product method is completed by the Equation (4).
 
@@
 Based on Alon \etal distance product algorithm, utilizing the sparseness judgment of the input matrix and the calculation result convergence judgment,
-with the network conforming to the power-law distribution and the precision of floating-point operation, and the name implies two characteristics of the limitation
-of floating-point precision on the scale-free social network and the computer hardware, the algorithm process flow is shown in Algorithm 1.
+with the network conforming to the power-law distribution and the precision of floating point operation, and the name implies two characteristics of the limitation
+of floating point precision on the scale-free social network and the computer hardware, the algorithm process flow is shown in Algorithm 1.
 
@@
 \hline\hline
-Floyd-Warshall~\cite{floyd1962algorithm,warshall1962theorem}  &	1055880s \\
+Floyd-Warshall~\cite{floyd1962algorithm,warshall1962theorem}  &	$10^6$s \\
 Alon \etal~\cite{alon1997exponent}  &	594.7s \\
@@
 
-This paper discussed a novel algorithm in all-pairs shortest path computation tasks, using distance product association law.
+This paper discussed a novel algorithm in the all-pairs shortest path computation tasks, using distance product association law.
 The time-bound of Alon \etal distance product algorithm with block matrix multiplication is \(O({\log{n}2n^3\over \Bbb B})\).
-To strengthen the conditions, on scale-free social networks, for the precision limit of floating-point operation on hardware, additional condition on the social network diameter is added to avoid floating-point operation overflow during the calculation process.
+To strengthen the conditions, on the scale-free social networks, for the precision limit of floating point operation on hardware, additional condition on the social network diameter is added to avoid floating point operation overflow during the calculation process.
 the algorithm has lower time-bound \(O({14n^3\over \Bbb B})\).
 With strengthened conditions, I proposed a novel algorithm, leveraging matrix sparseness judgment, and calculation convergence judgment.
-\textbf{Power-Law} refers to the network node numbers conforming to the characteristics that social networks power-law distribution, and \textbf{Bound} refers to the floating-point operations arithmetic limitation of accuracy on hardware.
+\textbf{Power-Law} refers to the network node degrees conforming to the characteristics that social networks power-law distribution, and \textbf{Bound} refers to the limit on floating point arithmetic operations precision on hardware.
 The experimental results show that \textbf{Power-LawBound} algorithm improves time performance by 39\% to 36.2 times on CPU/GPU hardware compared to Alon \etal's algorithm.
@@
 \bibliographystyle{ieee_fullname}
-\bibliography{cpvr}
+%\bibliography{cpvr}
+\begin{thebibliography}{10}
+
+\bibitem{alon1997exponent}
+Noga Alon, Zvi Galil, and Oded Margalit.
+\newblock On the exponent of the all pairs shortest path problem.
+\newblock {\em Journal of Computer and System Sciences}, 54(2):255--262, 1997.
+
+\bibitem{floyd1962algorithm}
+Robert~W Floyd.
+\newblock Algorithm 97: shortest path.
+\newblock {\em Communications of the ACM}, 5(6):345, 1962.
+
+\bibitem{warshall1962theorem}
+Stephen Warshall.
+\newblock A theorem on boolean matrices.
+\newblock {\em Journal of the ACM (JACM)}, 9(1):11--12, 1962.
+
+\bibitem{aho1974design}
+Alfred~V Aho and John~E Hopcroft.
+\newblock {\em The design and analysis of computer algorithms}.
+\newblock Pearson Education India, 1974.
+
+\bibitem{zwick2002all}
+Uri Zwick.
+\newblock All pairs shortest paths using bridging sets and rectangular matrix
+  multiplication.
+\newblock {\em Journal of the ACM (JACM)}, 49(3):289--317, 2002.
+
+\bibitem{garbow1985scaling}
+Harold~N Garbow.
+\newblock Scaling algorithms for network problems.
+\newblock {\em Journal of Computer and System Sciences}, 31(2):148--168, 1985.
+
+\bibitem{strassen1969gaussian}
+Volker Strassen.
+\newblock Gaussian elimination is not optimal.
+\newblock {\em Numerische mathematik}, 13(4):354--356, 1969.
+
+\bibitem{coppersmith1987matrix}
+Don Coppersmith and Shmuel Winograd.
+\newblock Matrix multiplication via arithmetic progressions.
+\newblock In {\em Proceedings of the nineteenth annual ACM symposium on Theory
+  of computing}, pages 1--6, 1987.
+
+\bibitem{davie2013improved}
+Alexander~Munro Davie and Andrew~James Stothers.
+\newblock Improved bound for complexity of matrix multiplication.
+\newblock {\em Proceedings. Section A, Mathematics-The Royal Society of
+  Edinburgh}, 143(2):351, 2013.
+
+\bibitem{le2014powers}
+Fran{\c{c}}ois Le~Gall.
+\newblock Powers of tensors and fast matrix multiplication.
+\newblock In {\em Proceedings of the 39th international symposium on symbolic
+  and algebraic computation}, pages 296--303, 2014.
+
+\bibitem{lam1991cache}
+Monica~D Lam, Edward~E Rothberg, and Michael~E Wolf.
+\newblock The cache performance and optimizations of blocked algorithms.
+\newblock {\em ACM SIGOPS Operating Systems Review}, 25(Special Issue):63--74,
+  1991.
+
+\bibitem{goto2008anatomy}
+Kazushige Goto and Robert A van~de Geijn.
+\newblock Anatomy of high-performance matrix multiplication.
+\newblock {\em ACM Transactions on Mathematical Software (TOMS)}, 34(3):1--25,
+  2008.
+
+\bibitem{albert1999diameter}
+R{\'e}ka Albert, Hawoong Jeong, and Albert-L{\'a}szl{\'o} Barab{\'a}si.
+\newblock Diameter of the world-wide web.
+\newblock {\em nature}, 401(6749):130--131, 1999.
+
+\bibitem{ieee1985ieee}
+IEEE Computer Society.~Standards Committee and American National~Standards
+  Institute.
+\newblock {\em IEEE standard for binary floating-point arithmetic}, volume 754.
+\newblock IEEE, 1985.
+
+\end{thebibliography}
+
 }

### 2020-10-23 A-BasicCommom/CVPR2021/cvpr_vision.tex
1. Fix and update template.

@@
   FC-GRU-CNN architecture exploits the long-term memory ability of the GRU layer in long sequences of film cast,
-  the mapping ability of the CNN layer in retrieving all-pairs shortest path feature of the actors' social relationship,
-  and non-linear capability of deep FC layer for movie text sentiments and other characteristics.
-  The proposed model accuracy is 14\% higher than Reed \etal's model.
+  the mapping ability of the CNN layer in retrieving all-pairs shortest path of the actors' social relationship,
+  and non-linear capability of deep fully connected layer for movie text sentiments and other characteristics.
+  The proposed model accuracy is 14\% higher than Reed \etal~\cite{reed2016learning}'s model.
 
@@
   all-pairs shortest path, social network text sentiments, and actors' artistic contribution characteristics,
-  as a result, it is 14\% higher in accuracy than Reed \etal ~\cite{reed2016learning}'s model.
+  as a result, it is 14\% higher in accuracy than Reed \etal~\cite{reed2016learning}'s model.
 
@@
 
-  Reed \etal ~\cite{reed2016learning} proposed a CNN-RNN classification model, using CNN layers for extracting the high-order dimensional representation of images,
+  Reed \etal proposed a CNN-RNN classification model, using CNN layers for extracting the high-order dimensional representation of images,
   and connecting to LSTM layers for description representation, the trained neural network model has accuracy of 56.8\% on Caltech-UCSD Birds dataset and accuracy of 65.6\% on the Flowers dataset.
@@
 
-\section{Representation Learning for Social Relationship, Network Characteristics And artisticContribution}
+\section{Representation Learning for Social Relationship, Network Characteristics and artisticContribution}
 
@@
 
-In summary, randomly choose 10 movies as a test set, as shown in Table 1.
+In summary, randomly choose 10 movies as the test set, as shown in Table 1.
 The accuracy of the binary classification model on the training set reached 99.61\%, the accuracy on the test set is 75\%.
@@
 Therefore, it can provide decision-making advice in the task of selecting suitable actors for a to-be-cast film,
-and in the box-office prediction task, the model can provide reasonable predictions in the market.
+and in the box-office prediction task, the model can provide more accurate predictions in the market.
 
@@
 \end{center}
-\caption{Performance comparison on the models.}
+\caption{Performance comparison on the prediction models.}
 \end{table}
@@
 
-According to the NEN(Non-Euclidean Net) box-office prediction model, this paper discussed the relationship between the movie metadata, Sina Weibo text sentiments, social relationship representations, network characteristics, and actors' artistic contribution in detail.
-I proposed an FC-GRU-CNN box-office prediction model, testing on a dataset of $1296$ movies released in China mainland from 2011 to 2015, the model accuracy improves 14\% compared to Reed \etal's model.
+According to the box-office prediction model, this paper discussed the relationship between the movie metadata, Sina Weibo text sentiments, social relationship representations, network characteristics, and actors' artistic contribution in detail.
+I proposed an FC-GRU-CNN box-office prediction model, tested on a dataset with $1296$ movies released in China mainland from 2011 to 2015, the model accuracy improves 14\% compared to Reed \etal's model.
 
@@
 \bibliographystyle{ieee_fullname}
-\bibliography{cpvr_movienet}
+%\bibliography{cpvr_movienet}
+\begin{thebibliography}{10}
+
+\bibitem{reed2016learning}
+Scott Reed, Zeynep Akata, Honglak Lee, and Bernt Schiele.
+\newblock Learning deep representations of fine-grained visual descriptions.
+\newblock In {\em Learning deep representations of fine-grained visual
+  descriptions}, volume 2016-December, pages 49 -- 58, Las Vegas, NV, United
+  states, 2016.
+
+\bibitem{fernandez2014we}
+Manuel Fern{\'a}ndez-Delgado, Eva Cernadas, Sen{\'e}n Barro, and Dinani Amorim.
+\newblock Do we need hundreds of classifiers to solve real world classification
+  problems?
+\newblock {\em The journal of machine learning research}, 15(1):3133--3181,
+  2014.
+
+\bibitem{jiang2018predicting}
+Luyao Jiang and Zhengduo Wang.
+\newblock Predicting box office and audience rating of chinese films using
+  machine learning.
+\newblock In {\em Proceedings of the 2018 International Conference on Education
+  Technology Management}, pages 58--62, 2018.
+
+\bibitem{quader2017machine}
+Nahid Quader, Md~Osman Gani, Dipankar Chaki, and Md~Haider Ali.
+\newblock A machine learning approach to predict movie box-office success.
+\newblock In {\em 2017 20th International Conference of Computer and
+  Information Technology (ICCIT)}, pages 1--7. IEEE, 2017.
+
+\bibitem{zhu2019film}
+Huike Zhu and Zhongjun Tang.
+\newblock Film box office forecasting methods based on partial least squares
+  regression model.
+\newblock In {\em Proceedings of the 11th International Conference on Computer
+  Modeling and Simulation}, pages 234--238, 2019.
+
+\bibitem{qiu2018microblog}
+Xiaoyang Qiu and Tiffany~Ya Tang.
+\newblock Microblog mood predicts the box office performance.
+\newblock In {\em Proceedings of the 2018 Artificial Intelligence and Cloud
+  Computing Conference}, pages 129--133, 2018.
+
+\bibitem{asur2010predicting}
+Sitaram Asur and Bernardo~A Huberman.
+\newblock Predicting the future with social media.
+\newblock In {\em 2010 IEEE/WIC/ACM international conference on web
+  intelligence and intelligent agent technology}, volume~1, pages 492--499.
+  IEEE, 2010.
+
+\bibitem{jain2013prediction}
+Vasu Jain.
+\newblock Prediction of movie success using sentiment analysis of tweets.
+\newblock {\em The International Journal of Soft Computing and Software
+  Engineering}, 3(3):308--313, 2013.
+
+\bibitem{chi2019does}
+Jianyu Chi, Enshu Gu, and Kewei Li.
+\newblock How does online word-of-mouth impact movie box office: An empirical
+  investigation of china.
+\newblock In {\em Proceedings of the 2019 International Conference on
+  Artificial Intelligence and Computer Science}, pages 730--735, 2019.
+
+\bibitem{joshi2010movie}
+Mahesh Joshi, Dipanjan Das, Kevin Gimpel, and Noah~A Smith.
+\newblock Movie reviews and revenues: An experiment in text regression.
+\newblock In {\em Human Language Technologies: The 2010 Annual Conference of
+  the North American Chapter of the Association for Computational Linguistics},
+  pages 293--296, 2010.
+
+\end{thebibliography}
+
 }

### 2020-10-23 A-BasicCommom/CVPR2021/cvpr_classification.tex
1. Fix and update template.

@@
 \bibliographystyle{ieee_fullname}
-\bibliography{cpvr_classification}
+%\bibliography{cpvr_classification}
+\begin{thebibliography}{10}
+
+  \bibitem{lee2009convolutional}
+Lee, H., Grosse, R., Ranganath, R. \&  Ng, A.~Y.
+\newblock {Convolutional deep belief networks for scalable unsupervised
+  learning of hierarchical representations}.
+\newblock In {\em Proceedings of the 26th annual international conference on
+  machine learning}, pages 609--616, 2009.
+
+\bibitem{nair2010rectified}
+Nair, V. \&  Hinton, G.~E.
+\newblock {Rectified linear units improve restricted boltzmann machines}.
+\newblock In {\em ICML}, 2010.
+
+\bibitem{mikolov2013distributed}
+Mikolov, T., Sutskever, I., Chen, K., Corrado, G.~S. \&  Dean, J.
+\newblock {Distributed representations of words and phrases and their
+  compositionality}.
+\newblock In {\em Advances in neural information processing systems}, pages
+  3111--3119, 2013.
+
+\bibitem{devlin2019bert}
+Devlin, J., Chang, M.-W., Lee, K. \&  Toutanova, K.
+\newblock {BERT: Pre-training of Deep Bidirectional Transformers for Language
+  Understanding}.
+\newblock In {\em NAACL-HLT (1)}, 2019.
+
+\bibitem{vincent2008extracting}
+Vincent, P., Larochelle, H., Bengio, Y. \&  Manzagol, P.-A.
+\newblock {Extracting and composing robust features with denoising
+  autoencoders}.
+\newblock In {\em Proceedings of the 25th international conference on Machine
+  learning}, pages 1096--1103, 2008.
+
+\bibitem{chen2020generative}
+Chen, M., Radford, A., Child, R., Wu, J., Jun, H., Dhariwal, P., Luan, D.
+ and Sutskever, I.
+\newblock {Generative Pretraining from Pixels}.
+\newblock In {\em Proceedings of the 37th International Conference on Machine
+  Learning}, 2020.
+
+\bibitem{wang2019development}
+Wang, W., Yang, Y., Wang, X., Wang, W. \&  Li, J.
+\newblock {Development of convolutional neural network and its application in
+  image classification: a survey}.
+\newblock {\em Optical Engineering}, 58(4):40901, 2019.
+
+\bibitem{lecun1990handwritten}
+LeCun, Y., Boser, B.~E., Denker, J.~S., Henderson, D., Howard, R.~E., Hubbard,
+  W.~E. \&  Jackel, L.~D.
+\newblock {Handwritten digit recognition with a back-propagation network}.
+\newblock In {\em Advances in neural information processing systems}, pages
+  396--404, 1990.
+
+\bibitem{krizhevsky2012imagenet}
+Krizhevsky, A., Sutskever, I. \&  Hinton, G.~E.
+\newblock {Imagenet classification with deep convolutional neural networks}.
+\newblock In {\em Advances in neural information processing systems}, pages
+  1097--1105, 2012.
+
+\bibitem{zeiler2014visualizing}
+Zeiler, M.~D. \&  Fergus, R.
+\newblock {Visualizing and understanding convolutional networks}.
+\newblock In {\em European conference on computer vision}, pages 818--833.
+  Springer, 2014.
+
+\bibitem{simonyan2014very}
+Simonyan, K. \&  Zisserman, A.
+\newblock {Very deep convolutional networks for large-scale image recognition}.
+\newblock In {\em 3rd International Conference on Learning Representations,
+  ICLR 2015 - Conference Track Proceedings}, San Diego, CA, United states,
+  2015.
+
+\bibitem{szegedy2015going}
+Szegedy, C., Liu, W., Jia, Y., Sermanet, P., Reed, S., Anguelov, D., Erhan, D.,
+  Vanhoucke, V. \&  Rabinovich, A.
+\newblock {Going deeper with convolutions}.
+\newblock In {\em Proceedings of the IEEE conference on computer vision and
+  pattern recognition}, pages 1--9, 2015.
+
+\bibitem{he2016deep}
+He, K., Zhang, X., Ren, S. \&  Sun, J.
+\newblock {Deep residual learning for image recognition}.
+\newblock In {\em Proceedings of the IEEE conference on computer vision and
+  pattern recognition}, pages 770--778, 2016.
+
+\bibitem{xie2017aggregated}
+Xie, S., Girshick, R., Doll{\'{a}}r, P., Tu, Z. \&  He, K.
+\newblock {Aggregated residual transformations for deep neural networks}.
+\newblock In {\em Proceedings of the IEEE conference on computer vision and
+  pattern recognition}, pages 1492--1500, 2017.
+
+\bibitem{szegedy2016inception}
+Szegedy, C., Ioffe, S., Vanhoucke, V. \&  Alemi, A.~A.
+\newblock {Inception-v4, inception-ResNet and the impact of residual
+  connections on learning}.
+\newblock In {\em 31st AAAI Conference on Artificial Intelligence, AAAI 2017},
+  pages 4278--4284, San Francisco, CA, United states, 2017.
+
+\bibitem{huang2016deep}
+Huang, G., Sun, Y., Liu, Z., Sedra, D. \&  Weinberger, K.~Q.
+\newblock {Deep networks with stochastic depth}.
+\newblock In {\em European conference on computer vision}, pages 646--661.
+  Springer, 2016.
+
+\bibitem{lu2007survey}
+Lu, D. \&  Weng, Q.
+\newblock {A survey of image classification methods and techniques for
+  improving classification performance}.
+\newblock {\em International journal of Remote sensing}, 28(5):823--870, 2007.
+
+\bibitem{cui2020revisiting}
+Cui, Y., Che, W., Liu, T., Qin, B., Wang, S. \&  Hu, G.
+\newblock {Revisiting Pre-Trained Models for Chinese Natural Language
+  Processing}.
+\newblock In {\em Findings of EMNLP}. Association for Computational
+  Linguistics, 2020.
+
+\bibitem{he2017fine}
+He, X. \&  Peng, Y.
+\newblock {Fine-grained image classification via combining vision and
+  language}.
+\newblock In {\em Proceedings of the IEEE Conference on Computer Vision and
+  Pattern Recognition}, pages 5994--6002, 2017.
+
+\bibitem{reed2016learning}
+Reed, S., Akata, Z., Lee, H. \&  Schiele, B.
+\newblock {Learning deep representations of fine-grained visual descriptions}.
+\newblock In {\em Proceedings of the IEEE Conference on Computer Vision and
+  Pattern Recognition}, pages 49--58, 2016.
+
+\bibitem{fernandez2014we}
+Fern{\'{a}}ndez-Delgado, M., Cernadas, E., Barro, S. \&  Amorim, D.
+  Amorim.
+\newblock {Do we need hundreds of classifiers to solve real world
+  classification problems?}
+\newblock {\em The journal of machine learning research}, 15(1):3133--3181,
+  2014.
+
+\bibitem{kim2014convolutional}
+Kim, Y.
+\newblock {Convolutional neural networks for sentence classification}.
+\newblock In {\em EMNLP 2014 - 2014 Conference on Empirical Methods in Natural
+  Language Processing, Proceedings of the Conference}, pages 1746--1751, Doha,
+  Qatar, 2014.
+
+\end{thebibliography}
 }

### 2020-10-24 A-BasicCommom/wordRepresentation/evaluate.py
1. word2vec

@@ -5,8 +5,8 @@ from scipy.stats import spearmanr
 from gensim.models import KeyedVectors
 
 def eval(analogy_file, similarity_file):
-    # model = joblib.load("word2vec.model")
-    model = KeyedVectors.load_word2vec_format('word2vec-1024.txt', binary=False)
+    model = joblib.load("word2vec.model")
+    # model = KeyedVectors.load_word2vec_format('word2vec-1024.txt', binary=False)
     vocab = list(model.wv.vocab.keys())
     analog = model.wv.most_similar(positive=vocab[0:2], negative=vocab[-1:1], topn=1)
     print('a+b-c',vocab[0:2],vocab[-1],analog)

### 2020-10-24 A-BasicCommom/wordRepresentation/train.py

@@ -14,7 +14,7 @@ parser.add_argument(
 
 #10.22 experiments showed that 1024 is better than 256
 parser.add_argument(
-    '-d', '--dimension', default=256,
+    '-d', '--dimension', default=512,
     help='model vector dimension')
 
 parser.add_argument(
@@ -67,11 +67,11 @@ args = parser.parse_args()
 class LawaIterable(object):
     def __init__(self, filename):
         self.source = filename
-        self.limit = None
+
 
     def __iter__(self):
         with open(self.source, 'r', encoding='utf-8') as fin:
-            for line in itertools.islice(fin, self.limit):
+            for x, line in enumerate(fin):
                 yield list(lawa.cut(line))
 
 
@@ -82,17 +82,17 @@ else:
     import lawa
     X = LawaIterable(args.config_file)
 
-for i in range(1,5):
-    model = Word2Vec(X, size=int(args.dimension) * i, min_count=int(args.min_count), window=int(args.window_size), sg=int(args.skip_gram), hs=int(args.hierarchical_softmax) * int(args.negative_sampling), negative=int(args.negative_sampling), workers=int(args.worker), iter=int(args.epoch),
-                     max_vocab_size=int(args.max_vocab_size))
-    joblib.dump(model, "word2vec.model", compress=3)
-    model.wv.save_word2vec_format(fname="word2vec.txt")
-    print('vocab:', len(model.wv.vocab.keys()), model.wv.vocab.keys())
-    vocab = list(model.wv.vocab.keys())
-    print('center word',vocab[-1], model.wv.most_similar(positive=[vocab[-1]], topn=10))
 
-    if args.analogy_file:
-        eval(args.analogy_file.split(":"), args.similarity_file.split(":"))
+model = Word2Vec(X, size=int(args.dimension), min_count=int(args.min_count), window=int(args.window_size), sg=int(args.skip_gram), hs=int(args.hierarchical_softmax) * int(args.negative_sampling), negative=int(args.negative_sampling), workers=int(args.worker), iter=int(args.epoch),
+                 max_vocab_size=int(args.max_vocab_size))
+joblib.dump(model, "word2vec.model", compress=3)
+model.wv.save_word2vec_format(fname="word2vec.txt")
+print('vocab:', len(model.wv.vocab.keys()), model.wv.vocab.keys())
+vocab = list(model.wv.vocab.keys())
[…]

### 2020-10-25 A-BasicCommom/CVPR2021/cvpr.tex
cvpr2021 3 papers final.

@@
 
-\def\cvprPaperID{6666} % \times \times \times  Enter the CVPR Paper ID here
+\def\cvprPaperID{297} % \times \times \times  Enter the CVPR Paper ID here
 \def\confYear{CVPR 2021}
@@
 \begin{abstract}
-  For the shortest path calculation task of all nodes in networks, Alon \etal~\cite{alon1997exponent} proposed an algorithm with matrix multiplication.
-  In this paper, with the distance product association law and block matrix multiplication, all-pairs shortest path algorithm has a lowered time-bound of \(O(\log{n}2n^3)\).
+  For the shortest path calculation of the all-pairs nodes in networks, Alon \etal~\cite{alon1997exponent} proposed an algorithm with matrix multiplication.
+  In this paper, with the distance product association law and block matrix multiplication, all-pairs shortest path algorithm has a lowered time-bound of \(O(2\log{n}n^3)\).
   The proposed all-pairs shortest path algorithm, which has an improved lower time-bound \(O(14n^3)\), leverages matrix sparseness judgment, convergence judgment, distance product with matrix multiplication, association law for distance product,
@@
 On the actors' social network, this paper implements Strassen block matrix multiplication, Copper-Winograd block matrix multiplication, and OpenBLAS matrix multiplication.
-On the computer hardware, compared the $8508\times 8508$ matrix multiplication time-cost.
+On the computer hardware, compared the $8508\times 8508$ matrix multiplication time cost.
 The block matrix multiplication based on Strassen and Coppersmith-Winograd takes 6 seconds for one iteration of matrix multiplication, and with the OpenBLAS library, it takes only 4 seconds.
@@
 
-Definition 1 (Outer Product Matrix Multiplication) Given matrices \(\Bbb A \in \Bbb R^{m\times r}\), \(\Bbb B \in \Bbb R^{r\times n}\) and \(\Bbb C \in \Bbb R^{m\times n}\), the outer product is:
+Definition 1 ($\textbf{Outer Product Matrix Multiplication}$) Given matrices \(\Bbb A \in \Bbb R^{m\times r}\), \(\Bbb B \in \Bbb R^{r\times n}\) and \(\Bbb C \in \Bbb R^{m\times n}\), the outer product is:
 \begin{equation}
@@
 
-Definition 2 (Distance Product Matrix Multiplication) Given matrices \(\Bbb A \in \Bbb R^{m\times r}\), \(\Bbb B \in \Bbb R^{r\times n}\) and \(\Bbb C \in \Bbb R^{m\times n}\), the distance product is:
+Definition 2 ($\textbf{Distance Product Matrix Multiplication}$) Given matrices \(\Bbb A \in \Bbb R^{m\times r}\), \(\Bbb B \in \Bbb R^{r\times n}\) and \(\Bbb C \in \Bbb R^{m\times n}\), the distance product is:
 \begin{equation}
@@
 \end{center}
-   \caption{Adjacent matrix, each iterations and the result matrix visualization of actors' social network.
-(a) initial state after each round of calculation, (b) the result matrix after the first round of calculation, (c) the result matrix of the second round of calculation, (d) the third and in the same time last round of calculation, the all-pairs nodes shortest path result matrix.}
+   \caption{Visualization for each epoch: start state of adjacent matrix, iteration states, and the result states of the actors' social network.
+   (a) initial state before calculation,
+   (b) the result matrix of the first epoch calculation,
+   (c) the result matrix of the second epoch calculation,
+   (d) the third epoch of calculation, which is also the final state, that is the all-pairs nodes shortest path result matrix.}
 \label{fig:short}
@@
 
-\subsection{Maximum Calculation}
+\subsection{Maximum Element Value Calculation}
 
-Calculate the largest value of the square matrix element $\widetilde X$, such as the Formula (4).
+Calculate the largest value of the square matrix element $\widetilde X$, this maximum value is latter used in the exponential computations.
 
@@
 
-The calculation precision of different computer hardware complies with the IEEE floating point operation standard~\cite{ieee1985ieee},
+The precision of different computer hardware complies with the IEEE floating point operation standard~\cite{ieee1985ieee},
 first of all, transform the input matrix by exponential transformation, to be specific, taking the number of nodes as the base,
-taking the difference between the largest value of the element $\widetilde X$ and the matrix elements as exponential, as shown in the Formula (5).
+taking the difference between the largest value of the element $\widetilde X$ and the matrix elements as exponential.
 For the actors' social network with 8508 nodes, the diameter of the network does not allow to exceed 9.8 and 78.4 when calculating precision of 32-bit floating point and 64-bit floating point,
@@
 
-\subsection{Distance Product Exchange Law}
+\subsection{Distance Product Association Law}
 
@@
 
-Definition 3 (Result Reuse in Distance Product) According to the nature of the Equation (8), the process of calculating the shortest path iteration using the last result of distance product follows in turn, as shown in Formula (11).
+Definition 3 ($\textbf{Result Reuse in Distance Product}$) According to the nature of the Equation (8), the process of calculating the shortest path iteration using the last result of distance product follows in turn, as shown in Formula (11).
 The shortest path needs to be calculated $\lceil{log_2(n-1)}\rceil$ times matrix multiplication, from the Formula (10), it can be seen that $(n-1)\leq2^{\lceil{log_2(n-1)}\rceil}$ is the same as the simple shortest path matrix calculation result $L^{(n-1)}$, so there is a Formula (12).
@@
 
-\subsection{The Shortest Path Algorithm Fusing Sparseness Judgment And Convergence Judgment}
+\subsection{The Shortest Path Algorithm with Joint Sparseness Judgment and Convergence Judgment}
 
@@
 This paper discussed a novel algorithm in the all-pairs shortest path computation tasks, using distance product association law.
-The time-bound of Alon \etal distance product algorithm with block matrix multiplication is \(O({\log{n}2n^3\over \Bbb B})\).
-To strengthen the conditions, on the scale-free social networks, for the precision limit of floating point operation on hardware, additional condition on the social network diameter is added to avoid floating point operation overflow during the calculation process.
-the algorithm has lower time-bound \(O({14n^3\over \Bbb B})\).
-With strengthened conditions, I proposed a novel algorithm, leveraging matrix sparseness judgment, and calculation convergence judgment.
-\textbf{Power-Law} refers to the network node degrees conforming to the characteristics that social networks power-law distribution, and \textbf{Bound} refers to the limit on floating point arithmetic operations precision on hardware.
-The experimental results show that \textbf{Power-LawBound} algorithm improves time performance by 39\% to 36.2 times on CPU/GPU hardware compared to Alon \etal's algorithm.
+The time-bound of Alon \etal distance product algorithm with block matrix multiplication is \(O({2\log{n}n^3\over \Bbb B})\).
+To strengthen the conditions, on the scale-free social networks, for the precision limit of floating point operation on hardware,
+additional condition on the social network diameter is added to avoid overflow in the floating point operations,
+the analysis showed that the algorithm has a lower time-bound \(O({14n^3\over \Bbb B})\).
+With a hypothesis that all the social networks have limit diameters, I proposed a novel algorithm,
+which leverages matrix sparseness judgment, and calculation convergence judgment.
+\textbf{Power-Law} refers to the network node degrees conforming to the characteristics that social networks power-law distribution,
+and \textbf{Bound} refers to the precision limit for diameters of floating point arithmetic operations on hardware.
+The experimental results show that \textbf{Power-LawBound} algorithm improves time performance by 39\% to 36.2 times
+on CPU/GPU hardware compared to Alon \etal's algorithm.
 

### 2020-10-25 A-BasicCommom/CVPR2021/cvpr_classification.tex
cvpr2021 3 papers final.

@@
 
-\def\cvprPaperID{7777} % *** Enter the CVPR Paper ID here
+\def\cvprPaperID{310} % *** Enter the CVPR Paper ID here
 \def\confYear{CVPR 2021}
@@
 
-  Unsupervised pre-training is important in modern research of deep learning.
-  Lee \etal~\cite{lee2009convolutional} used pre-training approaches
-  in Computer Vision tasks in 2009, and later from 2010 to 2016, Nair and Hinton~\cite{nair2010rectified} proved that the pre-training process is supplementary in the CV tasks,
+  Unsupervised pre-training is important to modern research of deep learning.
+  Lee \etal~\cite{lee2009convolutional} used the pre-training approaches
+  in Computer Vision tasks in 2009, and later from 2010 to 2016,
+  Nair and Hinton~\cite{nair2010rectified} proved that the pre-training process is supplementary in the Computer Vision tasks,
   thus, can be omitted in some cases.

### 2020-10-25 A-BasicCommom/CVPR2021/cvpr_vision.tex
cvpr2021 3 papers final.

@@
 
-\def\cvprPaperID{8888} % *** Enter the CVPR Paper ID here
+\def\cvprPaperID{308} % *** Enter the CVPR Paper ID here
 \def\confYear{CVPR 2021}
@@
 
-  In the film industry, visualizing actor stars' social media for analyzing audience intention towards movies is essential to movie producers.
-  However, non-Euclidean social media is hard to analyze, I propose an FC-GRU-CNN architecture, named as \underline{N}on-\underline{E}uclidean \underline{N}et, for social media visualization.
+  In the film industry, visualizing actor stars' social media for analyzing audience intention towards movies is essential for movie producers.
+  However, non-Euclidean social media is hard to analyze, I propose an FC-GRU-CNN architecture, named as \underline{N}on\underline{E}uclidean\underline{N}et, for social media visualization.
   On the analysis of social media, social relationship representations, network characteristics and media sentiments are key factors.
-  FC-GRU-CNN architecture exploits the long-term memory ability of the GRU layer in long sequences of film cast,
+  The FC-GRU-CNN architecture exploits the long-term memory ability of the GRU layer in the long sequences of film cast,
   the mapping ability of the CNN layer in retrieving all-pairs shortest path of the actors' social relationship,
-  and non-linear capability of deep fully connected layer for movie text sentiments and other characteristics.
+  and non-linear capability in deep fully connected layer for movie text sentiments and other characteristics.
   The proposed model accuracy is 14\% higher than Reed \etal~\cite{reed2016learning}'s model.
@@
 
-  With the development of social networks, actors' influence of social media is increasing, and the influence of actors' consumption spReeds through social networks,
-  and using long-term social network data to study the relationships between all actors, directors, and films remains a challenge.
-  It is easy to see that the relationship between box-office and the director, actors, scriptwriters, and producers are often non-linear, that is,
+  With the development of social networks, the actors' influence of social media is increasing,
+  and the influence of actors' consumption spreads through social networks,
+  and using the long-term social network data to study the relationships between all actors, directors, and films remains a challenge.
+  It is easy to see that the relationship between the box-office and the director, actors, scriptwriters, and producers are often non-linear, that is,
   it is difficult to use linear functions to build box-office prediction models.
-  By analyzing the social network characteristics of movie actors, sentiments of movies in Sina Weibo posts, all-pairs shortest path,
-  it is easy to get the priority of each characteristic by analysis of feature importance,
+  By analyzing the social network characteristics of the movie actors, sentiments of movies in Sina Weibo posts, all-pairs shortest path,
+  it is easy to summarize the priority of each characteristic by analysis of feature importance,
   the existing prediction algorithm only makes use of the film metadata, lacks the study on the social network characteristics of the actors,
@@
 
-\section{Representation Learning for Social Relationship, Network Characteristics and artisticContribution}
+\section{Representation Learning for Social Relationship, Network Characteristics and Artistic Contribution}
 
@@
 
-Machine learning methods such as Linear Regression, SVN, MLP, Logistic Regression, and Na{\'i}ve Bayes cannot converge on the data set,
+Machine learning methods such as Linear Regression, SVM, MLP, Logistic Regression, and Na{\'i}ve Bayes cannot converge on the data set,
 possibly because the sentiments on actors' social networks do not represent the commercial benefits of the film.
@@
 
-\section{FC-GRU-CNN Box-Office Prediction Model}
+\section{the FC-GRU-CNN Box-Office Prediction Model}
 
@@
 Look at the box-office distribution of $1296$ films released between 2011 and 2015,
-Consider box-office forecasts as a binary classification task.
+box-office forecasts can be seen as a binary classification task.
 To make the data evenly distributed, the film data were pre-processed by using the median box-office of $2.635$ million as the dividing line.
@@
 \end{itemize}
-Finally, the three parts are merged into one layer and then connect to a Softmax layer, and the $L_2$ regularization method is adopted to avoid overfitting.
+Finally, these three parts are merged into one layer and then connect to a Softmax layer, and the $L_2$ regularization method is adopted to avoid overfitting.
 

### 2020-10-28 A-BasicCommom/wordtovector/data.py
1.word2vector train model.

@@ -1,0 +1,507 @@
+"""Data processor for SMP-CAIL2020-Argmine.
+
+Author: Yixu GAO (yxgao19@fudan.edu.cn)
+
+In data file, each line contains 1 sc sentence and 5 bc sentences.
+The data processor convert each line into 5 samples,
+each sample with 1 sc sentence and 1 bc sentence.
+
+Usage:
+1. Tokenizer (used for RNN model):
+    from data import Tokenizer
+    vocab_file = 'vocab.txt'
+    sentence = '我饿了，想吃东西了。'
+    tokenizer = Tokenizer(vocab_file)
+    tokens = tokenizer.tokenize(sentence)
+    # ['我', '饿', '了', '，', '想', '吃', '东西', '了', '。']
+    ids = tokenizer.convert_tokens_to_ids(tokens)
+2. Data:
+    from data import Data
+    # For training, load train and valid set
+    # For BERT model
+    data = Data('model/bert/vocab.txt', model_type='bert')
+    datasets = data.load_train_and_valid_files(
+        'SMP-CAIL2020-train.csv', 'SMP-CAIL2020-valid.csv')
+    train_set, valid_set_train, valid_set_valid = datasets
+    # For RNN model
+    data = Data('model/rnn/vocab.txt', model_type='rnn')
+    datasets = data.load_all_files(
+        'SMP-CAIL2020-train.csv', 'SMP-CAIL2020-valid.csv')
+    train_set, valid_set_train, valid_set_valid = datasets
+    # For testing, load test set
+    data = Data('model/bert/vocab.txt', model_type='bert')
+    test_set = data.load_file('SMP-CAIL2020-test.csv', train=False)
+"""
+import os
+from typing import List, Dict, Tuple
+import jieba
+import lawa
+import nltk
+import torch
+from dataclasses import dataclass
+
+import pandas as pd
+from torch.nn.utils.rnn import pad_sequence
+
+from torch.utils.data import TensorDataset, Dataset
+from transformers import BertTokenizer
+from tqdm import tqdm
+from difflib import SequenceMatcher
+import logging
+logger = logging.getLogger(__name__)
+
+
+class Tokenizer:
+    """Tokenizer for Chinese given vocab.txt.
+
+    Attributes:
+        dictionary: Dict[str, int], {<word>: <index>}
+    """
+    def __init__(self, language='en', vocab_file='vocab.txt'):
+        """Initialize and build dictionary.
+
+        Args:
[…]

### 2020-10-28 A-BasicCommom/wordtovector/evaluate.py

@@ -1,0 +1,78 @@
+import joblib
+import pandas as pd
+from sklearn.metrics.pairwise import cosine_similarity
+from scipy.stats import spearmanr
+from gensim.models import KeyedVectors
+
+def eval(analogy_file, similarity_file):
+    # model = joblib.load("word2vec.model")
+    model = KeyedVectors.load_word2vec_format('word2vec.txt', binary=False)
+    vocab = list(model.wv.vocab.keys())
+    analog = model.wv.most_similar(positive=vocab[0:2], negative=vocab[-1:1], topn=1)
+    print('a+b-c',vocab[0:2],vocab[-1],analog)
+    similarity = model.wv.similarity(*vocab[0:2])
+    print(vocab[0:2],'sim score:', similarity)
+    #model.wv.save_word2vec_format(fname="wv.txt")
+
+    idx_to_word = [word for word in model.wv.vocab.keys()]
+    word_to_idx = {word: i for i, word in enumerate(idx_to_word)}
+
+    # 评估模型
+    def evaluate(filename, embedding_weights):
+        miss = 0
+        if filename.endswith('.csv'):
+            data = pd.read_csv(filename, sep=',', header=None)
+            miss += 1
+        else:
+            if 'analogy' in filename:
+                acclist = model.accuracy(filename)
+                correct = len(acclist[-1]['correct'])
+                total = correct + len(acclist[-1]['incorrect']) + miss
+                if total:
+                    return correct * 1.0 / total
+                return 0
+            else:
+                data = pd.read_csv(filename, sep='\t', header=None)
+
+        human_similarity = []
+        model_similarity = []
+
+        for row in data.itertuples(index=False):
+            word1, word2 = row[0], row[1]
+            # OOV 不计算精度
+            if word1 not in word_to_idx or word2 not in word_to_idx:
+                model_similarity.append(0.5)
+                human_similarity.append(float(row[2]))
+                continue
+            else:
+                # word1_idx, word2_idx = word_to_idx[word1], word_to_idx[word2]
+                word1_embed, word2_embed = embedding_weights[[word1]], embedding_weights[[word2]]
+                model_similarity.append(float(cosine_similarity(word1_embed, word2_embed)))
+                human_similarity.append(float(row[2]))
+
+        spears = spearmanr(human_similarity, model_similarity)
+        return spears.correlation
+
+    total = []
+    if isinstance(analogy_file, list):
+        for ana in analogy_file:
+            evals = evaluate(ana, embedding_weights=model.wv)
[…]

### 2020-10-28 A-BasicCommom/wordtovector/model.py

@@ -1,0 +1,20 @@
+import numpy as np
+import torch
+import torch.nn as nn
+import torch.optim as optim
+import matplotlib.pyplot as plt
+
+# Model
+class Word2Vec(nn.Module):
+    def __init__(self, config):
+        super(Word2Vec, self).__init__()
+        # W and WT is not Traspose relationship
+        self.config = config
+        self.W = nn.Linear(self.config.vocab_size, self.config.embedding_size, bias=False) # voc_size > embedding_size Weight
+        self.WT = nn.Linear(self.config.embedding_size, self.config.vocab_size, bias=False) # embedding_size > voc_size Weight
+
+    def forward(self, X):
+        # X : [batch_size, voc_size]
+        hidden_layer = self.W(X) # hidden_layer : [batch_size, embedding_size]
+        output_layer = self.WT(hidden_layer) # output_layer : [batch_size, voc_size]
+        return output_layer

### 2020-10-28 A-BasicCommom/wordtovector/train.py

@@ -1,0 +1,160 @@
+import json
+import os
+from types import SimpleNamespace
+
+import numpy
+import numpy as np
+import pandas
+import torch
+import torch.nn as nn
+import torch.optim as optim
+import matplotlib.pyplot as plt
+from torch.utils.data import DataLoader, RandomSampler
+from tqdm import tqdm
+from vocab import build_vocab
+from utils import get_path
+from model import Word2Vec
+from data import Data, LineByLineTextDataset, DataCollatorForLanguageModeling
+from evaluate import eval
+
+# def random_batch():
+#     random_inputs = []
+#     random_labels = []
+#     random_index = np.random.choice(range(len(skip_grams)), batch_size, replace=False)
+#
+#     for i in random_index:
+#         random_inputs.append(np.eye(voc_size)[skip_grams[i][0]])  # target
+#         random_labels.append(skip_grams[i][1])  # context word
+#
+#     return random_inputs, random_labels
+
+MODEL_MAP = {
+    'skipgram': Word2Vec
+}
+
+if __name__ == '__main__':
+    # batch_size = 2 # mini-batch size
+    # embedding_size = 2 # embedding size
+    #
+    # sentences = ["apple banana fruit", "banana orange fruit", "orange banana fruit",
+    #              "dog cat animal", "cat monkey animal", "monkey dog animal"]
+
+    # word_sequence = " ".join(sentences).split()
+    # word_list = " ".join(sentences).split()
+    # word_list = list(set(word_list))
+    # word_dict = {w: i for i, w in enumerate(word_list)}
+    # voc_size = len(word_list)
+    config_file = 'config/rnn_config.json'
+
+    with open(config_file) as fin:
+        config = json.load(fin, object_hook=lambda d: SimpleNamespace(**d))
+    get_path(os.path.join(config.model_path, config.experiment_name))
+    get_path(config.log_path)
+    # build_vocab(config.train_file_path, os.path.join(config.model_path,'vocab.txt'))
+
+    data = Data(vocab_file=os.path.join(config.model_path, 'vocab.txt'),
+                model_type=config.model_type, config=config)
+    train_dataset, collate_fn = data.load_train_and_valid_files(
+        train_file=config.train_file_path)
+    sampler_train = RandomSampler(train_dataset)
+    data_loader = DataLoader(
+        train_dataset,
+        batch_size=config.batch_size,
+        sampler=sampler_train,
+        collate_fn=collate_fn,
+        drop_last=True,
+    )
+
[…]

### 2020-10-28 A-BasicCommom/wordtovector/vocab.py

@@ -1,0 +1,98 @@
+"""Construct English/Chinese vocab for csv files.
+
+Author: Yixu GAO (yxgao19@fudan.edu.cn)
+
+Use nltk to cut English sentences.
+Use jieba to cut Chinese sentences.
+
+Usage:
+    from vocab import Vocab
+    vocab = Vocab('zh')
+    vocab.load_file_to_dict('SMP-CAIL2020-train.csv', list(range(2, 8)))
+    vocab.load_file_to_dict('SMP-CAIL2020-test1.csv', list(range(2, 8)))
+    vocab.load_file_to_dict('SMP-CAIL2020-test2.csv', list(range(2, 8)))
+    vocab.write2file('vocab.txt', False)
+
+In SMP-CAIL2020-Argmine task, simply run this file
+    python vocab.py
+or
+    from vocab import build_vocab
+    build_vocab()
+"""
+from typing import List, Dict
+
+import lawa
+import nltk
+nltk.download('punkt')
+import pandas as pd
+
+
+class Vocab:
+    """Build vocab for files and write to a file.
+
+    Attributes:
+        language: 'zh' for Chinese and 'en' for English
+        word_dict: word frequency dict, {<word>: frequency}
+            e.g. {'我': 30}
+    """
+
+    def __init__(self, language='zh', word_dict: Dict[str, int] = None):
+        """Initialize with language type and word_dict.
+
+        Args:
+            language: 'zh' or 'en'
+        """
+        self.language = language
+        self.word_dict = word_dict if word_dict else {}
+
+    def load_file_to_dict(
+            self, filename: str, cols: List[int] = None) -> Dict[str, int]:
+        """Load columns of a csv file to word_dict.
+
+        Args:
+            filename: a csv file with ',' as separator
+            cols: column indexes to be added to vocab
+
+        Returns:
+            word_dict: {<word>: frequency}
+        """
+        data_frame = pd.read_csv(filename)
+        if not cols:
+            cols = range(data_frame.shape[1])
+        for row in data_frame.itertuples(index=False):
+            for i in cols:
+                sentence = row[i]
+                if self.language == 'zh':
+                    words = lawa.lcut(sentence)
+                else:  # 'en'
+                    words = nltk.word_tokenize(sentence)
+                for word in words:
+                    self.word_dict[word] = self.word_dict.get(word, 0) + 1
+        return self.word_dict
+
+    def write2file(self,
+                   filename: str = 'vocab.txt', fre: bool = False) -> None:
[…]

### 2020-11-06 A-BasicCommom/CVPR2021/cvpr_covid.tex
1.cov

--- 2020-10-25 A-BasicCommom/CVPR2021/cvpr_classification.tex
@@
 %%%%%%%%% TITLE
-\title{Enhance Image Classification Performance Via Unsupervised Pre-trained Transformers Language Models}
+\title{Unify Language and Vision: An Efficient COVID-19 Tomography Image Classification Approach}
 
@@
 
-  Image classification and categorization are essential to the capability of telling the difference between images for a machine.
-  As \underline{B}idirectional \underline{E}ncoder \underline{R}epresentations from \underline{T}ransformers became popular in many tasks of natural language processing recent years,
-  it is intuitive to use these pre-trained language models for enhancing the computer vision tasks, \eg image classification.
-  In this paper, by encoding image pixels using pre-trained transformers, then connect to a fully connected layer,
-  the classification model outperforms the Wide ResNet model and the linear-probe iGPT-L model,
-  and achieved accuracy of $99.60\%\sim99.74\%$ on the CIFAR-10 image set and accuracy of $99.10\%\sim99.76\%$ on the CIFAR-100 image set.
+  An accurate and efficient image classification algorithm used in the COVID-19 detection for lung tomography can be of great help for doctors working in places without advance equipments.
+  The machine with high accuracy COVID-19 classification model can relief the burden by making testing and checking thousands of people's tomography images easy for a specific region which suffers from the COVID-19 outbreak incidents.
+  By encoding image pixels and metadata using the pre-trained language models of \underline{B}idirectional \underline{E}ncoder \underline{R}epresentations from \underline{T}ransformers,
+  then connect to a fully connected layer,
+  the classification model outperforms the ResNet model and the DenseNet image classification model,
+  and achieved accuracy of $99.51\%\sim100.00\%$ on the COVID-19 tomography image test set.
 
@@
 
+  Natural language processing and Computer Vision are two domains of the Computer Science.
+  However, the encoded representation for the languages and images showed that there are potential connections between what we see and what we write.
   Unsupervised pre-training is important to modern research of deep learning.
@@
 %-------------------------------------------------------------------------
+\subsection{Dataset}
+
+In total, 349 computed tomography images were collected from the COVID-19 reports in the MedPix, LUNA, Radiopaedia, PubMed Central databases, which sizes range from $1637\times1225$ to $148\times61$.
+
 \subsection{Approach}
 
-My approach consists of a pre-training state followed by a fine-tuning stage.
-In pre-training, I use BERT objectives and the sequence Transformer architecture to predict language tokens.
+My approach consists of a pre-training stage followed by a fine-tuning stage.
+In pre-training, I use the BERT objectives and the sequence Transformer architecture to predict language tokens.
 
@@
 
-\par I used RBTL3 and RoBERTa-wwm-ext-large pre-trained language model in two Chinese Judicial datasets, which has 2 and 4 classes.
-The \textit{Case-2} dataset annotated civil and criminal cases, and the \textit{Case-4} dataset annotated by civil, criminal, intellectual property, and administrative cases.
-The \textit{Case-2} dataset has $19508$ training documents and $2000$ test documents, and the \textit{Case-4} dataset has $34789$ training documents and $2013$ test documents.
-
 \par From table (1), by combining the pre-trained language model with fully connected layer as the document classification model,
@@
 Therefore, the pixel channels of an image can be properly represented by these pre-trained language models.
-
-\begin{table}
-\begin{center}
-\begin{tabular}{|l|c|r|}
-\hline
-Language Model 	& Dataset & Accuracy \\
-\hline\hline
-RoBERTa-wwm-ext-large & Case-2	&	99.80\% \\
-RoBERTa-wwm-ext-large & Case-4	&	99.76\% \\
-RBTL3  & Case-4	&	96.35\% \\
-\hline
-\end{tabular}
-\end{center}
-\caption{Comparision of accuracy of the pre-trained language models on different datasets in the document classification task.}
-\end{table}
-%-------------------------------------------------------------------------
 
@@
 I design simple classification models without too many layers, as Figure (1) shows.
-And use the CIFAR-10 and CIFAR-100 dataset as an example to show the architecture of the model.
+And use the COVID-19 lung tomography dataset as an example to show the architecture of the model.
 The model architecture has seven functional layers:
@@
 
-\par The CIFAR-10 dataset contains 60000 color images with a resolution of 32x32 in 10 classes, and the CIFAR-100 dataset has 100 classes containing 600 images each.
+\par The original tomography images are of different sizes and often too large to feed into the model.
+
+The COVID-19 lung tomography dataset contains 251 covid images and 291 covid negative images in the training set,
+and contains 98 covid image and 100 covid negative images in the test set.
+All images are resized to a resolution of 32x32 pixels, RGB channels are kept and the alpha channel is discarded.
 Encode the image by the sequence of RGB channel values, in the order of Red-channel, Green-channel, and Blue-channel,
-then encode other meta-data if provided, as a sequence of ASCII characters.
+then encode other metadata which is the file name of each image, as a sequence of ASCII characters.
 In the Concatenation layer, the pixel-channel value and metadata are concatenated, put a special token of $\textbf{[CLS]}$ at the start,
@@
 \par It is intuitive for the model to use both the channel values and the metadata during the training phase.
-For the CIFAR-10 and CIFAR-100 dataset, the metadata is the filename of the images, which can be treated as the supervised description of the image.
-Peek some the filenames, \eg \textit{wagon\_s\_001343.png}, \textit{banana\_boat\_s\_001615.png}, and \textit{delivery\_truck\_s\_001529.png},
+For the COVID-19 lung tomography dataset, the metadata is the filename of the images, which can be treated as the supervised description of the image.
+Peek some the filenames, \eg \textit{covid\_201\_1.png}, \textit{covid\_201\_2.png}, and \textit{noncovid\_001\_1.png},
 and it is beneficial for the classification model to understand the supervised descriptive information for the image.
@@
 \begin{center}
-  \fbox{\rule{0pt}{2in} \includegraphics[width=0.9\linewidth]{roberta-cifar.pdf}}
+  \fbox{\rule{0pt}{2in} \includegraphics[width=0.9\linewidth]{image-classification.pdf}}
 \end{center}
@@
 
-\par When fine-tuning, as Figure (2), I check the accuracy of the trained model on the test set and stopped training when it converges on $10^{-3}\sim10^{-4}$.
+\par When fine-tuning, as Figure (1), I check the accuracy of the trained model on the test set and stopped training when it converges on $10^{-3}\sim10^{-4}$.
 
@@
 \hline
-Language Model 	& Dataset & Epoch & Accuracy \\
+LM& Dimensions & Epochs & Accuracy \\
 \hline\hline
-RBT3   & CIFAR-10 & 6	&	99.74\% \\
-RBTL3  & CIFAR-10 & 6	&	99.72\% \\
-RoBERTa-large  & CIFAR-10 & 6	&	99.60\% \\
-\hline
-RBT3   & CIFAR-100 & 12	&	99.66\% \\
-RBTL3  & CIFAR-100 & 6  & 	99.10\% \\
-RoBERTa-large & CIFAR-100 & 16 &	99.76\% \\
+RBT3   & 768 & 8	&	99.51\% \\
+RBTL3  & 1024 & 3	&	100.00\% \\
+RoBERTa-large  & 1024  & 10	&	100.00\% \\
 \hline
@@
 \end{center}
-\caption{Comparision of accuracy of the pre-trained language models on the CIFAR-10 and CIFAR-100 datasets in the image classification task.
-RoBERTa-large is short for RoBERTa-wwm-ext-large.}
+\caption{Comparision of accuracy of the pre-trained language image classification models on the COVID-19 dataset.
+RoBERTa-large is short for RoBERTa-wwm-ext-large. LM is short for Language Model}
 \end{table}
@@
 This paper proposed a novel idea by using pre-trained language models for image representation and take image classification as an example of its performance in Computer Vision tasks.
- The finding might benefit various subjects, namely Education, Medical, Chemistry, Physics, Cosmology, Geography, Climate and Materials Science for their specific research.
+The finding might benefit the diagnostics of the COVID-19, and improve the accuracy by combining language pre-trained model and the metadata of the computed tomography.
 Tests showed that the proposed model outperforms the iGPT-L model without augmentation on the image dataset,
@@
 and accuracy of $99.10\%\sim99.76\%$ on the CIFAR-100 image set.
+Tested on the COVID-19 tomography image test set, the proposed model achieved accuracy of $99.51\%\sim100.00\%$.
 

### 2020-11-09 A-BasicCommom/CVPR2021/cvpr_covid.tex
1.add a new Paper.

@@
 
-\def\cvprPaperID{310} % *** Enter the CVPR Paper ID here
+\def\cvprPaperID{7435} % *** Enter the CVPR Paper ID here
 \def\confYear{CVPR 2021}
@@
 
-  An accurate and efficient image classification algorithm used in the COVID-19 detection for lung tomography can be of great help for doctors working in places without advance equipments.
-  The machine with high accuracy COVID-19 classification model can relief the burden by making testing and checking thousands of people's tomography images easy for a specific region which suffers from the COVID-19 outbreak incidents.
-  By encoding image pixels and metadata using the pre-trained language models of \underline{B}idirectional \underline{E}ncoder \underline{R}epresentations from \underline{T}ransformers,
+  An accurate and efficient image classification algorithm used in the COVID-19 detection from the lung computed tomography
+  can be of great help for the doctors working in places without advance equipments of diagnostics.
+  The machine with high accuracy COVID-19 classification model can relief the burden by making testing and checking
+  thousands of people's tomography images easier in a specific region, which is suffering from the COVID-19 outbreak incidents.
+  By encoding image pixels and metadata using the pre-trained language models of
+  \underline{B}idirectional \underline{E}ncoder \underline{R}epresentations from \underline{T}ransformers,
   then connect to a fully connected layer,
@@
 
-  Natural language processing and Computer Vision are two domains of the Computer Science.
-  However, the encoded representation for the languages and images showed that there are potential connections between what we see and what we write.
-  Unsupervised pre-training is important to modern research of deep learning.
+  Natural language processing and Computer Vision are two important domains in the Computer Science.
+  However, the encoded representation for the languages and images showed that there are potential connections
+  between what we see and what we write.
+  Most researches have laid lack of attention on the relevance between the Natural language processing and the Computer Vision.
+  In this paper, I discussed a novel method by unifying the representation of languages and visions from the representation layer.
+  Unsupervised pre-training is important to the modern research in deep learning.
   Lee \etal~\cite{lee2009convolutional} used the pre-training approaches
@@
   However, it started to flourish the natural language processing domain since Mikolov \etal~\cite{mikolov2013distributed} had proposed Word2Vec.
-  Not long before Devin \etal~\cite{devlin2019bert}'s BERT language model dominates in most frequently used tasks in natural language processing,
-  which is close resemble of Vicent \etal~\cite{vincent2008extracting}'s Denoising Autoencoder model, which was initially designed for images.
-  The pre-training process becomes one of the most important procedures in deep learning.
+  Not long before Devin \etal~\cite{devlin2019bert}'s Bidirectional Encoder Representations from Transformers language model dominates
+  in most frequently used tasks in the natural language processing domain,
+  which is close resemble of Vicent \etal~\cite{vincent2008extracting}'s denoising autoencoder model, which was initially designed for images.
+  Therefore, the pre-training process becomes one of the most important procedures in deep learning.
 
@@
 My approach consists of a pre-training stage followed by a fine-tuning stage.
-In pre-training, I use the BERT objectives and the sequence Transformer architecture to predict language tokens.
+In pre-training, I use the BERT objectives and the sequence Transformer architecture to predict the language tokens.
 
@@
 embedding for each position.
-Then I use a fully connected layer as a non-linear function from embeddings to image class.
-The dropout layer and the Softmax layer are used for better transfer performance between the training and the test dataset.
+Then I use a fully connected layer as a non-linear function from the embeddings to the image classes.
+A dropout layer and a Softmax layer are used for better transfer performance between the training dataset and the test dataset.
 
@@
 
-\subsection{Image Classification Model}
+\subsection{Model Architecture}
 
@@
 and contains 98 covid image and 100 covid negative images in the test set.
-All images are resized to a resolution of 32x32 pixels, RGB channels are kept and the alpha channel is discarded.
+All images are resized to a resolution of 32x32 pixels, the RGB channels are kept and the alpha channel is discarded.
 Encode the image by the sequence of RGB channel values, in the order of Red-channel, Green-channel, and Blue-channel,
@@
 and get the encoded representation of the token $\textbf{[CLS]}$ as the images' language model embeddings.
-In the Feature-Extraction layer, a combination of one dropout layer, one fully connected layer, and one softmax layer, as equation (2), is used.
+In the Feature-Extraction layer, the combination of a dropout layer, a fully connected layer, and a softmax layer, as equation (2), can provide
+transfer ability for the model from the training dataset to the test dataset.
 In the Output layer, the classification label of the image is feed in the model.
@@
 the metadata, which is the filename in this case, to the image class
-which makes it is unfair to compare the performance with other image classification models.
+which makes it unfair to compare the performance with other image classification models.
 Thus, to be more objective and fair, I add a preprocess for the metadata in the test phase, using the $\textbf{[MASK]}$ token to replace each
@@
 and gives the token-recovery capability to the downstream task model.
+
+\par The $\textbf{[MASK]}$ token provide a fair comparison during the test by masking the language features, therefore,
+it can be seen that the language and the vision fusions during the training and enhance the performance and accuracy for the classification model
+of the CIFAR dataset and the COVID-19 tonography dataset.
 
@@
 \end{center}
-   \caption{Accuracy of the image classification models with the pre-trained language encoder on the CIFAR-10 and CIFAR-100 dataset in the training epochs.}
+   \caption{Accuracy of the image classification models with the pre-trained language encoder on the CIFAR-10, CIFAR-100, and COVID-19 test dataset.}
 \label{fig:short}
@@
 Use the proposed model, and I tried different pre-trained language models to see the impact on classification accuracy.
-From the table-2, for the same size of a dataset with larger classes, it needs more epochs and training time for the classification model.
+From the table (1), it can be seen that the models are trained on the training dataset and validated on the test dataset.
+For the same size of a dataset with larger classes, it needs more epochs and training time for the classification model,
+and the training epochs ranges from 3 to 8.
 For the same RoBERTa language model with different numbers of transformer layers, 24 layers of transformers had better accuracy than 3 layers,

### 2020-11-11 A-BasicCommom/CVPR2021/cvpr_detrec.tex
1.cvpr

% This version of CVPR template is provided by Ming-Ming Cheng.
% Please leave an issue if you found a bug:
% https://github.com/MCG-NKU/CVPR_Template.

\documentclass[review]{cvpr}
%\documentclass[final]{cvpr}

\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[linesnumbered,lined,boxed,commentsnumbered]{algorithm2e}
% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,colorlinks,bookmarks=false]{hyperref}

\def\cvprPaperID{8182} % *** Enter the CVPR Paper ID here
\def\confYear{CVPR 2021}
%\setcounter{page}{4321} % For final version only

\begin{document}

%%%%%%%%% TITLE
\title{Text Detection and Chinese Character Recognition in Natural Scene Images via Pre-trained Vision and Language Models}

\author{Dezhou Shen\\
Department of Computer Science\\
Tsinghua University\\
Beijing, CN 100084\\
{\tt\small sdz15@mails.tsinghua.edu.cn}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
}

\maketitle

%%%%%%%%% ABSTRACT
\begin{abstract}

  Detecting and reading text from natural images is an essential computer vision tasks.
  And Chinese characters have more tokens than English characters, thus OCR in Chinese is harder than English.
  I encode high dimension features extracting from images by ResNet by the pre-trained language models of
  \underline{B}idirectional \underline{E}ncoder \underline{R}epresentations from \underline{T}ransformers,
  then connect to a recurrent neural network layer, and a fully connected layer for Character Recognize architecture
  the classification model outperforms the ResNet model and the DenseNet image classification model,
  and achieved accuracy of $80.0\%$ on the Baidu2019 street scene test set.

\end{abstract}

%%%%%%%%% BODY TEXT
\section{Introduction}

  Reading text from photographs is essential to Natural language processing and Computer Vision.
  OCR of printed documents and recognition of hand-written digits are already known as solved problems,
  however, recognizing characters in natural scenes is more difficult.
  Regarding to the fact that Chinese language has more characters than English, thus it is more difficult to get a satisfactory model.
  Most researches have laid lack of attention on the relevance between the Natural language processing and the Computer Vision.
  In this paper, I discussed a novel method by unifying the representation of languages and visions from the representation layer.
  Unsupervised pre-training is important to the modern research in deep learning.
  Lee \etal~\cite{lee2009convolutional} used the pre-training approaches
  in Computer Vision tasks in 2009, and later from 2010 to 2016,
  Nair and Hinton~\cite{nair2010rectified} proved that the pre-training process is supplementary in the Computer Vision tasks,
  thus, can be omitted in some cases.
  However, it started to flourish the natural language processing domain since Mikolov \etal~\cite{mikolov2013distributed} had proposed Word2Vec.
  Not long before Devin \etal~\cite{devlin2019bert}'s Bidirectional Encoder Representations from Transformers language model dominates
  in most frequently used tasks in the natural language processing domain,
  which is close resemble of Vicent \etal~\cite{vincent2008extracting}'s denoising autoencoder model, which was initially designed for images.
  Therefore, the pre-training process becomes one of the most important procedures in deep learning.

%-------------------------------------------------------------------------

\section{Recent Work}

\begin{figure*}
\begin{center}
  \fbox{\rule{0pt}{2in} \includegraphics[width=0.9\linewidth]{detectionnet.pdf}}
\end{center}
   \caption{Combination of the ResNet, Feature Pyramid Net and Differentiable Binarization Net for scene text detection task.}
\label{fig:short}
\end{figure*}

\subsection{Detection}

  Wang \etal~\cite{wang2012end} used CNN as detection model and achieved accuracy of 84\% by word-level on the ICDAR 2003~\cite{lucas2003icdar} test dataset and Street View Text~\cite{wang2011end} dataset.
  LeCun \etal~\cite{lecun1990handwritten}'s first experiment on handwritten digit recognition, CNN's great potential had been revealed.
  Liao \etal~\cite{liao2020real} proposed a Differentiable Binarization module for segmentation task for text detection, and achieved $82.8\%\sim84.9\%$ of F1 score on the TD500~\cite{yao2012detecting} dataset
   and $81.0\%\sim83.4\%$ on the CTW1500~\cite{liu2019curved} dataset.

\subsection{Recognition}

  Chen \etal~\cite{chen2020generative} trained image representation by sequence Transformers and tested on CIFAR-10 to show it is outperforming to Wide-ResNet
which was inspired by unsupervised natural language representation learning.
  Wang \etal~\cite{wang2019development} reviewed that convolutional neural networks had been proposed in the 1960s, and had its implementation in the 1980s.
  In the 2010s, Krizhevsky \etal~\cite{krizhevsky2012imagenet} proposed the deep architecture, AlexNet, by concatenating multiple components of CNN layers.
  Netzer \etal~\cite{netzer2011reading} used unsupervised feature learning K-means to classify the digits cropped from Street View images and achieved accuracy of 90.6\% in the test dataset.
  A lot of variants of AlexNet had been proposed by researchers and the accuracy of ImageNet had been greatly improved, \eg ZFNet~\cite{zeiler2014visualizing}, VGG~\cite{simonyan2014very}, GoogLeNet~\cite{szegedy2015going}, ResNet~\cite{he2016deep},
  ResNeXt~\cite{xie2017aggregated}, inception-ResNet-v2~\cite{szegedy2016inception}, DenseNet~\cite{huang2016deep}.
  Lin \etal~\cite{lin2017feature} proposed multi-scale convolutional network in feature extraction, and the average precision on the COCO dataset is 56.9\%.

\subsection{Representation of Images}

  Lu and Weng~\cite{lu2007survey} concluded that for the multi-source image classification tasks, additional information such as signatures, texture, context, and ancillary data can be combined to achieve better performance.
And it is difficult in handling the dichotomy between pixels and natural language texts in a single model.
  Cui \etal~\cite{cui2020revisiting} proposed several whole-word-masking pre-trained Chinese language models,
which are improved versions of BERT~\cite{devlin2019bert} pre-trained language models, namely RBT3, RBTL3, and RoBERTa-wwm-ext-large.
These models achieved better performance in Chinese machine reading comprehension, Chinese document classification, and other downstream natural language tasks.
  He and Peng~\cite{he2017fine} combined the vision stream and language stream as two parallel channels for extracting multi-source information in the image classification task,
and tested on the CUB-200-2011 image dataset and achieved $85.55\%$ by combining GoogLeNet~\cite{szegedy2015going} and CNN-RNN~\cite{reed2016learning}, the result outperformed many competitors.

%-------------------------------------------------------------------------

\section{Text Detection Models}

  Recent scene text detection methods can be classified into Regeression-based methods and Segementation-based methods.
  By directly regressing the boxes of the text instances, Xie \etal~\cite{xie2019scene} proposed a dimention-decomposition region to handle scale problem in scene text detection.
  By combining pixel-level prediction and post-precessing, Tian \etal~\cite{tian2019learning} proposed pixel embeddings to clusters for the segmentation results.

\subsection{Image Pre-processing}

  During the training phase, the region of interest in the images will be augmented by left-right flipping, image affine, size resize, random crop and border shrinks.
  These augmentation makes the model more robust and transferable from training dataset to test dataset.

\subsection{Model Architecture}
  As Figure (1) shows, I combined the Residual Net, Feature Pyramid Network, and Differentiable Binarization network for text detection task.

%-------------------------------------------------------------------------

\section{Text Character Recognition Models}

  Image are segmented by the detection model, then each segmentation is preprocessed to a fix size of $120\times32$.
The recogonition model takes the adjusted image as input, and predict the sequence of Chinese Character dictionary index as output.

\begin{figure*}
\begin{center}
  \fbox{\rule{0pt}{2in} \includegraphics[width=0.9\linewidth]{resbertnet.pdf}}
\end{center}
   \caption{Combination of the Residual Net, Bert, Long-Short Term Memory and Fully Connection Net for Chinese character recognition task.}
\label{fig:short}
\end{figure*}

%-------------------------------------------------------------------------
\subsection{Model Architecture}

 As Figure (2) shows, I use a combination of Residual Net, Bert, Long-Short Term Memory and Fully Connection Net for character recognition task.

The model architecture has five functional layers:

\begin{itemize}
\item {\bf Input layer}
\item {\bf Residual Bert layer}
\item {\bf Sequence Decode layer}
\item {\bf Fully Connected layer}
\item {\bf Output layer}
\end{itemize}

All images are resized to a resolution of 120x32 pixels.
Encode the image by the sequence of RGB channel values, in the order of Red-channel, Green-channel, and Blue-channel.
In the Residual Bert  layer, the pixel-channel value are extracted by the residual convolutional network,
then fed into the Bert language model to encode each sub-pixels.
In the Sequence Decode layer, two layers of Long-Short Term Memory networks to decode each Chinese character meanings.
In the Fully Connected layer, extracted tokens are connected to output layer.
In the Output layer, the encoded Chinese character index sequence are feed in the model.

\subsection{The Sub-pixel Encoder}

My approach consists of the feature extraction stage, the sequence decode stage, and the final character mapping state.
In the feature extraction stage, it is intuitive to use the Bert encoder from the pixel level of the image.
However, due to the computational resource limit and the time limit,
It is wise to encode at sub-pixel level.
To be specific, it is practical to encode after the Residual Network extraction, then use the Bert model to encode the result.

The BERT objectives and the sequence Transformer architecture to predict the language tokens.

\par Given an unlabeled dataset $\Bbb X$, the BERT objective samples a sub-sequence $\Bbb S \in \{C\}$,
$C$ represents all possible tokens, and such that for each index $i \in \Bbb S$,
there is independent probability $15\%$ of appearing in $\Bbb S$,
name the token $M$ as the BERT mask.
As equation (1), train the language model by minimizing the BERT objective of the "masked" elements $x_M$
conditioned on the "unmasked" ones $x_{\left[1,n\right]\backslash M}$.

\begin{equation}
  \lambda = \mathop{\Bbb E}\limits_{x\sim\Bbb X} \mathop{\Bbb E}\limits_{M} \sum_{i\in S}{\bigl[-\log{p(x_i\mid x_{\left[1,n \right]\backslash M})\bigr]}}
\end{equation}

\par The transformer decoder takes the image pixels and meta characters sequence $x_1,\cdots,x_n$ and produces a $d$-dimensional
embedding for each position.

For the per-pixel image classification approach, for every RGB channel of pixels in an image,
each pixel had its pixel-channel code, ranges from 0x00 to 0xff for different colors.
Thus, taking these pixels in an image is identical to ASCII characters in a document.
Generality speaking, the performance of the pre-trained language models achieved in the document classification tasks, can be transferred to image classification naturally.

\par Recall that Kim~\cite{kim2014convolutional} had proved that unsupervised pre-trained language model $word2vec$ and CNN outperformed many other machine learning algorithms,
\eg support vector machines and conditional random field, in many datasets such as movie reviews, Stanford sentiment treebank, and TREC question.
Cui \etal's pre-trained language model, namely RBT3, RBTL3, and RoBERTa-wwm-ext-large, had improved performances over many other machine learning algorithms.
BERT and RoBERTa-wwm-ext-large models both achieved an f1-score of 97.8\% in the THUCNews dataset, which contains 65 thousands of news in 10 domains.

\par From table (1), by combining the pre-trained language model with fully connected layer as the document classification model,
the test accuracy exceeds the other popular machine learning algorithms.
Therefore, the pixel channels of an image can be properly represented by these pre-trained language models.

\begin{equation}
  \sigma(\textbf{z})_j = {e^{\textbf{z}_j} \over {\sum_{k=1}^{\textit{K}} e^{\textbf{z}_k}}}, j=1,\cdots,\textit{K}.
\end{equation}

%-------------------------------------------------------------------------

\section{Experiments and Results}

\subsection{Training}

The Baidu Street View character dataset contains 188560 annotated images and from these randomly choose 892 images as the test set.

As Cui \etal~\cite{cui2020revisiting} reported that the training of the RBT3 language model was based on Devlin \etal's model,
moreover, the pre-trained Chinese language models use extra 5 billion training tokens comparing to Devlin \etal's 0.4 billion tokens.
I use a batch size of 32 and train for $10$ epochs using AdamW with $\beta_1=0.99$, $\beta_2=0.999$, and weight decay of $10^{-8}$.
I set the learning rate to $10^{-4}$ and no warmed up or decay are used.

\par The training time for each epoch batch size is 136ms, comparing to the 20ms for one epoch in the legacy model without the Bert encoding layer.
Thus, the time cost for the training increased 5.8 times of before.

\par The experiment was performed on a Google Cloud Nvidia v100, with 32GB of CPU RAM, and with 16GB of GPU memory,
which can provide 125 tera-flops of computation capability.

\subsection{Analysis}

Use the proposed model, and I tried different pre-trained language models to see the impact on classification accuracy.
From the table (1), it can be seen that the models are trained on the training dataset and validated on the test dataset.
For the same size of a dataset with larger classes, it needs more epochs and training time for the classification model.
For the same RoBERTa language model with different numbers of transformer layers, 24 layers of transformers had better accuracy than 3 layers,
however, its training cost grows for the larger language model.
For the same fine-tuned language model, classes number has some impact on the accuracy,
the fewer classes the dataset has, the more accurate results the model can achieve.

\begin{table}
\begin{center}
\begin{tabular}{|l|c|c|r|}
\hline
Model & Dimensions & Epochs & Accuracy \\
\hline\hline
ResNet   & 18 & 50	&	56.25\% \\
ResBertNet  & 18res+3trans & 10	&	80.00\% \\
\hline
\end{tabular}
\end{center}
\caption{Comparision of accuracy of character detection models on the Baidu Street View 2019 dataset.}
\end{table}

\subsection{Discussion}

 Compare to the accuracy of 56.4\% on the Baidu-Street-2019 dataset, our models have preferable better results.
The reason that the model's outstanding performance lies in the large pre-trained data for BERT, on top of that fine-tuned by RoBERTa, and use of extra language corpus of
$5.4$ billions of tokens of wiki data and other resources.
The transformers in the pre-trained language models use multiple layers for representing images and may be used in other Computer Vision task, \eg object detection, gesture prediction.

\section{Conclusion}

This paper proposed a novel idea by using pre-trained language models for scene Chinese text detection and recognition.
The finding improve the accuracy in OCR for Chinese street scene, and might improve the accuracy of other language scene detection and recognition.
Tests showed that the proposed model outperforms the ResNet model without augmentation on the image dataset,
the model achieved accuracy of $88.74\%$ on the Baidu 2019 street view text recognition set.

{\small
\bibliographystyle{ieee_fullname}
\bibliography{cpvr_detrec}
%\begin{thebibliography}{10}
%
%  \bibitem{lee2009convolutional}
%Lee, H., Grosse, R., Ranganath, R. \&  Ng, A.~Y.
%\newblock {Convolutional deep belief networks for scalable unsupervised
%  learning of hierarchical representations}.
%\newblock In {\em Proceedings of the 26th annual international conference on
%  machine learning}, pages 609--616, 2009.
%
%
%\bibitem{nair2010rectified}
%Nair, V. \&  Hinton, G.~E.
%\newblock {Rectified linear units improve restricted boltzmann machines}.
%\newblock In {\em ICML}, 2010.
%
%
%\bibitem{mikolov2013distributed}
%Mikolov, T., Sutskever, I., Chen, K., Corrado, G.~S. \&  Dean, J.
%\newblock {Distributed representations of words and phrases and their
%  compositionality}.
%\newblock In {\em Advances in neural information processing systems}, pages
%  3111--3119, 2013.
%
%
%\bibitem{devlin2019bert}
%Devlin, J., Chang, M.-W., Lee, K. \&  Toutanova, K.
%\newblock {BERT: Pre-training of Deep Bidirectional Transformers for Language
%  Understanding}.
%\newblock In {\em NAACL-HLT (1)}, 2019.
%
%
%\bibitem{vincent2008extracting}
%Vincent, P., Larochelle, H., Bengio, Y. \&  Manzagol, P.-A.
%\newblock {Extracting and composing robust features with denoising
%  autoencoders}.
%\newblock In {\em Proceedings of the 25th international conference on Machine
%  learning}, pages 1096--1103, 2008.
%
%
%\bibitem{chen2020generative}
%Chen, M., Radford, A., Child, R., Wu, J., Jun, H., Dhariwal, P., Luan, D.
% and Sutskever, I.
%\newblock {Generative Pretraining from Pixels}.
%\newblock In {\em Proceedings of the 37th International Conference on Machine
%  Learning}, 2020.
%
%
%\bibitem{wang2019development}
%Wang, W., Yang, Y., Wang, X., Wang, W. \&  Li, J.
%\newblock {Development of convolutional neural network and its application in
%  image classification: a survey}.
%\newblock {\em Optical Engineering}, 58(4):40901, 2019.
%
%
%\bibitem{lecun1990handwritten}
%LeCun, Y., Boser, B.~E., Denker, J.~S., Henderson, D., Howard, R.~E., Hubbard,
%  W.~E. \&  Jackel, L.~D.
%\newblock {Handwritten digit recognition with a back-propagation network}.
%\newblock In {\em Advances in neural information processing systems}, pages
%  396--404, 1990.
%
%
%\bibitem{krizhevsky2012imagenet}
%Krizhevsky, A., Sutskever, I. \&  Hinton, G.~E.
%\newblock {Imagenet classification with deep convolutional neural networks}.
%\newblock In {\em Advances in neural information processing systems}, pages
%  1097--1105, 2012.
%
%
%\bibitem{zeiler2014visualizing}
%Zeiler, M.~D. \&  Fergus, R.
%\newblock {Visualizing and understanding convolutional networks}.
%\newblock In {\em European conference on computer vision}, pages 818--833.
%  Springer, 2014.
%
%
%\bibitem{simonyan2014very}
%Simonyan, K. \&  Zisserman, A.
%\newblock {Very deep convolutional networks for large-scale image recognition}.
%\newblock In {\em 3rd International Conference on Learning Representations,
%  ICLR 2015 - Conference Track Proceedings}, San Diego, CA, United states,
%  2015.
%
%
%\bibitem{szegedy2015going}
%Szegedy, C., Liu, W., Jia, Y., Sermanet, P., Reed, S., Anguelov, D., Erhan, D.,
%  Vanhoucke, V. \&  Rabinovich, A.
%\newblock {Going deeper with convolutions}.
%\newblock In {\em Proceedings of the IEEE conference on computer vision and
%  pattern recognition}, pages 1--9, 2015.
%
%
%\bibitem{he2016deep}
%He, K., Zhang, X., Ren, S. \&  Sun, J.
%\newblock {Deep residual learning for image recognition}.
%\newblock In {\em Proceedings of the IEEE conference on computer vision and
%  pattern recognition}, pages 770--778, 2016.
%
%
%\bibitem{xie2017aggregated}
%Xie, S., Girshick, R., Doll{\'{a}}r, P., Tu, Z. \&  He, K.
%\newblock {Aggregated residual transformations for deep neural networks}.
%\newblock In {\em Proceedings of the IEEE conference on computer vision and
%  pattern recognition}, pages 1492--1500, 2017.
%
%
%
%\bibitem{szegedy2016inception}
%Szegedy, C., Ioffe, S., Vanhoucke, V. \&  Alemi, A.~A.
%\newblock {Inception-v4, inception-ResNet and the impact of residual
%  connections on learning}.
%\newblock In {\em 31st AAAI Conference on Artificial Intelligence, AAAI 2017},
%  pages 4278--4284, San Francisco, CA, United states, 2017.
%
%
%\bibitem{huang2016deep}
%Huang, G., Sun, Y., Liu, Z., Sedra, D. \&  Weinberger, K.~Q.
%\newblock {Deep networks with stochastic depth}.
%\newblock In {\em European conference on computer vision}, pages 646--661.
%  Springer, 2016.
%
%
%
%\bibitem{lu2007survey}
%Lu, D. \&  Weng, Q.
%\newblock {A survey of image classification methods and techniques for
%  improving classification performance}.
%\newblock {\em International journal of Remote sensing}, 28(5):823--870, 2007.
%
%
%\bibitem{cui2020revisiting}
%Cui, Y., Che, W., Liu, T., Qin, B., Wang, S. \&  Hu, G.
%\newblock {Revisiting Pre-Trained Models for Chinese Natural Language
%  Processing}.
%\newblock In {\em Findings of EMNLP}. Association for Computational
%  Linguistics, 2020.
%
%
%\bibitem{he2017fine}
%He, X. \&  Peng, Y.
%\newblock {Fine-grained image classification via combining vision and
%  language}.
%\newblock In {\em Proceedings of the IEEE Conference on Computer Vision and
%  Pattern Recognition}, pages 5994--6002, 2017.
%
%
%\bibitem{reed2016learning}
%Reed, S., Akata, Z., Lee, H. \&  Schiele, B.
%\newblock {Learning deep representations of fine-grained visual descriptions}.
%\newblock In {\em Proceedings of the IEEE Conference on Computer Vision and
%  Pattern Recognition}, pages 49--58, 2016.
%
%
%\bibitem{fernandez2014we}
%Fern{\'{a}}ndez-Delgado, M., Cernadas, E., Barro, S. \&  Amorim, D.
%  Amorim.
%\newblock {Do we need hundreds of classifiers to solve real world
%  classification problems?}
%\newblock {\em The journal of machine learning research}, 15(1):3133--3181,
%  2014.
%
%
%
%\bibitem{kim2014convolutional}
%Kim, Y.
%\newblock {Convolutional neural networks for sentence classification}.
%\newblock In {\em EMNLP 2014 - 2014 Conference on Empirical Methods in Natural
%  Language Processing, Proceedings of the Conference}, pages 1746--1751, Doha,
%  Qatar, 2014.
%
%
%
%\end{thebibliography}
}

\end{document}

### 2020-11-11 A-BasicCommom/CVPR2021/cvpr_detrec.tex
1.fix some typo mistakes.

@@
 
-  Detecting and reading text from natural images is an essential computer vision tasks.
-  And Chinese characters have more tokens than English characters, thus OCR in Chinese is harder than English.
-  I encode high dimension features extracting from images by ResNet by the pre-trained language models of
+  Detecting and reading text from natural scene images is an essential computer vision tasks.
+  Giving the fact that Chinese characters have more tokens than English characters, OCR in Chinese is much harder than English.
+  I encode high dimension features extracting from images by ResNet followed by the pre-trained language models of
   \underline{B}idirectional \underline{E}ncoder \underline{R}epresentations from \underline{T}ransformers,
-  then connect to a recurrent neural network layer, and a fully connected layer for Character Recognize architecture
-  the classification model outperforms the ResNet model and the DenseNet image classification model,
-  and achieved accuracy of $80.0\%$ on the Baidu2019 street scene test set.
+  then connect to a recurrent neural network layer, and a fully connected layer in the Character Recognize architecture.
+  The proposed recognition model outperforms the ResNet recognition model, and achieved accuracy of $71.74\%$ on the Baidu2019 street scene test set.
 
@@
   OCR of printed documents and recognition of hand-written digits are already known as solved problems,
-  however, recognizing characters in natural scenes is more difficult.
+  however, recognizing characters in natural scenes is far more difficult.
   Regarding to the fact that Chinese language has more characters than English, thus it is more difficult to get a satisfactory model.
-  Most researches have laid lack of attention on the relevance between the Natural language processing and the Computer Vision.
-  In this paper, I discussed a novel method by unifying the representation of languages and visions from the representation layer.
+  Most researchers had laid lack of attention on the relevance between the natural language processing and the Computer Vision.
+  In this paper, I discussed a novel method by unifying the representation of languages and visions in the representation layer.
+
   Unsupervised pre-training is important to the modern research in deep learning.
-  Lee \etal~\cite{lee2009convolutional} used the pre-training approaches
-  in Computer Vision tasks in 2009, and later from 2010 to 2016,
+  Lee \etal~\cite{lee2009convolutional} used the pre-training approaches in Computer Vision tasks in 2009, and later from 2010 to 2016,
   Nair and Hinton~\cite{nair2010rectified} proved that the pre-training process is supplementary in the Computer Vision tasks,
   thus, can be omitted in some cases.
-  However, it started to flourish the natural language processing domain since Mikolov \etal~\cite{mikolov2013distributed} had proposed Word2Vec.
-  Not long before Devin \etal~\cite{devlin2019bert}'s Bidirectional Encoder Representations from Transformers language model dominates
-  in most frequently used tasks in the natural language processing domain,
-  which is close resemble of Vicent \etal~\cite{vincent2008extracting}'s denoising autoencoder model, which was initially designed for images.
+  However, it started to flourish in the natural language processing domain since Mikolov \etal~\cite{mikolov2013distributed} had proposed Word2Vec for the word representation.
+  Not long after, Devin \etal~\cite{devlin2019bert}'s Bidirectional Encoder Representations from Transformers language model dominates
+  in most frequent tasks in the natural language processing domain,
+  which is close resemble of Vicent \etal~\cite{vincent2008extracting}'s Denoising Autoencoder model, which was initially designed for images.
   Therefore, the pre-training process becomes one of the most important procedures in deep learning.
@@
 
-  Wang \etal~\cite{wang2012end} used CNN as detection model and achieved accuracy of 84\% by word-level on the ICDAR 2003~\cite{lucas2003icdar} test dataset and Street View Text~\cite{wang2011end} dataset.
-  LeCun \etal~\cite{lecun1990handwritten}'s first experiment on handwritten digit recognition, CNN's great potential had been revealed.
-  Liao \etal~\cite{liao2020real} proposed a Differentiable Binarization module for segmentation task for text detection, and achieved $82.8\%\sim84.9\%$ of F1 score on the TD500~\cite{yao2012detecting} dataset
+  Wang \etal~\cite{wang2012end} used the convolutional neural networks as a detection model and achieved accuracy of 84\% by word-level on the ICDAR2003~\cite{lucas2003icdar} test dataset and Street View Text~\cite{wang2011end} dataset.
+  LeCun \etal~\cite{lecun1990handwritten} started their first experiment on handwritten digit recognition, convolutional neural networks' great potential had been revealed since.
+  Liao \etal~\cite{liao2020real} proposed a Differentiable Binarization module for the segmentation task in the text detection task, and achieved $82.8\%\sim84.9\%$ of F1-score on the TD500~\cite{yao2012detecting} dataset
    and $81.0\%\sim83.4\%$ on the CTW1500~\cite{liu2019curved} dataset.
@@
 
-  Chen \etal~\cite{chen2020generative} trained image representation by sequence Transformers and tested on CIFAR-10 to show it is outperforming to Wide-ResNet
+  Chen \etal~\cite{chen2020generative} trained the image representation using sequence Transformers and tested on the CIFAR-10 to show its outperforming to Wide-ResNet,
 which was inspired by unsupervised natural language representation learning.
-  Wang \etal~\cite{wang2019development} reviewed that convolutional neural networks had been proposed in the 1960s, and had its implementation in the 1980s.
-  In the 2010s, Krizhevsky \etal~\cite{krizhevsky2012imagenet} proposed the deep architecture, AlexNet, by concatenating multiple components of CNN layers.
+  Wang \etal~\cite{wang2019development} reviewed that convolutional neural networks had been first proposed in the 1960s, and had its implementation in the 1980s.
+  In the 2010s, Krizhevsky \etal~\cite{krizhevsky2012imagenet} proposed the deep architecture, AlexNet, by concatenating multiple components of convolutional neural network layers.
   Netzer \etal~\cite{netzer2011reading} used unsupervised feature learning K-means to classify the digits cropped from Street View images and achieved accuracy of 90.6\% in the test dataset.
@@
 
-  Recent scene text detection methods can be classified into Regeression-based methods and Segementation-based methods.
-  By directly regressing the boxes of the text instances, Xie \etal~\cite{xie2019scene} proposed a dimention-decomposition region to handle scale problem in scene text detection.
+  Recent scene text detection methods can be classified into Regression-based methods and Segmentation-based methods.
+  By directly regressing the boxes of the text instances, Xie \etal~\cite{xie2019scene} proposed a dimension-decomposition region to handle scale problem in scene text detection.
   By combining pixel-level prediction and post-precessing, Tian \etal~\cite{tian2019learning} proposed pixel embeddings to clusters for the segmentation results.
@@
 \subsection{Model Architecture}
+
   As Figure (1) shows, I combined the Residual Net, Feature Pyramid Network, and Differentiable Binarization network for text detection task.
-
+  The model has five important layers, such as: Input layer, Residual Convolutional layer, Feature Pyramid layer, Differentiable Binarization layer and Output layer.
+  The Residual Convolutional layer extract import high-level features from the image,
+  and the Feature Pyramid layer join the four parts of features with different size of filter kernels, such as $[64,128,256,512]$.
+  The Differentiable Binarization layer combines the features and use different mapping functions to find the power of the combination of features.
 %-------------------------------------------------------------------------
@@
   Image are segmented by the detection model, then each segmentation is preprocessed to a fix size of $120\times32$.
-The recogonition model takes the adjusted image as input, and predict the sequence of Chinese Character dictionary index as output.
+The recognition model takes the adjusted image as input, and predict the sequence of Chinese Character dictionary index as output.
 
@@
 
-All images are resized to a resolution of 120x32 pixels.
+All images are resized to a resolution of $120\times32$ pixels.
 Encode the image by the sequence of RGB channel values, in the order of Red-channel, Green-channel, and Blue-channel.
@@
 In the Sequence Decode layer, two layers of Long-Short Term Memory networks to decode each Chinese character meanings.
-In the Fully Connected layer, extracted tokens are connected to output layer.
-In the Output layer, the encoded Chinese character index sequence are feed in the model.
+In the Fully Connected layer, extracted tokens are connected to the output layer.
+In the Output layer, the encoded Chinese character index sequence are feed into the model.
 
@@
 \par Recall that Kim~\cite{kim2014convolutional} had proved that unsupervised pre-trained language model $word2vec$ and CNN outperformed many other machine learning algorithms,
-\eg support vector machines and conditional random field, in many datasets such as movie reviews, Stanford sentiment treebank, and TREC question.
+\eg support vector machines and conditional random field, in many datasets such as movie reviews, Stanford sentiment treebank, and the TREC question.
 Cui \etal's pre-trained language model, namely RBT3, RBTL3, and RoBERTa-wwm-ext-large, had improved performances over many other machine learning algorithms.
@@
 
-\par From table (1), by combining the pre-trained language model with fully connected layer as the document classification model,
+\par From Table (1), by combining the pre-trained language model with fully connected layer as the document classification model,
 the test accuracy exceeds the other popular machine learning algorithms.
@@
 
-The Baidu Street View character dataset contains 188560 annotated images and from these randomly choose 892 images as the test set.
+The Baidu Street View character dataset contains 188560 annotated images and randomly choose 892 images as the test set from the total images .
 
@@
 
-Use the proposed model, and I tried different pre-trained language models to see the impact on classification accuracy.
-From the table (1), it can be seen that the models are trained on the training dataset and validated on the test dataset.
-For the same size of a dataset with larger classes, it needs more epochs and training time for the classification model.
-For the same RoBERTa language model with different numbers of transformer layers, 24 layers of transformers had better accuracy than 3 layers,
-however, its training cost grows for the larger language model.
-For the same fine-tuned language model, classes number has some impact on the accuracy,
-the fewer classes the dataset has, the more accurate results the model can achieve.
+For the Bert language model layer, the Table (1) showed that the accuracy of the test set has improved compare to the model without Bert layer.
+For the Bert language model, there are different number of layers ranging from $3\sim24$, and for each layer,
+there are different hidden numbers of neurons for each layer ranging from $768\sim1024$.
+As for the purpose of this paper is to show that the Bert model enhances the accuracy in the Chinese character recognition task,
+I use the least layer and least number of neuron for the bert language model, named RBT3 provided by Cui \etal,
+which was fully pre-trained using the corpus with 4.5 billions of Chinese tokens.
+The model can be easily modified and trained on other languages, \eg English,
+and take less time to train for the less amount of the character types comparing to
+4095 different type in Chinese.
 
@@
 \begin{center}
-\begin{tabular}{|l|c|c|r|}
+\begin{tabular}{|l|c|c|c|r|}
 \hline
-Model & Dimensions & Epochs & Accuracy \\
+Model & Dim & Dataset& Epochs & Accuracy \\
 \hline\hline
-ResNet   & 18 & 50	&	56.25\% \\
-ResBertNet  & 18res+3trans & 10	&	80.00\% \\
+ResNet      & 18 &  ICDAR2015 &50 &	23.67\% \\
+ResNet      & 18 &  Baidu2019	  &50 &	56.25\% \\
+ResBertNet  & 18+3 & Baidu2019    & 50	&	71.74\% \\
 \hline
@@
 \end{center}
-\caption{Comparision of accuracy of character detection models on the Baidu Street View 2019 dataset.}
+\caption{Comparision of accuracy of character detection models on the Baidu Street View 2019 dataset and the ICDAR2015 dataset.
+The ResBertNet uses 18 layers of Residual Network and 3 layers of Transformers.}
 \end{table}
@@
 
- Compare to the accuracy of 56.4\% on the Baidu-Street-2019 dataset, our models have preferable better results.
+From Table (1) we can see that, on the ICDAR2015~\cite{karatzas2015icdar} dataset, the ResNet text recognition model has accuracy of 23.67\%,
+though the ICDAR2015 test set only contains 92 different English characters, numbers and punctuations,
+the ResNet model cannot achieve a satisfactory result after 50 epochs.
+It shows that Street Scene View text recognition task is a hard problem and there is no easy way out.
+Moreover, the Baidu Chinese street text view dataset contains 4095 different character types.
+Compare to the accuracy of 56.25\% on the Baidu2019 street view text dataset, our models have preferable better results.
 The reason that the model's outstanding performance lies in the large pre-trained data for BERT, on top of that fine-tuned by RoBERTa, and use of extra language corpus of
@@
 
-This paper proposed a novel idea by using pre-trained language models for scene Chinese text detection and recognition.
-The finding improve the accuracy in OCR for Chinese street scene, and might improve the accuracy of other language scene detection and recognition.
+This paper proposes a novel idea by using pre-trained language models for Chinese scene text detection and recognition.
+The finding improves the accuracy in OCR for Chinese street scene, and might improve the accuracy of other language scene detection and recognition.
 Tests showed that the proposed model outperforms the ResNet model without augmentation on the image dataset,
-the model achieved accuracy of $88.74\%$ on the Baidu 2019 street view text recognition set.
+the model achieved accuracy of $71.74\%$ on the Baidu 2019 street view text recognition set.
 
@@
 \bibliographystyle{ieee_fullname}
-\bibliography{cpvr_detrec}
-%\begin{thebibliography}{10}
-%
-%  \bibitem{lee2009convolutional}
-%Lee, H., Grosse, R., Ranganath, R. \&  Ng, A.~Y.
-%\newblock {Convolutional deep belief networks for scalable unsupervised
-%  learning of hierarchical representations}.
-%\newblock In {\em Proceedings of the 26th annual international conference on
-%  machine learning}, pages 609--616, 2009.
-%
-%
-%\bibitem{nair2010rectified}
-%Nair, V. \&  Hinton, G.~E.
-%\newblock {Rectified linear units improve restricted boltzmann machines}.
-%\newblock In {\em ICML}, 2010.
-%
-%
-%\bibitem{mikolov2013distributed}
-%Mikolov, T., Sutskever, I., Chen, K., Corrado, G.~S. \&  Dean, J.
-%\newblock {Distributed representations of words and phrases and their
-%  compositionality}.
-%\newblock In {\em Advances in neural information processing systems}, pages
-%  3111--3119, 2013.
-%
-%
-%\bibitem{devlin2019bert}
-%Devlin, J., Chang, M.-W., Lee, K. \&  Toutanova, K.
-%\newblock {BERT: Pre-training of Deep Bidirectional Transformers for Language
-%  Understanding}.
-%\newblock In {\em NAACL-HLT (1)}, 2019.
-%
-%
-%\bibitem{vincent2008extracting}
-%Vincent, P., Larochelle, H., Bengio, Y. \&  Manzagol, P.-A.
-%\newblock {Extracting and composing robust features with denoising
-%  autoencoders}.
-%\newblock In {\em Proceedings of the 25th international conference on Machine
-%  learning}, pages 1096--1103, 2008.
-%
-%
-%\bibitem{chen2020generative}
-%Chen, M., Radford, A., Child, R., Wu, J., Jun, H., Dhariwal, P., Luan, D.
-% and Sutskever, I.
-%\newblock {Generative Pretraining from Pixels}.
-%\newblock In {\em Proceedings of the 37th International Conference on Machine
-%  Learning}, 2020.
-%
-%
-%\bibitem{wang2019development}
-%Wang, W., Yang, Y., Wang, X., Wang, W. \&  Li, J.
-%\newblock {Development of convolutional neural network and its application in
-%  image classification: a survey}.
-%\newblock {\em Optical Engineering}, 58(4):40901, 2019.
-%
-%
-%\bibitem{lecun1990handwritten}
-%LeCun, Y., Boser, B.~E., Denker, J.~S., Henderson, D., Howard, R.~E., Hubbard,
-%  W.~E. \&  Jackel, L.~D.
-%\newblock {Handwritten digit recognition with a back-propagation network}.
-%\newblock In {\em Advances in neural information processing systems}, pages
-%  396--404, 1990.
-%
-%
-%\bibitem{krizhevsky2012imagenet}
-%Krizhevsky, A., Sutskever, I. \&  Hinton, G.~E.
-%\newblock {Imagenet classification with deep convolutional neural networks}.
-%\newblock In {\em Advances in neural information processing systems}, pages
-%  1097--1105, 2012.
-%
-%
-%\bibitem{zeiler2014visualizing}
-%Zeiler, M.~D. \&  Fergus, R.
-%\newblock {Visualizing and understanding convolutional networks}.
-%\newblock In {\em European conference on computer vision}, pages 818--833.
-%  Springer, 2014.
-%
-%
-%\bibitem{simonyan2014very}
-%Simonyan, K. \&  Zisserman, A.
-%\newblock {Very deep convolutional networks for large-scale image recognition}.
-%\newblock In {\em 3rd International Conference on Learning Representations,
-%  ICLR 2015 - Conference Track Proceedings}, San Diego, CA, United states,
-%  2015.
-%
-%
-%\bibitem{szegedy2015going}
-%Szegedy, C., Liu, W., Jia, Y., Sermanet, P., Reed, S., Anguelov, D., Erhan, D.,
-%  Vanhoucke, V. \&  Rabinovich, A.
-%\newblock {Going deeper with convolutions}.
-%\newblock In {\em Proceedings of the IEEE conference on computer vision and
-%  pattern recognition}, pages 1--9, 2015.
-%
-%
-%\bibitem{he2016deep}
-%He, K., Zhang, X., Ren, S. \&  Sun, J.
-%\newblock {Deep residual learning for image recognition}.
-%\newblock In {\em Proceedings of the IEEE conference on computer vision and
-%  pattern recognition}, pages 770--778, 2016.
-%
-%
-%\bibitem{xie2017aggregated}
-%Xie, S., Girshick, R., Doll{\'{a}}r, P., Tu, Z. \&  He, K.
-%\newblock {Aggregated residual transformations for deep neural networks}.
-%\newblock In {\em Proceedings of the IEEE conference on computer vision and
-%  pattern recognition}, pages 1492--1500, 2017.
-%
-%
-%
-%\bibitem{szegedy2016inception}
-%Szegedy, C., Ioffe, S., Vanhoucke, V. \&  Alemi, A.~A.
-%\newblock {Inception-v4, inception-ResNet and the impact of residual
-%  connections on learning}.
-%\newblock In {\em 31st AAAI Conference on Artificial Intelligence, AAAI 2017},
-%  pages 4278--4284, San Francisco, CA, United states, 2017.
-%
-%
-%\bibitem{huang2016deep}
-%Huang, G., Sun, Y., Liu, Z., Sedra, D. \&  Weinberger, K.~Q.
-%\newblock {Deep networks with stochastic depth}.
-%\newblock In {\em European conference on computer vision}, pages 646--661.
-%  Springer, 2016.
-%
-%
-%
-%\bibitem{lu2007survey}
-%Lu, D. \&  Weng, Q.
-%\newblock {A survey of image classification methods and techniques for
-%  improving classification performance}.
-%\newblock {\em International journal of Remote sensing}, 28(5):823--870, 2007.
-%
-%
-%\bibitem{cui2020revisiting}
-%Cui, Y., Che, W., Liu, T., Qin, B., Wang, S. \&  Hu, G.
-%\newblock {Revisiting Pre-Trained Models for Chinese Natural Language
-%  Processing}.
-%\newblock In {\em Findings of EMNLP}. Association for Computational
-%  Linguistics, 2020.
-%
-%
-%\bibitem{he2017fine}
-%He, X. \&  Peng, Y.
-%\newblock {Fine-grained image classification via combining vision and
-%  language}.
-%\newblock In {\em Proceedings of the IEEE Conference on Computer Vision and
-%  Pattern Recognition}, pages 5994--6002, 2017.
-%
-%
-%\bibitem{reed2016learning}
-%Reed, S., Akata, Z., Lee, H. \&  Schiele, B.
-%\newblock {Learning deep representations of fine-grained visual descriptions}.
-%\newblock In {\em Proceedings of the IEEE Conference on Computer Vision and
-%  Pattern Recognition}, pages 49--58, 2016.
-%
-%
-%\bibitem{fernandez2014we}
-%Fern{\'{a}}ndez-Delgado, M., Cernadas, E., Barro, S. \&  Amorim, D.
-%  Amorim.
-%\newblock {Do we need hundreds of classifiers to solve real world
-%  classification problems?}
-%\newblock {\em The journal of machine learning research}, 15(1):3133--3181,
-%  2014.
-%
-%
-%
-%\bibitem{kim2014convolutional}
-%Kim, Y.
-%\newblock {Convolutional neural networks for sentence classification}.
-%\newblock In {\em EMNLP 2014 - 2014 Conference on Empirical Methods in Natural
-%  Language Processing, Proceedings of the Conference}, pages 1746--1751, Doha,
-%  Qatar, 2014.
-%
-%
-%
-%\end{thebibliography}
+%\bibliography{cpvr_detrec}
+\begin{thebibliography}{10}
+
+  \bibitem{lee2009convolutional}
+Honglak Lee, Roger Grosse, Rajesh Ranganath, and Andrew~Y Ng.
+\newblock Convolutional deep belief networks for scalable unsupervised learning
+  of hierarchical representations.
+\newblock In {\em Proceedings of the 26th annual international conference on
+  machine learning}, pages 609--616, 2009.
+
+\bibitem{nair2010rectified}
+Vinod Nair and Geoffrey~E Hinton.
+\newblock Rectified linear units improve restricted boltzmann machines.
+\newblock In {\em ICML}, 2010.
+
+\bibitem{mikolov2013distributed}
+Tomas Mikolov, Ilya Sutskever, Kai Chen, Greg~S Corrado, and Jeff Dean.
+\newblock Distributed representations of words and phrases and their
+  compositionality.
+\newblock In {\em Advances in neural information processing systems}, pages
+  3111--3119, 2013.
+
+\bibitem{devlin2019bert}
+Jacob Devlin, Ming-Wei Chang, Kenton Lee, and Kristina Toutanova.
+\newblock Bert: Pre-training of deep bidirectional transformers for language
+  understanding.
+\newblock In {\em NAACL-HLT (1)}, 2019.
+
+\bibitem{vincent2008extracting}
+Pascal Vincent, Hugo Larochelle, Yoshua Bengio, and Pierre-Antoine Manzagol.
+\newblock Extracting and composing robust features with denoising autoencoders.
+\newblock In {\em Proceedings of the 25th international conference on Machine
+  learning}, pages 1096--1103, 2008.
+
+\bibitem{wang2012end}
+Tao Wang, David~J Wu, Adam Coates, and Andrew~Y Ng.
+\newblock End-to-end text recognition with convolutional neural networks.
+\newblock In {\em Proceedings of the 21st international conference on pattern
+  recognition (ICPR2012)}, pages 3304--3308. IEEE, 2012.
+
+\bibitem{lucas2003icdar}
+Simon~M Lucas, Alex Panaretos, Luis Sosa, Anthony Tang, Shirley Wong, and
+  Robert Young.
+\newblock Icdar 2003 robust reading competitions.
+\newblock In {\em Seventh International Conference on Document Analysis and
+  Recognition, 2003. Proceedings.}, pages 682--687. Citeseer, 2003.
+
+\bibitem{wang2011end}
+Kai Wang, Boris Babenko, and Serge Belongie.
+\newblock End-to-end scene text recognition.
+\newblock In {\em 2011 International Conference on Computer Vision}, pages
+  1457--1464. IEEE, 2011.
+
+\bibitem{lecun1990handwritten}
+Yann LeCun, Bernhard~E Boser, John~S Denker, Donnie Henderson, Richard~E
+  Howard, Wayne~E Hubbard, and Lawrence~D Jackel.
+\newblock Handwritten digit recognition with a back-propagation network.
+\newblock In {\em Advances in neural information processing systems}, pages
+  396--404, 1990.
+
+\bibitem{liao2020real}
+Minghui Liao, Zhaoyi Wan, Cong Yao, Kai Chen, and Xiang Bai.
+\newblock Real-time scene text detection with differentiable binarization.
+\newblock In {\em AAAI}, pages 11474--11481, 2020.
+
+\bibitem{yao2012detecting}
+Cong Yao, Xiang Bai, Wenyu Liu, Yi~Ma, and Zhuowen Tu.
+\newblock Detecting texts of arbitrary orientations in natural images.
+\newblock In {\em 2012 IEEE conference on computer vision and pattern
+  recognition}, pages 1083--1090. IEEE, 2012.
+
+  \bibitem{liu2019curved}
+Yuliang Liu, Lianwen Jin, Shuaitao Zhang, Canjie Luo, and Sheng Zhang.
+\newblock Curved scene text detection via transverse and longitudinal sequence
+  connection.
+\newblock {\em Pattern Recognition}, 90:337--345, 2019.
+
+\bibitem{chen2020generative}
+Mark Chen, Alec Radford, Rewon Child, Jeff Wu, Heewoo Jun, Prafulla Dhariwal,
+  David Luan, and Ilya Sutskever.
+\newblock Generative pretraining from pixels.
+\newblock In {\em Proceedings of the 37th International Conference on Machine
+  Learning}, 2020.
+
+\bibitem{wang2019development}
+Wei Wang, Yujing Yang, Xin Wang, Weizheng Wang, and Ji~Li.
+\newblock Development of convolutional neural network and its application in
+  image classification: a survey.
+\newblock {\em Optical Engineering}, 58(4):040901, 2019.
+
+  \bibitem{krizhevsky2012imagenet}
+Alex Krizhevsky, Ilya Sutskever, and Geoffrey~E Hinton.
+\newblock Imagenet classification with deep convolutional neural networks.
+\newblock In {\em Advances in neural information processing systems}, pages
+  1097--1105, 2012.
+
+\bibitem{netzer2011reading}
+Yuval Netzer, Tao Wang, Adam Coates, Alessandro Bissacco, Bo~Wu, and Andrew~Y
+  Ng.
+\newblock Reading digits in natural images with unsupervised feature learning.
+\newblock 2011.
+
+\bibitem{zeiler2014visualizing}
+Matthew~D Zeiler and Rob Fergus.
+\newblock Visualizing and understanding convolutional networks.
+\newblock In {\em European conference on computer vision}, pages 818--833.
+  Springer, 2014.
+
+  \bibitem{simonyan2014very}
+Karen Simonyan and Andrew Zisserman.
+\newblock Very deep convolutional networks for large-scale image recognition.
+\newblock San Diego, CA, United states, 2015.
+\newblock Convnet;Convolution filters;Convolutional networks;Localisation;Prior
+  arts;State of the art;Visual representations;.
+
+\bibitem{szegedy2015going}
+Christian Szegedy, Wei Liu, Yangqing Jia, Pierre Sermanet, Scott Reed, Dragomir
+  Anguelov, Dumitru Erhan, Vincent Vanhoucke, and Andrew Rabinovich.
+\newblock Going deeper with convolutions.
+\newblock In {\em Proceedings of the IEEE conference on computer vision and
+  pattern recognition}, pages 1--9, 2015.
+
+\bibitem{he2016deep}
+Kaiming He, Xiangyu Zhang, Shaoqing Ren, and Jian Sun.
+\newblock Deep residual learning for image recognition.
+\newblock In {\em Proceedings of the IEEE conference on computer vision and
+  pattern recognition}, pages 770--778, 2016.
+
+\bibitem{xie2017aggregated}
+Saining Xie, Ross Girshick, Piotr Doll{\'a}r, Zhuowen Tu, and Kaiming He.
+\newblock Aggregated residual transformations for deep neural networks.
+\newblock In {\em Proceedings of the IEEE conference on computer vision and
+  pattern recognition}, pages 1492--1500, 2017.
+
+\bibitem{szegedy2016inception}
+Christian Szegedy, Sergey Ioffe, Vincent Vanhoucke, and Alexander~A. Alemi.
+\newblock Inception-v4, inception-resnet and the impact of residual connections
+  on learning.
+\newblock pages 4278 -- 4284, San Francisco, CA, United states, 2017.
+\newblock Classification tasks;Computational costs;Convolutional
+  networks;Single frames;State-of-the-art performance;Test sets;Traditional
+  architecture;.
+
+\bibitem{huang2016deep}
+Gao Huang, Yu~Sun, Zhuang Liu, Daniel Sedra, and Kilian~Q Weinberger.
+\newblock Deep networks with stochastic depth.
+\newblock In {\em European conference on computer vision}, pages 646--661.
+  Springer, 2016.
+
+\bibitem{lin2017feature}
+Tsung-Yi Lin, Piotr Doll{\'a}r, Ross Girshick, Kaiming He, Bharath Hariharan,
+  and Serge Belongie.
+\newblock Feature pyramid networks for object detection.
+\newblock In {\em Proceedings of the IEEE conference on computer vision and
+  pattern recognition}, pages 2117--2125, 2017.
+
+\bibitem{lu2007survey}
+Dengsheng Lu and Qihao Weng.
+\newblock A survey of image classification methods and techniques for improving
+  classification performance.
+\newblock {\em International journal of Remote sensing}, 28(5):823--870, 2007.
+
+\bibitem{cui2020revisiting}
+Yiming Cui, Wanxiang Che, Ting Liu, Bing Qin, Shijin Wang, and Guoping Hu.
+\newblock Revisiting pre-trained models for chinese natural language
+  processing.
+\newblock In {\em Findings of EMNLP}. Association for Computational
+  Linguistics, 2020.
+
+\bibitem{he2017fine}
+Xiangteng He and Yuxin Peng.
+\newblock Fine-grained image classification via combining vision and language.
+\newblock In {\em Proceedings of the IEEE Conference on Computer Vision and
+  Pattern Recognition}, pages 5994--6002, 2017.
+
+\bibitem{reed2016learning}
+Scott Reed, Zeynep Akata, Honglak Lee, and Bernt Schiele.
+\newblock Learning deep representations of fine-grained visual descriptions.
+\newblock In {\em Proceedings of the IEEE Conference on Computer Vision and
+  Pattern Recognition}, pages 49--58, 2016.
+
+\bibitem{xie2019scene}
+Enze Xie, Yuhang Zang, Shuai Shao, Gang Yu, Cong Yao, and Guangyao Li.
+\newblock Scene text detection with supervised pyramid context network.
+\newblock In {\em Proceedings of the AAAI Conference on Artificial
+  Intelligence}, volume~33, pages 9038--9045, 2019.
+
+\bibitem{tian2019learning}
+Zhuotao Tian, Michelle Shu, Pengyuan Lyu, Ruiyu Li, Chao Zhou, Xiaoyong Shen,
+  and Jiaya Jia.
+\newblock Learning shape-aware embedding for scene text detection.
+\newblock In {\em Proceedings of the IEEE Conference on Computer Vision and
+  Pattern Recognition}, pages 4234--4243, 2019.
+
+\bibitem{kim2014convolutional}
+Yoon Kim.
+\newblock Convolutional neural networks for sentence classification.
+\newblock pages 1746 -- 1751, Doha, Qatar, 2014.
+\newblock Classification tasks;Convolutional neural
+  network;Hyper-parameter;Learning tasks;Question classification;Sentence
+  classifications;Simple modifications;State of the art;.
+
+\bibitem{karatzas2015icdar}
+Dimosthenis Karatzas, Lluis Gomez-Bigorda, Anguelos Nicolaou, Suman Ghosh,
+  Andrew Bagdanov, Masakazu Iwamura, Jiri Matas, Lukas Neumann,
+  Vijay~Ramaseshan Chandrasekhar, Shijian Lu, et~al.
+\newblock Icdar 2015 competition on robust reading.
+\newblock In {\em 2015 13th International Conference on Document Analysis and
+  Recognition (ICDAR)}, pages 1156--1160. IEEE, 2015.
+
+\end{thebibliography}
+
 }

### 2020-11-11 A-BasicCommom/CVPR2021/cvpr_covid.tex
1.fix some typo mistakes for x.

@@
   between what we see and what we write.
-  Most researches have laid lack of attention on the relevance between the Natural language processing and the Computer Vision.
+  Most research have laid lack of attention on the relevance between the natural language processing and the Computer Vision.
   In this paper, I discussed a novel method by unifying the representation of languages and visions from the representation layer.
   Unsupervised pre-training is important to the modern research in deep learning.
-  Lee \etal~\cite{lee2009convolutional} used the pre-training approaches
-  in Computer Vision tasks in 2009, and later from 2010 to 2016,
+  Lee \etal~\cite{lee2009convolutional} used the pre-training approaches in Computer Vision tasks in 2009, and later from 2010 to 2016,
   Nair and Hinton~\cite{nair2010rectified} proved that the pre-training process is supplementary in the Computer Vision tasks,
   thus, can be omitted in some cases.
-  However, it started to flourish the natural language processing domain since Mikolov \etal~\cite{mikolov2013distributed} had proposed Word2Vec.
-  Not long before Devin \etal~\cite{devlin2019bert}'s Bidirectional Encoder Representations from Transformers language model dominates
-  in most frequently used tasks in the natural language processing domain,
-  which is close resemble of Vicent \etal~\cite{vincent2008extracting}'s denoising autoencoder model, which was initially designed for images.
+  However, it started to flourish in the natural language processing domain since Mikolov \etal~\cite{mikolov2013distributed} had proposed Word2Vec.
+  Not long after, Devin \etal~\cite{devlin2019bert}'s Bidirectional Encoder Representations from Transformers language model dominates
+  in most frequently used tasks in the natural language processing domain, which is close resemble of Vicent \etal~\cite{vincent2008extracting}'s denoising autoencoder model, which was initially designed for images.
   Therefore, the pre-training process becomes one of the most important procedures in deep learning.
@@
 
-  Chen \etal~\cite{chen2020generative} trained image representation by sequence Transformers and tested on CIFAR-10 to show it is outperforming to Wide-ResNet
+  Chen \etal~\cite{chen2020generative} trained image representation by sequence Transformers and tested on the CIFAR-10 dataset to show it is outperforming to Wide-ResNet,
 which was inspired by unsupervised natural language representation learning.
@@
   Lu and Weng~\cite{lu2007survey} concluded that for the multi-source image classification tasks, additional information such as signatures, texture, context, and ancillary data can be combined to achieve better performance.
-And it is difficult in handling the dichotomy between pixels and natural language texts in a single model.
+And it is difficult to handle the dichotomy between pixels and natural language texts in a single model.
   Cui \etal~\cite{cui2020revisiting} proposed several whole-word-masking pre-trained Chinese language models,
-which are improved versions of BERT~\cite{devlin2019bert} pre-trained language models, namely RBT3, RBTL3, and RoBERTa-wwm-ext-large.
+which are improved versions of BERT~\cite{devlin2019bert}, one of the popular pre-trained language models, namely RBT3, RBTL3, and RoBERTa-wwm-ext-large.
 These models achieved better performance in Chinese machine reading comprehension, Chinese document classification, and other downstream natural language tasks.
@@
 
-In total, 349 computed tomography images were collected from the COVID-19 reports in the MedPix, LUNA, Radiopaedia, PubMed Central databases, which sizes range from $1637\times1225$ to $148\times61$.
+In total, 349 computed tomography images were collected from the COVID-19 reports in the MedPix, LUNA, Radiopaedia,
+PubMed Central databases, which sizes range from $1637\times1225$ to $148\times61$.
 
@@
 
-My approach consists of a pre-training stage followed by a fine-tuning stage.
-In pre-training, I use the BERT objectives and the sequence Transformer architecture to predict the language tokens.
+My approach consists of one pre-training stage followed by one fine-tuning stage.
+In pre-training stage, I use the BERT objectives and the sequence Transformer architecture to predict the language tokens.
 
@@
 embedding for each position.
-Then I use a fully connected layer as a non-linear function from the embeddings to the image classes.
+Then I use a fully connected layer as a non-linear function mapping from the embeddings to the image classes.
 A dropout layer and a Softmax layer are used for better transfer performance between the training dataset and the test dataset.
@@
 
-For the per-pixel image classification approach, for every RGB channel of pixels in an image,
-each pixel had its pixel-channel code, ranges from 0x00 to 0xff for different colors.
-Thus, taking these pixels in an image is identical to ASCII characters in a document.
-Generality speaking, the performance of the pre-trained language models achieved in the document classification tasks, can be transferred to image classification naturally.
+In the per-pixel image classification approach, for every RGB channel of pixels in an image,
+each pixel has its pixel-channel code, ranging from $0x00$ to $0xff$ for different colors.
+Thus, these pixels of an image are resemble to ASCII characters in a document.
+Generality speaking, the performance of the pre-trained language models achieved in the document classification tasks,
+can be transferred to image classification naturally.
 
 \par Recall that Kim~\cite{kim2014convolutional} had proved that unsupervised pre-trained language model $word2vec$ and CNN outperformed many other machine learning algorithms,
-\eg support vector machines and conditional random field, in many datasets such as movie reviews, Stanford sentiment treebank, and TREC question.
+\eg support vector machines and conditional random field, in many datasets such as movie reviews, Stanford sentiment treebank, and the \underline{T}ext \underline{RE}trieval \underline{C}onference question.
 Cui \etal's pre-trained language model, namely RBT3, RBTL3, and RoBERTa-wwm-ext-large, had improved performances over many other machine learning algorithms.
@@
 
-\par From table (1), by combining the pre-trained language model with fully connected layer as the document classification model,
+\par From Table (1), by combining the pre-trained language model with the fully connected layer as the document classification model,
 the test accuracy exceeds the other popular machine learning algorithms.
@@
 and contains 98 covid image and 100 covid negative images in the test set.
-All images are resized to a resolution of 32x32 pixels, the RGB channels are kept and the alpha channel is discarded.
+All images are resized to a resolution of $32\times32$ pixels, the RGB channels are kept and the alpha channel values are discarded.
 Encode the image by the sequence of RGB channel values, in the order of Red-channel, Green-channel, and Blue-channel,
@@
 Keep the first 256 characters and last 256 characters of the concatenated sequence, trimmed result contains the first 255 red-channel value,
-some blue-channel value, and all the meta value in common cases.
+some blue-channel value, and all the meta value for common cases.
 In the Encoder layer and the Embedding layer, trimmed sequence of values are encoded by BERT-like models,
 and get the encoded representation of the token $\textbf{[CLS]}$ as the images' language model embeddings.
-In the Feature-Extraction layer, the combination of a dropout layer, a fully connected layer, and a softmax layer, as equation (2), can provide
+In the Feature Extraction layer, the combination of a dropout layer, a fully connected layer, and a softmax layer, as equation (2), can provide
 transfer ability for the model from the training dataset to the test dataset.
-In the Output layer, the classification label of the image is feed in the model.
+In the Output layer, the classification label of the image is feed into the model.
 
@@
 
-\subsection{The Mask Token for Test}
+\subsection{Fair Comparison for Test: The Mask Token}
 
@@
 
-\par However, in the test phase, if feeding the metadata to the model, people might argue that the model learns only the mapping function from
+\par Recall that the $\textbf{[MASK]}$ token in the BERT language model is a special token which can be used to trim the vocabulary size,
+and gives the token-recovery capability to the downstream task model.
+
+\par However, in the test phase, if feeding the metadata to the model, other people might argue that the model learns only the mapping function from
 the metadata, which is the filename in this case, to the image class
@@
 
-\par Recall that the $\textbf{[MASK]}$ token in the BERT language model is a special token which can be used to trim the vocabulary size,
-and gives the token-recovery capability to the downstream task model.
-
 \par The $\textbf{[MASK]}$ token provide a fair comparison during the test by masking the language features, therefore,
 it can be seen that the language and the vision fusions during the training and enhance the performance and accuracy for the classification model
-of the CIFAR dataset and the COVID-19 tonography dataset.
+of the CIFAR dataset and the COVID-19 tomography dataset.
 
@@
 
-\par When fine-tuning, as Figure (1), I check the accuracy of the trained model on the test set and stopped training when it converges on $10^{-3}\sim10^{-4}$.
+\par For the fine-tuning stage, as Figure (1), I check the accuracy of the trained model on the test set and stopped training when it converges on $10^{-3}\sim10^{-4}$.
 
@@
 Use the proposed model, and I tried different pre-trained language models to see the impact on classification accuracy.
-From the table (1), it can be seen that the models are trained on the training dataset and validated on the test dataset.
+From the Table (1), it can be seen that the models are trained on the training dataset and validated on the test dataset.
 For the same size of a dataset with larger classes, it needs more epochs and training time for the classification model,

### 2020-11-12 A-BasicCommom/CVPR2021/cvpr_apsp.tex
1. comfort all papers.

--- 2020-10-25 A-BasicCommom/CVPR2021/cvpr.tex
@@
   In this paper, with the distance product association law and block matrix multiplication, all-pairs shortest path algorithm has a lowered time-bound of \(O(2\log{n}n^3)\).
-  The proposed all-pairs shortest path algorithm, which has an improved lower time-bound \(O(14n^3)\), leverages matrix sparseness judgment, convergence judgment, distance product with matrix multiplication, association law for distance product,
-  scale-free characteristics of the social networks degrees and precision limit of floating point operations on the modern hardware.
-  Tested on the movie actors' social network dataset, the algorithm has an improvement of 39\% to 36.2 times in performance on the CPU/GPU platforms comparing to Alon \etal's all-pairs shortest path algorithm.
+  The proposed all-pairs shortest path algorithm, which has an improved lower time-bound \(O(14n^3)\), leverages the following improvements:
+  matrix sparseness judgment, convergence judgment, distance product by matrix multiplication, association law for distance product,
+  scale-free characteristics of the social networks degrees and the precision limit of floating point operations on the modern hardware.
+  Comparing to Alon \etal's algorithm, the algorithm has an improvement of 39\% on CPU and 36.2 times on GPU on the movie actors' social network dataset.
 \end{abstract}
@@
 
-In recent years, driven by the Asian film industries such as China and India, the global box office has maintained a steady growth trend, and with the rapid development of social network applications, more and more actors use social networks for work communication.
-Therefore, the social network has become an important tool for film distribution, marketing, promotion, and an important medium for film actors and fans to interact.
-Previous studies have lacked research on actors' social networks, PageRank, an existing node influence algorithm, is not accurate in evaluating social network influence.
+In recent years, driven by the Asian film industries, such as China and India, the global box office has maintained a steady growth trend.
+With the rapid development of social network applications, more and more actors use social networks for work communication.
+Therefore, the social network has become an important tool in film distribution, marketing, promotion, and an important medium for film actors and fans to interact.
+Previous studies are lack of research on actors' social networks, PageRank, a widely used web page influence algorithm, is not accurate in evaluating social network influence.
 Social network feature measurement is an important task in social network data mining, some network characteristics, such as betweenness and closeness, need to calculate the distances between nodes.
@@
 On the actors' social network, this paper implements Strassen block matrix multiplication, Copper-Winograd block matrix multiplication, and OpenBLAS matrix multiplication.
-On the computer hardware, compared the $8508\times 8508$ matrix multiplication time cost.
+On the computer hardware, compared the $8508\times8508$ matrix multiplication time cost.
 The block matrix multiplication based on Strassen and Coppersmith-Winograd takes 6 seconds for one iteration of matrix multiplication, and with the OpenBLAS library, it takes only 4 seconds.
@@
 
-\subsection{The Shortest Path Algorithm with Joint Sparseness Judgment and Convergence Judgment}
+\subsection{Algorithm with Joint Sparseness Judgment and Convergence Judgment}
 
@@
 
-Firstly, compared to Floyd-Warshall algorithm implemented on CPU, the Alon \etal algorithm implementation with matrix multiplication of block cache optimization on GPU has a time performance improvement, see Table 1.
+Firstly, compared to Floyd-Warshall algorithm implemented on CPU, the Alon \etal algorithm implementation with matrix multiplication of block cache optimization on GPU has a time performance improvement, see Table (1).
 $Power-LawBound(a-f)$ shows that using different libraries on CPU/GPU, the proposed algorithm has significant performance improvement over Alon \etal algorithm.
@@
 and \textbf{Bound} refers to the precision limit for diameters of floating point arithmetic operations on hardware.
-The experimental results show that \textbf{Power-LawBound} algorithm improves time performance by 39\% to 36.2 times
-on CPU/GPU hardware compared to Alon \etal's algorithm.
+Comparing to Alon \etal's algorithm, the experimental results show that \textbf{Power-LawBound} algorithm has an improvement of 39\% on CPU and 36.2 times on GPU on the movie actors' social network dataset.
 

### 2020-11-12 A-BasicCommom/CVPR2021/cvpr_classification.tex
1.add a new Paper.
1. comfort all papers.

@@
 
-  Image classification and categorization are essential to the capability of telling the difference between images for a machine.
+  Image classification and categorization are essential to the capability of telling the difference between images for a machine
+  which is initially designed for vision purposes.
   As \underline{B}idirectional \underline{E}ncoder \underline{R}epresentations from \underline{T}ransformers became popular in many tasks of natural language processing recent years,
@@
 
-My approach consists of a pre-training state followed by a fine-tuning stage.
+My approach consists of a pre-training stage followed by a fine-tuning stage.
 In pre-training, I use BERT objectives and the sequence Transformer architecture to predict language tokens.
@@
 Cui \etal's pre-trained language model, namely RBT3, RBTL3, and RoBERTa-wwm-ext-large, had improved performances over many other machine learning algorithms.
-BERT and RoBERTa-wwm-ext-large models both achieved an f1-score of 97.8\% in the THUCNews dataset, which contains 65 thousands of news in 10 domains.
+BERT and RoBERTa-wwm-ext-large models both achieved an f1-score of 97.8\% in the THUCNews dataset, which contains 65 thousands news reports in 10 domains.
 
 \par I used RBTL3 and RoBERTa-wwm-ext-large pre-trained language model in two Chinese Judicial datasets, which has 2 and 4 classes.
-The \textit{Case-2} dataset annotated civil and criminal cases, and the \textit{Case-4} dataset annotated by civil, criminal, intellectual property, and administrative cases.
-The \textit{Case-2} dataset has $19508$ training documents and $2000$ test documents, and the \textit{Case-4} dataset has $34789$ training documents and $2013$ test documents.
+The \textit{Two-Case} dataset annotated civil and criminal cases, and the \textit{Four-Case} dataset annotated by civil, criminal, intellectual property, and administrative cases.
+The \textit{Two-Case} dataset has $19508$ training documents and $2000$ test documents, and the \textit{Four-Case} dataset has $34789$ training documents and $2013$ test documents.
 
-\par From table (1), by combining the pre-trained language model with fully connected layer as the document classification model,
+\par From Table (1), by combining the pre-trained language model with fully connected layer as the document classification model,
 the test accuracy exceeds the other popular machine learning algorithms.
@@
 \hline\hline
-RoBERTa-wwm-ext-large & Case-2	&	99.80\% \\
-RoBERTa-wwm-ext-large & Case-4	&	99.76\% \\
-RBTL3  & Case-4	&	96.35\% \\
+RoBERTa-wwm-ext-large & Two-Case	&	99.80\% \\
+RoBERTa-wwm-ext-large & Four-Case	&	99.76\% \\
+RBTL3  & Four-Case	&	96.35\% \\
 \hline
@@
 
-I design simple classification models without too many layers, as Figure (1) shows.
-And use the CIFAR-10 and CIFAR-100 dataset as an example to show the architecture of the model.
+I design simple classification models without too many layers, as Figure (1) shows,
+and use the CIFAR-10 and CIFAR-100 dataset as an example to show the architecture of the model.
 The model architecture has seven functional layers:
@@
 
-\par The CIFAR-10 dataset contains 60000 color images with a resolution of 32x32 in 10 classes, and the CIFAR-100 dataset has 100 classes containing 600 images each.
+\par The CIFAR-10 dataset contains 60000 color images with a resolution of $32\times32$ in 10 classes, and the CIFAR-100 dataset has 100 classes containing 600 images each.
 Encode the image by the sequence of RGB channel values, in the order of Red-channel, Green-channel, and Blue-channel,
@@
 
-\subsection{The Mask Token for Test}
+\subsection{More Fair Comparison by The Mask Token}
 
-\par It is intuitive for the model to use both the channel values and the metadata during the training phase.
+\par It is intuitive for the model to use both the channel values and the metadata in the training phase.
 For the CIFAR-10 and CIFAR-100 dataset, the metadata is the filename of the images, which can be treated as the supervised description of the image.
@@
 
-\par However, in the test phase, if feeding the metadata to the model, people might argue that the model learns only the mapping function from
-the metadata, which is the filename in this case, to the image class
-which makes it is unfair to compare the performance with other image classification models.
-Thus, to be more objective and fair, I add a preprocess for the metadata in the test phase, using the $\textbf{[MASK]}$ token to replace each
-ASCII character of the filename then feeds into the model to do the inference.
-
 \par Recall that the $\textbf{[MASK]}$ token in the BERT language model is a special token which can be used to trim the vocabulary size,
 and gives the token-recovery capability to the downstream task model.
+
+\par However, in the test phase, if feeding the metadata to the model, people might argue that the model learns only the mapping function from
+the metadata, which is the filename in this case, to the image class, which makes it is unfair to compare the performance with other image classification models.
+Thus, to be more objective and fair, I add a preprocess step for the metadata in the test phase, using the $\textbf{[MASK]}$ token to replace each
+ASCII character of the filename then feeds into the model to do the inference.
 
@@
 
-Use the proposed model, and I tried different pre-trained language models to see the impact on classification accuracy.
-From the table-2, for the same size of a dataset with larger classes, it needs more epochs and training time for the classification model.
+Using the proposed model, I tried different pre-trained language models to see the impact on classification accuracy.
+From the Table (2), for the same size of a dataset with larger classes, it needs more epochs and training time for the classification model.
 For the same RoBERTa language model with different numbers of transformer layers, 24 layers of transformers had better accuracy than 3 layers,
 however, its training cost grows for the larger language model.
-For the same fine-tuned language model, classes number has some impact on the accuracy,
+For the same fine-tuned language model, classes number has positive impact on the accuracy,
 the fewer classes the dataset has, the more accurate results the model can achieve.

### 2020-11-12 A-BasicCommom/CVPR2021/cvpr_detrec.tex
1. comfort all papers.

@@
   then connect to a recurrent neural network layer, and a fully connected layer in the Character Recognize architecture.
-  The proposed recognition model outperforms the ResNet recognition model, and achieved accuracy of $71.74\%$ on the Baidu2019 street scene test set.
+  The proposed recognition model outperforms the ResNet recognition model, and achieved accuracy of $77.24\%$ on the Baidu2019 street scene test set.
 
@@
 \hline\hline
-ResNet      & 18 &  ICDAR2015 &50 &	23.67\% \\
-ResNet      & 18 &  Baidu2019	  &50 &	56.25\% \\
-ResBertNet  & 18+3 & Baidu2019    & 50	&	71.74\% \\
+ResNet      & 18 &  ICDAR2015     & 50 &	23.67\% \\
+ResNet      & 18 &  Baidu2019	  & 30 &	56.25\% \\
+ResBertNet  & 18+3 & Baidu2019    & 64	&	77.24\% \\
 \hline
@@
 the ResNet model cannot achieve a satisfactory result after 50 epochs.
+From the training logs, I can see that the model has converged on a optimal point that after the 30th epoch,
+and has no improvement in accuracy afterwards.
 It shows that Street Scene View text recognition task is a hard problem and there is no easy way out.
@@
 Tests showed that the proposed model outperforms the ResNet model without augmentation on the image dataset,
-the model achieved accuracy of $71.74\%$ on the Baidu 2019 street view text recognition set.
+the model achieved accuracy of $77.24\%$ on the Baidu 2019 street view text recognition set.
 

### 2020-11-12 A-BasicCommom/CVPR2021/cvpr_vision.tex
1. comfort all papers.

@@
 
-  In the film industry, visualizing actor stars' social media for analyzing audience intention towards movies is essential for movie producers.
-  However, non-Euclidean social media is hard to analyze, I propose an FC-GRU-CNN architecture, named as \underline{N}on\underline{E}uclidean\underline{N}et, for social media visualization.
-  On the analysis of social media, social relationship representations, network characteristics and media sentiments are key factors.
+  In the film industry, visualizing actor stars' social media to analyze audience intention towards movies is essential for the movie producers.
+  However, non-Euclidean social media are hard to analyze,
+  I propose an FC-GRU-CNN architecture, named as \underline{N}on\underline{E}uclidean\underline{N}et, for the social media visualization.
+  On the analysis of social media, social relationship representations, network characteristics and media sentiments are the key factors.
   The FC-GRU-CNN architecture exploits the long-term memory ability of the GRU layer in the long sequences of film cast,
-  the mapping ability of the CNN layer in retrieving all-pairs shortest path of the actors' social relationship,
+  the mapping ability of the convolutional neural network layer in retrieving all-pairs shortest path of the actors' social relationship,
   and non-linear capability in deep fully connected layer for movie text sentiments and other characteristics.
@@
 
-  With the development of social networks, the actors' influence of social media is increasing,
+  With the development of social networks, the actors' influence in social media is increasing,
   and the influence of actors' consumption spreads through social networks,
@@
   The film industry is a multi-billion-dollar business, as China's box-office exceeding 6 billion dollars in 2018, reaching 6.09 billion dollars.
-  Predicting the acceptance and adoption of new films among the audience is a challenging topic.
+  Predicting the acceptance and adoption of new films among the audience is a challenging task.
   Fern{\'a}ndez \etal ~\cite{fernandez2014we} showed that the best classifiers are the random forest,
-  followed by SVM, neural networks, and boosting ensembles among 17 families.
+  followed by Support Vector Machines, neural networks, and boosting ensembles among 17 families.
 
@@
   Jiang and Wang~\cite{jiang2018predicting} collected 34 high-grossing films from 2015 to 2017, using 10 features, such as film metadata, director awards, and actor awards, then I used voting feature selection algorithms to select important features,
-  training SVM models for film box-office and user-comment score prediction.
+  training Support Vector Machines models for film box-office and user-comment score prediction.
   Quader \etal~\cite{quader2017machine} collected 755 film reviews in four film review sites from 2012 to 2015, collected characteristics including film ratings, MPAA categories,
   director total box-office, actor total box-office, release time, budget, screen numbers, user reviews, and review text sentiments,
-  the trained SVM model has a prediction accuracy of 44.4\%.
+  the trained Support Vector Machines model has a prediction accuracy of 44.4\%.
 
@@
 
-Machine learning methods such as Linear Regression, SVM, MLP, Logistic Regression, and Na{\'i}ve Bayes cannot converge on the data set,
+Machine learning methods such as Linear Regression, Support Vector Machines, Multiple Layer Perception, Logistic Regression, and Na{\'i}ve Bayes cannot converge on the data set,
 possibly because the sentiments on actors' social networks do not represent the commercial benefits of the film.
-Actors, as creators of films, have a role to play in the box-office, but lack of other important features that also have a significant impact on the box-office,
+Actors, as creators of films, play a role in the box-office, but lack of other important features that also have a significant impact on the box-office,
 so the machine learning fitting process can't converge in a given time.
@@
 Look at the box-office distribution of $1296$ films released between 2011 and 2015,
-box-office forecasts can be seen as a binary classification task.
+the box-office forecasts can be seen as a binary classification task.
 To make the data evenly distributed, the film data were pre-processed by using the median box-office of $2.635$ million as the dividing line.

### 2020-11-12 A-BasicCommom/CVPR2021/cvpr_detrec.tex
1.fix some typo mistakes for x.

@@
   then connect to a recurrent neural network layer, and a fully connected layer in the Character Recognize architecture.
-  The proposed recognition model outperforms the ResNet recognition model, and achieved accuracy of $77.24\%$ on the Baidu2019 street scene test set.
+  The proposed recognition model outperforms the ResNet recognition model, and achieved accuracy of $79.82\%$ on the Baidu2019 street scene test set.
 
@@
 ResNet      & 18 &  Baidu2019	  & 30 &	56.25\% \\
-ResBertNet  & 18+3 & Baidu2019    & 64	&	77.24\% \\
+ResBertNet  & 18+3 & Baidu2019    & 72	&	79.82\% \\
 \hline
@@
 Tests showed that the proposed model outperforms the ResNet model without augmentation on the image dataset,
-the model achieved accuracy of $77.24\%$ on the Baidu 2019 street view text recognition set.
+the model achieved accuracy of $79.82\%$ on the Baidu 2019 street view text recognition set.
 

### 2020-11-16 A-BasicCommom/CVPR2021/cvpr_apsp.tex
1.fix some typo mistakes for x.

@@
 \begin{abstract}
-  For the shortest path calculation of the all-pairs nodes in networks, Alon \etal~\cite{alon1997exponent} proposed an algorithm with matrix multiplication.
-  In this paper, with the distance product association law and block matrix multiplication, all-pairs shortest path algorithm has a lowered time-bound of \(O(2\log{n}n^3)\).
-  The proposed all-pairs shortest path algorithm, which has an improved lower time-bound \(O(14n^3)\), leverages the following improvements:
+  For the calculation of the all-pairs nodes shortest path in networks,
+  Alon \etal proposed an efficient algorithm with matrix multiplication.
+  In this paper, with the distance product association law and block matrix multiplication,
+  the all-pairs shortest path algorithm has lower time-bound of $O(14n^3)$.
+  The proposed algorithm leverages the following improvements:
   matrix sparseness judgment, convergence judgment, distance product by matrix multiplication, association law for distance product,
   scale-free characteristics of the social networks degrees and the precision limit of floating point operations on the modern hardware.
-  Comparing to Alon \etal's algorithm, the algorithm has an improvement of 39\% on CPU and 36.2 times on GPU on the movie actors' social network dataset.
+  Comparing to Alon \etal's algorithm, the algorithm has improvement of 39\% on CPU and improvement of 36.2 times on GPU
+  on the Chinese Movie Celebrity Network $2011\sim2015$ dataset.
 \end{abstract}
@@
 \item For the distance product optimization, Zwick proposed the distance product with block matrix multiplication, therefore choose proper computation device library with optimized cache for block matrix multiplication.
-\item For the iteration optimization, Aho proved distance product is isomorphic to the matrix multiplication, and regard to that the distance product association law, I optimize the iteration process by reusing the distance product result of the epochs.
+\item For the iteration optimization, Aho and Hopcroft proved distance product is isomorphic to the matrix multiplication, and regard to that the distance product association law, I optimize the iteration process by reusing the distance product result of the epochs.
 \end{enumerate}
@@
 
-From January 1, 2011, to March 31, 2015, I collected the film actors' social network following relationship, profile information, and text message on Sina Weibo, one of the popular social media in China.
-In all, 8508 actors, 577775 edges, and 12526114 Sina Weibo posts are collected.
+From January 1, 2011, to March 31, 2015, I collected the film actors' social network following relationship, profile information,
+and text message on Sina Weibo, one of the most popular social media in China.
+In all, 8508 actors, 577,775 edges, and 12,526,114 Sina Weibo posts are collected.
+This dataset is named as Chinese Movie Celebrity Network $2011\sim2015$ dataset.
 Experiments are made on a server with two Intel Xeon E5-2620 v4 CPUs and one NVIDIA GeForce GTX 1080 Ti GPU, in total 32 cores with a frequency of 2.1Ghz, 128G system memory, and 11G GPU memory in my experiment.
@@
 
-On the actors' social network, this paper implements Strassen block matrix multiplication, Copper-Winograd block matrix multiplication, and OpenBLAS matrix multiplication.
+On the Chinese Movie Celebrity Network $2011\sim2015$ dataset, this paper implements Strassen block matrix multiplication,
+Copper-Winograd block matrix multiplication, and OpenBLAS matrix multiplication.
 On the computer hardware, compared the $8508\times8508$ matrix multiplication time cost.
-The block matrix multiplication based on Strassen and Coppersmith-Winograd takes 6 seconds for one iteration of matrix multiplication, and with the OpenBLAS library, it takes only 4 seconds.
-The performance of optimized cache block matrix multiplication, such as the OpenBLAS matrix computation library, is higher than Strassen and Copper-Winograd block matrix multiplication algorithm.
-Therefore, the distance product algorithm proposed by Zwick with OpenBLAS block matrix multiplication is better than the distance product algorithm with Strassen and Coppersmith-Winograd.
+The block matrix multiplication based on Strassen and Coppersmith-Winograd takes 6 seconds for the matrix multiplication,
+while the OpenBLAS library takes only 4 seconds.
+The performance of optimized cache block matrix multiplication, such as the OpenBLAS matrix computation library,
+is higher than Strassen and Copper-Winograd block matrix multiplication algorithm.
+Therefore, the distance product algorithm proposed by Zwick with OpenBLAS block matrix multiplication is better than
+the distance product algorithm with Strassen and Coppersmith-Winograd.
 
@@
 
-\section{Time-Bound Of Distance Product Algorithm With Cache Optimized Block Matrix Multiplication}
+\section{Time-Bound Of Distance Product Algorithm With Optimized Block Matrix Multiplication}
 
@@
 
-\subsection{Maximum Element Value Calculation}
+\subsection{Maximum Element Calculation}
 
-Calculate the largest value of the square matrix element $\widetilde X$, this maximum value is latter used in the exponential computations.
+Calculate the largest value of the square matrix elements $\widetilde X$,
+this maximum value is latter used in the exponential computations.
 
@@
 
-The precision of different computer hardware complies with the IEEE floating point operation standard~\cite{ieee1985ieee},
+The precisions of floating point operation on different computer hardware comply with the IEEE standard~\cite{ieee1985ieee},
 first of all, transform the input matrix by exponential transformation, to be specific, taking the number of nodes as the base,
-taking the difference between the largest value of the element $\widetilde X$ and the matrix elements as exponential.
-For the actors' social network with 8508 nodes, the diameter of the network does not allow to exceed 9.8 and 78.4 when calculating precision of 32-bit floating point and 64-bit floating point,
-otherwise, the exponential operation on the computer platform will overflow.
+taking the difference between the largest value of the elements $\widetilde X$ and the matrix elements as exponential.
+For the actors' social network with 8508 nodes, the diameter of the network does not allow to exceed 9.8 and 78.4
+in calculating for the precision of 32-bit floating point and 64-bit floating point,
+otherwise, the exponential operation on the computer platform shall overflow.
 
 \subsection{Matrix Multiplication}
-Use different matrix libraries to speed up the matrix multiplication on the computer hardware, as shown in Table 3, choose proper device-based optimized matrix multiplication libraries according to different conditions, such as matrix sparseness, calculation hardware, and programming language.
+
+Different matrix libraries have various speed in the matrix multiplication on the computer hardware, as shown in Table (3),
+choose proper device-based optimized matrix multiplication libraries according to different conditions,
+such as matrix sparseness, calculation hardware, and programming language.
 
@@
 \caption{Lower Bounds Convergence Matrix Products in the All-Pairs Shortest Path}\label{algorithm}
-\KwData{Adjacent Matrix $\Bbb W$, Matrix Row $n$, Network Diameter $\Bbb D$}
+\KwData{Adjacent Matrix $\Bbb W$, Matrix Row count $n$, Network Diameter $\Bbb D$}
 \KwResult{The shortest path result $L^{(m)}$}
@@
 
-As shown in Table 1, observing the adjacent matrix represented by the network diagram is usually a sparse matrix, and the matrix gradually becomes dense during iterations,
+As shown in Table (1), observed the adjacent matrix represented by the network diagram is usually a sparse matrix, and the matrix gradually becomes dense during iterations,
 and one idea of optimization is to use sparse matrix multiplication to speed up the iteration when the matrix is sparse, and when the matrix becomes denser, the sparse matrix multiplication is much time-consuming.
@@
 
+\textbf{PowerLaw} refers to the network node degrees conforming to the characteristics that social networks power-law distribution,
+and \textbf{Bound} refers to the precision limit for diameters of floating point arithmetic operations on hardware.
 Firstly, compared to Floyd-Warshall algorithm implemented on CPU, the Alon \etal algorithm implementation with matrix multiplication of block cache optimization on GPU has a time performance improvement, see Table (1).
-$Power-LawBound(a-f)$ shows that using different libraries on CPU/GPU, the proposed algorithm has significant performance improvement over Alon \etal algorithm.
+PowerLaw-Bound$(a\sim f)$ shows that using different libraries on CPU/GPU, the proposed algorithm has significant performance improvement over Alon \etal algorithm.
 
@@
 \hline
-Algorithm	& Time Cost \\
+Algorithm	& Time Cost(sec) \\
 \hline\hline
-Floyd-Warshall~\cite{floyd1962algorithm,warshall1962theorem}  &	$10^6$s \\
-Alon \etal~\cite{alon1997exponent}  &	594.7s \\
-$Power-LawBound(a)$ &	427.9s \\
-$Power-LawBound(b)$	&	328.4s \\
-$Power-LawBound(c)$	&	95.0s \\
-$Power-LawBound(d)$	&	45.0s \\
-$Power-LawBound(e)$	&	19.32s \\
-$Power-LawBound(f)$	&	15.98s \\
+Floyd-Warshall~\cite{floyd1962algorithm,warshall1962theorem}  &	$10^6$ \\
+Alon \etal~\cite{alon1997exponent}  &	594.7 \\
+PowerLaw-Bound$(a)$ &	427.9 \\
+PowerLaw-Bound$(b)$	&	328.4 \\
+PowerLaw-Bound$(c)$	&	95.0 \\
+PowerLaw-Bound$(d)$	&	45.0 \\
+PowerLaw-Bound$(e)$	&	19.32 \\
+PowerLaw-Bound$(f)$	&	15.98 \\
 \hline
@@
 which leverages matrix sparseness judgment, and calculation convergence judgment.
-\textbf{Power-Law} refers to the network node degrees conforming to the characteristics that social networks power-law distribution,
-and \textbf{Bound} refers to the precision limit for diameters of floating point arithmetic operations on hardware.
-Comparing to Alon \etal's algorithm, the experimental results show that \textbf{Power-LawBound} algorithm has an improvement of 39\% on CPU and 36.2 times on GPU on the movie actors' social network dataset.
+Comparing to Alon \etal's algorithm, the experimental results show that \textbf{PowerLaw-Bound} algorithm
+has improvement of 39\% on CPU and improvement of 36.2 times on GPU on the Chinese Movie Celebrity Network $2011\sim2015$ dataset.
 

### 2020-11-16 A-BasicCommom/CVPR2021/cvpr_detrec.tex
1.fix some typo mistakes for x.

@@
   then connect to a recurrent neural network layer, and a fully connected layer in the Character Recognize architecture.
-  The proposed recognition model outperforms the ResNet recognition model, and achieved accuracy of $79.82\%$ on the Baidu2019 street scene test set.
+  The proposed recognition model outperforms the ResNet recognition model, and achieved accuracy of $83.74\%$ on the Baidu2019 street scene test set.
 
@@
 ResNet      & 18 &  Baidu2019	  & 30 &	56.25\% \\
-ResBertNet  & 18+3 & Baidu2019    & 72	&	79.82\% \\
+ResBertNet  & 18+3 & Baidu2019    & 96	&	83.74\% \\
 \hline
@@
 The finding improves the accuracy in OCR for Chinese street scene, and might improve the accuracy of other language scene detection and recognition.
-Tests showed that the proposed model outperforms the ResNet model without augmentation on the image dataset,
-the model achieved accuracy of $79.82\%$ on the Baidu 2019 street view text recognition set.
+Tests showed that the proposed model outperforms the ResNet model with augmentation on the image dataset,
+the model achieved accuracy of $83.74\%$ on the Baidu 2019 street view text recognition set.
 

### 2020-11-16 A-BasicCommom/CVPR2021/cvpr_classification.tex
1.fix some typo mistakes for x.

@@
 
-  Image classification and categorization are essential to the capability of telling the difference between images for a machine
-  which is initially designed for vision purposes.
-  As \underline{B}idirectional \underline{E}ncoder \underline{R}epresentations from \underline{T}ransformers became popular in many tasks of natural language processing recent years,
+  Image classification and categorization are essential to the capability of telling the difference between images for a machine vision task.
+  As the \underline{B}idirectional \underline{E}ncoder \underline{R}epresentations from \underline{T}ransformers became popular in many tasks of natural language processing recent years,
   it is intuitive to use these pre-trained language models for enhancing the computer vision tasks, \eg image classification.
@@
 
-\par Recall that Kim~\cite{kim2014convolutional} had proved that unsupervised pre-trained language model $word2vec$ and CNN outperformed many other machine learning algorithms,
+Recall that Kim~\cite{kim2014convolutional} had proved that unsupervised pre-trained language model $word2vec$ and CNN outperformed many other machine learning algorithms,
 \eg support vector machines and conditional random field, in many datasets such as movie reviews, Stanford sentiment treebank, and TREC question.
@@
 
-\par I used RBTL3 and RoBERTa-wwm-ext-large pre-trained language model in two Chinese Judicial datasets, which has 2 and 4 classes.
+I used RBTL3 and RoBERTa-wwm-ext-large pre-trained language model in two Chinese Judicial datasets, which has 2 and 4 classes.
 The \textit{Two-Case} dataset annotated civil and criminal cases, and the \textit{Four-Case} dataset annotated by civil, criminal, intellectual property, and administrative cases.
@@
 
-\par From Table (1), by combining the pre-trained language model with fully connected layer as the document classification model,
+From Table (1), by combining the pre-trained language model with fully connected layer as the document classification model,
 the test accuracy exceeds the other popular machine learning algorithms.
@@
 
-\par The CIFAR-10 dataset contains 60000 color images with a resolution of $32\times32$ in 10 classes, and the CIFAR-100 dataset has 100 classes containing 600 images each.
+\par The CIFAR-10 dataset contains 60,000 color images with a resolution of $32\times32$ in 10 classes, and the CIFAR-100 dataset has 100 classes containing 600 images each.
 Encode the image by the sequence of RGB channel values, in the order of Red-channel, Green-channel, and Blue-channel,
@@
 and get the encoded representation of the token $\textbf{[CLS]}$ as the images' language model embeddings.
-In the Feature-Extraction layer, a combination of one dropout layer, one fully connected layer, and one softmax layer, as equation (2), is used.
+In the Feature-Extraction layer, a combination of one dropout layer, one fully connected layer, and one softmax layer, as Equation (2), is used.
 In the Output layer, the classification label of the image is feed in the model.
@@
 however, its training cost grows for the larger language model.
-For the same fine-tuned language model, classes number has positive impact on the accuracy,
-the fewer classes the dataset has, the more accurate results the model can achieve.
+For the same fine-tuned language model, classes number has positive impact on the accuracy.
+And the fewer classes the dataset has, the more accurate results the model can achieve.
 
@@
 RoBERTa-large & CIFAR-100 & 16 &	99.76\% \\
+\hline\hline
+iGPT-L & CIFAR-10 & $18_a$ & 99.0\%\\
+iGPT-L & CIFAR-100 & $18_a$ & 88.5\%\\
 \hline
@@
 \end{center}
-\caption{Comparision of accuracy of the pre-trained language models on the CIFAR-10 and CIFAR-100 datasets in the image classification task.
-RoBERTa-large is short for RoBERTa-wwm-ext-large.}
+\caption{Comparision of accuracy of the pre-trained language models and iGPT-L on the CIFAR-10 and CIFAR-100 datasets in the image classification task.
+RoBERTa-large is short for RoBERTa-wwm-ext-large. (a) iGPT-L model was trained far more than 18 epochs, it was trained by 1,000,000 iterations of pre-training and a few epochs for fine-tuning.}
 \end{table}
@@
 
+The iGPT-L was trained on the ImageNet dataset, and it has 48 layers of transoformers and 1.4 billion parameters, and the embedding size takes 1536,
+so it has almost identical layers with GPT-2 language model, except for 1.5 billion parameters and 1600 embedding size.
 Compare to iGPT-L's accuracy of 96.3\% on the CIFAR-10 dataset without augmentation and 82.8\% on the CIFAR-100 dataset, our models have preferable better results.
@@
 
- This paper proposed a novel idea by using pre-trained language models for image representation and take image classification as an example of its performance in Computer Vision tasks.
- The finding might benefit various subjects, namely Education, Medical, Chemistry, Physics, Cosmology, Geography, Climate and Materials Science for their specific research.
+ This paper proposed a novel idea by using the pre-trained language models for image representation and take image classification
+ as an example to prove its performance for Computer Vision tasks, such as image classification.
+ The finding might benefit various subjects, namely  for their specific research.
 Tests showed that the proposed model outperforms the iGPT-L model without augmentation on the image dataset,

### 2020-11-16 A-BasicCommom/CVPR2021/cvpr_vision.tex
1.fix some typo mistakes for x.

@@
   However, non-Euclidean social media are hard to analyze,
-  I propose an FC-GRU-CNN architecture, named as \underline{N}on\underline{E}uclidean\underline{N}et, for the social media visualization.
-  On the analysis of social media, social relationship representations, network characteristics and media sentiments are the key factors.
-  The FC-GRU-CNN architecture exploits the long-term memory ability of the GRU layer in the long sequences of film cast,
-  the mapping ability of the convolutional neural network layer in retrieving all-pairs shortest path of the actors' social relationship,
-  and non-linear capability in deep fully connected layer for movie text sentiments and other characteristics.
-  The proposed model accuracy is 14\% higher than Reed \etal~\cite{reed2016learning}'s model.
+  In the analysis of social media task, social relationship representations, network characteristics and media sentiments are three key factors.
+  Thus, I propose an FC-GRU-CNN architecture from the key visualization factors,
+  also named as \underline{N}on \underline{E}uclidean \underline{N}et, for the social media visualization.
+  The proposed architecture exploits the long-term memory ability of the GRU layers in the long sequences of film cast,
+  the mapping ability of the convolutional neural network layers in retrieving the all-pairs shortest path of the actors' social relationship,
+  and non-linear capability in the deep fully connected layers for movie text sentiments and other social media characteristics.
+  The proposed model achieved accuracy of 75\% in the Chinese Movie Box-Office Forecast $2011\sim2015$ dataset, which is higher than Reed \etal's model.
 
@@
   With the development of social networks, the actors' influence in social media is increasing,
-  and the influence of actors' consumption spreads through social networks,
+  and the influence of actors' consumption spreads through the social networks,
   and using the long-term social network data to study the relationships between all actors, directors, and films remains a challenge.
@@
 
-Look at the box-office distribution of $1296$ films released between 2011 and 2015,
-the box-office forecasts can be seen as a binary classification task.
+I collected $1296$ Chinese films released from 2011 to 2015, and their corresponding social media of the key actors, named as Chinese Movie Box-Office Forecast $2011\sim2015$ dataset.
+Look at the box-office distribution of the dataset, the box-office forecasts can be seen as a binary classification task.
 To make the data evenly distributed, the film data were pre-processed by using the median box-office of $2.635$ million as the dividing line.
@@
 \begin{itemize}
-\item The first part is the fully connected layer, its input feature is the film metadata and movie-related Sina Weibo sentiments, in a total of 5 dimensions.
-\item The second part is the GRU layer, the input feature is the actor social network measurement characteristics and artistic characteristics, the film cast is a long list,
+\item The first part is the fully connected layers, its input feature is the film metadata and movie-related Sina Weibo sentiments, in total of 5 dimensions.
+\item The second part is the GRU layers, the input feature is the actor social network measurement characteristics and artistic characteristics, the film cast is a long list,
 the longest 225 actors, for less than 225 actors using the front-end padding, the GRU layer is to solve the long-term memory loss of the structure.
@@
 
-In summary, randomly choose 10 movies as the test set, as shown in Table 1.
+In summary, randomly choose 10 movies as the test set, as shown in Table (1).
 The accuracy of the binary classification model on the training set reached 99.61\%, the accuracy on the test set is 75\%.
-Compared to Reed \etal model, see Table 2, the proposed FC-GRU-CNN model converges on the training set and achieves better prediction results on the test set.
+Compared to Reed \etal model, see Table (2), the proposed model converges on the training set and achieves better prediction results on the test set.
 Therefore, it can provide decision-making advice in the task of selecting suitable actors for a to-be-cast film,
@@
 \hline
-Movie& Score &BoxOffice\\
+Movie& is\_Hit &BoxOffice\\
 \hline\hline
@@
 \end{center}
-\caption{box-office model predictions in movie test dataset with 10 samples.}
+\caption{The box-office model predictions in movie test dataset of 10 samples.}
 \end{table}
@@
 Reed \etal  & 61.54\% \\
-This paper & 75.0\% \\
+FGC & 75.0\% \\
 \hline
@@
 According to the box-office prediction model, this paper discussed the relationship between the movie metadata, Sina Weibo text sentiments, social relationship representations, network characteristics, and actors' artistic contribution in detail.
-I proposed an FC-GRU-CNN box-office prediction model, tested on a dataset with $1296$ movies released in China mainland from 2011 to 2015, the model accuracy improves 14\% compared to Reed \etal's model.
+I proposed an FC-GRU-CNN prediction model, tested on the Chinese Movie Box-Office Forecast $2011\sim2015$ dataset, the model has accuracy of 75\%, which has improved 14\% compared to Reed \etal's model.
 

### 2020-11-18 A-BasicCommom/wordRepresentation/evaluate.py
1. 词向量表示

@@ -6,7 +6,7 @@ from gensim.models import KeyedVectors
 
 def eval(analogy_file, similarity_file):
     model = joblib.load("word2vec.model")
-    # model = KeyedVectors.load_word2vec_format('word2vec-1024.txt', binary=False)
+    # model = KeyedVectors.load_word2vec_format('word2vec.txt', binary=False)
     vocab = list(model.wv.vocab.keys())
     analog = model.wv.most_similar(positive=vocab[0:2], negative=vocab[-1:1], topn=1)
     print('a+b-c',vocab[0:2],vocab[-1],analog)

### 2020-11-18 A-BasicCommom/wordRepresentation/torch_server.py

@@ -1,0 +1,91 @@
+import argparse
+import logging
+import sys
+import time
+from types import SimpleNamespace
+
+import falcon
+from falcon_cors import CORS
+import json
+import waitress
+import lawa
+from gensim.models import KeyedVectors
+
+if sys.hexversion < 0x03070000:
+    ft = time.process_time
+else:
+    ft = time.process_time_ns
+    
+logging.basicConfig(level=logging.INFO, format='%(asctime)-18s %(message)s')
+logger = logging.getLogger()
+cors_allow_all = CORS(allow_all_origins=True,
+                      allow_origins_list=['*'],
+                      allow_all_headers=True,
+                      allow_all_methods=True,
+                      allow_credentials_all_origins=True
+                      )
+
+parser = argparse.ArgumentParser()
+parser.add_argument(
+    '-c', '--config_file', default='config/bert_config.json',
+    help='model config file')
+parser.add_argument(
+    '-p', '--port', default=58085,
+    help='falcon server port')
+parser.add_argument(
+    '-m', '--for_search', default=1,
+    help='falcon server port')
+args = parser.parse_args()
+model_config = args.config_file
+
+
+class TorchResource:
+
+    def __init__(self):
+        logger.info("...")
+        with open(model_config) as fin:
+            config = json.load(fin, object_hook=lambda d: SimpleNamespace(**d))
+        self.model = KeyedVectors.load_word2vec_format(config.trained_weight, binary=False, encoding='utf-8')
+        logger.info("###")
+
+    def process_context(self, pos, neg, topn= 1):
+        start = ft()
+        analog = self.model.most_similar(positive=pos, negative=neg, topn=topn)
+        logger.info("cut:{}ns".format(ft() - start))
+        return {'data': analog}
+
+    def on_get(self, req, resp):
+        logger.info("...")
+        resp.set_header('Access-Control-Allow-Origin', '*')
+        resp.set_header('Access-Control-Allow-Methods', '*')
+        resp.set_header('Access-Control-Allow-Headers', '*')
+        resp.set_header('Access-Control-Allow-Credentials', 'true')
+        pos = req.get_param('pos', True)
+        pos = pos.split(',')
+        neg = req.get_param('neg', True)
+        neg = neg.split(',')
+        resp.media = self.process_context(pos, neg)
+        logger.info("###")
+
+    def on_post(self, req, resp):
+        """Handles POST requests"""
[…]

### 2020-11-18 A-BasicCommom/wordRepresentation/train.py

@@ -67,11 +67,11 @@ args = parser.parse_args()
 class LawaIterable(object):
     def __init__(self, filename):
         self.source = filename
-
+        self.limit = None
 
     def __iter__(self):
         with open(self.source, 'r', encoding='utf-8') as fin:
-            for x, line in enumerate(fin):
+            for line in itertools.islice(fin, self.limit):
                 yield list(lawa.cut(line))
 
 

### 2020-12-17 A-BasicCommom/ACL2021/acl_summary.tex
1. upload to avoid disk file corruption.

%
% File acl2020.tex
%
%% Based on the style files for ACL 2020, which were
%% Based on the style files for ACL 2018, NAACL 2018/19, which were
%% Based on the style files for ACL-2015, with some improvements
%%  taken from the NAACL-2016 style
%% Based on the style files for ACL-2014, which were, in turn,
%% based on ACL-2013, ACL-2012, ACL-2011, ACL-2010, ACL-IJCNLP-2009,
%% EACL-2009, IJCNLP-2008...
%% Based on the style files for EACL 2006 by 
%%e.agirre@ehu.es or Sergi.Balari@uab.es
%% and that of ACL 08 by Joakim Nivre and Noah Smith

\documentclass[11pt,a4paper]{article}
\usepackage[hyperref]{acl2020}
\usepackage{times}
\usepackage{latexsym}
\renewcommand{\UrlFont}{\ttfamily\small}

% This is not strictly necessary, and may be commented out,
% but it will improve the layout of the manuscript,
% and will typically save some space.
\usepackage{microtype}

%\aclfinalcopy % Uncomment this line for the final submission
%\def\aclpaperid{***} %  Enter the acl Paper ID here

%\setlength\titlebox{5cm}
% You can expand the titlebox if you need extra space
% to show all the authors. Please do not make the titlebox
% smaller than 5cm (the original size); we will check this
% in the camera-ready version and ask you to change it back.

\newcommand\BibTeX{B\textsc{ib}\TeX}

\title{A Transformer-based Pretrained Language Model for Automatic Document Summarization}

\author{Dezhou Shen \\
  Department of Computer Science\\
  Tsinghua University\\
  Beijing, CN 100084\\
  \texttt{sdz15@mails.tsinghua.edu.cn} \\}

\date{}

\begin{document}
\maketitle
\begin{abstract}
 Document summarization is an essential task in the information retrieval.
 User intention for specific documents is hard to satisfy for the information overload,
 thus there are rarely golden standards for matching a certain document.
 I propose a multi-grained summarization model for documents that uses attention on paragraphs,
 supervised learning on the sentence importance, and sequence-to-sequence learning on characters and words.
 Tested on the 2020 Chinese Law Summarization Dataset, the proposed model achieved
 better performance than other modern summarization models.

\end{abstract}

\section{Introduction}

Document matching is an essential task in daily work and study.
Because the matching algorithm is not capable of choosing important words from the massive documents,
to use the content of a document as the matching criteria often fails in returning unintended documents.
Document summarization condenses long documents into short paragraphs by retaining core information.
Thus, a much wiser way for the document matching is using the summarization instead of the content.

\section{Related Work}

\citet{bhargava2020deep} use Convolutional neural network and Long-Short Term Memory network in the paraphrase detection of
documents and summaries, then using multi-grained Convolutional neural networks as the sentence extraction model,
as a result, the F1 scores on the English and Malayalam summarization corpus are 31.57\% and 53.57\%.

\citet{erera2019summarization} consider the summarization problem as a query problem, use query
saliency, entities coverage, diversity, text coverage and sentence length as the objectives.

\citet{altmami2020automatic} concluded the special pattern for the summarization of scientific articles,
and found that abstract generation-based and citation-based are two notice-worth solutions. statistical

\section{Length of Submission}
\label{sec:length}

The conference accepts submissions of long papers and short papers.
Long papers may consist of up to eight (8) pages of content plus unlimited pages for references.
Upon acceptance, final versions of long papers will be given one additional page -- up to nine (9) pages of content plus unlimited pages for references -- so that reviewers' comments can be taken into account.
Short papers may consist of up to four (4) pages of content, plus unlimited pages for references.
Upon acceptance, short papers will be given five (5) pages in the proceedings and unlimited pages for references. 
For both long and short papers, all illustrations and tables that are part of the main text must be accommodated within these page limits, observing the formatting instructions given in the present document.
Papers that do not conform to the specified length and formatting requirements are subject to be rejected without review.

The conference encourages the submission of additional material that is relevant to the reviewers but not an integral part of the paper.
There are two such types of material: appendices, which can be read, and non-readable supplementary materials, often data or code.
Additional material must be submitted as separate files, and must adhere to the same anonymity guidelines as the main paper.
The paper must be self-contained: it is optional for reviewers to look at the supplementary material.
Papers should not refer, for further detail, to documents, code or data resources that are not available to the reviewers.
Refer to Appendices~\ref{sec:appendix} and \ref{sec:supplemental} for further information.

Workshop chairs may have different rules for allowed length and whether supplemental material is welcome.
As always, the respective call for papers is the authoritative source.

\section{Anonymity}
As reviewing will be double-blind, papers submitted for review should not include any author information (such as names or affiliations). Furthermore, self-references that reveal the author's identity, \emph{e.g.},
\begin{quote}
We previously showed \citep{Gusfield:97} \ldots
\end{quote}
should be avoided. Instead, use citations such as 
\begin{quote}
\citet{Gusfield:97} previously showed\ldots
\end{quote}
Please do not use anonymous citations and do not include acknowledgements.
\textbf{Papers that do not conform to these requirements may be rejected without review.}

Any preliminary non-archival versions of submitted papers should be listed in the submission form but not in the review version of the paper.
Reviewers are generally aware that authors may present preliminary versions of their work in other venues, but will not be provided the list of previous presentations from the submission form.

Once a paper has been accepted to the conference, the camera-ready version of the paper should include the author's names and affiliations, and is allowed to use self-references.

\paragraph{\LaTeX-specific details:}
For an anonymized submission, ensure that {\small\verb|\aclfinalcopy|} at the top of this document is commented out, and that you have filled in the paper ID number (assigned during the submission process on softconf) where {\small\verb|***|} appears in the {\small\verb|\def\aclpaperid{***}|} definition at the top of this document.
For a camera-ready submission, ensure that {\small\verb|\aclfinalcopy|} at the top of this document is not commented out.

\section{Multiple Submission Policy}
Papers that have been or will be submitted to other meetings or publications must indicate this at submission time in the START submission form, and must be withdrawn from the other venues if accepted by ACL 2020. Authors of papers accepted for presentation at ACL 2020 must notify the program chairs by the camera-ready deadline as to whether the paper will be presented. We will not accept for publication or presentation the papers that overlap significantly in content or results with papers that will be (or have been) published elsewhere.

Authors submitting more than one paper to ACL 2020 must ensure that submissions do not overlap significantly (>25\%) with each other in content or results.

\section{Formatting Instructions}

Manuscripts must be in two-column format.
Exceptions to the two-column format include the title, authors' names and complete addresses, which must be centered at the top of the first page, and any full-width figures or tables (see the guidelines in Section~\ref{ssec:title-authors}).
\textbf{Type single-spaced.}
Start all pages directly under the top margin.
The manuscript should be printed single-sided and its length should not exceed the maximum page limit described in Section~\ref{sec:length}.
Pages should be numbered in the version submitted for review, but \textbf{pages should not be numbered in the camera-ready version}.

\paragraph{\LaTeX-specific details:}
The style files will generate page numbers when {\small\verb|\aclfinalcopy|} is commented out, and remove them otherwise.

\subsection{File Format}
\label{sect:pdf}

For the production of the electronic manuscript you must use Adobe's Portable Document Format (PDF).
Please make sure that your PDF file includes all the necessary fonts (especially tree diagrams, symbols, and fonts with Asian characters).
When you print or create the PDF file, there is usually an option in your printer setup to include none, all or just non-standard fonts.
Please make sure that you select the option of including ALL the fonts.
\textbf{Before sending it, test your PDF by printing it from a computer different from the one where it was created.}
Moreover, some word processors may generate very large PDF files, where each page is rendered as an image.
Such images may reproduce poorly.
In this case, try alternative ways to obtain the PDF.
One way on some systems is to install a driver for a postscript printer, send your document to the printer specifying ``Output to a file'', then convert the file to PDF.

It is of utmost importance to specify the \textbf{A4 format} (21 cm x 29.7 cm) when formatting the paper.
Print-outs of the PDF file on A4 paper should be identical to the hardcopy version.
If you cannot meet the above requirements about the production of your electronic submission, please contact the publication chairs as soon as possible.

\paragraph{\LaTeX-specific details:}
PDF files are usually produced from \LaTeX{} using the \texttt{\small pdflatex} command.
If your version of \LaTeX{} produces Postscript files, \texttt{\small ps2pdf} or \texttt{\small dvipdf} can convert these to PDF.
To ensure A4 format in \LaTeX, use the command {\small\verb|\special{papersize=210mm,297mm}|}
in the \LaTeX{} preamble (below the {\small\verb|\usepackage|} commands) and use \texttt{\small dvipdf} and/or \texttt{\small pdflatex}; or specify \texttt{\small -t a4} when working with \texttt{\small dvips}.

\subsection{Layout}
\label{ssec:layout}

Format manuscripts two columns to a page, in the manner these
instructions are formatted.
The exact dimensions for a page on A4 paper are:

\begin{itemize}
\item Left and right margins: 2.5 cm
\item Top margin: 2.5 cm
\item Bottom margin: 2.5 cm
\item Column width: 7.7 cm
\item Column height: 24.7 cm
\item Gap between columns: 0.6 cm
\end{itemize}

\noindent Papers should not be submitted on any other paper size.
If you cannot meet the above requirements about the production of your electronic submission, please contact the publication chairs above as soon as possible.

\subsection{Fonts}

For reasons of uniformity, Adobe's \textbf{Times Roman} font should be used.
If Times Roman is unavailable, you may use Times New Roman or \textbf{Computer Modern Roman}.

Table~\ref{font-table} specifies what font sizes and styles must be used for each type of text in the manuscript.

\begin{table}
\centering
\begin{tabular}{lrl}
\hline \textbf{Type of Text} & \textbf{Font Size} & \textbf{Style} \\ \hline
paper title & 15 pt & bold \\
author names & 12 pt & bold \\
author affiliation & 12 pt & \\
the word ``Abstract'' & 12 pt & bold \\
section titles & 12 pt & bold \\
subsection titles & 11 pt & bold \\
document text & 11 pt  &\\
captions & 10 pt & \\
abstract text & 10 pt & \\
bibliography & 10 pt & \\
footnotes & 9 pt & \\
\hline
\end{tabular}
\caption{\label{font-table} Font guide. }
\end{table}

\paragraph{\LaTeX-specific details:}
To use Times Roman in \LaTeX2e{}, put the following in the preamble:
\begin{quote}
\small
\begin{verbatim}
\usepackage{times}
\usepackage{latexsym}
\end{verbatim}
\end{quote}

\subsection{Ruler}
A printed ruler (line numbers in the left and right margins of the article) should be presented in the version submitted for review, so that reviewers may comment on particular lines in the paper without circumlocution.
The presence or absence of the ruler should not change the appearance of any other content on the page.
The camera ready copy should not contain a ruler.

\paragraph{Reviewers:}
note that the ruler measurements may not align well with lines in the paper -- this turns out to be very difficult to do well when the paper contains many figures and equations, and, when done, looks ugly.
In most cases one would expect that the approximate location will be adequate, although you can also use fractional references (\emph{e.g.}, this line ends at mark $295.5$).

\paragraph{\LaTeX-specific details:}
The style files will generate the ruler when {\small\verb|\aclfinalcopy|} is commented out, and remove it otherwise.

\subsection{Title and Authors}
\label{ssec:title-authors}

Center the title, author's name(s) and affiliation(s) across both columns.
Do not use footnotes for affiliations.
Place the title centered at the top of the first page, in a 15-point bold font.
Long titles should be typed on two lines without a blank line intervening.
Put the title 2.5 cm from the top of the page, followed by a blank line, then the author's names(s), and the affiliation on the following line.
Do not use only initials for given names (middle initials are allowed).
Do not format surnames in all capitals (\emph{e.g.}, use ``Mitchell'' not ``MITCHELL'').
Do not format title and section headings in all capitals except for proper names (such as ``BLEU'') that are
conventionally in all capitals.
The affiliation should contain the author's complete address, and if possible, an electronic mail address.

The title, author names and addresses should be completely identical to those entered to the electronical paper submission website in order to maintain the consistency of author information among all publications of the conference.
If they are different, the publication chairs may resolve the difference without consulting with you; so it is in your own interest to double-check that the information is consistent.

Start the body of the first page 7.5 cm from the top of the page.
\textbf{Even in the anonymous version of the paper, you should maintain space for names and addresses so that they will fit in the final (accepted) version.}

\subsection{Abstract}
Use two-column format when you begin the abstract.
Type the abstract at the beginning of the first column.
The width of the abstract text should be smaller than the
width of the columns for the text in the body of the paper by 0.6 cm on each side.
Center the word \textbf{Abstract} in a 12 point bold font above the body of the abstract.
The abstract should be a concise summary of the general thesis and conclusions of the paper.
It should be no longer than 200 words.
The abstract text should be in 10 point font.

\subsection{Text}
Begin typing the main body of the text immediately after the abstract, observing the two-column format as shown in the present document.

Indent 0.4 cm when starting a new paragraph.

\subsection{Sections}

Format section and subsection headings in the style shown on the present document.
Use numbered sections (Arabic numerals) to facilitate cross references.
Number subsections with the section number and the subsection number separated by a dot, in Arabic numerals.

\subsection{Footnotes}
Put footnotes at the bottom of the page and use 9 point font.
They may be numbered or referred to by asterisks or other symbols.\footnote{This is how a footnote should appear.}
Footnotes should be separated from the text by a line.\footnote{Note the line separating the footnotes from the text.}

\subsection{Graphics}

Place figures, tables, and photographs in the paper near where they are first discussed, rather than at the end, if possible.
Wide illustrations may run across both columns.
Color is allowed, but adhere to Section~\ref{ssec:accessibility}'s guidelines on accessibility.

\paragraph{Captions:}
Provide a caption for every illustration; number each one sequentially in the form:
``Figure 1. Caption of the Figure.''
``Table 1. Caption of the Table.''
Type the captions of the figures and tables below the body, using 10 point text.
Captions should be placed below illustrations.
Captions that are one line are centered (see Table~\ref{font-table}).
Captions longer than one line are left-aligned (see Table~\ref{tab:accents}).

\begin{table}
\centering
\begin{tabular}{lc}
\hline
\textbf{Command} & \textbf{Output}\\
\hline
\verb|{\"a}| & {\"a} \\
\verb|{\^e}| & {\^e} \\
\verb|{\`i}| & {\`i} \\ 
\verb|{\.I}| & {\.I} \\ 
\verb|{\o}| & {\o} \\
\verb|{\'u}| & {\'u}  \\ 
\verb|{\aa}| & {\aa}  \\\hline
\end{tabular}
\begin{tabular}{lc}
\hline
\textbf{Command} & \textbf{Output}\\
\hline
\verb|{\c c}| & {\c c} \\ 
\verb|{\u g}| & {\u g} \\ 
\verb|{\l}| & {\l} \\ 
\verb|{\~n}| & {\~n} \\ 
\verb|{\H o}| & {\H o} \\ 
\verb|{\v r}| & {\v r} \\ 
\verb|{\ss}| & {\ss} \\
\hline
\end{tabular}
\caption{Example commands for accented characters, to be used in, \emph{e.g.}, \BibTeX\ names.}\label{tab:accents}
\end{table}

\paragraph{\LaTeX-specific details:}
The style files are compatible with the caption and subcaption packages; do not add optional arguments.
\textbf{Do not override the default caption sizes.}

\subsection{Hyperlinks}
Within-document and external hyperlinks are indicated with Dark Blue text, Color Hex \#000099.

\subsection{Citations}
Citations within the text appear in parentheses as~\citep{Gusfield:97} or, if the author's name appears in the text itself, as \citet{Gusfield:97}.
Append lowercase letters to the year in cases of ambiguities.  
Treat double authors as in~\citep{Aho:72}, but write as in~\citep{Chandra:81} when more than two authors are involved. Collapse multiple citations as in~\citep{Gusfield:97,Aho:72}.

Refrain from using full citations as sentence constituents.
Instead of
\begin{quote}
  ``\citep{Gusfield:97} showed that ...''
\end{quote}
write
\begin{quote}
``\citet{Gusfield:97} showed that ...''
\end{quote}

\begin{table*}
\centering
\begin{tabular}{lll}
\hline
\textbf{Output} & \textbf{natbib command} & \textbf{Old ACL-style command}\\
\hline
\citep{Gusfield:97} & \small\verb|\citep| & \small\verb|\cite| \\
\citealp{Gusfield:97} & \small\verb|\citealp| & no equivalent \\
\citet{Gusfield:97} & \small\verb|\citet| & \small\verb|\newcite| \\
\citeyearpar{Gusfield:97} & \small\verb|\citeyearpar| & \small\verb|\shortcite| \\
\hline
\end{tabular}
\caption{\label{citation-guide}
Citation commands supported by the style file.
The style is based on the natbib package and supports all natbib citation commands.
It also supports commands defined in previous ACL style files for compatibility.
}
\end{table*}

\paragraph{\LaTeX-specific details:}
Table~\ref{citation-guide} shows the syntax supported by the style files.
We encourage you to use the natbib styles.
You can use the command {\small\verb|\citet|} (cite in text) to get ``author (year)'' citations as in \citet{Gusfield:97}.
You can use the command {\small\verb|\citep|} (cite in parentheses) to get ``(author, year)'' citations as in \citep{Gusfield:97}.
You can use the command {\small\verb|\citealp|} (alternative cite without  parentheses) to get ``author year'' citations (which is useful for  using citations within parentheses, as in \citealp{Gusfield:97}).

\subsection{References}
Gather the full set of references together under the heading \textbf{References}; place the section before any Appendices. 
Arrange the references alphabetically by first author, rather than by order of occurrence in the text.

Provide as complete a citation as possible, using a consistent format, such as the one for \emph{Computational Linguistics\/} or the one in the  \emph{Publication Manual of the American 
Psychological Association\/}~\citep{APA:83}.
Use full names for authors, not just initials.

Submissions should accurately reference prior and related work, including code and data.
If a piece of prior work appeared in multiple venues, the version that appeared in a refereed, archival venue should be referenced.
If multiple versions of a piece of prior work exist, the one used by the authors should be referenced.
Authors should not rely on automated citation indices to provide accurate references for prior and related work.

The following text cites various types of articles so that the references section of the present document will include them.
\begin{itemize}
\item Example article in journal: \citep{Ando2005}.
\item Example article in proceedings, with location: \citep{borschinger-johnson-2011-particle}.
\item Example article in proceedings, without location: \citep{andrew2007scalable}.
\item Example arxiv paper: \citep{rasooli-tetrault-2015}. 
\end{itemize}

\paragraph{\LaTeX-specific details:}
The \LaTeX{} and Bib\TeX{} style files provided roughly follow the American Psychological Association format.
If your own bib file is named \texttt{\small acl2020.bib}, then placing the following before any appendices in your \LaTeX{}  file will generate the references section for you:
\begin{quote}\small
\verb|\bibliographystyle{acl_natbib}|\\
\verb|\bibliography{acl2020}|
\end{quote}

You can obtain the complete ACL Anthology as a Bib\TeX\ file from \url{https://aclweb.org/anthology/anthology.bib.gz}.
To include both the anthology and your own bib file, use the following instead of the above.
\begin{quote}\small
\verb|\bibliographystyle{acl_natbib}|\\
\verb|\bibliography{anthology,acl2020}|
\end{quote}

\subsection{Digital Object Identifiers}
As part of our work to make ACL materials more widely used and cited outside of our discipline, ACL has registered as a CrossRef member, as a registrant of Digital Object Identifiers (DOIs), the standard for registering permanent URNs for referencing scholarly materials.

All camera-ready references are required to contain the appropriate DOIs (or as a second resort, the hyperlinked ACL Anthology Identifier) to all cited works.
Appropriate records should be found for most materials in the current ACL Anthology at \url{http://aclanthology.info/}.
As examples, we cite \citep{goodman-etal-2016-noise} to show you how papers with a DOI will appear in the bibliography.
We cite \citep{harper-2014-learning} to show how papers without a DOI but with an ACL Anthology Identifier will appear in the bibliography.

\paragraph{\LaTeX-specific details:}
Please ensure that you use Bib\TeX\ records that contain DOI or URLs for any of the ACL materials that you reference.
If the Bib\TeX{} file contains DOI fields, the paper title in the references section will appear as a hyperlink to the DOI, using the hyperref \LaTeX{} package.

\subsection{Appendices}
Appendices, if any, directly follow the text and the
references (but only in the camera-ready; see Appendix~\ref{sec:appendix}).
Letter them in sequence and provide an informative title:
\textbf{Appendix A. Title of Appendix}.

\section{Accessibility}
\label{ssec:accessibility}

In an effort to accommodate people who are color-blind (as well as those printing to paper), grayscale readability is strongly encouraged.
Color is not forbidden, but authors should ensure that tables and figures do not rely solely on color to convey critical distinctions.
A simple criterion:
All curves and points in your figures should be clearly distinguishable without color.

\section{Translation of non-English Terms}

It is also advised to supplement non-English characters and terms with appropriate transliterations and/or translations since not all readers understand all such characters and terms.
Inline transliteration or translation can be represented in the order of:
\begin{center}
\begin{tabular}{c}
original-form \\
transliteration \\
``translation''
\end{tabular}
\end{center}

\section{\LaTeX{} Compilation Issues}
You may encounter the following error during compilation: 
\begin{quote}
{\small\verb|\pdfendlink|} ended up in different nesting level than {\small\verb|\pdfstartlink|}.
\end{quote}
This happens when \texttt{\small pdflatex} is used and a citation splits across a page boundary.
To fix this, the style file contains a patch consisting of two lines:
(1) {\small\verb|\RequirePackage{etoolbox}|} (line 455 in \texttt{\small acl2020.sty}), and
(2) A long line below (line 456 in \texttt{\small acl2020.sty}).

If you still encounter compilation issues even with the patch enabled, disable the patch by commenting the two lines, and then disable the \texttt{\small hyperref} package by loading the style file with the \texttt{\small nohyperref} option:

\noindent
{\small\verb|\usepackage[nohyperref]{acl2020}|}

\noindent
Then recompile, find the problematic citation, and rewrite the sentence containing the citation. (See, {\em e.g.}, \url{http://tug.org/errors.html})

\section*{Acknowledgments}

The acknowledgments should go immediately before the references. Do not number the acknowledgments section.
Do not include this section when submitting your paper for review.

\bibliography{anthology,acl2020}
\bibliographystyle{acl_natbib}

\appendix

\section{Appendices}
\label{sec:appendix}
Appendices are material that can be read, and include lemmas, formulas, proofs, and tables that are not critical to the reading and understanding of the paper. 
Appendices should be \textbf{uploaded as supplementary material} when submitting the paper for review.
Upon acceptance, the appendices come after the references, as shown here.

\paragraph{\LaTeX-specific details:}
Use {\small\verb|\appendix|} before any appendix section to switch the section numbering over to letters.

\section{Supplemental Material}
\label{sec:supplemental}
Submissions may include non-readable supplementary material used in the work and described in the paper.
Any accompanying software and/or data should include licenses and documentation of research review as appropriate.
Supplementary material may report preprocessing decisions, model parameters, and other details necessary for the replication of the experiments reported in the paper.
Seemingly small preprocessing decisions can sometimes make a large difference in performance, so it is crucial to record such decisions to precisely characterize state-of-the-art methods.

Nonetheless, supplementary material should be supplementary (rather than central) to the paper.
\textbf{Submissions that misuse the supplementary material may be rejected without review.}
Supplementary material may include explanations or details of proofs or derivations that do not fit into the paper, lists of
features or feature templates, sample inputs and outputs for a system, pseudo-code or source code, and data.
(Source code and data should be separate uploads, rather than part of the paper).

The paper should not rely on the supplementary material: while the paper may refer to and cite the supplementary material and the supplementary material will be available to the reviewers, they will not be asked to review the supplementary material.

\end{document}

### 2020-12-20 A-BasicCommom/ACL2021/acl_summary.tex
1. Summarization for Document.

@@
 \usepackage{latexsym}
+\usepackage{graphicx}
+\usepackage{amsmath}
+\usepackage{amssymb}
 \renewcommand{\UrlFont}{\ttfamily\small}
@@
 \citet{altmami2020automatic} concluded the special pattern for the summarization of scientific articles,
-and found that abstract generation-based and citation-based are two notice-worth solutions. statistical
+and found that abstract generation-based and citation-based are two notice-worth solutions.
 
-\section{Length of Submission}
-\label{sec:length}
+\citet{polsley2016casesummarizer} used a combined word frequency and domain knowledge summary method for the legal text abstraction,
+and achieved an average of 10.9\% ROUGE score between automatically-generated summaries, and the expert-generated summaries.
 
-The conference accepts submissions of long papers and short papers.
-Long papers may consist of up to eight (8) pages of content plus unlimited pages for references.
-Upon acceptance, final versions of long papers will be given one additional page -- up to nine (9) pages of content plus unlimited pages for references -- so that reviewers' comments can be taken into account.
-Short papers may consist of up to four (4) pages of content, plus unlimited pages for references.
-Upon acceptance, short papers will be given five (5) pages in the proceedings and unlimited pages for references. 
-For both long and short papers, all illustrations and tables that are part of the main text must be accommodated within these page limits, observing the formatting instructions given in the present document.
-Papers that do not conform to the specified length and formatting requirements are subject to be rejected without review.
+\citet{iqbal2020survey} showed that the deep learning approaches have achieved many satisfactory results in several domains,
+Word embeddings, such as Word2Vec, Glove, and FastText are widely used in the Natural Language Processing.
+Variational Auto-Encoders and Generative Adversarial Networks have been used for the text generations.
 
-The conference encourages the submission of additional material that is relevant to the reviewers but not an integral part of the paper.
-There are two such types of material: appendices, which can be read, and non-readable supplementary materials, often data or code.
-Additional material must be submitted as separate files, and must adhere to the same anonymity guidelines as the main paper.
-The paper must be self-contained: it is optional for reviewers to look at the supplementary material.
-Papers should not refer, for further detail, to documents, code or data resources that are not available to the reviewers.
-Refer to Appendices~\ref{sec:appendix} and \ref{sec:supplemental} for further information.
+\citet{litvak2019easy} studied the evaluation system for text summarization,
+and showed that ROUGE, MeMoG for quality evaluation, Latent Dirichlet allocation for topic evaluation,
+and grammar analysis for the readability evaluation.
 
-Workshop chairs may have different rules for allowed length and whether supplemental material is welcome.
-As always, the respective call for papers is the authoritative source.
+\citet{deng2020two} used a Sequence-to-Sequence generation model and an adversarial model in the text summarization for Chinese texts.
 
-\section{Anonymity}
-As reviewing will be double-blind, papers submitted for review should not include any author information (such as names or affiliations).
-Furthermore, self-references that reveal the author's identity, \emph{e.g.},
-\begin{quote}
-We previously showed \citep{Gusfield:97} \ldots
-\end{quote}
-should be avoided. Instead, use citations such as 
-\begin{quote}
-\citet{Gusfield:97} previously showed\ldots
-\end{quote}
-Please do not use anonymous citations and do not include acknowledgements.
-\textbf{Papers that do not conform to these requirements may be rejected without review.}
+\citet{zhang2019pretraining} used the Transformer network in encoder-decoder framework for the text summarization task, and
+achieved a Rouge score of 33.48\% in the CNN/DailyMail dataset for news summarization.
 
-Any preliminary non-archival versions of submitted papers should be listed in the submission form but not in the review version of the paper.
-Reviewers are generally aware that authors may present preliminary versions of their work in other venues, but will not be provided the list of previous presentations from the submission form.
+\citet{xiao2019extractive} used the extractive LSTM-Minus model in the text summarization task, and by combining
+global document level, sentence level and topic segment representation in the network, achieved a Rouge score of 31.99\%
+in the Pubmed summarization dataset.
 
-Once a paper has been accepted to the conference, the camera-ready version of the paper should include the author's names and affiliations, and is allowed to use self-references.
+\citet{liakata2013discourse} used the CRF and SVM models for the sentence extractive summarization for the scientific articles.
+\citet{cohan2015scientific} use the important sections in scientific papers as criteria for selecting important sentence.
 
-\paragraph{\LaTeX-specific details:}
-For an anonymized submission, ensure that {\small\verb|\aclfinalcopy|} at the top of this document is commented out, and that you have filled in the paper ID number (assigned during the submission process on softconf) where {\small\verb|***|} appears in the {\small\verb|\def\aclpaperid{***}|} definition at the top of this document.
-For a camera-ready submission, ensure that {\small\verb|\aclfinalcopy|} at the top of this document is not commented out.
+\citet{sutskever2013importance} started to use sequence-to-sequence neural networks in abstractive summarization.
+\citet{vinyals2015pointer} introduced copy mechanism from source to summary in sequence-to-sequence models.
 
-\section{Multiple Submission Policy}
-Papers that have been or will be submitted to other meetings or publications must indicate this at submission time in the START submission form, and must be withdrawn from the other venues if accepted by ACL 2020.
-Authors of papers accepted for presentation at ACL 2020 must notify the program chairs by the camera-ready deadline as to whether the paper will be presented.
-We will not accept for publication or presentation the papers that overlap significantly in content or results with papers that will be (or have been) published elsewhere.
+\begin{figure*}
+\begin{center}
+  \fbox{\rule{0pt}{2in} \includegraphics[width=0.9\linewidth]{SummaryRule.pdf}}
+\end{center}
+   \caption{Rule based segment and importance based summarization.}
+\label{fig:short}
+\end{figure*}
 
-Authors submitting more than one paper to ACL 2020 must ensure that submissions do not overlap significantly (>25\%) with each other in content or results.
+\section{Hierachical Multi-grained Summarization}
+\label{sec:hireachy}
 
-\section{Formatting Instructions}
+Documents have their own organizations by different purposes, take the civil legal documents as an example,
+There are 123 different kinds of arguing reasons in the Chinese Court Sentence Documents.
+Largely list as follows:
+\begin{itemize}
+\item Disputes over personality rights,
+\item Marriage, family, inheritance disputes,
+\item Property rights disputes,
+\item Contract, management without cause, disputes over unjust enrichment,
+\item Labor disputes, personnel disputes,
+\item Maritime disputes,
+\item Civil disputes related to companies, securities, insurance, bills, etc.
+\item Inciting disputes
+\end{itemize}
+However, each of these documents follow the same organization of segments, for example,
+the purpose, the facts, the court opinions and the trail results.
+Thus, for a meaningful text summarization includes all there segments of importance and ignore other segments.
 
-Manuscripts must be in two-column format.
-Exceptions to the two-column format include the title, authors' names and complete addresses, which must be centered at the top of the first page, and any full-width figures or tables (see the guidelines in Section~\ref{ssec:title-authors}).
-\textbf{Type single-spaced.}
-Start all pages directly under the top margin.
-The manuscript should be printed single-sided and its length should not exceed the maximum page limit described in Section~\ref{sec:length}.
-Pages should be numbered in the version submitted for review, but \textbf{pages should not be numbered in the camera-ready version}.
+\subsection{Segment Extraction}
+The document of the court sentence usually states the arguing point of the two entities.
+In this paper, a dictionary based arguing reason extractor was designed.
+A total of 123 arguing reasons were classified by the legal experts out of 70 million
+civil documents collected from the Chinese Court Sentence website.
 
-\paragraph{\LaTeX-specific details:}
-The style files will generate page numbers when {\small\verb|\aclfinalcopy|} is commented out, and remove them otherwise.
+Then I use several rule-based filters to extract meaningful segments. As Figure-1 shows, the document has been split into several
+paragraphs, the paragraph with important words are kept and other paragraphs are discarded.
 
-\subsection{File Format}
-\label{sect:pdf}
+\subsection{Extractive Sentence Summarization}
 
-For the production of the electronic manuscript you must use Adobe's Portable Document Format (PDF).
-Please make sure that your PDF file includes all the necessary fonts (especially tree diagrams, symbols, and fonts with Asian characters).
-When you print or create the PDF file, there is usually an option in your printer setup to include none, all or just non-standard fonts.
-Please make sure that you select the option of including ALL the fonts.
-\textbf{Before sending it, test your PDF by printing it from a computer different from the one where it was created.}
-Moreover, some word processors may generate very large PDF files, where each page is rendered as an image.
-Such images may reproduce poorly.
-In this case, try alternative ways to obtain the PDF.
-One way on some systems is to install a driver for a postscript printer, send your document to the printer specifying ``Output to a file'', then convert the file to PDF.
+For the sentence importance scoring model, the experts wrote the summarization for each legal document.
+Base on the written summarization, each sentence importance can be easily computed by checking the overlap words.
+I use the pre-trained Chinese language model, which has multiple layers of transformers,
+for encoding sentences.
+As Figure-2 shows, the model layers are organized as follows:
+Take the last two layers of the RoBERTa encoding, then do the concatenation and take the Maximum element from the character
+sequence as representation for each sentence, then concatenating to a dropout layer, a softmax layer,
+and the output layer.
 
-It is of utmost importance to specify the \textbf{A4 format} (21 cm x 29.7 cm) when formatting the paper.
-Print-outs of the PDF file on A4 paper should be identical to the hardcopy version.
-If you cannot meet the above requirements about the production of your electronic submission, please contact the publication chairs as soon as possible.
+The learning rate is $10^{-4}$, the max sequence length is 50, the dropout rate is 5\%, and the batch size is 1.
+The epoch number is 3. The experiment was carried on a Google Cloud TPU v3, with 32GB of RAM, and 8 chips with 16GB of the high speed of memory each,
+which can provide 420 tera-flops of computation capability.
 
-\paragraph{\LaTeX-specific details:}
-PDF files are usually produced from \LaTeX{} using the \texttt{\small pdflatex} command.
-If your version of \LaTeX{} produces Postscript files, \texttt{\small ps2pdf} or \texttt{\small dvipdf} can convert these to PDF.
-To ensure A4 format in \LaTeX, use the command {\small\verb|\special{papersize=210mm,297mm}|}
-in the \LaTeX{} preamble (below the {\small\verb|\usepackage|} commands) and use \texttt{\small dvipdf} and/or \texttt{\small pdflatex}; or specify \texttt{\small -t a4} when working with \texttt{\small dvips}.
+The classification dataset is unbalanced, thus I copy the positive samples multiple times to balance the dataset.
+In total, there are 782,895 samples for training and 42 samples for test in the Legal Sentence Importance dataset.
+The test accuracy is 92.06\%.
 
-\subsection{Layout}
-\label{ssec:layout}
+\subsection{Sequence To Sequence Summarization}
 
-Format manuscripts two columns to a page, in the manner these
-instructions are formatted.
-The exact dimensions for a page on A4 paper are:
+For the token generation in the summarization step, I use a sequence-to-sequence model.
+By tagging each token existence in the corresponding summary, a sentence has its unique sequence of code for the token importance.
+For the 14,908 samples of important sentences for training and 108 samples for test in the Legal Token Summarization Dataset, I design a token summarization model as follows:
+First, encode the sentence by RoBERTa language model, and concatenate the first and last layers as the sentence representation.
+Then concatenate to a CapsuleNet layer, then concatenates the output layer.
 
-\begin{itemize}
-\item Left and right margins: 2.5 cm
-\item Top margin: 2.5 cm
-\item Bottom margin: 2.5 cm
-\item Column width: 7.7 cm
-\item Column height: 24.7 cm
-\item Gap between columns: 0.6 cm
-\end{itemize}
-
-\noindent Papers should not be submitted on any other paper size.
-If you cannot meet the above requirements about the production of your electronic submission, please contact the publication chairs above as soon as possible.
-
-\subsection{Fonts}
-
-For reasons of uniformity, Adobe's \textbf{Times Roman} font should be used.
-If Times Roman is unavailable, you may use Times New Roman or \textbf{Computer Modern Roman}.
-
-Table~\ref{font-table} specifies what font sizes and styles must be used for each type of text in the manuscript.
+The learning rate is $10^{-3}$, and the bach size is 2, and the accumulation step is 8.
+The training epoch is 10, and the accuracy of the best model in the test set is 42.05\%.
+From Table(1) we can see that different number of transformer layers has no significant performance improvement for accuracy in the test set.
+The RBT3, BRT3L and RoBERTa vary in number of neurons and number of layers,
+which was popular pre-trained language models trained on 4.5 billion of Chinese tokens by \citet{cui2020revisiting}.
 
@@
 \centering
-\begin{tabular}{lrl}
-\hline \textbf{Type of Text} & \textbf{Font Size} & \textbf{Style} \\ \hline
-paper title & 15 pt & bold \\
-author names & 12 pt & bold \\
-author affiliation & 12 pt & \\
-the word ``Abstract'' & 12 pt & bold \\
-section titles & 12 pt & bold \\
-subsection titles & 11 pt & bold \\
-document text & 11 pt  &\\
-captions & 10 pt & \\
-abstract text & 10 pt & \\
-bibliography & 10 pt & \\
-footnotes & 9 pt & \\
+\begin{tabular}{cccc}
+\hline
+\textbf{Model} & \textbf{Neurons}& \textbf{Layers} & \textbf{Accuracy} \\
+\hline
+RoBERTa & 768 & 12 & 42.05\% \\
+RBT3 & 768 & 3 & 40.18\% \\
+RBT3L & 1024 & 3 & 41.22\% \\
 \hline
 \end{tabular}
-\caption{\label{font-table} Font guide. }
+\caption{Different Pre-trained Language models accuracy in the sequence to sequece training steps.}
 \end{table}
 
-\paragraph{\LaTeX-specific details:}
-To use Times Roman in \LaTeX2e{}, put the following in the preamble:
-\begin{quote}
-\small
-\begin{verbatim}
-\usepackage{times}
-\usepackage{latexsym}
-\end{verbatim}
-\end{quote}
+For balancing the readability and quality of the summary, I did not use the sequence predicted by the token summarization model directly.
+Instead, a bigger threshold for the output of the model can improve the readability and the quality.
+As a practical result, I choose 87.5\% as the threshold for keeping the important token.
+That is to say, keeping the most important 87.5\% tokens for each inference shall get the best summarization result.
 
-\subsection{Ruler}
-A printed ruler (line numbers in the left and right margins of the article) should be presented in the version submitted for review, so that reviewers may comment on particular lines in the paper without circumlocution.
-The presence or absence of the ruler should not change the appearance of any other content on the page.
-The camera ready copy should not contain a ruler.
+\begin{figure*}
+\begin{center}
+  \fbox{\rule{0pt}{2in} \includegraphics[width=0.9\linewidth]{SummaryModel.pdf}}
+\end{center}
+   \caption{Different architectures for multi-grained summarization.
+   (a) Extractive Sentence Summarization,
+   (b) Sequence To Sequence Summarization.}
+\label{fig:short}
+\end{figure*}
 
-\paragraph{Reviewers:}
-note that the ruler measurements may not align well with lines in the paper -- this turns out to be very difficult to do well when the paper contains many figures and equations, and, when done, looks ugly.
-In most cases one would expect that the approximate location will be adequate, although you can also use fractional references (\emph{e.g.}, this line ends at mark $295.5$).
+\subsection{Summarization Evaluation}
 
-\paragraph{\LaTeX-specific details:}
-The style files will generate the ruler when {\small\verb|\aclfinalcopy|} is commented out, and remove it otherwise.
+\citet{lin2004rouge} represents a set of similar metrics such as ROUGE-N, ROUGE-L, ROUGE-W, ROUGE-S, and ROUGE-SU.
+In this paper, I use ROUGE-1, ROUGE-2, ROUGE-L and ROUGE-W as the summarization evaluation metrics.
+The ROUGE-W score is computed using Formula (1).
 
-\subsection{Title and Authors}
-\label{ssec:title-authors}
-
-Center the title, author's name(s) and affiliation(s) across both columns.
-Do not use footnotes for affiliations.
-Place the title centered at the top of the first page, in a 15-point bold font.
-Long titles should be typed on two lines without a blank line intervening.
-Put the title 2.5 cm from the top of the page, followed by a blank line, then the author's names(s), and the affiliation on the following line.
-Do not use only initials for given names (middle initials are allowed).
-Do not format surnames in all capitals (\emph{e.g.}, use ``Mitchell'' not ``MITCHELL'').
-Do not format title and section headings in all capitals except for proper names (such as ``BLEU'') that are
-conventionally in all capitals.
-The affiliation should contain the author's complete address, and if possible, an electronic mail address.
-
-The title, author names and addresses should be completely identical to those entered to the electronical paper submission website in order to maintain the consistency of author information among all publications of the conference.
-If they are different, the publication chairs may resolve the difference without consulting with you; so it is in your own interest to double-check that the information is consistent.
-
-Start the body of the first page 7.5 cm from the top of the page.
-\textbf{Even in the anonymous version of the paper, you should maintain space for names and addresses so that they will fit in the final (accepted) version.}
-
-\subsection{Abstract}
-Use two-column format when you begin the abstract.
-Type the abstract at the beginning of the first column.
-The width of the abstract text should be smaller than the
-width of the columns for the text in the body of the paper by 0.6 cm on each side.
-Center the word \textbf{Abstract} in a 12 point bold font above the body of the abstract.
-The abstract should be a concise summary of the general thesis and conclusions of the paper.
-It should be no longer than 200 words.
-The abstract text should be in 10 point font.
-
-\subsection{Text}
-Begin typing the main body of the text immediately after the abstract, observing the two-column format as shown in the present document.
-
-Indent 0.4 cm when starting a new paragraph.
-
-\subsection{Sections}
-
-Format section and subsection headings in the style shown on the present document.
-Use numbered sections (Arabic numerals) to facilitate cross references.
-Number subsections with the section number and the subsection number separated by a dot, in Arabic numerals.
-
-\subsection{Footnotes}
-Put footnotes at the bottom of the page and use 9 point font.
-They may be numbered or referred to by asterisks or other symbols.\footnote{This is how a footnote should appear.}
-Footnotes should be separated from the text by a line.\footnote{Note the line separating the footnotes from the text.}
-
-\subsection{Graphics}
-
-Place figures, tables, and photographs in the paper near where they are first discussed, rather than at the end, if possible.
-Wide illustrations may run across both columns.
-Color is allowed, but adhere to Section~\ref{ssec:accessibility}'s guidelines on accessibility.
-
-\paragraph{Captions:}
-Provide a caption for every illustration; number each one sequentially in the form:
-``Figure 1. Caption of the Figure.''
-``Table 1. Caption of the Table.''
-Type the captions of the figures and tables below the body, using 10 point text.
-Captions should be placed below illustrations.
-Captions that are one line are centered (see Table~\ref{font-table}).
-Captions longer than one line are left-aligned (see Table~\ref{tab:accents}).
+\begin{equation}
+  {R_W} = {R_1} * 0.2 + {R_2} * 0.4 + {R_L} * 0.4
+\end{equation}
 
@@
 \centering
-\begin{tabular}{lc}
+\begin{tabular}{cccc}
 \hline
-\textbf{Command} & \textbf{Output}\\
+\textbf{R-1} & \textbf{R-2} & \textbf{R-L} & \textbf{R-W} \\
 \hline
-\verb|{\"a}| & {\"a} \\
-\verb|{\^e}| & {\^e} \\
-\verb|{\`i}| & {\`i} \\ 
-\verb|{\.I}| & {\.I} \\ 
-\verb|{\o}| & {\o} \\
-\verb|{\'u}| & {\'u}  \\ 
-\verb|{\aa}| & {\aa}  \\\hline
-\end{tabular}
-\begin{tabular}{lc}
-\hline
-\textbf{Command} & \textbf{Output}\\
-\hline
-\verb|{\c c}| & {\c c} \\ 
-\verb|{\u g}| & {\u g} \\ 
-\verb|{\l}| & {\l} \\ 
-\verb|{\~n}| & {\~n} \\ 
-\verb|{\H o}| & {\H o} \\ 
-\verb|{\v r}| & {\v r} \\ 
-\verb|{\ss}| & {\ss} \\
+32.62\% & 15.63\% & 31.79\% & 25.49\% \\
 \hline
 \end{tabular}
-\caption{Example commands for accented characters, to be used in, \emph{e.g.}, \BibTeX\ names.}\label{tab:accents}
+\caption{F-score for text summarization in the dataset.}
 \end{table}
 
-\paragraph{\LaTeX-specific details:}
-The style files are compatible with the caption and subcaption packages; do not add optional arguments.
-\textbf{Do not override the default caption sizes.}
+\section{Conclusion}
 
-\subsection{Hyperlinks}
-Within-document and external hyperlinks are indicated with Dark Blue text, Color Hex \#000099.
+In this paper, I introduced a novel summarization method, which leveraging hierarchical features of the document.
+By extracting multi-grained level from the document, the summary contains the paragraph-level, sentence-level and token-level key information.
+The evaluation results showed that the multiple layers of transformers have improved the Rouge evaluation performance
+and achieved a Rouge-W score of 25.49\% on the Chinese Legal Case Abstraction dataset.
 
-\subsection{Citations}
-Citations within the text appear in parentheses as~\citep{Gusfield:97} or, if the author's name appears in the text itself, as \citet{Gusfield:97}.
-Append lowercase letters to the year in cases of ambiguities.  
-Treat double authors as in~\citep{Aho:72}, but write as in~\citep{Chandra:81} when more than two authors are involved. Collapse multiple citations as in~\citep{Gusfield:97,Aho:72}.
-
-Refrain from using full citations as sentence constituents.
-Instead of
-\begin{quote}
-  ``\citep{Gusfield:97} showed that ...''
-\end{quote}
-write
-\begin{quote}
-``\citet{Gusfield:97} showed that ...''
-\end{quote}
-
-\begin{table*}
-\centering
-\begin{tabular}{lll}
-\hline
-\textbf{Output} & \textbf{natbib command} & \textbf{Old ACL-style command}\\
-\hline
-\citep{Gusfield:97} & \small\verb|\citep| & \small\verb|\cite| \\
-\citealp{Gusfield:97} & \small\verb|\citealp| & no equivalent \\
-\citet{Gusfield:97} & \small\verb|\citet| & \small\verb|\newcite| \\
-\citeyearpar{Gusfield:97} & \small\verb|\citeyearpar| & \small\verb|\shortcite| \\
-\hline
-\end{tabular}
-\caption{\label{citation-guide}
-Citation commands supported by the style file.
-The style is based on the natbib package and supports all natbib citation commands.
-It also supports commands defined in previous ACL style files for compatibility.
-}
-\end{table*}
-
-\paragraph{\LaTeX-specific details:}
-Table~\ref{citation-guide} shows the syntax supported by the style files.
-We encourage you to use the natbib styles.
-You can use the command {\small\verb|\citet|} (cite in text) to get ``author (year)'' citations as in \citet{Gusfield:97}.
-You can use the command {\small\verb|\citep|} (cite in parentheses) to get ``(author, year)'' citations as in \citep{Gusfield:97}.
-You can use the command {\small\verb|\citealp|} (alternative cite without  parentheses) to get ``author year'' citations (which is useful for  using citations within parentheses, as in \citealp{Gusfield:97}).
-
-\subsection{References}
-Gather the full set of references together under the heading \textbf{References}; place the section before any Appendices. 
-Arrange the references alphabetically by first author, rather than by order of occurrence in the text.
-
-Provide as complete a citation as possible, using a consistent format, such as the one for \emph{Computational Linguistics\/} or the one in the  \emph{Publication Manual of the American 
-Psychological Association\/}~\citep{APA:83}.
-Use full names for authors, not just initials.
-
-Submissions should accurately reference prior and related work, including code and data.
-If a piece of prior work appeared in multiple venues, the version that appeared in a refereed, archival venue should be referenced.
-If multiple versions of a piece of prior work exist, the one used by the authors should be referenced.
-Authors should not rely on automated citation indices to provide accurate references for prior and related work.
-
-The following text cites various types of articles so that the references section of the present document will include them.
-\begin{itemize}
-\item Example article in journal: \citep{Ando2005}.
-\item Example article in proceedings, with location: \citep{borschinger-johnson-2011-particle}.
-\item Example article in proceedings, without location: \citep{andrew2007scalable}.
-\item Example arxiv paper: \citep{rasooli-tetrault-2015}. 
-\end{itemize}
-
-\paragraph{\LaTeX-specific details:}
-The \LaTeX{} and Bib\TeX{} style files provided roughly follow the American Psychological Association format.
-If your own bib file is named \texttt{\small acl2020.bib}, then placing the following before any appendices in your \LaTeX{}  file will generate the references section for you:
-\begin{quote}\small
-\verb|\bibliographystyle{acl_natbib}|\\
-\verb|\bibliography{acl2020}|
-\end{quote}
-
-You can obtain the complete ACL Anthology as a Bib\TeX\ file from \url{https://aclweb.org/anthology/anthology.bib.gz}.
-To include both the anthology and your own bib file, use the following instead of the above.
-\begin{quote}\small
-\verb|\bibliographystyle{acl_natbib}|\\
-\verb|\bibliography{anthology,acl2020}|
-\end{quote}
-
-\subsection{Digital Object Identifiers}
-As part of our work to make ACL materials more widely used and cited outside of our discipline, ACL has registered as a CrossRef member, as a registrant of Digital Object Identifiers (DOIs), the standard for registering permanent URNs for referencing scholarly materials.
-
-All camera-ready references are required to contain the appropriate DOIs (or as a second resort, the hyperlinked ACL Anthology Identifier) to all cited works.
-Appropriate records should be found for most materials in the current ACL Anthology at \url{http://aclanthology.info/}.
-As examples, we cite \citep{goodman-etal-2016-noise} to show you how papers with a DOI will appear in the bibliography.
-We cite \citep{harper-2014-learning} to show how papers without a DOI but with an ACL Anthology Identifier will appear in the bibliography.
-
-\paragraph{\LaTeX-specific details:}
-Please ensure that you use Bib\TeX\ records that contain DOI or URLs for any of the ACL materials that you reference.
-If the Bib\TeX{} file contains DOI fields, the paper title in the references section will appear as a hyperlink to the DOI, using the hyperref \LaTeX{} package.
-
-\subsection{Appendices}
-Appendices, if any, directly follow the text and the
-references (but only in the camera-ready; see Appendix~\ref{sec:appendix}).
-Letter them in sequence and provide an informative title:
-\textbf{Appendix A. Title of Appendix}.
-
-\section{Accessibility}
-\label{ssec:accessibility}
-
-In an effort to accommodate people who are color-blind (as well as those printing to paper), grayscale readability is strongly encouraged.
-Color is not forbidden, but authors should ensure that tables and figures do not rely solely on color to convey critical distinctions.
-A simple criterion:
-All curves and points in your figures should be clearly distinguishable without color.
-
-\section{Translation of non-English Terms}
-
-It is also advised to supplement non-English characters and terms with appropriate transliterations and/or translations since not all readers understand all such characters and terms.
-Inline transliteration or translation can be represented in the order of:
-\begin{center}
-\begin{tabular}{c}
-original-form \\
-transliteration \\
-``translation''
-\end{tabular}
-\end{center}
-
-\section{\LaTeX{} Compilation Issues}
-You may encounter the following error during compilation: 
-\begin{quote}
-{\small\verb|\pdfendlink|} ended up in different nesting level than {\small\verb|\pdfstartlink|}.
-\end{quote}
-This happens when \texttt{\small pdflatex} is used and a citation splits across a page boundary.
-To fix this, the style file contains a patch consisting of two lines:
-(1) {\small\verb|\RequirePackage{etoolbox}|} (line 455 in \texttt{\small acl2020.sty}), and
-(2) A long line below (line 456 in \texttt{\small acl2020.sty}).
-
-If you still encounter compilation issues even with the patch enabled, disable the patch by commenting the two lines, and then disable the \texttt{\small hyperref} package by loading the style file with the \texttt{\small nohyperref} option:
-
-\noindent
-{\small\verb|\usepackage[nohyperref]{acl2020}|}
-
-\noindent
-Then recompile, find the problematic citation, and rewrite the sentence containing the citation. (See, {\em e.g.}, \url{http://tug.org/errors.html})
-
-\section*{Acknowledgments}
-
-The acknowledgments should go immediately before the references. Do not number the acknowledgments section.
-Do not include this section when submitting your paper for review.
-
-\bibliography{anthology,acl2020}
+\bibliography{anthology,acl2020,acl_summary}
 \bibliographystyle{acl_natbib}
 
-\appendix
-
-\section{Appendices}
-\label{sec:appendix}
-Appendices are material that can be read, and include lemmas, formulas, proofs, and tables that are not critical to the reading and understanding of the paper. 
-Appendices should be \textbf{uploaded as supplementary material} when submitting the paper for review.
-Upon acceptance, the appendices come after the references, as shown here.
-
-\paragraph{\LaTeX-specific details:}
-Use {\small\verb|\appendix|} before any appendix section to switch the section numbering over to letters.
-
-\section{Supplemental Material}
-\label{sec:supplemental}
-Submissions may include non-readable supplementary material used in the work and described in the paper.
-Any accompanying software and/or data should include licenses and documentation of research review as appropriate.
-Supplementary material may report preprocessing decisions, model parameters, and other details necessary for the replication of the experiments reported in the paper.
-Seemingly small preprocessing decisions can sometimes make a large difference in performance, so it is crucial to record such decisions to precisely characterize state-of-the-art methods.
-
-Nonetheless, supplementary material should be supplementary (rather than central) to the paper.
-\textbf{Submissions that misuse the supplementary material may be rejected without review.}
-Supplementary material may include explanations or details of proofs or derivations that do not fit into the paper, lists of
-features or feature templates, sample inputs and outputs for a system, pseudo-code or source code, and data.
-(Source code and data should be separate uploads, rather than part of the paper).
-
-The paper should not rely on the supplementary material: while the paper may refer to and cite the supplementary material and the supplementary material will be available to the reviewers, they will not be asked to review the supplementary material.
-
 \end{document}

### 2021-01-05 A-BasicCommom/ACL2021/acl_law_examination.tex
1. add law examination model.

--- 2020-12-20 A-BasicCommom/ACL2021/acl_summary.tex
@@
 %
-% File acl2020.tex
+% File acl2021.tex
 %
+%% Based on the style files for EMNLP 2020, which were
 %% Based on the style files for ACL 2020, which were
@@
 \documentclass[11pt,a4paper]{article}
-\usepackage[hyperref]{acl2020}
+\usepackage[hyperref]{acl2021}
 \usepackage{times}
@@
 
-\title{A Transformer-based Pretrained Language Model for Automatic Document Summarization}
+\title{A Transformer-based Pretrained Language Model for Chinese Law Examination}
 
@@
 \begin{abstract}
- Document summarization is an essential task in the information retrieval.
- User intention for specific documents is hard to satisfy for the information overload,
- thus there are rarely golden standards for matching a certain document.
- I propose a multi-grained summarization model for documents that uses attention on paragraphs,
- supervised learning on the sentence importance, and sequence-to-sequence learning on characters and words.
- Tested on the 2020 Chinese Law Summarization Dataset, the proposed model achieved
- better performance than other modern summarization models.
-
+ Teaching machines to take examinations of the National Judicial Examination of China is a meaningful task.
+ However, until now perfect solution for the Question Answering is still missing.
+ In this paper, I demonstrate a novel model which leverage the Transformers and Convolutional Neural Networks for the Judicial Examination task,
+    propose model achieved 35\% in accuracy.
 \end{abstract}
@@
 
-Document matching is an essential task in daily work and study.
-Because the matching algorithm is not capable of choosing important words from the massive documents,
-to use the content of a document as the matching criteria often fails in returning unintended documents.
-Document summarization condenses long documents into short paragraphs by retaining core information.
-Thus, a much wiser way for the document matching is using the summarization instead of the content.
+  Legal Question Answering aims to provide explanations, advice and solutions for legal issues.
+Reading Comprehension and Open-domain Question Answering are two of the most studied topics in the natural processing language.
 
@@
 
-\citet{bhargava2020deep} use Convolutional neural network and Long-Short Term Memory network in the paraphrase detection of
-documents and summaries, then using multi-grained Convolutional neural networks as the sentence extraction model,
-as a result, the F1 scores on the English and Malayalam summarization corpus are 31.57\% and 53.57\%.
+\citet{hermann2015teaching} found that the combination of the Deep LSTM encoders, and the Attention model works better on the Daily Mail reading comprehension dataset,
+ and by document representation with the token-level question representation the Attention model achieved better result on the CNN reading comprehension dataset.
 
-\citet{erera2019summarization} consider the summarization problem as a query problem, use query
-saliency, entities coverage, diversity, text coverage and sentence length as the objectives.
+\citet{hashemi2019performance} proposed an efficient evaluation method for the question answering, compared to the extensive study in
+the retrieval tasks, the proposed neural model for evaluating query performance prediction showed that its outstanding in all the methods in the QA domain.
 
-\citet{altmami2020automatic} concluded the special pattern for the summarization of scientific articles,
-and found that abstract generation-based and citation-based are two notice-worth solutions.
+\citet{huang2019knowledge} borrowed idea from the knowledge graph completion and recommender system, they use the low-dimensional vector learned from knowledge graph,
+then trained the question answering model.
 
-\citet{polsley2016casesummarizer} used a combined word frequency and domain knowledge summary method for the legal text abstraction,
-and achieved an average of 10.9\% ROUGE score between automatically-generated summaries, and the expert-generated summaries.
+\citet{karki2019question} broke the question answering problem into several subtasks, such as table retrieval and element classification.
+the performace of the translation from a question to SQL clause is still far from satisfactory, with 15.6\% to 19.5\% in the F1 score on the test dataset.
 
-\citet{iqbal2020survey} showed that the deep learning approaches have achieved many satisfactory results in several domains,
-Word embeddings, such as Word2Vec, Glove, and FastText are widely used in the Natural Language Processing.
-Variational Auto-Encoders and Generative Adversarial Networks have been used for the text generations.
+\citet{mcelvain2019non} showed that for the non-factoid question answering task in the legal domain, legally correct, jurisdictional relevant, and conversationally responsive answers
+are three key factors.
 
-\citet{litvak2019easy} studied the evaluation system for text summarization,
-and showed that ROUGE, MeMoG for quality evaluation, Latent Dirichlet allocation for topic evaluation,
-and grammar analysis for the readability evaluation.
+\citet{jin2019video} described that by understanding the question and the contextual images, the Attention model learn the answers, the total accuracy achieved 30.2\% in the YouTube-QA Dataset.
 
-\citet{deng2020two} used a Sequence-to-Sequence generation model and an adversarial model in the text summarization for Chinese texts.
+\citet{pizzato2008indexing} proposed the weight based bag-of-words, partial relation and full relation to model semantic roles for questions as labels in the training procedure.
 
-\citet{zhang2019pretraining} used the Transformer network in encoder-decoder framework for the text summarization task, and
-achieved a Rouge score of 33.48\% in the CNN/DailyMail dataset for news summarization.
+\citet{zhan2020medical} proposed an Attention-based reasoning model in the medical visual question answering.
 
-\citet{xiao2019extractive} used the extractive LSTM-Minus model in the text summarization task, and by combining
-global document level, sentence level and topic segment representation in the network, achieved a Rouge score of 31.99\%
-in the Pubmed summarization dataset.
+\citet{qu2020open} studied a transformer-based conversational QA system, and use retrieval and rerank pattern to solve the problem.
 
-\citet{liakata2013discourse} used the CRF and SVM models for the sentence extractive summarization for the scientific articles.
-\citet{cohan2015scientific} use the important sections in scientific papers as criteria for selecting important sentence.
-
-\citet{sutskever2013importance} started to use sequence-to-sequence neural networks in abstractive summarization.
-\citet{vinyals2015pointer} introduced copy mechanism from source to summary in sequence-to-sequence models.
-
-\begin{figure*}
-\begin{center}
-  \fbox{\rule{0pt}{2in} \includegraphics[width=0.9\linewidth]{SummaryRule.pdf}}
-\end{center}
-   \caption{Rule based segment and importance based summarization.}
-\label{fig:short}
-\end{figure*}
-
-\section{Hierachical Multi-grained Summarization}
+\section{Methodology}
 \label{sec:hireachy}
-
-Documents have their own organizations by different purposes, take the civil legal documents as an example,
-There are 123 different kinds of arguing reasons in the Chinese Court Sentence Documents.
-Largely list as follows:
-\begin{itemize}
-\item Disputes over personality rights,
-\item Marriage, family, inheritance disputes,
-\item Property rights disputes,
-\item Contract, management without cause, disputes over unjust enrichment,
-\item Labor disputes, personnel disputes,
-\item Maritime disputes,
-\item Civil disputes related to companies, securities, insurance, bills, etc.
-\item Inciting disputes
-\end{itemize}
-However, each of these documents follow the same organization of segments, for example,
-the purpose, the facts, the court opinions and the trail results.
-Thus, for a meaningful text summarization includes all there segments of importance and ignore other segments.
 
@@
 
-Then I use several rule-based filters to extract meaningful segments. As Figure-1 shows, the document has been split into several
-paragraphs, the paragraph with important words are kept and other paragraphs are discarded.
+Then I use several rule-based filters to extract meaningful segments.
+As Figure-1 shows, the document has been split into several paragraphs,
+the paragraph with important words are kept and other paragraphs are discarded.
 
@@
 The learning rate is $10^{-4}$, the max sequence length is 50, the dropout rate is 5\%, and the batch size is 1.
-The epoch number is 3. The experiment was carried on a Google Cloud TPU v3, with 32GB of RAM, and 8 chips with 16GB of the high speed of memory each,
+The epoch number is 3.
+The experiment was carried on a Google Cloud TPU v3, with 32GB of RAM, and 8 chips with 16GB of the high speed of memory each,
 which can provide 420 tera-flops of computation capability.
@@
 By tagging each token existence in the corresponding summary, a sentence has its unique sequence of code for the token importance.
-For the 14,908 samples of important sentences for training and 108 samples for test in the Legal Token Summarization Dataset, I design a token summarization model as follows:
+For the 14,908 samples of important sentences for training and 108 samples for test in the Legal Token Summarization Dataset,
+I design a token summarization model as follows:
 First, encode the sentence by RoBERTa language model, and concatenate the first and last layers as the sentence representation.
@@
 \end{tabular}
-\caption{Different Pre-trained Language models accuracy in the sequence to sequece training steps.}
+\caption{Pre-trained language models accuracy in the sequence-to-sequece training steps.}
 \end{table}
@@
 
-\bibliography{anthology,acl2020,acl_summary}
 \bibliographystyle{acl_natbib}
+\bibliography{anthology,acl2021,acl_examination}
+
+%\appendix
 

### 2021-01-16 A-BasicCommom/ACL2021/acl_word_segment.tex
1.acl2021 CN word segment.

%
% File acl2021.tex
%
%% Based on the style files for EMNLP 2020, which were
%% Based on the style files for ACL 2020, which were
%% Based on the style files for ACL 2018, NAACL 2018/19, which were
%% Based on the style files for ACL-2015, with some improvements
%%  taken from the NAACL-2016 style
%% Based on the style files for ACL-2014, which were, in turn,
%% based on ACL-2013, ACL-2012, ACL-2011, ACL-2010, ACL-IJCNLP-2009,
%% EACL-2009, IJCNLP-2008...
%% Based on the style files for EACL 2006 by 
%%e.agirre@ehu.es or Sergi.Balari@uab.es
%% and that of ACL 08 by Joakim Nivre and Noah Smith

\documentclass[11pt,a4paper]{article}
\usepackage[hyperref]{acl2021}
\usepackage{times}
\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\renewcommand{\UrlFont}{\ttfamily\small}

% This is not strictly necessary, and may be commented out,
% but it will improve the layout of the manuscript,
% and will typically save some space.
\usepackage{microtype}

%\aclfinalcopy % Uncomment this line for the final submission
%\def\aclpaperid{***} %  Enter the acl Paper ID here

%\setlength\titlebox{5cm}
% You can expand the titlebox if you need extra space
% to show all the authors. Please do not make the titlebox
% smaller than 5cm (the original size); we will check this
% in the camera-ready version and ask you to change it back.

\newcommand\BibTeX{B\textsc{ib}\TeX}

\title{Extra Large Sequence Transformer Model for Chinese Word Segment}

\author{Dezhou Shen \\
  Department of Computer Science\\
  Tsinghua University\\
  Beijing, CN 100084\\
  \texttt{sdz15@mails.tsinghua.edu.cn} \\}

\date{}

\begin{document}
\maketitle
\begin{abstract}
 Chinese word segment is widely used in document analysis.
 In this paper, combining the Transformer-XL layer, the Fully-Connect layer, and the Conditional Random Field layer,
 the proposed model improved 5\% comparing to the BERT+CRF model in the MSR2005 Chinese word segment test dataset.
\end{abstract}

\section{Introduction}

 As a fundamental study for the semantic document segment, the Chinese word segment has been studied for decades.

 By tagging the status of each token, intended entities with longer than one character could be drawn out of documents,
 and unintended tokens are assigned special token type which are one character each.

\section{Related Work}

  \citet{devlin2019bert} proposed Bidirectional Encoder Representations from Transformers, and achieved 92.8\% on the CoNLL-2003 test set by
fine-tuning BERT on the downstream Named Entity Recognition task.

  \citet{yang2019xlnet} proposed an autoregressive language model which overcomes the limitations of BERT in sequence length,
results showed that XLNet achieved promising results on question answering, natural language inference, sentiment analysis, and document ranking tasks.

  \citet{tian2020improving} showed that extra trained BERT language model as encoder concatenate to the CRF can achieve 98.28\% to 98.40\% on the MSR2005 Chinese word segment test dataset.

  \citet{cui2019hierarchically} proposed a hierarchically-refined label attention network in Named Entity Recognition task, the result showed that LSTM+CRF is less competitive than their LSTM+LAN model on the WSJ,
Universal Dependencies v2.2, OntoNotes 5.0, and CCGBank dataset.

  \citet{Lafferty2001Conditional} proposed the Conditional Random Fields probabilistic model to segment and label sequence data, and outperforms the hidden Markov models and maximum entropy Markov models by 0.14\%~0.82\% in accuracy on the Penn treebank POS dataset.

\section{Methodology}
\label{sec:hireachy}

\subsection{Data Augment}

For the Chinese 8-bit Unicode Transformation Format encodings, there are two different encoding for the same printable ASCII tokens, one is named as the half character encoding,
and the other is named as the full character encoding.
Their difference relies on that one token take one byte or three bytes. The MSR2005 Chinese word segment dataset used the full character encoding, but in most cases,
people tend to use the half character encoding to comply with ASCII code for compatibility reason.
In this paper, I use a conversion function to convert the MSR2005 training dataset tokens to half character encoding for the tokens which have the corresponding tokens in the ASCII table.
Thanks to the data augment method, training dataset sentences size is increased from 86,924 to 166,740.

\subsection{Tokenization, Encoding And Labeling}

For a document with multiple sentences and paragraphs, the first step is splitting the document into lines by carefully choosing the separator token.
For Chinese sentences, the line-breaks, commas, periods are the most common separator tokens.
Before encoding the tokens, sentences are padded with padding token [0] to the max sequence length, I choose 128 as the max sequence length for the MSR2005 dataset.
After tokenization, I use the XLNet encoder to represent each token as the token integers.
Each token has been labeled according to its type, for the one character entity, its status is labeled to [0].
For the longer than one character entity, the first character is labeled to [1], the last character is labeled to [3], and the rest characters are labeled to [2].

\subsection{Sequence Encoder}

After the encoding steps, the tokens are encoded to token integers which represents their vocabulary indices.
To encode by XLNet, the mask tokens and the segment tokens are prepared.
The non-padding tokens' mask tokens are set to [1], and the segment tokens are set to [0].
The padding tokens' make tokens are set to [0], and the segment tokens are set to [1] for telling the model the boundary of the sentences.
For encoding the sequence, all the layers are preserved for later usage.

\subsection{Sequence Hidden Representation}

For a naive solution, it is perfect to add a softmax layer or a CRF layer.
However, I designed a multiple layers to take advantage of the different layers for the transfer learning.
Firstly, take the first layer, and the last layer of the XLNet sequence encoding.
Then use two dropout layers with each dropout rate pf 5\%, which means the probability of an element to be zeroed.
Thirdly, I use a fully connected layer to map the hidden size of XLNet to the status types, which is 4 in the Chinese word segment task.
Lastly, take the logarithm, and a softmax conversion before concatenating to the CRF layer.

\subsection{Conditional Random Field}

Conditional Random Field is a traditional method to keep the output of the sequence following a reasonable pattern.
Each token sequence has a corresponding mask sequence to show its margin, the token [True] shows that the token is a non-padding token,
and the token [False] shows that the token is a padding token.

\subsection{Additional Loss function}

Besides, the Conditional Random Field loss for training, I added a type loss for training speed.
After the two dropout layer, an extra fully connected layer was concatenated to the last dropout layer to get the type loss.
Then use a multi-label one-versus-all loss based on max-entropy to get the sequence type loss.
The type sequence target was smoothed by 0 and 1 values, the type [0] for the token status of [0], and the type [1] for the other token status.

\begin{figure*}
\begin{center}
  \fbox{\rule{0pt}{2in} \includegraphics[width=0.9\linewidth]{SummaryModel.pdf}}
\end{center}
   \caption{Different architectures for multi-grained summarization.
   (a) Extractive Sentence Summarization,
   (b) Sequence To Sequence Summarization.}
\label{fig:short}
\end{figure*}

\section{Experiments}

\subsection{Common Setups}

\par The experiment was performed on a Google Cloud NVIDIA V100 with 16GB of the high speed of memory each, with 32GB of RAM,
which can provide 112 tera-flops of computation capability.

The learning rate is $4^{-5}$, and the batch size is 64, for the BERT and XLNet.
The learning rate is $2^{-3}$, and the batch size is 512 for the bidirectional LSTM.
The max sequence length is 128, and the training epoch is 10.
The RoBERTa in this paper is popular pre-trained RoBERTa language models trained on 4.5 billion of Chinese tokens by \citet{cui2020revisiting}.
The XLNet in this paper is another pre-trained XLNet language models trained on 4.5 billion of Chinese tokens by \citet{cui2020revisiting}.

\begin{table}
\centering
\begin{tabular}{cccc}
\hline
\textbf{Model} & \textbf{Neurons}& \textbf{Layers} & \textbf{macro-F1} \\
\hline
RNN & 256 & 2 & 92.62\% \\
RoBERTa & 768 & 12 & 92.62\% \\
XLNet & 768 & 12 & 97.88\% \\
\hline
\end{tabular}
\caption{Pre-trained language models macro-F1 scores for the Chinese word segement task.}
\end{table}

All the Table (1) models share almost the same network architecture except for the embedding of the tokens.

\section{Conclusion}

In this paper, I introduced a novel Chinese word segment architecture, which leveraging hierarchical layers of the document encoding layers.
By keeping the Conditional Random Field layer, I proposed a novel sequence hidden representation of the document sequence, which achieved 5\% performance gain in macro F1-score than
the bidirectional lstm and CRF architecture on the MSR2005 Chinese word segment test dataset.

\bibliographystyle{acl_natbib}
\bibliography{anthology,acl2021,acl_word}

%\appendix

\end{document}

### 2021-01-16 A-BasicCommom/ACL2021/acl_law_examination.tex
1.acl2021 CN word segment.

@@
 
-\subsection{Segment Extraction}
-The document of the court sentence usually states the arguing point of the two entities.
-In this paper, a dictionary based arguing reason extractor was designed.
-A total of 123 arguing reasons were classified by the legal experts out of 70 million
-civil documents collected from the Chinese Court Sentence website.
+\subsection{Legal Question Answering Dataset}
 
-Then I use several rule-based filters to extract meaningful segments.
-As Figure-1 shows, the document has been split into several paragraphs,
-the paragraph with important words are kept and other paragraphs are discarded.
+I use a dataset collected by Zhong \etal, which contains 7775 knowledge-based QA pairs and 13297 case-analysis QA pairs.
+Some questions have multiple options correct in the answer, while some have single option correct.
 
-\subsection{Extractive Sentence Summarization}
+\subsection{Context Representation}
 
-For the sentence importance scoring model, the experts wrote the summarization for each legal document.
-Base on the written summarization, each sentence importance can be easily computed by checking the overlap words.
-I use the pre-trained Chinese language model, which has multiple layers of transformers,
-for encoding sentences.
-As Figure-2 shows, the model layers are organized as follows:
-Take the last two layers of the RoBERTa encoding, then do the concatenation and take the Maximum element from the character
-sequence as representation for each sentence, then concatenating to a dropout layer, a softmax layer,
-and the output layer.
+There are three descriptive information, namely question, options, and paragraphs for each item in the dataset.
+The paragraph is optional for the knowledge based QA-pair and mandatory for the case analysis QA-pair.
+The paragraph and the question always come together in a single paragraph.
+There are always four options, and the correct options are not variant according to the question.
 
-The learning rate is $10^{-4}$, the max sequence length is 50, the dropout rate is 5\%, and the batch size is 1.
-The epoch number is 3.
-The experiment was carried on a Google Cloud TPU v3, with 32GB of RAM, and 8 chips with 16GB of the high speed of memory each,
-which can provide 420 tera-flops of computation capability.
-
-The classification dataset is unbalanced, thus I copy the positive samples multiple times to balance the dataset.
-In total, there are 782,895 samples for training and 42 samples for test in the Legal Sentence Importance dataset.
-The test accuracy is 92.06\%.
+I use the BERT model as the representation for the question and option encoding.
+In total, seven different BERT pre-trained language model were compared.
+Google BERT for Chinese, Roberta BERT for Chinese, Roberta BERT 3 layers for Chinese,
+Roberta BERT 3 layers for Chinese(1024 dim), Roberta BERT 24 layers for Chinese (1024 dim),
+Extra Roberta BERT 24 layers for Chinese (1024 dim), Extra More Steps Roberta BERT 24 layers for Chinese (1024 dim).
 

### 2021-01-16 A-BasicCommom/ACL2021/acl_word_segment.tex
1.acl2021 CN word segment.

@@
 After the encoding steps, the tokens are encoded to token integers which represents their vocabulary indices.
-To encode by XLNet, the mask tokens and the segment tokens are prepared.
+To encode by XLNet and BERT model, the mask tokens and the segment tokens are prepared.
 The non-padding tokens' mask tokens are set to [1], and the segment tokens are set to [0].
@@
 For encoding the sequence, all the layers are preserved for later usage.
+The vocabulary encoding used by LSTM word embedding doesn't need the mask tokens and segment tokens, the vocabulary was formed by characters extracted from the MSR2005 training dataset, its conversion from character set to half character encoding set,
+and one padding token [PAD], and one unknown token [UNK]. There are 5245 tokens in the vocabulary, and the embedding size is 256.
 
@@
 
+\subsection{Summary}
+
+As Figure (1) shows, the Chinese word segment architecture are formed by input layer, encoder layer, concatenating layer, representation layer, CRF layer, and output layer.
+In this paper, I mainly focus on discussing the improvement on the encoder layer
 \begin{figure*}
 \begin{center}
-  \fbox{\rule{0pt}{2in} \includegraphics[width=0.9\linewidth]{SummaryModel.pdf}}
+  \fbox{\rule{0pt}{2in} \includegraphics[width=0.9\linewidth]{cws-architecture.pdf}}
 \end{center}
-   \caption{Different architectures for multi-grained summarization.
-   (a) Extractive Sentence Summarization,
-   (b) Sequence To Sequence Summarization.}
+   \caption{The Network Architecture for the Chinese word segment task.}
 \label{fig:short}

### 2021-01-17 A-BasicCommom/ACL2021/acl_word_segment.tex
1. Finish the draft version of CWS.

@@
 
-%\aclfinalcopy % Uncomment this line for the final submission
+\aclfinalcopy % Uncomment this line for the final submission
 %\def\aclpaperid{***} %  Enter the acl Paper ID here
@@
 \begin{abstract}
- Chinese word segment is widely used in document analysis.
+ Chinese word segment is widely studied in document analysis.
  In this paper, combining the Transformer-XL layer, the Fully-Connect layer, and the Conditional Random Field layer,
- the proposed model improved 5\% comparing to the BERT+CRF model in the MSR2005 Chinese word segment test dataset.
+ the proposed model improved 3.23\% in macro-F1 score, comparing to the BERT+CRF model, on the MSR2005 Chinese word segment test dataset.
 \end{abstract}
@@
  By tagging the status of each token, intended entities with longer than one character could be drawn out of documents,
- and unintended tokens are assigned special token type which are one character each.
+ and unintended tokens are assigned with a special token type which are normally one character length.
 
@@
 
-  \citet{devlin2019bert} proposed Bidirectional Encoder Representations from Transformers, and achieved 92.8\% on the CoNLL-2003 test set by
+  \citet{devlin2019bert} proposed Bidirectional Encoder Representations from Transformers(BERT), and achieved 92.8\% on the CoNLL-2003 test set by
 fine-tuning BERT on the downstream Named Entity Recognition task.
@@
 
-  \citet{tian2020improving} showed that extra trained BERT language model as encoder concatenate to the CRF can achieve 98.28\% to 98.40\% on the MSR2005 Chinese word segment test dataset.
+  \citet{tian2020improving} showed that extra trained BERT language model as encoder concatenate to the Conditional Random Fields(CRF) can achieve 98.28\% to 98.40\% on the MSR2005 Chinese word segment test dataset.
 
@@
 
-  \citet{Lafferty2001Conditional} proposed the Conditional Random Fields probabilistic model to segment and label sequence data, and outperforms the hidden Markov models and maximum entropy Markov models by 0.14\%~0.82\% in accuracy on the Penn treebank POS dataset.
+  \citet{Lafferty2001Conditional} proposed the CRF probabilistic model to segment and label sequence data, and outperforms the hidden Markov models and maximum entropy Markov models by 0.14\%~0.82\% in accuracy on the Penn treebank POS dataset.
 
@@
 and the other is named as the full character encoding.
-Their difference relies on that one token take one byte or three bytes. The MSR2005 Chinese word segment dataset used the full character encoding, but in most cases,
+Their difference relies on that one token take one byte or three bytes.
+The MSR Chinese word segment dataset\citet{emerson2005second} used the full character encoding, but in most cases,
 people tend to use the half character encoding to comply with ASCII code for compatibility reason.
@@
 After the encoding steps, the tokens are encoded to token integers which represents their vocabulary indices.
+Transformer-XL\citet{dai2019transformer} also named as XLNet, a novel neural architecture that enables learning dependency beyond a fixed length without disrupting temporal coherence.
 To encode by XLNet and BERT model, the mask tokens and the segment tokens are prepared.
@@
 For encoding the sequence, all the layers are preserved for later usage.
-The vocabulary encoding used by LSTM word embedding doesn't need the mask tokens and segment tokens, the vocabulary was formed by characters extracted from the MSR2005 training dataset, its conversion from character set to half character encoding set,
-and one padding token [PAD], and one unknown token [UNK]. There are 5245 tokens in the vocabulary, and the embedding size is 256.
+The vocabulary encoding used by the LSTM word embedding doesn't need the mask tokens and segment tokens,
+the vocabulary was composites by characters extracted from the MSR2005 training dataset, its conversion from character set to half character encoding set,
+and one padding token [PAD], and one unknown token [UNK].
+There are 5245 tokens in the vocabulary, and the embedding size is 256.
 
@@
 
-For a naive solution, it is perfect to add a softmax layer or a CRF layer.
+For a naive solution, it is perfect to add a softmax layer, or a CRF layer.
 However, I designed a multiple layers to take advantage of the different layers for the transfer learning.
@@
 
+\subsection{Dataset}
+
+ The MSR Chinese word dataset has 2.37 million words in the training set with 88 thousand vocabulary size,
+ and has 107 thousand words in the test set with 13 thousand vocabulary size.
+ As \citet{emerson2005second} reported that, during the second international Chinese word segment competition,
+the best F1-score achieved was 97.2\% with permission of using the additional corpus on the MSR test dataset.
+
 \subsection{Common Setups}
 
-\par The experiment was performed on a Google Cloud NVIDIA V100 with 16GB of the high speed of memory each, with 32GB of RAM,
+The experiment was performed on a Google Cloud NVIDIA V100 with 16GB of the high speed of memory each, with 32GB of RAM,
 which can provide 112 tera-flops of computation capability.
@@
 The max sequence length is 128, and the training epoch is 10.
-The RoBERTa in this paper is popular pre-trained RoBERTa language models trained on 4.5 billion of Chinese tokens by \citet{cui2020revisiting}.
-The XLNet in this paper is another pre-trained XLNet language models trained on 4.5 billion of Chinese tokens by \citet{cui2020revisiting}.
+I use the popular pre-trained RoBERTa language models trained on 4.5 billion of Chinese tokens by \citet{cui2020revisiting}.
+And I use the pre-trained XLNet language models trained on 4.5 billion of Chinese tokens by \citet{cui2020revisiting}.
 
@@
 \hline
-RNN & 256 & 2 & 92.62\% \\
-RoBERTa & 768 & 12 & 92.62\% \\
+LSTM & 256 & 2 & 92.62\% \\
+RoBERTa & 768 & 12 & 94.65\% \\
 XLNet & 768 & 12 & 97.88\% \\
@@
 \end{tabular}
-\caption{Pre-trained language models macro-F1 scores for the Chinese word segement task.}
+\caption{Comparison of the pre-trained language models on the MSR2005 Chinese word segement task.}
 \end{table}
@@
 In this paper, I introduced a novel Chinese word segment architecture, which leveraging hierarchical layers of the document encoding layers.
-By keeping the Conditional Random Field layer, I proposed a novel sequence hidden representation of the document sequence, which achieved 5\% performance gain in macro F1-score than
-the bidirectional lstm and CRF architecture on the MSR2005 Chinese word segment test dataset.
+By keeping the Conditional Random Field layer, I proposed a novel sequence hidden representation of the document sequence, which achieved 3.23\% performance gain in macro F1-score than
+the BERT and CRF architecture on the MSR2005 Chinese word segment test dataset.
+Not surprisingly, the performance of the proposed XLNet-CRF model also exceed the best result of the Second International Chinese Word Segmentation Competition.
 

### 2021-01-17 A-BasicCommom/ACL2021/acl_word_segment.tex
1. minor modification.

@@
  Chinese word segment is widely studied in document analysis.
+ The accuracy of the current popular word segment model, LSTM+CRF, is still not satisfactory.
+ Models trained by the popular dataset often fails in the out-domain situation.
  In this paper, combining the Transformer-XL layer, the Fully-Connect layer, and the Conditional Random Field layer,
- the proposed model improved 3.23\% in macro-F1 score, comparing to the BERT+CRF model, on the MSR2005 Chinese word segment test dataset.
+ the proposed model improved 3.23\% in the macro-F1 score, comparing to the BERT+CRF model, on the MSR2005 Chinese word segment test dataset.
 \end{abstract}
@@
 
-  \citet{tian2020improving} showed that extra trained BERT language model as encoder concatenate to the Conditional Random Fields(CRF) can achieve 98.28\% to 98.40\% on the MSR2005 Chinese word segment test dataset.
+  \citet{cui2020revisiting} fine-tuned BERT and XLNet with extra 4.5 billion Chinese tokens, and improved the performance of many downstream tasks.
+
+  \citet{tian2020improving} showed that the extra pre-trained BERT language model as encoder concatenating to the Conditional Random Fields(CRF) can achieve 98.28\% to 98.40\% on the MSR2005 Chinese word segment test dataset.
 
@@
 Their difference relies on that one token take one byte or three bytes.
-The MSR Chinese word segment dataset\citet{emerson2005second} used the full character encoding, but in most cases,
+The MSR Chinese word segment dataset reported in \citet{emerson2005second} used the full character encoding, but in most cases,
 people tend to use the half character encoding to comply with ASCII code for compatibility reason.
 In this paper, I use a conversion function to convert the MSR2005 training dataset tokens to half character encoding for the tokens which have the corresponding tokens in the ASCII table.
-Thanks to the data augment method, training dataset sentences size is increased from 86,924 to 166,740.
+Thanks to the data augment method, training dataset sentences size is increased from 86,924 to 166,740,
+and moreover, models trained shall perform well in both the half character and full character corpus.
+Data augment solves the problem that when the dataset are full character encoding characters, however, most use cases are mixed character encodings by half and full.
 
@@
 For a document with multiple sentences and paragraphs, the first step is splitting the document into lines by carefully choosing the separator token.
-For Chinese sentences, the line-breaks, commas, periods are the most common separator tokens.
+For Chinese sentences, the line-breaks, commas, periods, question marks, and exclamation marks are the most common separator tokens.
 Before encoding the tokens, sentences are padded with padding token [0] to the max sequence length, I choose 128 as the max sequence length for the MSR2005 dataset.
@@
 After the encoding steps, the tokens are encoded to token integers which represents their vocabulary indices.
-Transformer-XL\citet{dai2019transformer} also named as XLNet, a novel neural architecture that enables learning dependency beyond a fixed length without disrupting temporal coherence.
+Transformer-XL proposed by \citet{dai2019transformer} also named as XLNet, a novel neural architecture that enables learning dependency beyond a fixed length without disrupting temporal coherence.
 To encode by XLNet and BERT model, the mask tokens and the segment tokens are prepared.
@@
 Firstly, take the first layer, and the last layer of the XLNet sequence encoding.
-Then use two dropout layers with each dropout rate pf 5\%, which means the probability of an element to be zeroed.
+Then use two dropout layers with each dropout rate of 5\%, which means the probability of an element to be zeroed.
 Thirdly, I use a fully connected layer to map the hidden size of XLNet to the status types, which is 4 in the Chinese word segment task.
@@
 Besides, the Conditional Random Field loss for training, I added a type loss for training speed.
-After the two dropout layer, an extra fully connected layer was concatenated to the last dropout layer to get the type loss.
+After the two dropout layers, an extra fully connected layer was concatenated to the last dropout layer to get the type loss.
 Then use a multi-label one-versus-all loss based on max-entropy to get the sequence type loss.
 The type sequence target was smoothed by 0 and 1 values, the type [0] for the token status of [0], and the type [1] for the other token status.
+
+\subsection{Decoder}
+
+For the decoding steps, if the status is [0], then the entity is the corresponding token.
+If the status is [1], it shows that the token belongs to a new entity, and if the status is [2], it tells that the token belongs to current working entity,
+and if the status is [3], it tells that the token belongs to current working entity and the entity reached an end token.
+When decoding, I use a CRF decoder, which benefits from the state transfer matrix and avoids error state sequence during the decoding steps.
+The decoder used the Viterbi algorithm propose by \citet{forney1973viterbi} which make the decoding steps faster.
 
@@
 The max sequence length is 128, and the training epoch is 10.
-I use the popular pre-trained RoBERTa language models trained on 4.5 billion of Chinese tokens by \citet{cui2020revisiting}.
-And I use the pre-trained XLNet language models trained on 4.5 billion of Chinese tokens by \citet{cui2020revisiting}.
+For the LSTM model, I use the word embedding layer with embedding size of 256, and the bidirectional LSTM layers with 384 neurons in each layer.
+I use the popular pre-trained RoBERTa language models trained on 4.5 billion of Chinese tokens by \citet{cui2020revisiting},
+and use the pre-trained XLNet language models trained on 4.5 billion of Chinese tokens by \citet{cui2020revisiting}.
 
@@
 
+\subsection{Reproducibility}
+
+The data augment, the LSTM, RoBERTa, XLNet, CRF codes and pre-trained Chinese word segment models are available at https://drive.google.com/drive/folders/1--GwAkEPtQsIm0PqD6a26TOvVrxJg3mR.
+And the supplementary codes are available at https://github.com/ShenDezhou/EXLNet.
+
 \section{Conclusion}

### 2021-01-19 A-BasicCommom/CVPR2021/cvpr_classification_rebuttal.tex
1.classification and covid rebuttal.

\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}

% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}

%%%%%%%%% PAPER ID  - PLEASE UPDATE
\def\cvprPaperID{310} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

\begin{document}

%%%%%%%%% TITLE - PLEASE UPDATE
\title{Enhance Image Classification Performance Via Unsupervised Pre-trained Transformers Language Models}  % **** Enter the paper title here

\maketitle
\thispagestyle{empty}

%%%%%%%%% BODY TEXT - ENTER YOUR RESPONSE BELOW
\section{Introduction}

Greetings to Reviewers,

I wrote this paper for seven reasons:

1) For many years, CVPR has been the pioneer conference that leading the AI forward, such as CNN, ImageNet and many other precise work made by the pioneers, until last two years the Transformer network has been brought to our sight;

2) Interestingly, it is the ACL conference that first proposed the BERT model which improved the NLP tasks quite a lot;

3) With my finding in this paper that the BERT model also can improve the performance of CV tasks, such as image classification, and benefit us.

4) I tested three datasets: two open datasets (CIFAR10 and CIFAR100), and one private COVID-19 dataset which has even impressing performance see paperID \#7435;

5) As Reviewer \#2 says: 99.76\% seems to good for the current state-of-the-art is around 94\%, I have to say, WELL, that is the contribution in my paper I want to share with you all;

6) If we check the code carefully, we can see from the code file:data.py, in line 217 to line 219, in the training phase, I use the metadata for the model, however, for the test phase, the metadata are totally replaced by [MASK] token, there is no way to do the trick;

7) And for the experiment log file:imagecls.ipynb, if we check the line 537 and line 962, we can conclude that by encoding the pixels with the BERT model, the accuracy jumps from 95.14\% after the epoch-1 to 99.76\% after the epoch-5.

Accepting this paper shall benefit the CV community, by absorbing the advanced BERT encoder, the computer vision scientist can achieve even greater work than ever, or else we shall let behind by the NLP community which is the last thing I want to see.

Cheers,

The Author.

{\small
\bibliographystyle{ieee}
%\bibliography{egbib}
}

\end{document}

### 2021-01-19 A-BasicCommom/CVPR2021/cvpr_covid_rebuttal.tex
1.classification and covid rebuttal.

\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}

% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}

%%%%%%%%% PAPER ID  - PLEASE UPDATE
\def\cvprPaperID{7435} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

\begin{document}

%%%%%%%%% TITLE - PLEASE UPDATE
\title{Unify Language and Vision: An Efficient COVID-19 Tomography Image Classification Approach}  % **** Enter the paper title here

\maketitle
\thispagestyle{empty}

%%%%%%%%% BODY TEXT - ENTER YOUR RESPONSE BELOW
\section{Introduction}

Greetings to Reviewers,

I wrote this paper for eight reasons:

1) During the past year, unfortunately sever disease come to human beings, it would be great if the CV community could help fight against the COVID19.

2) However, most of the current state-of-the-art model like CNN lack of accuracy for real world needs.

3) For many years, CVPR has been the pioneer conference that leading the AI forward, such as CNN, ImageNet and many other precise work made by the pioneers, until last two years the Transformer network has been brought to our sight;

4) With my finding in this paper that the BERT model also can improve the performance of CV tasks, such as image classification, and benefit us.

5) I tested three datasets: two open datasets (CIFAR10 and CIFAR100), and one private COVID-19 dataset which has even impressing performance 99\%;

5) As Reviewer \#1 says: 99.76\% must be impossible in CIFAR-100, however, I have to say, WELL, that is the contribution in my paper I want to share with you all;

6) If we check the code carefully, we can see from the code file:data.py, in line 217 to line 219, in the training phase, I use the metadata for the model, however, for the test phase, the metadata are totally replaced by [MASK] token, there is no way to do the trick;

7) For the experiment log file:covfl.ipynb, if we check the line 5839, line 5238, and line 4639, we can conclude that by encoding the pixels with the 3-layer BERT, 3-layer BERT-Large, 24-layer BERT model, the accuracy account to 99\% after several epochs for the CIFAR-100 test dataset;

8) For the COVID-19 images dataset, we can check line 656, line 805, and line 508(file:covfl.ipynb), these three experiments are similar to those on the CIFAR-10 and CIFAR-100 datasets.

Accepting this paper shall benefit the human being for an accurate and fast way of checking COVID-19 lung Tomography images, the COVID-19 shall be defeated with the help from the CV community,
by absorbing the advanced BERT encoder, the computer vision scientists can achieve even greater work than ever.

Cheers,

The Author.

{\small
\bibliographystyle{ieee}
%\bibliography{egbib}
}

\end{document}

### 2021-01-22 A-BasicCommom/ACL2021/acl_word_segment.tex
1.two ACL2021 papers.

@@
 
-\aclfinalcopy % Uncomment this line for the final submission
-%\def\aclpaperid{***} %  Enter the acl Paper ID here
+%\aclfinalcopy % Uncomment this line for the final submission
+\def\aclpaperid{509} %  Enter the acl Paper ID here
 
@@
 For a naive solution, it is perfect to add a softmax layer, or a CRF layer.
-However, I designed a multiple layers to take advantage of the different layers for the transfer learning.
+However, I designed multiple layers to take advantage of the different layers for the transfer learning.
 Firstly, take the first layer, and the last layer of the XLNet sequence encoding.
@@
 
-\subsection{Reproducibility}
-
-The data augment, the LSTM, RoBERTa, XLNet, CRF codes and pre-trained Chinese word segment models are available at https://drive.google.com/drive/folders/1--GwAkEPtQsIm0PqD6a26TOvVrxJg3mR.
-And the supplementary codes are available at https://github.com/ShenDezhou/EXLNet.
+%\subsection{Reproducibility}
+%
+%The data augment, the LSTM, RoBERTa, XLNet, CRF codes and pre-trained Chinese word segment models are available at https://drive.google.com/drive/folders/1--GwAkEPtQsIm0PqD6a26TOvVrxJg3mR.
+%And the supplementary codes are available at https://github.com/ShenDezhou/EXLNet.
 

### 2021-01-24 A-BasicCommom/ACL2021/acl_comprehension.tex
ACL: reading comprehension model.

--- 2021-01-17 A-BasicCommom/ACL2021/acl_word_segment.tex
@@
 
-\aclfinalcopy % Uncomment this line for the final submission
-%\def\aclpaperid{***} %  Enter the acl Paper ID here
+%\aclfinalcopy % Uncomment this line for the final submission
+%\def\aclpaperid{509} %  Enter the acl Paper ID here
 
@@
 
-\title{Extra Large Sequence Transformer Model for Chinese Word Segment}
+\title{Transformer based Reading Comprehension model for China Court Cases}
 
@@
 \begin{abstract}
- Chinese word segment is widely studied in document analysis.
- In this paper, combining the Transformer-XL layer, the Fully-Connect layer, and the Conditional Random Field layer,
- the proposed model improved 3.23\% in macro-F1 score, comparing to the BERT+CRF model, on the MSR2005 Chinese word segment test dataset.
+ Teaching machines to read court cases remains an elusive challenge.
+ In this paper, I proposed a Transformer based model that learn to read real documents and answer complex questions.
+ Test on the CJRC2019 dataset, proposed model achieved 2\% improvement on the macro-F1 score compared to the BERT model.
+
 \end{abstract}
@@
 
- As a fundamental study for the semantic document segment, the Chinese word segment has been studied for decades.
-
- By tagging the status of each token, intended entities with longer than one character could be drawn out of documents,
- and unintended tokens are assigned with a special token type which are normally one character length.
+  Progress on the machines reading and understanding documents has been made recently.
+  Supervised natural language reading comprehension datasets have been brought recently, \eg \citet{duan2019cjrc}, \citet{cui2019span}.
+  \citet{Hermann2015Teaching} observed that summary and paraphrase sentences from the documents can be converted to the context-query-answer pattern.
+  In this paper, I emphasize solving the problem that given a context, and a corresponding question, the answer can be generated by the entity detection out of the context,
+  or answering the question by affirmative, disagreement, and not-responding.
 
@@
 
-  \citet{tian2020improving} showed that extra trained BERT language model as encoder concatenate to the Conditional Random Fields(CRF) can achieve 98.28\% to 98.40\% on the MSR2005 Chinese word segment test dataset.
+  \citet{cui2020revisiting} fine-tuned BERT and XLNet with extra 4.5 billion Chinese tokens, and improved the performance of many downstream tasks.
 
-  \citet{cui2019hierarchically} proposed a hierarchically-refined label attention network in Named Entity Recognition task, the result showed that LSTM+CRF is less competitive than their LSTM+LAN model on the WSJ,
-Universal Dependencies v2.2, OntoNotes 5.0, and CCGBank dataset.
+  \citet{Hermann2015Teaching} proposed LSTM models in building full natural language understanding systems, and achieved accuracy of 63.8\% on the CNN dataset and accuracy of 69.0\% on the Daily Mail dataset.
 
-  \citet{Lafferty2001Conditional} proposed the CRF probabilistic model to segment and label sequence data, and outperforms the hidden Markov models and maximum entropy Markov models by 0.14\%~0.82\% in accuracy on the Penn treebank POS dataset.
+  \citet{cui2019span} proposed a BERT machine reading comprehension model and achieved the F1-score of 86.0\% on the CMRC2018 test dataset,
+and showed that the multilingual pretrained model outperforms the Chinese pretrained model by around 0.8\% in the F1-score on the CMRC2018 test dataset.
+
+  \citet{duan2019cjrc} proposed a BERT based Span-extraction reading comprehension model, and a China court case reading comprehension dataset CJRC2019.
 
@@
 
-\subsection{Data Augment}
+\subsection{The China Judical Reading Comprehension Dataset}
 
-For the Chinese 8-bit Unicode Transformation Format encodings, there are two different encoding for the same printable ASCII tokens, one is named as the half character encoding,
-and the other is named as the full character encoding.
-Their difference relies on that one token take one byte or three bytes.
-The MSR Chinese word segment dataset\citet{emerson2005second} used the full character encoding, but in most cases,
-people tend to use the half character encoding to comply with ASCII code for compatibility reason.
-In this paper, I use a conversion function to convert the MSR2005 training dataset tokens to half character encoding for the tokens which have the corresponding tokens in the ASCII table.
-Thanks to the data augment method, training dataset sentences size is increased from 86,924 to 166,740.
-
-\subsection{Tokenization, Encoding And Labeling}
+    There are 39333 training records, 6000 development records, and 6000 test records in the CJRC2019 dataset,
+and there are 5053 training records and 1565 test records in the CJRC2020 dataset.
 
     For a document with multiple sentences and paragraphs, the first step is splitting the document into lines by carefully choosing the separator token.
-For Chinese sentences, the line-breaks, commas, periods are the most common separator tokens.
-Before encoding the tokens, sentences are padded with padding token [0] to the max sequence length, I choose 128 as the max sequence length for the MSR2005 dataset.
-After tokenization, I use the XLNet encoder to represent each token as the token integers.
-Each token has been labeled according to its type, for the one character entity, its status is labeled to [0].
-For the longer than one character entity, the first character is labeled to [1], the last character is labeled to [3], and the rest characters are labeled to [2].
+    For Chinese sentences, the line-breaks, commas, periods, and semicolons are the most common separator tokens.
 
-\subsection{Sequence Encoder}
+    Each record in the dataset has four components: the context, the question, the answer, and the supporting facts segment indices.
+    The dataset context-query-answer format has converted to less nested format for clarity, and the context has limited by a maximum size of 512 according to the answer span index.
+    And the context was split by separator tokens, and the answer related sentences were tagged in the record,
+    and this paper also focus on the problem that finding out the supporting sentences for the answer to the question in the context.
 
-After the encoding steps, the tokens are encoded to token integers which represents their vocabulary indices.
-Transformer-XL\citet{dai2019transformer} also named as XLNet, a novel neural architecture that enables learning dependency beyond a fixed length without disrupting temporal coherence.
-To encode by XLNet and BERT model, the mask tokens and the segment tokens are prepared.
+\subsection{Tokenization And Encoding}
+
+For each record, I concatenate the context, and the question then use the BERT tokenizer and converted to BERT token identification sequeces.
+Then, the answer's token start and end positions were computed, and the answer type indicating one of the four types: span, affirmative, disagreement, and not-responding.
+
+After the tokenization steps, the tokens are encoded to token integers which represents their vocabulary indices.
+To encode by the BERT model, the mask tokens and the segment tokens are prepared.
 The non-padding tokens' mask tokens are set to [1], and the segment tokens are set to [0].
@@
 For encoding the sequence, all the layers are preserved for later usage.
-The vocabulary encoding used by the LSTM word embedding doesn't need the mask tokens and segment tokens,
-the vocabulary was composites by characters extracted from the MSR2005 training dataset, its conversion from character set to half character encoding set,
-and one padding token [PAD], and one unknown token [UNK].
-There are 5245 tokens in the vocabulary, and the embedding size is 256.
 
-\subsection{Sequence Hidden Representation}
+The supporting states and the last layer of the BERT encoder were multiplied, and the max value of the sequence was kept,
+then connected to a fully connected layer for the supporting sentences.
 
-For a naive solution, it is perfect to add a softmax layer, or a CRF layer.
-However, I designed a multiple layers to take advantage of the different layers for the transfer learning.
-Firstly, take the first layer, and the last layer of the XLNet sequence encoding.
-Then use two dropout layers with each dropout rate pf 5\%, which means the probability of an element to be zeroed.
-Thirdly, I use a fully connected layer to map the hidden size of XLNet to the status types, which is 4 in the Chinese word segment task.
-Lastly, take the logarithm, and a softmax conversion before concatenating to the CRF layer.
+Then from the output of the start and the end position tensors, the maximum possible start and end position were calculated
+using the positional probability addition of the all possible start-end pairs.
 
-\subsection{Conditional Random Field}
+\subsection{Sequence Hidden Representation: The Capsule Net}
 
-Conditional Random Field is a traditional method to keep the output of the sequence following a reasonable pattern.
-Each token sequence has a corresponding mask sequence to show its margin, the token [True] shows that the token is a non-padding token,
-and the token [False] shows that the token is a padding token.
+After the encoding layers, the hidden layers of the BERT layers are kept, and the last two layers are concatenated and connected
+two Fully Connected layers for the starting index and the ending index for the answer span indices in the context.
 
-\subsection{Additional Loss function}
+Then last hidden layer of the BERT encoder was retrieved and then connected to the Capsule Net.
+The Capsule Net has three dimensions, representing different grains for the features, the parameters for the channels are 2, 4, and 8.
+Then for each channel, the convolutional layer with input channel size of 512, output channel of 32, convolutional kernel is the feature kernel,
+that's 2, 4, 8, and the stride size of 2.
+After the convolutional layers, the three output layers are concatenated,
+then connects to the primary capsule layer with capsule number of 128, input channel size of 32, output channel size of 32, kernel size and stride size of 1.
+Then a flatten-capsule layer, a compression layer, and a fully-connected capsule layer were connected.
+Finally, a fully connected layer was used for the result type indicating the answer type is a span or affirmative, disagreement, and not-responding.
 
-Besides, the Conditional Random Field loss for training, I added a type loss for training speed.
-After the two dropout layer, an extra fully connected layer was concatenated to the last dropout layer to get the type loss.
-Then use a multi-label one-versus-all loss based on max-entropy to get the sequence type loss.
-The type sequence target was smoothed by 0 and 1 values, the type [0] for the token status of [0], and the type [1] for the other token status.
+\subsection{Loss Function And Training Hyper Parameters}
 
-\subsection{Summary}
+Three losses were added with weighted and then use the stochastic gradient descent to train the network parameters.
+The start position loss, the end position loss, the type loss, and the supporting sentence loss were added with weighted.
+The start and end loss use the Cross Entropy Loss function, the type uses binary cross entropy with logits,
+and the support loss used the binary cross entropy with logits between the output and the gold value, then get the mean of each record.
+The support loss has a weight of 5 for its importance in finding the destination answer span, and all other loss has the weight of 1.
+And the threshold for the supporting sentence is 0.5.
+The learning rate is $5e{-4]}$, the dropout rate is 5\%, the document max sequence length for the document(the question and the context) is 512, and the max sequence length for the question is 45, the epoch size is 10.
+The batch size is 16,8, or 4 for the RBT3, RoBERTa-wwm-ext, and RoBERTa-Large model, for the GPU memory limit.
 
-As Figure (1) shows, the Chinese word segment architecture are formed by input layer, encoder layer, concatenating layer, representation layer, CRF layer, and output layer.
-In this paper, I mainly focus on discussing the improvement on the encoder layer
+The experiment was performed on a Google Cloud NVIDIA V100 with 16GB of the high speed of memory each, with 32GB of RAM,
+which can provide 112 tera-flops of computation capability.
+
 \begin{figure*}
@@
 
-The experiment was performed on a Google Cloud NVIDIA V100 with 16GB of the high speed of memory each, with 32GB of RAM,
-which can provide 112 tera-flops of computation capability.
-
-The learning rate is $4^{-5}$, and the batch size is 64, for the BERT and XLNet.
-The learning rate is $2^{-3}$, and the batch size is 512 for the bidirectional LSTM.
-The max sequence length is 128, and the training epoch is 10.
-I use the popular pre-trained RoBERTa language models trained on 4.5 billion of Chinese tokens by \citet{cui2020revisiting}.
-And I use the pre-trained XLNet language models trained on 4.5 billion of Chinese tokens by \citet{cui2020revisiting}.
-
 \begin{table}
@@
 \hline
-\textbf{Model} & \textbf{Neurons}& \textbf{Layers} & \textbf{macro-F1} \\
+\textbf{Model} & \textbf{Neurons}& \textbf{Layers} & \textbf{F1} \\
 \hline
-LSTM & 256 & 2 & 92.62\% \\
+RBT3 & 768 & 3 & 92.62\% \\
 RoBERTa & 768 & 12 & 94.65\% \\
-XLNet & 768 & 12 & 97.88\% \\
+RoBERTa-Large & 1024 & 24 & 97.88\% \\
 \hline
@@
 All the Table (1) models share almost the same network architecture except for the embedding of the tokens.
+
+%\subsection{Reproducibility}
+%
+%The data augment, the LSTM, RoBERTa, XLNet, CRF codes and pre-trained Chinese word segment models are available at https://drive.google.com/drive/folders/1--GwAkEPtQsIm0PqD6a26TOvVrxJg3mR.
+%And the supplementary codes are available at https://github.com/ShenDezhou/EXLNet.
 

### 2021-01-25 A-BasicCommom/ACL2021/acl_comprehension.tex
1.完成阅读理解ACL2021文章

@@
 %\aclfinalcopy % Uncomment this line for the final submission
-%\def\aclpaperid{509} %  Enter the acl Paper ID here
+\def\aclpaperid{1367} %  Enter the acl Paper ID here
 
@@
  Teaching machines to read court cases remains an elusive challenge.
- In this paper, I proposed a Transformer based model that learn to read real documents and answer complex questions.
- Test on the CJRC2019 dataset, proposed model achieved 2\% improvement on the macro-F1 score compared to the BERT model.
+ In this paper, I proposed an XLNet based model, and use the Capsule Net as hidden representation layers,
+ and use multi-task learning for the question type, start-end indices, and supporting sentence indices,
+ thanks to the deep neural architecture, the proposed model learns to read real documents and answer complex questions.
+ Test on the CJRC2019 validation dataset, proposed model achieved 1.57\% improvement on the span F1-score and 1.35\% on the supporting sentence F1-score comparing to the BERT model.
 
@@
   Progress on the machines reading and understanding documents has been made recently.
-  Supervised natural language reading comprehension datasets have been brought recently, \eg \citet{duan2019cjrc}, \citet{cui2019span}.
+  Supervised natural language reading comprehension datasets have been brought recently, e.g. CJRC2019 by \citet{duan2019cjrc}, and CMRC2018 by \citet{cui2019span}.
   \citet{Hermann2015Teaching} observed that summary and paraphrase sentences from the documents can be converted to the context-query-answer pattern.
@@
 
+The network model architecture is shown in Figure (1).
+
+\begin{figure*}
+\begin{center}
+  \fbox{\rule{0pt}{2in} \includegraphics[width=0.9\linewidth]{architecture-cjrc.pdf}}
+\end{center}
+   \caption{The Machine Reading Comprehension Network Architecture for the China Judicial Reading Comprehension task.}
+\label{fig:short}
+\end{figure*}
+
 \subsection{The China Judical Reading Comprehension Dataset}
@@
 and there are 5053 training records and 1565 test records in the CJRC2020 dataset.
+    The CJRC2020 followed the same format as this paper proposed, however, the annotation records has limit size, thus, I focus on the revised CJRC2019 dataset.
 
@@
 
-Then from the output of the start and the end position tensors, the maximum possible start and end position were calculated
+Then from the output of the start, and the end position tensors, the maximum possible start and end position were calculated
 using the positional probability addition of the all possible start-end pairs.
@@
 
-After the encoding layers, the hidden layers of the BERT layers are kept, and the last two layers are concatenated and connected
-two Fully Connected layers for the starting index and the ending index for the answer span indices in the context.
+After the encoding layers, the hidden layers of the BERT layers are kept, and the last two layers are concatenated and connected to
+two Fully Connected layers for the starting index, and the ending index for the answer span indices in the context.
+
+Recall that \citet{Sabour2017Dynamic} proposed the Capsules which are convolutions with the block non-linearity and routing, with fewer parameters than convolutional layers,
+try to build better model hierarchical relationships inside of internal knowledge representation.
+
+In general, the Capsule Net architecture in the model contains six components: three convolutional layers, the concatenating layer, the primary capsule layer, the flatten capsule layer,
+the compression layer, and the fully connecting capsule layer.
 
@@
 
-Three losses were added with weighted and then use the stochastic gradient descent to train the network parameters.
+The experiment was performed on a Google Cloud NVIDIA V100 with 16GB of the high speed of memory each, with 32GB of RAM,
+which can provide 112 tera-flops of computation capability.
+
+Three losses were added with weight and then use the stochastic gradient descent to train the network parameters.
 The start position loss, the end position loss, the type loss, and the supporting sentence loss were added with weighted.
@@
 And the threshold for the supporting sentence is 0.5.
-The learning rate is $5e{-4]}$, the dropout rate is 5\%, the document max sequence length for the document(the question and the context) is 512, and the max sequence length for the question is 45, the epoch size is 10.
-The batch size is 16,8, or 4 for the RBT3, RoBERTa-wwm-ext, and RoBERTa-Large model, for the GPU memory limit.
+The learning rate is $5e{-5}$ for the RBT3 and XLNet model, learning rate is $5e{-4}$ for the RoBERTa model, the dropout rate is 5\%, the document max sequence length for the document(the question and the context) is 512, and the max sequence length for the question is 45, the epoch size is 10.
+The batch size is 16 for the RBT3, RoBERTa, XLNet model.
 
-The experiment was performed on a Google Cloud NVIDIA V100 with 16GB of the high speed of memory each, with 32GB of RAM,
-which can provide 112 tera-flops of computation capability.
-
-\begin{figure*}
-\begin{center}
-  \fbox{\rule{0pt}{2in} \includegraphics[width=0.9\linewidth]{cws-architecture.pdf}}
-\end{center}
-   \caption{The Network Architecture for the Chinese word segment task.}
-\label{fig:short}
-\end{figure*}
+For the RoBERTa and XLNet model, I use the gradient accumulation steps for the training, the loss are accumulated between batches,
+and every two batches, the backward result was calculated.
+In this way, the large pretrained models, such as RoBERTa and XLNet, were able to be trained on the Nvidia V100 16GB of memory.
 
@@
 
- The MSR Chinese word dataset has 2.37 million words in the training set with 88 thousand vocabulary size,
- and has 107 thousand words in the test set with 13 thousand vocabulary size.
- As \citet{emerson2005second} reported that, during the second international Chinese word segment competition,
-the best F1-score achieved was 97.2\% with permission of using the additional corpus on the MSR test dataset.
+ The CJRC2019 dataset proposed by \citet{duan2019cjrc} lacks the supporting sentence annotations.
+For the multiple questions in one paragraph, I use the answer starting position as anchors to retrieve
+the attentional subparagraph, and use the 512 characters subparagraph containing the answer as the revised context.
+Also, I use the answer occurrence in the sentence as the flag to annotate the supporting sentences.
 
-\subsection{Common Setups}
+\subsection{Results}
+
+As Table (1) shows, on the CJRC2019 development dataset, the RBT3 model achieved 39.65\% of the F1 score on the span and 36.84\% of the F1 score on the supporting sentence.
+And the RoBERTa model improved performance significantly for the 12 layers of transformers, comparing to RBT3's 3 layers,
+achieved 44.37\% of the F1 score on the span and 48.00\% of the F1 score on the supporting sentence.
+The XLNet model achieved the best performance with 45.94\% of th F1 score on the span, and 49.35\% F1 score on the supporting sentence.
 
@@
 \hline
-\textbf{Model} & \textbf{Neurons}& \textbf{Layers} & \textbf{F1} \\
+\textbf{Model} & \textbf{Layers}& \textbf{span-F1} & \textbf{sup-F1} \\
 \hline
-RBT3 & 768 & 3 & 92.62\% \\
-RoBERTa & 768 & 12 & 94.65\% \\
-RoBERTa-Large & 1024 & 24 & 97.88\% \\
+RBT3 & 3 & 39.65\% & 36.86\% \\
+RoBERTa & 12 & 44.37\% & 48.00\% \\
+XLNet & 12 & 45.94\% & 49.35\% \\
 \hline
 \end{tabular}
-\caption{Comparison of the pre-trained language models on the MSR2005 Chinese word segement task.}
+\caption{Comparison of the pre-trained language models on the CJRC2019 Machine Reading Comprehension validation task.}
 \end{table}
-
-All the Table (1) models share almost the same network architecture except for the embedding of the tokens.
 
@@
 
-In this paper, I introduced a novel Chinese word segment architecture, which leveraging hierarchical layers of the document encoding layers.
-By keeping the Conditional Random Field layer, I proposed a novel sequence hidden representation of the document sequence, which achieved 3.23\% performance gain in macro F1-score than
-the BERT and CRF architecture on the MSR2005 Chinese word segment test dataset.
-Not surprisingly, the performance of the proposed XLNet-CRF model also exceed the best result of the Second International Chinese Word Segmentation Competition.
+In this paper, I introduced a novel Chinese Reading Comprehension model for Court Cases, which leveraging hierarchical layers of the document encoding layers.
+By making use of the Capsule Net layers, the multi task model predicts the starting and ending span index, and the supporting sentence indices in the context.
+Proposed model achieved 1.57\% improvement on the span F1-score and 1.35\% on the supporting sentence F1-score comparing to the BERT model in the CJRC2019 validation dataset.
 
 \bibliographystyle{acl_natbib}
-\bibliography{anthology,acl2021,acl_word}
+\bibliography{anthology,acl2021,acl_comprehension}
 

### 2021-01-26 A-BasicCommom/ACL2021/acl_comprehension.tex
1. modify the results of the experiments.

@@
  thanks to the deep neural architecture, the proposed model learns to read real documents and answer complex questions.
- Test on the CJRC2019 validation dataset, proposed model achieved 1.57\% improvement on the span F1-score and 1.35\% on the supporting sentence F1-score comparing to the BERT model.
+ Test on the CJRC2019 validation dataset, proposed model achieved 2.51\% improvement on the span F1-score and 2.63\% on the supporting sentence F1-score comparing to the BERT model.
 
@@
 RBT3 & 3 & 39.65\% & 36.86\% \\
-RoBERTa & 12 & 44.37\% & 48.00\% \\
-XLNet & 12 & 45.94\% & 49.35\% \\
+RoBERTa & 12 & 44.58\% & 50.04\% \\
+XLNet & 12 & 47.09\% & 52.67\% \\
 \hline
@@
 By making use of the Capsule Net layers, the multi task model predicts the starting and ending span index, and the supporting sentence indices in the context.
-Proposed model achieved 1.57\% improvement on the span F1-score and 1.35\% on the supporting sentence F1-score comparing to the BERT model in the CJRC2019 validation dataset.
+Proposed model achieved 2.51\% improvement on the span F1-score and 2.63\% on the supporting sentence F1-score comparing to the BERT model in the CJRC2019 validation dataset.
 

### 2021-03-11 A-BasicCommom/ICCV2021/iccv_apsp.tex
1. ICCV2021 I am coming~

--- 2020-11-16 A-BasicCommom/CVPR2021/cvpr_apsp.tex
@@
-% This version of CVPR template is provided by Ming-Ming Cheng.
-% Please leave an issue if you found a bug:
-% https://github.com/MCG-NKU/CVPR_Template.
+\documentclass[10pt,twocolumn,letterpaper]{article}
 
-\documentclass[review]{cvpr}
-%\documentclass[final]{cvpr}
-
+\usepackage{iccv}
 \usepackage{times}
@@
 \usepackage[linesnumbered,lined,boxed,commentsnumbered]{algorithm2e}
+
 % Include other packages here, before hyperref.
@@
 % run, let it finish, and you should be clear).
-\usepackage[pagebackref=true,breaklinks=true,colorlinks,bookmarks=false]{hyperref}
+\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
 
-\def\cvprPaperID{297} % \times \times \times  Enter the CVPR Paper ID here
-\def\confYear{CVPR 2021}
-%\setcounter{page}{4321} % For final version only
+% \iccvfinalcopy % *** Uncomment this line for the final submission
+
+\def\iccvPaperID{11047} % *** Enter the ICCV Paper ID here
+\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}
+
+% Pages are numbered in submission mode, and unnumbered in camera-ready
+\ificcvfinal\pagestyle{empty}\fi
 
@@
 \maketitle
+% Remove page # from the first page of camera-ready.
+\ificcvfinal\thispagestyle{empty}\fi
 
@@
 \begin{abstract}
+
   For the calculation of the all-pairs nodes shortest path in networks,
@@
   on the Chinese Movie Celebrity Network $2011\sim2015$ dataset.
+
 \end{abstract}

### 2021-03-11 A-BasicCommom/ICCV2021/iccv_classification.tex
1. ICCV2021 I am coming~

--- 2020-11-16 A-BasicCommom/CVPR2021/cvpr_classification.tex
@@
 \usepackage{amssymb}
-\usepackage[linesnumbered,lined,boxed,commentsnumbered]{algorithm2e}
+
 % Include other packages here, before hyperref.
@@
 % run, let it finish, and you should be clear).
-\usepackage[pagebackref=true,breaklinks=true,colorlinks,bookmarks=false]{hyperref}
+\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
 
-\def\cvprPaperID{310} % *** Enter the CVPR Paper ID here
-\def\confYear{CVPR 2021}
-%\setcounter{page}{4321} % For final version only
+% \iccvfinalcopy % *** Uncomment this line for the final submission
+
+\def\iccvPaperID{11033} % *** Enter the ICCV Paper ID here
+\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}
+
+% Pages are numbered in submission mode, and unnumbered in camera-ready
+\ificcvfinal\pagestyle{empty}\fi
 
@@
   In this paper, by encoding image pixels using pre-trained transformers, then connect to a fully connected layer,
-  the classification model outperforms the Wide ResNet model and the linear-probe iGPT-L model,
+  the classification model outperforms the ResNet model,
   and achieved accuracy of $99.60\%\sim99.74\%$ on the CIFAR-10 image set and accuracy of $99.10\%\sim99.76\%$ on the CIFAR-100 image set.
@@
 
-  Unsupervised pre-training is important to modern research of deep learning.
-  Lee \etal~\cite{lee2009convolutional} used the pre-training approaches
-  in Computer Vision tasks in 2009, and later from 2010 to 2016,
-  Nair and Hinton~\cite{nair2010rectified} proved that the pre-training process is supplementary in the Computer Vision tasks,
-  thus, can be omitted in some cases.
-  However, it started to flourish the natural language processing domain since Mikolov \etal~\cite{mikolov2013distributed} had proposed Word2Vec.
-  Not long before Devin \etal~\cite{devlin2019bert}'s BERT language model dominates in most frequently used tasks in natural language processing,
-  which is close resemble of Vicent \etal~\cite{vincent2008extracting}'s Denoising Autoencoder model, which was initially designed for images.
-  The pre-training process becomes one of the most important procedures in deep learning.
+  Convolutional neural networks have achieved dominant performance in vision tasks for the rich representation for images.
+  The LeNet architecture has been proved efficient than the Feed forward networks, and the Residual-style Networks have become popular recent years.
+  VGGNet, ResNet, GoogLeNet showed that the depth, width are important factors for networks.
+  Vicent \etal~\cite{vincent2008extracting}'s Denoising Autoencoder model, which was initially designed for images.
+
+  In the natural language processing domain, unsupervised pre-training becomes popular for the gigantic data collected by the industrial production.
+  It started to flourish the natural language processing domain since Mikolov \etal~\cite{mikolov2013distributed} had proposed Word2Vec.
+  Vaswani \etal~\cite{vaswani2017attention} used the Attention layers in the language translation task, and showed that the Attention layer overcome the drawback of the Recurrent Neural Networks
+in parallel training.
+Devin \etal~\cite{devlin2019bert} employed the Transformer model, which take part of the Vaswani's Attention model and used Gigantic corpus in the pre-training phase, dominates in almost all natural language processing tasks in recent years.
+
+  Lee \etal~\cite{lee2009convolutional} used the pre-training approaches in Computer Vision tasks in 2009, and later from 2010 to 2016,
+  Nair and Hinton~\cite{nair2010rectified} proved that the pre-training process is supplementary in the Computer Vision tasks.
+
+  Some works use the Transformer networks in the image pixel pre-training, and use the model to generate image pixels.
 
@@
 and tested on the CUB-200-2011 image dataset and achieved $85.55\%$ by combining GoogLeNet~\cite{szegedy2015going} and CNN-RNN~\cite{reed2016learning}, the result outperformed many competitors.
-
-%-------------------------------------------------------------------------
-
-\section{Image Classification via Pre-trained Transformers Language Models}
-
   Three of the most popular approaches for image classification tasks are per-pixel, subpixel, and heterogeneous.
@@
 %-------------------------------------------------------------------------
+
+\section{Image Classification via Pre-trained Transformers Language Models}
+
+%-------------------------------------------------------------------------
 \subsection{Approach}
@@
 My approach consists of a pre-training stage followed by a fine-tuning stage.
-In pre-training, I use BERT objectives and the sequence Transformer architecture to predict language tokens.
+In pre-training, I use BERT objectives, and the sequence Transformer architecture to predict language tokens.
 
@@
 
+\subsection{The Chinese Pre-trained Transformer Language model}
+
+\par The Transformer model is intended to be used as replacement of CNN layers for extracting information from Images.
+Here, I describe how to train the Transformer language model in detail.
+
+\subsection{The Chinese Word Piece Tokenization Model}
+
+\par The BERT model use a tokenization method, named WordPiece, which breaks down a English word by high frequent suffix and prefix.
+The vocabulary size can be greatly reduced by the sharing suffix and prefix between words.
+Before training the custom WorkPiece model, the final vocabulary size and minimal word-piece frequency need to be assigned.
+I use 21128 as the model vocabulary size and add several model specific tokens like $[PAD]$, $[UNK]$, $[MASK]$ used by the BERT model.
+
+\subsection{The Chinese Pre-trained Transformer Language model}
+
 \subsection{Per-pixel Encoder}
@@
 
-From Table (1), by combining the pre-trained language model with fully connected layer as the document classification model,
+From Table (1), by combining the pre-trained language model with a fully connected layer as the document classification model,
 the test accuracy exceeds the other popular machine learning algorithms.
 Therefore, the pixel channels of an image can be properly represented by these pre-trained language models.
+
+\subsection{Per-pixel Encoder}
 
@@
 
+%-------------------------------------------------------------------------
+\subsection{The Effectiveness of the Pre-training Language Model Pixel Encoder}
+
+\par I design two experiments to show how the pre-training on the Transformer model impact the accuracy of the image classification model.
+With the same model architecture, and the pixel encoding approach, I choose a pre-trained language model and a same architecture without any pre-training.
+With the same hyper parameters for the training, tested on the CIFAR-10 dataset, the pre-trained Transformer model has an accuracy of ?\%.
+The random initialized three-layer-transformer model have achieved 26.85\% of accuracy on the CIFAR-10 test dataset, comparing to the accuracy of 40.63\% achieved by the
+pre-trained transformer model with same architecture. 13.78\% is a significant improvement with the 4.5 billion tokens of Chinese language, it shows that with the unsupervised
+training preprocess, the image classification accuracy can be greatly improved.
+
+\subsection{Supervised Learning with Filenames}
+
+\par I design two experiments to show if use the image class tag name during the training improve the performance or not.
+The filename is the image classification information which represents the English name of the image object.
+
+The encoded filename information randomly replace the image pixels and then feed to the transformer models.
+However, with the filename information, the model performance has dropped by 0.51\% comparing to the pixels' information only.
+
+Experiments showed that, the supervised filename rarely has positive impact on the performance of the classification model.
+
 \subsection{More Fair Comparison by The Mask Token}
@@
 \par However, in the test phase, if feeding the metadata to the model, people might argue that the model learns only the mapping function from
-the metadata, which is the filename in this case, to the image class, which makes it is unfair to compare the performance with other image classification models.
-Thus, to be more objective and fair, I add a preprocess step for the metadata in the test phase, using the $\textbf{[MASK]}$ token to replace each
+the metadata, which is the filename in this case, to the image classes, which makes it is unfair to compare the performance with other image classification models.
+Thus, to be more objective and fair, I add a preprocessing step for the metadata in the test phase, using the $\textbf{[MASK]}$ token to replace each
 ASCII character of the filename then feeds into the model to do the inference.
 
-%-------------------------------------------------------------------------
+Experiments show that the class tag information has improved the accuracy of ?\% on the CIFAR-10 dataset.
 
@@
 which can provide 420 tera-flops of computation capability.
+
+\subsection{Multi-head Attention based ResNet model}
+
+A vision system is an Attention mechanism that focuses limited attention on the key information, saving resources and getting the most efficient information quickly.
+Attention models are less complex and have fewer parameters than CNN and RNN. So the demand for calculation is even smaller.
+Attention addresses an issue in which RNN cannot be calculated in parallel.
+The Attention mechanism does not rely on the calculations of the next step, so it can be processed in parallel with CNN.
+Before the introduction of the Attention mechanism, there was a problem that long distances of information would be weakened,
+just as people with weak memory could not remember the past.
+
+\par RESNET has been proved to be efficient and effective in Computer Vision modeling, thus, a lot of time could be saved by supervised learning on a new CV task.
+It is not surprising that the residual mechanism can learn deep layers with some layers skipped for different tasks.
+
+\par I use the RESNET with two 1x1 Convolutional layers for matching the gap between output of the RESNET and the Attention.
+The Attention has multiple heads and use the Self-Attention, the Query, Key, and Value dimensions are all same, 512 is an empirical value.
+
+\par I use the Jittor library as the modeling tool, and the TsinghuaDog dataset to compare the performance with competitors.
+
+\begin{table}
+\begin{center}
+\begin{tabular}{|l|r|}
+\hline
+Model   & Accuracy \\
+\hline\hline
+Attention-RESNET152 &  	78.29\% \\
+RESNET152  	&	85.14\% \\
+SE-RESNET152  	&	83.34\% \\
+\hline
+DENSENET121   	&	75.29\% \\
+shufflenet\_v2\_x0\_5  &	45.38\% \\
+\hline
+mobilenet\_v2 & 63.65\%\\
+GoogLeNet & 68.84\%\\
+Alexnet & 41.73\%\\
+\hline
+SE-RESNET50 & 79.47\% \\
+RESNET50 & 72.64\%\\
+
+\hline
+\end{tabular}
+\end{center}
+\caption{Comparision of accuracy of the Attention-RESNET model.}
+\end{table}
 
@@
 \bibliographystyle{ieee_fullname}
-%\bibliography{cpvr_classification}
-\begin{thebibliography}{10}
-
-  \bibitem{lee2009convolutional}
-Lee, H., Grosse, R., Ranganath, R. \&  Ng, A.~Y.
-\newblock {Convolutional deep belief networks for scalable unsupervised
-  learning of hierarchical representations}.
-\newblock In {\em Proceedings of the 26th annual international conference on
-  machine learning}, pages 609--616, 2009.
-
-\bibitem{nair2010rectified}
-Nair, V. \&  Hinton, G.~E.
-\newblock {Rectified linear units improve restricted boltzmann machines}.
-\newblock In {\em ICML}, 2010.
-
-\bibitem{mikolov2013distributed}
-Mikolov, T., Sutskever, I., Chen, K., Corrado, G.~S. \&  Dean, J.
-\newblock {Distributed representations of words and phrases and their
-  compositionality}.
-\newblock In {\em Advances in neural information processing systems}, pages
-  3111--3119, 2013.
-
-\bibitem{devlin2019bert}
-Devlin, J., Chang, M.-W., Lee, K. \&  Toutanova, K.
-\newblock {BERT: Pre-training of Deep Bidirectional Transformers for Language
-  Understanding}.
-\newblock In {\em NAACL-HLT (1)}, 2019.
-
-\bibitem{vincent2008extracting}
-Vincent, P., Larochelle, H., Bengio, Y. \&  Manzagol, P.-A.
-\newblock {Extracting and composing robust features with denoising
-  autoencoders}.
-\newblock In {\em Proceedings of the 25th international conference on Machine
-  learning}, pages 1096--1103, 2008.
-
-\bibitem{chen2020generative}
-Chen, M., Radford, A., Child, R., Wu, J., Jun, H., Dhariwal, P., Luan, D.
- and Sutskever, I.
-\newblock {Generative Pretraining from Pixels}.
-\newblock In {\em Proceedings of the 37th International Conference on Machine
-  Learning}, 2020.
-
-\bibitem{wang2019development}
-Wang, W., Yang, Y., Wang, X., Wang, W. \&  Li, J.
-\newblock {Development of convolutional neural network and its application in
-  image classification: a survey}.
-\newblock {\em Optical Engineering}, 58(4):40901, 2019.
-
-\bibitem{lecun1990handwritten}
-LeCun, Y., Boser, B.~E., Denker, J.~S., Henderson, D., Howard, R.~E., Hubbard,
-  W.~E. \&  Jackel, L.~D.
-\newblock {Handwritten digit recognition with a back-propagation network}.
-\newblock In {\em Advances in neural information processing systems}, pages
-  396--404, 1990.
-
-\bibitem{krizhevsky2012imagenet}
-Krizhevsky, A., Sutskever, I. \&  Hinton, G.~E.
-\newblock {Imagenet classification with deep convolutional neural networks}.
-\newblock In {\em Advances in neural information processing systems}, pages
-  1097--1105, 2012.
-
-\bibitem{zeiler2014visualizing}
-Zeiler, M.~D. \&  Fergus, R.
-\newblock {Visualizing and understanding convolutional networks}.
-\newblock In {\em European conference on computer vision}, pages 818--833.
-  Springer, 2014.
-
-\bibitem{simonyan2014very}
-Simonyan, K. \&  Zisserman, A.
-\newblock {Very deep convolutional networks for large-scale image recognition}.
-\newblock In {\em 3rd International Conference on Learning Representations,
-  ICLR 2015 - Conference Track Proceedings}, San Diego, CA, United states,
-  2015.
-
-\bibitem{szegedy2015going}
-Szegedy, C., Liu, W., Jia, Y., Sermanet, P., Reed, S., Anguelov, D., Erhan, D.,
-  Vanhoucke, V. \&  Rabinovich, A.
-\newblock {Going deeper with convolutions}.
-\newblock In {\em Proceedings of the IEEE conference on computer vision and
-  pattern recognition}, pages 1--9, 2015.
-
-\bibitem{he2016deep}
-He, K., Zhang, X., Ren, S. \&  Sun, J.
-\newblock {Deep residual learning for image recognition}.
-\newblock In {\em Proceedings of the IEEE conference on computer vision and
-  pattern recognition}, pages 770--778, 2016.
-
-\bibitem{xie2017aggregated}
-Xie, S., Girshick, R., Doll{\'{a}}r, P., Tu, Z. \&  He, K.
-\newblock {Aggregated residual transformations for deep neural networks}.
-\newblock In {\em Proceedings of the IEEE conference on computer vision and
-  pattern recognition}, pages 1492--1500, 2017.
-
-\bibitem{szegedy2016inception}
-Szegedy, C., Ioffe, S., Vanhoucke, V. \&  Alemi, A.~A.
-\newblock {Inception-v4, inception-ResNet and the impact of residual
-  connections on learning}.
-\newblock In {\em 31st AAAI Conference on Artificial Intelligence, AAAI 2017},
-  pages 4278--4284, San Francisco, CA, United states, 2017.
-
-\bibitem{huang2016deep}
-Huang, G., Sun, Y., Liu, Z., Sedra, D. \&  Weinberger, K.~Q.
-\newblock {Deep networks with stochastic depth}.
-\newblock In {\em European conference on computer vision}, pages 646--661.
-  Springer, 2016.
-
-\bibitem{lu2007survey}
-Lu, D. \&  Weng, Q.
-\newblock {A survey of image classification methods and techniques for
-  improving classification performance}.
-\newblock {\em International journal of Remote sensing}, 28(5):823--870, 2007.
-
-\bibitem{cui2020revisiting}
-Cui, Y., Che, W., Liu, T., Qin, B., Wang, S. \&  Hu, G.
-\newblock {Revisiting Pre-Trained Models for Chinese Natural Language
-  Processing}.
-\newblock In {\em Findings of EMNLP}. Association for Computational
-  Linguistics, 2020.
-
-\bibitem{he2017fine}
-He, X. \&  Peng, Y.
-\newblock {Fine-grained image classification via combining vision and
-  language}.
-\newblock In {\em Proceedings of the IEEE Conference on Computer Vision and
-  Pattern Recognition}, pages 5994--6002, 2017.
-
-\bibitem{reed2016learning}
-Reed, S., Akata, Z., Lee, H. \&  Schiele, B.
-\newblock {Learning deep representations of fine-grained visual descriptions}.
-\newblock In {\em Proceedings of the IEEE Conference on Computer Vision and
-  Pattern Recognition}, pages 49--58, 2016.
-
-\bibitem{fernandez2014we}
-Fern{\'{a}}ndez-Delgado, M., Cernadas, E., Barro, S. \&  Amorim, D.
-  Amorim.
-\newblock {Do we need hundreds of classifiers to solve real world
-  classification problems?}
-\newblock {\em The journal of machine learning research}, 15(1):3133--3181,
-  2014.
-
-\bibitem{kim2014convolutional}
-Kim, Y.
-\newblock {Convolutional neural networks for sentence classification}.
-\newblock In {\em EMNLP 2014 - 2014 Conference on Empirical Methods in Natural
-  Language Processing, Proceedings of the Conference}, pages 1746--1751, Doha,
-  Qatar, 2014.
-
-\end{thebibliography}
+\bibliography{iccv_classification}
 }

### 2021-03-18 A-BasicCommom/ICCV2021/iccv_classification.tex
1. Fix some type.

@@
 
-  Image classification and categorization are essential to the capability of telling the difference between images for a machine vision task.
+  Image classification and categorization are essential for the machine vision task.
   As the \underline{B}idirectional \underline{E}ncoder \underline{R}epresentations from \underline{T}ransformers became popular in many tasks of natural language processing recent years,
-  it is intuitive to use these pre-trained language models for enhancing the computer vision tasks, \eg image classification.
+  it is intuitive to use these pre-trained language models to enhance the computer vision tasks.
   In this paper, by encoding image pixels using pre-trained transformers, then connect to a fully connected layer,
@@
   In the 2010s, Krizhevsky \etal~\cite{krizhevsky2012imagenet} proposed the deep architecture, AlexNet, by concatenating multiple components of CNN layers.
-Several years later, a lot of variants of AlexNet had been proposed by researchers and the accuracy of ImageNet had been greatly improved, \eg ZFNet~\cite{zeiler2014visualizing}, VGG~\cite{simonyan2014very}, GoogLeNet~\cite{szegedy2015going}, ResNet~\cite{he2016deep},
+Several years later, a lot of variants of AlexNet had been proposed by researchers, and the accuracy of ImageNet had been greatly improved, \eg ZFNet~\cite{zeiler2014visualizing}, VGG~\cite{simonyan2014very}, GoogLeNet~\cite{szegedy2015going}, ResNet~\cite{he2016deep},
  ResNeXt~\cite{xie2017aggregated}, inception-ResNet-v2~\cite{szegedy2016inception}, DenseNet~\cite{huang2016deep}.
@@
 My approach consists of a pre-training stage followed by a fine-tuning stage.
-In pre-training, I use BERT objectives, and the sequence Transformer architecture to predict language tokens.
+In the pre-training, we use BERT objectives, and the sequence Transformer architecture to predict language tokens.
 
@@
 embedding for each position.
-Then I use a fully connected layer as a non-linear function from embeddings to image class.
-The dropout layer and the Softmax layer are used for better transfer performance between the training and the test dataset.
+Then a fully connected layer as a non-linear mapping function from embeddings to image class.
+The dropout layer, and the Softmax layer are used for transfer performance between the training dataset and the test dataset.
 
@@
 \par The Transformer model is intended to be used as replacement of CNN layers for extracting information from Images.
-Here, I describe how to train the Transformer language model in detail.
+Here, We describe how to train the Transformer language model in detail.
 
@@
 
-\par The BERT model use a tokenization method, named WordPiece, which breaks down a English word by high frequent suffix and prefix.
+\par The BERT model use a tokenization method, named WordPiece, which breaks down an English word by high frequent suffix and prefix.
 The vocabulary size can be greatly reduced by the sharing suffix and prefix between words.
 Before training the custom WorkPiece model, the final vocabulary size and minimal word-piece frequency need to be assigned.
-I use 21128 as the model vocabulary size and add several model specific tokens like $[PAD]$, $[UNK]$, $[MASK]$ used by the BERT model.
-
-\subsection{The Chinese Pre-trained Transformer Language model}
+We use 21128 as the model vocabulary size and add several model specific tokens like $[PAD]$, $[UNK]$, $[MASK]$ used by the BERT model.
 
@@
 
-Recall that Kim~\cite{kim2014convolutional} had proved that unsupervised pre-trained language model $word2vec$ and CNN outperformed many other machine learning algorithms,
+Recall that Kim~\cite{kim2014convolutional} had proved that unsupervised pre-trained language model $word2vec$, and CNN outperformed many other machine learning algorithms,
 \eg support vector machines and conditional random field, in many datasets such as movie reviews, Stanford sentiment treebank, and TREC question.
-Cui \etal's pre-trained language model, namely RBT3, RBTL3, and RoBERTa-wwm-ext-large, had improved performances over many other machine learning algorithms.
-BERT and RoBERTa-wwm-ext-large models both achieved an f1-score of 97.8\% in the THUCNews dataset, which contains 65 thousands news reports in 10 domains.
+Cui \etal's pre-trained language model, namely RoBERTa-3layers, RoBERTa-large-3layers, and RoBERTa-large-24layers, had improved performances over many other machine learning algorithms.
+BERT and RoBERTa-large-24layers models both achieved an f1-score of 97.8\% in the THUCNews dataset, which contains 65 thousands news reports in 10 domains.
 
-I used RBTL3 and RoBERTa-wwm-ext-large pre-trained language model in two Chinese Judicial datasets, which has 2 and 4 classes.
+We used RoBERTa-large-3layers, and RoBERTa-large-24layers pre-trained language model in two Chinese Judicial datasets, which has 2 and 4 classes.
 The \textit{Two-Case} dataset annotated civil and criminal cases, and the \textit{Four-Case} dataset annotated by civil, criminal, intellectual property, and administrative cases.
-The \textit{Two-Case} dataset has $19508$ training documents and $2000$ test documents, and the \textit{Four-Case} dataset has $34789$ training documents and $2013$ test documents.
+The \textit{Two-Case} dataset has $19,508$ training documents and $2,000$ test documents, and the \textit{Four-Case} dataset has $34,789$ training documents and $2,013$ test documents.
 
@@
 \hline\hline
-RoBERTa-wwm-ext-large & Two-Case	&	99.80\% \\
-RoBERTa-wwm-ext-large & Four-Case	&	99.76\% \\
-RBTL3  & Four-Case	&	96.35\% \\
+RoBERTa-large(24l) & Two-Case	&	99.80\% \\
+RoBERTa-large(24l) & Four-Case	&	99.76\% \\
+RoBERTa-large(3l)  & Four-Case	&	96.35\% \\
 \hline
@@
 \end{center}
-\caption{Comparision of accuracy of the pre-trained language models on different datasets in the document classification task.}
+\caption{Comparision of accuracy of the pre-trained language models on different datasets on the document classification task.}
 \end{table}
@@
 \end{center}
-   \caption{Concatenation, encoder, representation, and extraction layers for image classification task.}
+   \caption{Concatenation, encoder, representation, and extraction layers for the image classification task.}
 \label{fig:short}
@@
 
-I design simple classification models without too many layers, as Figure (1) shows,
-and use the CIFAR-10 and CIFAR-100 dataset as an example to show the architecture of the model.
+We design simple classification models without too many layers, as Figure (1) shows,
+and use the CIFAR-10 and CIFAR-100 dataset as examples to show the architecture of the model.
 The model architecture has seven functional layers:
@@
 In the Feature-Extraction layer, a combination of one dropout layer, one fully connected layer, and one softmax layer, as Equation (2), is used.
+The softmax layer is an approach that make the probability $z$ of each class more focused by taking exponent of it, then use normalization for each class probability.
 In the Output layer, the classification label of the image is feed in the model.
@@
 
-\par I design two experiments to show how the pre-training on the Transformer model impact the accuracy of the image classification model.
-With the same model architecture, and the pixel encoding approach, I choose a pre-trained language model and a same architecture without any pre-training.
-With the same hyper parameters for the training, tested on the CIFAR-10 dataset, the pre-trained Transformer model has an accuracy of ?\%.
+\par We design two experiments to show how the pre-training on the Transformer model impact the accuracy of the image classification model.
+With the same model architecture, and the pixel encoding approach, We choose a pre-trained language model and a same architecture without any pre-training.
+With the same hyper parameters for the training, tested on the CIFAR-10 dataset, the pre-trained Transformer model has an accuracy of 40.63\%.
 The random initialized three-layer-transformer model have achieved 26.85\% of accuracy on the CIFAR-10 test dataset, comparing to the accuracy of 40.63\% achieved by the
-pre-trained transformer model with same architecture. 13.78\% is a significant improvement with the 4.5 billion tokens of Chinese language, it shows that with the unsupervised
+pre-trained transformer model with same architecture.
+
+\par 13.78\% is a significant improvement with the 4.5 billion tokens of Chinese language, it shows that with the unsupervised
 training preprocess, the image classification accuracy can be greatly improved.
@@
 
-\par I design two experiments to show if use the image class tag name during the training improve the performance or not.
+\par We design two experiments to show if use the image class tag name during the training improve the performance or not.
 The filename is the image classification information which represents the English name of the image object.
@@
 and gives the token-recovery capability to the downstream task model.
+However, the $\textbf{[MASK]}$ ocupy the index $103$ in the BERT vocabulary, which conflicts with the image pixel values (0-255), thus in this case no replacement for $[MASK]$ token on the filename processing.
 
@@
 the metadata, which is the filename in this case, to the image classes, which makes it is unfair to compare the performance with other image classification models.
-Thus, to be more objective and fair, I add a preprocessing step for the metadata in the test phase, using the $\textbf{[MASK]}$ token to replace each
+Thus, to be more objective and fair, We add a preprocessing step for the metadata in the test phase, using the $\textbf{[MASK]}$ token to replace each
 ASCII character of the filename then feeds into the model to do the inference.
-
-Experiments show that the class tag information has improved the accuracy of ?\% on the CIFAR-10 dataset.
 
@@
 moreover, the pre-trained Chinese language models use extra 5 billion training tokens comparing to Devlin \etal's 0.4 billion tokens.
-I use a batch size of 512 and train for $6\sim16$ epochs using AdamW with $\beta_1=0.99$, $\beta_2=0.999$, and weight decay of $10^{-8}$.
-I set the learning rate to $10^{-4}$ and no warmed up or decay are used.
+We use a batch size of 512 and train for $6\sim16$ epochs using AdamW with $\beta_1=0.99$, $\beta_2=0.999$, and weight decay of $10^{-8}$.
+We set the learning rate to $10^{-4}$ and no warmed up or decay are used.
 The dropout rate is $0.05$.
 
-\par When fine-tuning, as Figure (2), I check the accuracy of the trained model on the test set and stopped training when it converges on $10^{-3}\sim10^{-4}$.
+\par When fine-tuning, as Figure (2), We check the accuracy of the trained model on the test set and stopped training when it converges on $10^{-3}\sim10^{-4}$.
 
@@
 
-\par I use the RESNET with two 1x1 Convolutional layers for matching the gap between output of the RESNET and the Attention.
+\par We use the RESNET with two 1x1 Convolutional layers for matching the gap between output of the RESNET and the Attention.
 The Attention has multiple heads and use the Self-Attention, the Query, Key, and Value dimensions are all same, 512 is an empirical value.
 
-\par I use the Jittor library as the modeling tool, and the TsinghuaDog dataset to compare the performance with competitors.
+\par We use the Jittor\cite{hu2020jittor} library as the modeling tool, and the TsinghuaDog\cite{Zou2020ThuDogs} dataset to compare the performance with competitors.
+
+\par The experiment was performed on an Nvidia V100, with 16GB of RAM,
+which can provide 100 tera-flops of computation capability.
 
@@
 \end{center}
-\caption{Comparision of accuracy of the Attention-RESNET model.}
+\caption{Comparision of accuracy of the Attention-RESNET model on the ThuDogs dataset.}
 \end{table}
+
+Result from Table (2) showed that the Multi-head Attention doesn't improve the performance on the TsinghuaDog test dataset, there is 6.85\% gap with the RESNET152 model.
+It might because the Multi-head takes special care on hyper-parameter tuning on the number of heads, or for most of the time, the Attention on the ResNet doesn't show improvement.
 
@@
 
-Using the proposed model, I tried different pre-trained language models to see the impact on classification accuracy.
+Using the proposed model, we tried different pre-trained language models to see the impact on classification accuracy.
 From the Table (2), for the same size of a dataset with larger classes, it needs more epochs and training time for the classification model.
@@
 \hline
-Language Model 	& Dataset & Epoch & Accuracy \\
+Language Model 	& Dataset  & Accuracy \\
 \hline\hline
-RBT3   & CIFAR-10 & 6	&	99.74\% \\
-RBTL3  & CIFAR-10 & 6	&	99.72\% \\
-RoBERTa-large  & CIFAR-10 & 6	&	99.60\% \\
+RoBERTa-(3l)   & CIFAR-10 	&	99.74\% \\
+RoBERTa-large(3l)  & CIFAR-10 	&	99.72\% \\
+RoBERTa-large(24l)  & CIFAR-10 	&	99.60\% \\
 \hline
-RBT3   & CIFAR-100 & 12	&	99.66\% \\
-RBTL3  & CIFAR-100 & 6  & 	99.10\% \\
-RoBERTa-large & CIFAR-100 & 16 &	99.76\% \\
+RoBERTa-(3l)    & CIFAR-100 	&	99.66\% \\
+RoBERTa-large(3l)  & CIFAR-100   & 	99.10\% \\
+RoBERTa-large(24l) & CIFAR-100  &	99.76\% \\
 \hline\hline
-iGPT-L & CIFAR-10 & $18_a$ & 99.0\%\\
-iGPT-L & CIFAR-100 & $18_a$ & 88.5\%\\
+iGPT-L & CIFAR-10  & 99.0\% \\
+iGPT-L & CIFAR-100 & 88.5\% \\
 \hline
@@
 
-The iGPT-L was trained on the ImageNet dataset, and it has 48 layers of transoformers and 1.4 billion parameters, and the embedding size takes 1536,
+The iGPT-L was trained on the ImageNet dataset, and it has 48 layers of transformers and 1.4 billion parameters, and the embedding size takes 1536,
 so it has almost identical layers with GPT-2 language model, except for 1.5 billion parameters and 1600 embedding size.

### 2021-04-14 A-BasicCommom/CICAI2021/image_classification.tex
1.CICAI2021

--- 2021-03-18 A-BasicCommom/ICCV2021/iccv_classification.tex
@@
-\documentclass[10pt,twocolumn,letterpaper]{article}
-
-\usepackage{iccv}
-\usepackage{times}
-\usepackage{epsfig}
+% This is samplepaper.tex, a sample chapter demonstrating the
+% LLNCS macro package for Springer Computer Science proceedings;
+% Version 2.20 of 2017/10/04
+%
+\documentclass[runningheads]{llncs}
+%
+\usepackage{comment}
 \usepackage{graphicx}
-\usepackage{amsmath}
-\usepackage{amssymb}
-
-% Include other packages here, before hyperref.
-
-% If you comment hyperref and then uncomment it, you should delete
-% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
-% run, let it finish, and you should be clear).
-\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
-
-% \iccvfinalcopy % *** Uncomment this line for the final submission
-
-\def\iccvPaperID{11033} % *** Enter the ICCV Paper ID here
-\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}
-
-% Pages are numbered in submission mode, and unnumbered in camera-ready
-\ificcvfinal\pagestyle{empty}\fi
+% Used for displaying a sample figure. If possible, figure files should
+% be included in EPS format.
+%
+% If you use the hyperref package, please uncomment the following line
+% to display URLs in blue roman font according to Springer's eBook style:
+% \renewcommand\UrlFont{\color{blue}\rmfamily}
 
 \begin{document}
+%
+\title{Enhance Image Classification Performance}
 
-%%%%%%%%% TITLE
-\title{Enhance Image Classification Performance Via Unsupervised Pre-trained Transformers Language Models}
+% INITIAL SUBMISSION 
+\def\YOFOSubNumber{98}  % Insert your submission number here
+%\begin{comment}
+\titlerunning{CICAI2021 submission ID \YOFOSubNumber} 
+\authorrunning{CICAI2021 submission ID \YOFOSubNumber} 
+\author{Anonymous CICAI submission}
+\institute{Paper ID \YOFOSubNumber}
+%\end{comment}
+%******************
 
-\author{Dezhou Shen\\
-Department of Computer Science\\
-Tsinghua University\\
-Beijing, CN 100084\\
-{\tt\small sdz15@mails.tsinghua.edu.cn}
-% For a paper whose authors are all at the same institution,
-% omit the following lines up until the closing ``}''.
-% Additional authors and addresses can be added with ``\and'',
-% just like the second author.
-% To save space, use either the email address or home page, not both
-}
+% CAMERA READY SUBMISSION
+\begin{comment}
+\titlerunning{Abbreviated paper title}
+% If the paper title is too long for the running head, you can set
+% an abbreviated paper title here
+%
+\author{First Author\inst{1}\orcidID{0000-1111-2222-3333} \and
+Second Author\inst{2,3}\orcidID{1111-2222-3333-4444} \and
+Third Author\inst{3}\orcidID{2222--3333-4444-5555}}
+%
+\authorrunning{F. Author et al.}
+% First names are abbreviated in the running head.
+% If there are more than two authors, 'et al.' is used.
+%
+\institute{Princeton University, Princeton NJ 08544, USA \and
+Springer Heidelberg, Tiergartenstr. 17, 69121 Heidelberg, Germany
+\email{lncs@springer.com}\\
+\url{http://www.springer.com/gp/computer-science/lncs} \and
+ABC Institute, Rupert-Karls-University Heidelberg, Heidelberg, Germany\\
+\email{\{abc,lncs\}@uni-heidelberg.de}}
+\end{comment}
+%******************
+\maketitle              % typeset the header of the contribution
 
-\maketitle
-% Remove page # from the first page of camera-ready.
-\ificcvfinal\thispagestyle{empty}\fi
-
-%%%%%%%%% ABSTRACT
 \begin{abstract}
 
-  Image classification and categorization are essential for the machine vision task.
+  Image classification and categorization are essential to the capability of telling the difference between images for a machine vision task.
   As the \underline{B}idirectional \underline{E}ncoder \underline{R}epresentations from \underline{T}ransformers became popular in many tasks of natural language processing recent years,
-  it is intuitive to use these pre-trained language models to enhance the computer vision tasks.
+  it is intuitive to use these pre-trained language models for enhancing the computer vision tasks, e.g. image classification.
   In this paper, by encoding image pixels using pre-trained transformers, then connect to a fully connected layer,
-  the classification model outperforms the ResNet model,
+  the classification model outperforms the Wide ResNet model, and the linear-probe iGPT-L model,
   and achieved accuracy of $99.60\%\sim99.74\%$ on the CIFAR-10 image set and accuracy of $99.10\%\sim99.76\%$ on the CIFAR-100 image set.
 
+\keywords{Image Classification  \and Transformers \and Attention.}
 \end{abstract}
+%
+%
+%
 
@@
 
-  Convolutional neural networks have achieved dominant performance in vision tasks for the rich representation for images.
-  The LeNet architecture has been proved efficient than the Feed forward networks, and the Residual-style Networks have become popular recent years.
-  VGGNet, ResNet, GoogLeNet showed that the depth, width are important factors for networks.
-  Vicent \etal~\cite{vincent2008extracting}'s Denoising Autoencoder model, which was initially designed for images.
-
-  In the natural language processing domain, unsupervised pre-training becomes popular for the gigantic data collected by the industrial production.
-  It started to flourish the natural language processing domain since Mikolov \etal~\cite{mikolov2013distributed} had proposed Word2Vec.
-  Vaswani \etal~\cite{vaswani2017attention} used the Attention layers in the language translation task, and showed that the Attention layer overcome the drawback of the Recurrent Neural Networks
-in parallel training.
-Devin \etal~\cite{devlin2019bert} employed the Transformer model, which take part of the Vaswani's Attention model and used Gigantic corpus in the pre-training phase, dominates in almost all natural language processing tasks in recent years.
-
-  Lee \etal~\cite{lee2009convolutional} used the pre-training approaches in Computer Vision tasks in 2009, and later from 2010 to 2016,
-  Nair and Hinton~\cite{nair2010rectified} proved that the pre-training process is supplementary in the Computer Vision tasks.
-
-  Some works use the Transformer networks in the image pixel pre-training, and use the model to generate image pixels.
+  Unsupervised pre-training is important to modern research of deep learning.
+  Lee et al.~\cite{lee2009convolutional} used the pre-training approaches
+  in Computer Vision tasks in 2009, and later from 2010 to 2016,
+  Nair and Hinton~\cite{nair2010rectified} proved that the pre-training process is supplementary in the Computer Vision tasks,
+  thus, can be omitted in some cases.
+  However, it started to flourish in the natural language processing domain since Mikolov et al.~\cite{mikolov2013distributed} had proposed Word2Vec.
+  Not long before Devin et al.~\cite{devlin2019bert}'s BERT language model dominates in most tasks in natural language processing,
+  which is close resemble of Vicent et al.~\cite{vincent2008extracting}'s Denoising Autoencoder model, which was initially designed for images.
+  The pre-training process becomes one of the most important procedures in deep learning.
 
@@
 
-  Chen \etal~\cite{chen2020generative} trained image representation by sequence Transformers and tested on CIFAR-10 to show it is outperforming to Wide-ResNet
+  Chen et al.~\cite{chen2020generative} trained image representation by sequence Transformers and tested on CIFAR-10 to show it is outperforming to Wide-ResNet
 which was inspired by unsupervised natural language representation learning.
-  Wang \etal~\cite{wang2019development} reviewed that convolutional neural networks had been proposed in the 1960s, and had its implementation in the 1980s,
-and until LeCun \etal~\cite{lecun1990handwritten}'s first experiment on handwritten digit recognition, CNN's great potential had been revealed.
-  In the 2010s, Krizhevsky \etal~\cite{krizhevsky2012imagenet} proposed the deep architecture, AlexNet, by concatenating multiple components of CNN layers.
-Several years later, a lot of variants of AlexNet had been proposed by researchers, and the accuracy of ImageNet had been greatly improved, \eg ZFNet~\cite{zeiler2014visualizing}, VGG~\cite{simonyan2014very}, GoogLeNet~\cite{szegedy2015going}, ResNet~\cite{he2016deep},
+  Wang et al.~\cite{wang2019development} reviewed that convolutional neural networks had been proposed in the 1960s, and had its implementation in the 1980s,
+and until LeCun et al.~\cite{lecun1990handwritten}'s first experiment on handwritten digit recognition, CNN's great potential had been revealed.
+  In the 2010s, Krizhevsky et al.~\cite{krizhevsky2012imagenet} proposed the deep architecture, AlexNet, by concatenating multiple components of CNN layers.
+Several years later, a lot of variants of AlexNet had been proposed by researchers and the accuracy of ImageNet had been greatly improved, e.g.
+ZFNet~\cite{zeiler2014visualizing}, VGG~\cite{simonyan2014very}, GoogLeNet~\cite{szegedy2015going}, ResNet~\cite{he2016deep},
  ResNeXt~\cite{xie2017aggregated}, inception-ResNet-v2~\cite{szegedy2016inception}, DenseNet~\cite{huang2016deep}.
@@
 And it is difficult in handling the dichotomy between pixels and natural language texts in a single model.
-  Cui \etal~\cite{cui2020revisiting} proposed several whole-word-masking pre-trained Chinese language models,
+  Cui et al.~\cite{cui2020revisiting} proposed several whole-word-masking pre-trained Chinese language models,
 which are improved versions of BERT~\cite{devlin2019bert} pre-trained language models, namely RBT3, RBTL3, and RoBERTa-wwm-ext-large.
@@
 and tested on the CUB-200-2011 image dataset and achieved $85.55\%$ by combining GoogLeNet~\cite{szegedy2015going} and CNN-RNN~\cite{reed2016learning}, the result outperformed many competitors.
-  Three of the most popular approaches for image classification tasks are per-pixel, subpixel, and heterogeneous.
-Lu and Weng found that, for per-pixel approach, non-parametric classifiers, \eg neural networks, support vector machines, and decision trees,
+  Lu and Weng found that, for per-pixel approach, non-parametric classifiers, e.g. neural networks, support vector machines, and decision trees,
 are the most well-known algorithms for their performance and generalization advantages in the late 1990s and 2000s.
-  Fern{\'a}ndez \etal~\cite{fernandez2014we} compared different classifiers in small datasets, and they found that the random forest algorithm ranks first among the 179 classifiers.
+Fern{\'a}ndez et al.~\cite{fernandez2014we} compared different classifiers in small datasets, and they found that the random forest algorithm ranks first among the 179 classifiers.
+  Recall that Kim~\cite{kim2014convolutional} had proved that unsupervised pre-trained language model $word2vec$ and CNN outperformed many other machine learning algorithms,
+e.g. support vector machines and conditional random field, in many datasets such as movie reviews, Stanford sentiment treebank, and TREC question.
+Cui et al.'s pre-trained language model, namely RoBERTa(3), RoBERTa-large(3), and RoBERTa-large(24), had improved performances over many other machine learning algorithms.
+BERT and RoBERTa-large(24) models both achieved an f1-score of 97.8\% in the THUCNews dataset, which contains 65,000 news reports in 10 domains.
 
@@
 
+\section{Image Classification by Convolutional and Transformer networks}
+
+Three of the most popular approaches for image classification tasks are per-pixel, subpixel, and heterogeneous.
+
+\subsection{Convolutional Neural Networks for Image Classification}
+
+\par CNN models are fundamental architectures to compare the performance.
+A vision system is an Attention mechanism that focuses limited attention on the key information, saving resources and getting the most efficient information quickly.
+Attention models are less complex and have fewer parameters than CNN and RNN. So the demand for calculation is even smaller.
+Attention addresses an issue in which RNN cannot be calculated in parallel.
+The Attention mechanism does not rely on the calculations of the next step, so it can be processed in parallel with CNN.
+Before the introduction of the Attention mechanism, there was a problem that long distances of information would be weakened,
+just as people with weak memory could not remember the past.
+
+\par We use the Jittor\cite{hu2020jittor} library as the modeling tool, and the TsinghuaDog\cite{Zou2020ThuDogs} dataset to compare the performance with competitors.
+Image pre-process steps including resizing to $256*256$, center-cropping by $224*224$, a random horizontal flip, conversion to (0,1), and normalization to 0.485 of mean value and 0.229 of standard error.
+
+\par RESNET has been proved to be efficient and effective in Computer Vision modeling, thus, a lot of time could be saved by supervised learning on a new CV task.
+It is not surprising that the residual mechanism can learn deep layers with some layers skipped for different tasks.
+
+\par We use the RESNET with two 1x1 Convolutional layers for matching the gap between output of the RESNET and the Attention.
+The Attention has multiple heads and use the Self-Attention, the Query, Key, and Value dimensions are all same, 512 is an empirical value.
+
+\par The experiment was performed on an Nvidia V100, with 16GB of RAM,
+which can provide 100 tera-flops of computation capability.
+
+\begin{table}
+\begin{center}
+\begin{tabular}{|l|r|}
+\hline
+Model   &  Accuracy \\
+\hline
+\hline
+Alexnet & 41.73\%\\
+GoogLeNet & 68.84\%\\
+mobilenet\_v2 & 63.65\%\\
+shufflenet\_v2\_x0\_5  &	45.38\% \\
+Attention-RESNET152-4H-256L &  	55.00\% \\
+Attention-RESNET152-1H-1024L &  	67.57\% \\
+\hline
+\hline
+\hline
+Attention-RESNET152-1H-1024L &  	78.38\% \\
+DENSENET121   	&	75.29\% \\
+SE-RESNET50 & 79.47\% \\
+RESNET50 & 82.50\%\\
+Gelu-RESNET152 &	64.06\% \\
+RESNET152  	&	85.14\% \\
+SE-RESNET152  	&	83.34\% \\
+SE-RESNET152+RESNET152 & 82.62\% \\
+SE-RESNET152+Alexnet & 80.38\% \\
+RESNET200  	&	73.19\% \\
+\hline
+\hline
+\hline
+RESNET152  	&	84.87\% \\
+SE-RESNET152  	&	82.92\% \\
+\hline
+\end{tabular}
+\end{center}
+\caption{Comparision of model accuracy on the ThuDogs dataset. The top part models use 10\% of the whole ThuDogs data, the middle part models use 80\% of the ThuDogs data,
+and the bottom part models use 100\% of the ThuDogs data.}
+\end{table}
+
+\subsection{Dataset Amount Usage}
+From the Table (1) RESNET152 and SE-RESNET152 in the middle part and the bottom part, we can see that because of the imbalance of the dataset on different class, the top class has 7449 instance,
+and the bottom class has 200 instance. As a result, using 80\% of the ThuDogs data might beat the 100\% under Stochastic gradient descent optimizer.
+For later discussion, we use 80\% of the ThuDogs data to train the model discussed for best performance and accuracy.
+
+\subsection{Model Description}
+
+All models in the Table (1) share a common architecture that a base feature selection layer, such as AlexNet, followed by a fully connected layer which was used as a mapping function from ImageNet dataset classes to ThuDogs dataset classes.
+The Attention based model use two $1*1$ convolutional layers serves as transition between the average-pool layer and the fully connected layer.
+Between that we use the Multi-head Attention layer with 1024 as the max sequence and 1 head, the k-dim and v-dim are 1024 and the self attention mechanism was used.
+The Alexnet, GoogLeNet, mobilenet, shufflenet, Densenet, Resnet, SE-RESNET are the well-known models. The Gelu-Resnet replace the Relu with Gelu function.
+The RESNET200 increase the third phase parameter from 36 to 48, with a parameter of $[3,8,48,3]$.
+The Attention-RESNET152-4H-256L and Attention-RESNET152-1H-1024L model differs only on the number of heads, and the input dimension, the first model has 4 heads and 256 dimension for embedding dimension, K-dim and V-dim.
+For the Attention layer, the shape of the input was transformed to (batch, channel, sequence), then transposed to (batch, sequence, channel) for the Attention layer.
+After the Attention operation, the shape of the image was transposed back to (batch, channel, sequence), and then for the rest of the operations.
+
+\subsection{Discussion}
+
+From the Table(1) we can see that the Attention layer doesn't improve the performance on the ThuDogs validation dataset, there is 6.85\% gap comparing to the RESNET152 model.
+Experiment on the Attention model number of heads and sequence length showed that, (Attention-RESNET152-4H-256L \&  	55.00\%, Attention-RESNET152-1H-1024L \&  	67.57\%),
+increasing the number of head and reducing the sequence length have negative impact on the accuracy of the ThuDogs Dataset.
+Experiment showed that, the Attention mechanism following the ResNet doesn't show improvement on the accuracy, and so as the Squeeze-Extract mechanism, Gelu activation, and combination of Resnet with other networks, such as AlexNet or SERESNET.
+
+%-------------------------------------------------------------------------
 \section{Image Classification via Pre-trained Transformers Language Models}
 
-%-------------------------------------------------------------------------
 \subsection{Approach}
@@
 My approach consists of a pre-training stage followed by a fine-tuning stage.
-In the pre-training, we use BERT objectives, and the sequence Transformer architecture to predict language tokens.
+In the pre-training, I use the BERT objectives, and the sequence Transformer architecture to predict language tokens.
 
-\par Given an unlabeled dataset $\Bbb X$, the BERT objective samples a sub-sequence $\Bbb S \in \{C\}$,
-$C$ represents all possible tokens, and such that for each index $i \in \Bbb S$,
-there is independent probability $15\%$ of appearing in $\Bbb S$,
+\par Given an unlabeled dataset $ X$, the BERT objective samples a sub-sequence $ S \in \{C\}$,
+$C$ represents all possible tokens, and such that for each index $i \in  S$,
+there is independent probability $15\%$ of appearing in $ S$,
 name the token $M$ as the BERT mask.
@@
 \begin{equation}
-  \lambda = \mathop{\Bbb E}\limits_{x\sim\Bbb X} \mathop{\Bbb E}\limits_{M} \sum_{i\in S}{\bigl[-\log{p(x_i\mid x_{\left[1,n \right]\backslash M})\bigr]}}
+  \lambda = \mathop{ E}\limits_{x\sim X} \mathop{ E}\limits_{M} \sum_{i\in S}{\bigl[-\log{p(x_i\mid x_{\left[1,n \right]\backslash M})\bigr]}}
 \end{equation}
@@
 embedding for each position.
-Then a fully connected layer as a non-linear mapping function from embeddings to image class.
-The dropout layer, and the Softmax layer are used for transfer performance between the training dataset and the test dataset.
+Then I use a fully connected layer as a non-linear function from embeddings to image classes.
+The dropout layer and the Softmax layer are used for better transfer performance between the training and the test datasets.
 
-\subsection{The Chinese Pre-trained Transformer Language model}
+\subsection{The Power of the Transformer Encoder on the Document Classification}
 
-\par The Transformer model is intended to be used as replacement of CNN layers for extracting information from Images.
-Here, We describe how to train the Transformer language model in detail.
+Generality speaking, the performance of the pre-trained language models achieved in the document classification tasks.
 
-\subsection{The Chinese Word Piece Tokenization Model}
-
-\par The BERT model use a tokenization method, named WordPiece, which breaks down an English word by high frequent suffix and prefix.
-The vocabulary size can be greatly reduced by the sharing suffix and prefix between words.
-Before training the custom WorkPiece model, the final vocabulary size and minimal word-piece frequency need to be assigned.
-We use 21128 as the model vocabulary size and add several model specific tokens like $[PAD]$, $[UNK]$, $[MASK]$ used by the BERT model.
-
-\subsection{Per-pixel Encoder}
-
-For the per-pixel image classification approach, for every RGB channel of pixels in an image,
-each pixel had its pixel-channel code, ranges from 0x00 to 0xff for different colors.
-Thus, taking these pixels in an image is identical to ASCII characters in a document.
-Generality speaking, the performance of the pre-trained language models achieved in the document classification tasks, can be transferred to image classification naturally.
-
-Recall that Kim~\cite{kim2014convolutional} had proved that unsupervised pre-trained language model $word2vec$, and CNN outperformed many other machine learning algorithms,
-\eg support vector machines and conditional random field, in many datasets such as movie reviews, Stanford sentiment treebank, and TREC question.
-Cui \etal's pre-trained language model, namely RoBERTa-3layers, RoBERTa-large-3layers, and RoBERTa-large-24layers, had improved performances over many other machine learning algorithms.
-BERT and RoBERTa-large-24layers models both achieved an f1-score of 97.8\% in the THUCNews dataset, which contains 65 thousands news reports in 10 domains.
-
-We used RoBERTa-large-3layers, and RoBERTa-large-24layers pre-trained language model in two Chinese Judicial datasets, which has 2 and 4 classes.
+We used the RoBERTa-large with 3 and 12 layers as encoder, and tested on two Chinese Judicial datasets, which has two and four classes.
 The \textit{Two-Case} dataset annotated civil and criminal cases, and the \textit{Four-Case} dataset annotated by civil, criminal, intellectual property, and administrative cases.
@@
 
-From Table (1), by combining the pre-trained language model with a fully connected layer as the document classification model,
+From Table (2), by combining the pre-trained language model with a fully connected layer as the document classification model,
 the test accuracy exceeds the other popular machine learning algorithms.
 Therefore, the pixel channels of an image can be properly represented by these pre-trained language models.
-
-\subsection{Per-pixel Encoder}
 
@@
 \hline\hline
-RoBERTa-large(24l) & Two-Case	&	99.80\% \\
-RoBERTa-large(24l) & Four-Case	&	99.76\% \\
-RoBERTa-large(3l)  & Four-Case	&	96.35\% \\
+RoBERTa-large(24) & Two-Case	&	99.80\% \\
+RoBERTa-large(24) & Four-Case	&	99.76\% \\
+RoBERTa-large(3)  & Four-Case	&	96.35\% \\
 \hline
@@
 \end{center}
-\caption{Comparision of accuracy of the pre-trained language models on different datasets on the document classification task.}
+\caption{Comparision of accuracy of the pre-trained language models on different datasets in the document classification task.}
 \end{table}
@@
 
-\subsection{Image Classification Model}
+\subsection{Image Classification Model with Transformer Encoder}
+
+For the per-pixel image classification approach, for every RGB channel of pixels in an image,
+each pixel had its pixel-channel code, ranging from 0x00 to 0xff for different colors.
+Thus, taking these pixels in an image is resembled to ASCII characters in a document.
+An experiment show that document classification capability can be transferred to image classification naturally.
 
@@
 \end{center}
-   \caption{Concatenation, encoder, representation, and extraction layers for the image classification task.}
+   \caption{Concatenation, encoder, representation, and extraction layers for image classification task.}
 \label{fig:short}
@@
 
-We design simple classification models without too many layers, as Figure (1) shows,
-and use the CIFAR-10 and CIFAR-100 dataset as examples to show the architecture of the model.
+I design simple classification models without too many layers, as Figure (1) shows,
+and use the CIFAR-10 and CIFAR-100 dataset as an example to show the architecture of the model.
 The model architecture has seven functional layers:
@@
 
-%-------------------------------------------------------------------------
-\subsection{The Effectiveness of the Pre-training Language Model Pixel Encoder}
-
-\par We design two experiments to show how the pre-training on the Transformer model impact the accuracy of the image classification model.
-With the same model architecture, and the pixel encoding approach, We choose a pre-trained language model and a same architecture without any pre-training.
-With the same hyper parameters for the training, tested on the CIFAR-10 dataset, the pre-trained Transformer model has an accuracy of 40.63\%.
-The random initialized three-layer-transformer model have achieved 26.85\% of accuracy on the CIFAR-10 test dataset, comparing to the accuracy of 40.63\% achieved by the
-pre-trained transformer model with same architecture.
-
-\par 13.78\% is a significant improvement with the 4.5 billion tokens of Chinese language, it shows that with the unsupervised
-training preprocess, the image classification accuracy can be greatly improved.
-
-\subsection{Supervised Learning with Filenames}
-
-\par We design two experiments to show if use the image class tag name during the training improve the performance or not.
-The filename is the image classification information which represents the English name of the image object.
-
-The encoded filename information randomly replace the image pixels and then feed to the transformer models.
-However, with the filename information, the model performance has dropped by 0.51\% comparing to the pixels' information only.
-
-Experiments showed that, the supervised filename rarely has positive impact on the performance of the classification model.
-
 \subsection{More Fair Comparison by The Mask Token}
@@
 For the CIFAR-10 and CIFAR-100 dataset, the metadata is the filename of the images, which can be treated as the supervised description of the image.
-Peek some the filenames, \eg \textit{wagon\_s\_001343.png}, \textit{banana\_boat\_s\_001615.png}, and \textit{delivery\_truck\_s\_001529.png},
+Peek some the filenames, e.g. \textit{wagon\_s\_001343.png}, \textit{banana\_boat\_s\_001615.png}, and \textit{delivery\_truck\_s\_001529.png},
 and it is beneficial for the classification model to understand the supervised descriptive information for the image.
@@
 and gives the token-recovery capability to the downstream task model.
-However, the $\textbf{[MASK]}$ ocupy the index $103$ in the BERT vocabulary, which conflicts with the image pixel values (0-255), thus in this case no replacement for $[MASK]$ token on the filename processing.
 
 \par However, in the test phase, if feeding the metadata to the model, people might argue that the model learns only the mapping function from
-the metadata, which is the filename in this case, to the image classes, which makes it is unfair to compare the performance with other image classification models.
-Thus, to be more objective and fair, We add a preprocessing step for the metadata in the test phase, using the $\textbf{[MASK]}$ token to replace each
+the metadata, which is the filename in this case, to the image class, which makes it is unfair to compare the performance with other image classification models.
+Thus, to be more objective and fair, I add a preprocess step for the metadata in the test phase, using the $\textbf{[MASK]}$ token to replace each
 ASCII character of the filename then feeds into the model to do the inference.
+
+%-------------------------------------------------------------------------
 
@@
 
-As Cui \etal~\cite{cui2020revisiting} reported that the training of the RBT3 language model was based on Devlin \etal's model,
-moreover, the pre-trained Chinese language models use extra 5 billion training tokens comparing to Devlin \etal's 0.4 billion tokens.
+As Cui et. al.~\cite{cui2020revisiting} reported that the training of the RBT3 language model was based on Devlin et. al.'s model,
+moreover, the pre-trained Chinese language models use extra 5 billion training tokens comparing to Devlin et. al.'s 0.4 billion tokens.
 We use a batch size of 512 and train for $6\sim16$ epochs using AdamW with $\beta_1=0.99$, $\beta_2=0.999$, and weight decay of $10^{-8}$.
@@
 
-\subsection{Multi-head Attention based ResNet model}
-
-A vision system is an Attention mechanism that focuses limited attention on the key information, saving resources and getting the most efficient information quickly.
-Attention models are less complex and have fewer parameters than CNN and RNN. So the demand for calculation is even smaller.
-Attention addresses an issue in which RNN cannot be calculated in parallel.
-The Attention mechanism does not rely on the calculations of the next step, so it can be processed in parallel with CNN.
-Before the introduction of the Attention mechanism, there was a problem that long distances of information would be weakened,
-just as people with weak memory could not remember the past.
-
-\par RESNET has been proved to be efficient and effective in Computer Vision modeling, thus, a lot of time could be saved by supervised learning on a new CV task.
-It is not surprising that the residual mechanism can learn deep layers with some layers skipped for different tasks.
-
-\par We use the RESNET with two 1x1 Convolutional layers for matching the gap between output of the RESNET and the Attention.
-The Attention has multiple heads and use the Self-Attention, the Query, Key, and Value dimensions are all same, 512 is an empirical value.
-
-\par We use the Jittor\cite{hu2020jittor} library as the modeling tool, and the TsinghuaDog\cite{Zou2020ThuDogs} dataset to compare the performance with competitors.
-
-\par The experiment was performed on an Nvidia V100, with 16GB of RAM,
-which can provide 100 tera-flops of computation capability.
-
-\begin{table}
-\begin{center}
-\begin{tabular}{|l|r|}
-\hline
-Model   & Accuracy \\
-\hline\hline
-Attention-RESNET152 &  	78.29\% \\
-RESNET152  	&	85.14\% \\
-SE-RESNET152  	&	83.34\% \\
-\hline
-DENSENET121   	&	75.29\% \\
-shufflenet\_v2\_x0\_5  &	45.38\% \\
-\hline
-mobilenet\_v2 & 63.65\%\\
-GoogLeNet & 68.84\%\\
-Alexnet & 41.73\%\\
-\hline
-SE-RESNET50 & 79.47\% \\
-RESNET50 & 72.64\%\\
-
-\hline
-\end{tabular}
-\end{center}
-\caption{Comparision of accuracy of the Attention-RESNET model on the ThuDogs dataset.}
-\end{table}
-
-Result from Table (2) showed that the Multi-head Attention doesn't improve the performance on the TsinghuaDog test dataset, there is 6.85\% gap with the RESNET152 model.
-It might because the Multi-head takes special care on hyper-parameter tuning on the number of heads, or for most of the time, the Attention on the ResNet doesn't show improvement.
-
 \subsection{Results}
@@
 Using the proposed model, we tried different pre-trained language models to see the impact on classification accuracy.
-From the Table (2), for the same size of a dataset with larger classes, it needs more epochs and training time for the classification model.
+From the Table (3), for the same size of a dataset with larger classes, it needs more epochs and training time for the classification model.
 For the same RoBERTa language model with different numbers of transformer layers, 24 layers of transformers had better accuracy than 3 layers,
@@
 \hline\hline
-RoBERTa-(3l)   & CIFAR-10 	&	99.74\% \\
-RoBERTa-large(3l)  & CIFAR-10 	&	99.72\% \\
-RoBERTa-large(24l)  & CIFAR-10 	&	99.60\% \\
+RoBERTa-large(3)   & CIFAR-10 	&	99.74\% \\
+RoBERTa-large(3)  & CIFAR-10 	&	99.72\% \\
+RoBERTa-large(2)  & CIFAR-10 	&	99.60\% \\
 \hline
-RoBERTa-(3l)    & CIFAR-100 	&	99.66\% \\
-RoBERTa-large(3l)  & CIFAR-100   & 	99.10\% \\
-RoBERTa-large(24l) & CIFAR-100  &	99.76\% \\
+RoBERTa-large(3)    & CIFAR-100 	&	99.66\% \\
+RoBERTa-large(3)  & CIFAR-100   & 	99.10\% \\
+RoBERTa-large(24) & CIFAR-100  &	99.76\% \\
 \hline\hline
@@
 $5.4$ billions of tokens of wiki data and other resources.
-The transformers in the pre-trained language models use multiple layers for representing images and may be used in other Computer Vision task, \eg object detection, gesture prediction.
+The transformers in the pre-trained language models use multiple layers for representing images and may be used in other Computer Vision task, e.g. object detection, gesture prediction.
 
@@
 
+%
+% ---- Bibliography ----
+%
+% BibTeX users should specify bibliography style 'splncs04'.
+% References will then be sorted and formatted in the correct style.
+%
+% \bibliographystyle{splncs04}
+% \bibliography{mybibliography}
+%
 {\small
-\bibliographystyle{ieee_fullname}
-\bibliography{iccv_classification}
+\bibliographystyle{splncs04}
+\bibliography{cpvr_classification}
+
 }

### 2021-04-16 A-BasicCommom/CICAI2021/image_classification.tex
1. writeup the paper.

@@
 \usepackage{graphicx}
+\usepackage[breaklinks=true]{hyperref}
 % Used for displaying a sample figure. If possible, figure files should
@@
   As the \underline{B}idirectional \underline{E}ncoder \underline{R}epresentations from \underline{T}ransformers became popular in many tasks of natural language processing recent years,
-  it is intuitive to use these pre-trained language models for enhancing the computer vision tasks, e.g. image classification.
-  In this paper, by encoding image pixels using pre-trained transformers, then connect to a fully connected layer,
-  the classification model outperforms the Wide ResNet model, and the linear-probe iGPT-L model,
-  and achieved accuracy of $99.60\%\sim99.74\%$ on the CIFAR-10 image set and accuracy of $99.10\%\sim99.76\%$ on the CIFAR-100 image set.
+  it is intuitive to use these pre-trained language models for enhancing the computer vision tasks.
+  In this paper, by encoding image pixels using pre-trained transformers models, then connect to a fully connected layer,
+  the classification model outperforms the iGPT-L model, and achieved accuracy of $99.60\%\sim99.74\%$ on the CIFAR-10 image set,
+  accuracy of $99.10\%\sim99.76\%$ on the CIFAR-100 image set, and achieved accuracy of $99.51\%\sim100.00\%$ on the COVID-19 tomography image test set.
 
@@
   Unsupervised pre-training is important to modern research of deep learning.
-  Lee et al.~\cite{lee2009convolutional} used the pre-training approaches
-  in Computer Vision tasks in 2009, and later from 2010 to 2016,
-  Nair and Hinton~\cite{nair2010rectified} proved that the pre-training process is supplementary in the Computer Vision tasks,
-  thus, can be omitted in some cases.
-  However, it started to flourish in the natural language processing domain since Mikolov et al.~\cite{mikolov2013distributed} had proposed Word2Vec.
-  Not long before Devin et al.~\cite{devlin2019bert}'s BERT language model dominates in most tasks in natural language processing,
-  which is close resemble of Vicent et al.~\cite{vincent2008extracting}'s Denoising Autoencoder model, which was initially designed for images.
-  The pre-training process becomes one of the most important procedures in deep learning.
+  Lee et al.~\cite{lee2009convolutional} used the pre-training approaches in Computer Vision tasks in 2009,
+  and, Nair and Hinton~\cite{nair2010rectified} proved that the pre-training process is supplementary, which can be omitted in some cases, in the Computer Vision tasks later from 2010 to 2016,
+  However, it started to flourish since Mikolov et al.~\cite{mikolov2013distributed} had proposed Word2Vec in the natural language processing,
+  recently, Devin et al.~\cite{devlin2019bert}'s BERT language model dominates in most tasks in natural language processing.
+  The pre-training approach in natural language processing is close resemble to Vicent et al.~\cite{vincent2008extracting}'s Denoising Autoencoder model initially designed for images processing.
+  Thus, the pre-training step becomes important in CV and NLP.
 
@@
 And it is difficult in handling the dichotomy between pixels and natural language texts in a single model.
+For per-pixel approach, non-parametric classifiers, e.g.
+neural networks, support vector machines, and decision trees,
+are the most well-known algorithms for their performance and generalization advantages in the late 1990s and 2000s.
   Cui et al.~\cite{cui2020revisiting} proposed several whole-word-masking pre-trained Chinese language models,
-which are improved versions of BERT~\cite{devlin2019bert} pre-trained language models, namely RBT3, RBTL3, and RoBERTa-wwm-ext-large.
+which are improved versions of BERT~\cite{devlin2019bert} pre-trained language models, namely RoBERTa(3), RoBERTa-L(3), and RoBERTa-L(24).
+The training of the RoBERTa(3) language model was based on Devlin et.
+al.'s BERT model,
+moreover, the pre-trained Chinese language models use extra 5 billion training tokens comparing to 0.4 billion tokens in the BERT model.
 These models achieved better performance in Chinese machine reading comprehension, Chinese document classification, and other downstream natural language tasks.
@@
 and tested on the CUB-200-2011 image dataset and achieved $85.55\%$ by combining GoogLeNet~\cite{szegedy2015going} and CNN-RNN~\cite{reed2016learning}, the result outperformed many competitors.
-  Lu and Weng found that, for per-pixel approach, non-parametric classifiers, e.g. neural networks, support vector machines, and decision trees,
-are the most well-known algorithms for their performance and generalization advantages in the late 1990s and 2000s.
   Fern{\'a}ndez et al.~\cite{fernandez2014we} compared different classifiers in small datasets, and they found that the random forest algorithm ranks first among the 179 classifiers.
@@
 e.g. support vector machines and conditional random field, in many datasets such as movie reviews, Stanford sentiment treebank, and TREC question.
-Cui et al.'s pre-trained language model, namely RoBERTa(3), RoBERTa-large(3), and RoBERTa-large(24), had improved performances over many other machine learning algorithms.
-BERT and RoBERTa-large(24) models both achieved an f1-score of 97.8\% in the THUCNews dataset, which contains 65,000 news reports in 10 domains.
+Cui et al.'s pre-trained language model, namely RoBERTa(3), RoBERTa-L(3), and RoBERTa-L(24), had improved performances over many other machine learning algorithms.
+BERT and RoBERTa-L(24) models both achieved an f1-score of 97.8\% in the THUCNews dataset, which contains 65,000 news reports in 10 domains.
 
@@
 
-\section{Image Classification by Convolutional and Transformer networks}
+\section{Image Classification by Convolutional and Transformer Networks}
 
-Three of the most popular approaches for image classification tasks are per-pixel, subpixel, and heterogeneous.
+We use the Jittor\cite{hu2020jittor} library as the modeling tool, and the TsinghuaDogs\cite{Zou2020TsinghuaDogs} dataset to compare the performance with competitors.The experiment was performed on an Nvidia V100, with 16GB of RAM,
+which can provide 100 tera-flops of computation capability.
 
@@
 
-\par CNN models are fundamental architectures to compare the performance.
-A vision system is an Attention mechanism that focuses limited attention on the key information, saving resources and getting the most efficient information quickly.
-Attention models are less complex and have fewer parameters than CNN and RNN. So the demand for calculation is even smaller.
-Attention addresses an issue in which RNN cannot be calculated in parallel.
-The Attention mechanism does not rely on the calculations of the next step, so it can be processed in parallel with CNN.
-Before the introduction of the Attention mechanism, there was a problem that long distances of information would be weakened,
+\par Three of the most popular approaches for image classification tasks are per-pixel, subpixel, and heterogeneous.
+CNN models are fundamental and often used as baselines to compare the classification performance.
+The vision system of human has a mechanism that focuses limited attention on the key information to save resources and to get the most efficient information quickly.
+Before introduction of the Attention mechanism, there was a problem in RNN that long distances of information would be weakened,
 just as people with weak memory could not remember the past.
 
-\par We use the Jittor\cite{hu2020jittor} library as the modeling tool, and the TsinghuaDog\cite{Zou2020ThuDogs} dataset to compare the performance with competitors.
-Image pre-process steps including resizing to $256*256$, center-cropping by $224*224$, a random horizontal flip, conversion to (0,1), and normalization to 0.485 of mean value and 0.229 of standard error.
+\par Image pre-process steps including resizing to $256*256$, center-cropping by $224*224$, a random horizontal flip, conversion to (0,1), and normalization to 0.485 of mean value and 0.229 of standard error.
 
-\par RESNET has been proved to be efficient and effective in Computer Vision modeling, thus, a lot of time could be saved by supervised learning on a new CV task.
+\par The ResNet has been proved to be efficient and effective, thus, a lot of time could be saved by starting from a pre-trained model for a new Computer Vision task.
 It is not surprising that the residual mechanism can learn deep layers with some layers skipped for different tasks.
-
-\par We use the RESNET with two 1x1 Convolutional layers for matching the gap between output of the RESNET and the Attention.
-The Attention has multiple heads and use the Self-Attention, the Query, Key, and Value dimensions are all same, 512 is an empirical value.
-
-\par The experiment was performed on an Nvidia V100, with 16GB of RAM,
-which can provide 100 tera-flops of computation capability.
 
@@
 \hline
-Alexnet & 41.73\%\\
+AlexNet & 41.73\%\\
 GoogLeNet & 68.84\%\\
-mobilenet\_v2 & 63.65\%\\
-shufflenet\_v2\_x0\_5  &	45.38\% \\
-Attention-RESNET152-4H-256L &  	55.00\% \\
-Attention-RESNET152-1H-1024L &  	67.57\% \\
+MobileNet\_v2 & 63.65\%\\
+ShuffleNet\_v2\_x0\_5  &	45.38\% \\
+Attention-ResNet152-4H-256L &  	55.00\% \\
+Attention-ResNet152-1H-1024L &  	67.57\% \\
 \hline
 \hline
-\hline
-Attention-RESNET152-1H-1024L &  	78.38\% \\
-DENSENET121   	&	75.29\% \\
-SE-RESNET50 & 79.47\% \\
-RESNET50 & 82.50\%\\
-Gelu-RESNET152 &	64.06\% \\
-RESNET152  	&	85.14\% \\
-SE-RESNET152  	&	83.34\% \\
-SE-RESNET152+RESNET152 & 82.62\% \\
-SE-RESNET152+Alexnet & 80.38\% \\
-RESNET200  	&	73.19\% \\
+Attention-ResNet152-1H-1024L &  	78.38\% \\
+DenseNet121   	&	75.29\% \\
+SE-ResNet50 & 79.47\% \\
+ResNet50 & 82.50\%\\
+Gelu-ResNet152 &	64.06\% \\
+ResNet152  	&	85.14\% \\
+SE-ResNet152  	&	83.34\% \\
+SE-ResNet152+ResNet152 & 82.62\% \\
+SE-ResNet152+AlexNet & 80.38\% \\
+ResNet200  	&	73.19\% \\
 \hline
 \hline
-\hline
-RESNET152  	&	84.87\% \\
-SE-RESNET152  	&	82.92\% \\
+ResNet152  	&	84.87\% \\
+SE-ResNet152  	&	82.92\% \\
 \hline
@@
 \end{center}
-\caption{Comparision of model accuracy on the ThuDogs dataset. The top part models use 10\% of the whole ThuDogs data, the middle part models use 80\% of the ThuDogs data,
-and the bottom part models use 100\% of the ThuDogs data.}
+\caption{Comparision of model accuracy on the TsinghuaDogs dataset. The top part models use 10\% of the whole TsinghuaDogs data, the middle part models use 80\% of the TsinghuaDogs data,
+and the bottom part models use 100\% of the TsinghuaDogs data.}
 \end{table}
@@
 \subsection{Dataset Amount Usage}
-From the Table (1) RESNET152 and SE-RESNET152 in the middle part and the bottom part, we can see that because of the imbalance of the dataset on different class, the top class has 7449 instance,
-and the bottom class has 200 instance. As a result, using 80\% of the ThuDogs data might beat the 100\% under Stochastic gradient descent optimizer.
-For later discussion, we use 80\% of the ThuDogs data to train the model discussed for best performance and accuracy.
+
+From the Table (1) ResNet152 and SE-ResNet152 in the middle part and the bottom part, we can see that there is imbalance on the dataset for different classes, the top class has 7449 instances,
+and the bottom class has 200 instances. As a result, using 80\% of the TsinghuaDogs data might beat the 100\% under Stochastic Gradient Descent optimizer.
+In later discussion, we use 80\% of the TsinghuaDogs data to train the model for best performance and accuracy.
 
@@
 
-All models in the Table (1) share a common architecture that a base feature selection layer, such as AlexNet, followed by a fully connected layer which was used as a mapping function from ImageNet dataset classes to ThuDogs dataset classes.
+All models in the Table (1) share a common architecture that a base feature selection layer, such as AlexNet, followed by a fully connected layer which was used as a mapping function from ImageNet dataset classes to TsinghuaDogs dataset classes.
 The Attention based model use two $1*1$ convolutional layers serves as transition between the average-pool layer and the fully connected layer.
 Between that we use the Multi-head Attention layer with 1024 as the max sequence and 1 head, the k-dim and v-dim are 1024 and the self attention mechanism was used.
-The Alexnet, GoogLeNet, mobilenet, shufflenet, Densenet, Resnet, SE-RESNET are the well-known models. The Gelu-Resnet replace the Relu with Gelu function.
-The RESNET200 increase the third phase parameter from 36 to 48, with a parameter of $[3,8,48,3]$.
-The Attention-RESNET152-4H-256L and Attention-RESNET152-1H-1024L model differs only on the number of heads, and the input dimension, the first model has 4 heads and 256 dimension for embedding dimension, K-dim and V-dim.
+The AlexNet, GoogLeNet, MobileNet, ShuffleNet, DenseNet, ResNet, SE-ResNet are the well-known models. The Gelu-ResNet replace the Relu with Gelu function.
+The ResNet200 increase the third phase parameter from 36 to 48, with a parameter of $[3,8,48,3]$.
+The Attention-ResNet152-4H-256L and Attention-ResNet152-1H-1024L model differs only on the number of heads, and the input dimension, the first model has 4 heads and 256 dimension for embedding dimension, K-dim and V-dim.
 For the Attention layer, the shape of the input was transformed to (batch, channel, sequence), then transposed to (batch, sequence, channel) for the Attention layer.
@@
 
-From the Table(1) we can see that the Attention layer doesn't improve the performance on the ThuDogs validation dataset, there is 6.85\% gap comparing to the RESNET152 model.
-Experiment on the Attention model number of heads and sequence length showed that, (Attention-RESNET152-4H-256L \&  	55.00\%, Attention-RESNET152-1H-1024L \&  	67.57\%),
-increasing the number of head and reducing the sequence length have negative impact on the accuracy of the ThuDogs Dataset.
-Experiment showed that, the Attention mechanism following the ResNet doesn't show improvement on the accuracy, and so as the Squeeze-Extract mechanism, Gelu activation, and combination of Resnet with other networks, such as AlexNet or SERESNET.
+From the Table (1) we can see that the Attention layer doesn't improve the performance on the TsinghuaDogs validation dataset, there is 6.85\% gap comparing to the ResNet152 model.
+Experiment on the Attention model number of heads and sequence length showed that, (Attention-ResNet152-4H-256L \&  	55.00\%, Attention-ResNet152-1H-1024L \&  	67.57\%),
+increasing the number of head and reducing the sequence length have negative impact on the accuracy of the TsinghuaDogs Dataset.
+Experiment showed that, the Attention mechanism following the ResNet doesn't show improvement on the accuracy, and so as the Squeeze-Extract mechanism, Gelu activation, and combination of ResNet with other networks, such as AlexNet or SEResNet.
+\par To state it clear that, by adding the Transformer layer around the ResNet doesn't improve the overall performance of the image classification task.
+Careful architecture design should be performed, otherwise, there would be negative gain from the architecture redesign.
+Experiment showed that the ResNet152 is still a strong baseline for the Image Classification task.
 
@@
 
-My approach consists of a pre-training stage followed by a fine-tuning stage.
-In the pre-training, I use the BERT objectives, and the sequence Transformer architecture to predict language tokens.
+Our approach consists of a pre-training stage followed by a fine-tuning stage.
+In the pre-training, we use the BERT objectives, and the sequence Transformer architecture to predict language tokens.
 
@@
 embedding for each position.
-Then I use a fully connected layer as a non-linear function from embeddings to image classes.
+Then we use a fully connected layer as a non-linear function from embeddings to image classes.
 The dropout layer and the Softmax layer are used for better transfer performance between the training and the test datasets.
@@
 
-We used the RoBERTa-large with 3 and 12 layers as encoder, and tested on two Chinese Judicial datasets, which has two and four classes.
+We used the RoBERTa-L with 3 and 24 layers as encoder, and tested on two Chinese Judicial datasets, which has two and four classes.
 The \textit{Two-Case} dataset annotated civil and criminal cases, and the \textit{Four-Case} dataset annotated by civil, criminal, intellectual property, and administrative cases.
@@
 \hline\hline
-RoBERTa-large(24) & Two-Case	&	99.80\% \\
-RoBERTa-large(24) & Four-Case	&	99.76\% \\
-RoBERTa-large(3)  & Four-Case	&	96.35\% \\
+RoBERTa-L(24) & Two-Case	&	99.80\% \\
+RoBERTa-L(24) & Four-Case	&	99.76\% \\
+RoBERTa-L(3)  & Four-Case	&	96.35\% \\
 \hline
@@
 
-I design simple classification models without too many layers, as Figure (1) shows,
+We design simple classification models without too many layers, as Figure (1) shows,
 and use the CIFAR-10 and CIFAR-100 dataset as an example to show the architecture of the model.
@@
 
+\par In total, 349 computed tomography images were collected from the COVID-19 reports in the MedPix, LUNA, Radiopaedia,
+PubMed Central databases, which sizes range from $1637\times1225$ to $148\times61$.
+The COVID19 lung tomography dataset contains 251 covid images and 291 covid negative images in the training set,
+and contains 98 covid image and 100 covid negative images in the test set.
+All images are resized to a resolution of $32\times32$ pixels, the RGB channels are kept and the alpha channel values are discarded.
+For the COVID-19 lung tomography dataset, the metadata is the filename of the images, which can be treated as the supervised description of the image.
+Peek some the filenames, e.g. \textit{covid\_201\_1.png}, \textit{covid\_201\_2.png}, and \textit{noncovid\_001\_1.png},
+
 \par The CIFAR-10 dataset contains 60,000 color images with a resolution of $32\times32$ in 10 classes, and the CIFAR-100 dataset has 100 classes containing 600 images each.
@@
 In the Feature-Extraction layer, a combination of one dropout layer, one fully connected layer, and one softmax layer, as Equation (2), is used.
-The softmax layer is an approach that make the probability $z$ of each class more focused by taking exponent of it, then use normalization for each class probability.
-In the Output layer, the classification label of the image is feed in the model.
+The Softmax layer is an approach that make the probability $z$ of each class more focused by taking exponent of it, then use normalization for each class probability.
+In the Output layer, the classification label of the image is fed into the model.
 
@@
 
-\subsection{More Fair Comparison by The Mask Token}
-
 \par It is intuitive for the model to use both the channel values and the metadata in the training phase.
@@
 and it is beneficial for the classification model to understand the supervised descriptive information for the image.
-
-\par Recall that the $\textbf{[MASK]}$ token in the BERT language model is a special token which can be used to trim the vocabulary size,
-and gives the token-recovery capability to the downstream task model.
-
-\par However, in the test phase, if feeding the metadata to the model, people might argue that the model learns only the mapping function from
-the metadata, which is the filename in this case, to the image class, which makes it is unfair to compare the performance with other image classification models.
-Thus, to be more objective and fair, I add a preprocess step for the metadata in the test phase, using the $\textbf{[MASK]}$ token to replace each
-ASCII character of the filename then feeds into the model to do the inference.
 
@@
 \begin{center}
-  \fbox{\rule{0pt}{2in} \includegraphics[width=0.9\linewidth]{roberta-cifar.pdf}}
+  \fbox{\rule{0pt}{0in} \includegraphics[width=0.9\linewidth]{image-classification(3).pdf}}
 \end{center}
@@
 
-As Cui et. al.~\cite{cui2020revisiting} reported that the training of the RBT3 language model was based on Devlin et. al.'s model,
-moreover, the pre-trained Chinese language models use extra 5 billion training tokens comparing to Devlin et. al.'s 0.4 billion tokens.
 We use a batch size of 512 and train for $6\sim16$ epochs using AdamW with $\beta_1=0.99$, $\beta_2=0.999$, and weight decay of $10^{-8}$.
-We set the learning rate to $10^{-4}$ and no warmed up or decay are used.
+We set the learning rate to $10^{-4}$ and no warm-up or decay are used.
 The dropout rate is $0.05$.
 
-\par When fine-tuning, as Figure (2), We check the accuracy of the trained model on the test set and stopped training when it converges on $10^{-3}\sim10^{-4}$.
+\par When fine-tuning, as Figure (2), we check the accuracy of the trained model on the test set and stopped training when it converges on $10^{-3}\sim10^{-4}$.
 
@@
 From the Table (3), for the same size of a dataset with larger classes, it needs more epochs and training time for the classification model.
-For the same RoBERTa language model with different numbers of transformer layers, 24 layers of transformers had better accuracy than 3 layers,
-however, its training cost grows for the larger language model.
-For the same fine-tuned language model, classes number has positive impact on the accuracy.
+For the same RoBERTa language model with different numbers of transformer layers, 24 layers had better accuracy than 3 layers,
+however, the training cost grows for the larger language model.
+For the same fine-tuned language model, class number has positive impact on the accuracy.
 And the fewer classes the dataset has, the more accurate results the model can achieve.
+
+\par RoBERTa-S is short for RoBERTa-Small which has 768 hidden dimension, RoBERTa-L is short for RoBERTa-Large  which has 1024 hidden dimension.
 
@@
 Language Model 	& Dataset  & Accuracy \\
-\hline\hline
-RoBERTa-large(3)   & CIFAR-10 	&	99.74\% \\
-RoBERTa-large(3)  & CIFAR-10 	&	99.72\% \\
-RoBERTa-large(2)  & CIFAR-10 	&	99.60\% \\
 \hline
-RoBERTa-large(3)    & CIFAR-100 	&	99.66\% \\
-RoBERTa-large(3)  & CIFAR-100   & 	99.10\% \\
-RoBERTa-large(24) & CIFAR-100  &	99.76\% \\
+\hline
+RoBERTa-S(3)   & COVID19 	&	100.0\% \\
+RoBERTa-L(3)  & COVID19 	&	99.51\% \\
+RoBERTa-L(24)  & COVID19 	&	100.0\% \\
+\hline
+RoBERTa-S(3)   & CIFAR-10 	&	99.74\% \\
+RoBERTa-L(3)  & CIFAR-10 	&	99.72\% \\
+RoBERTa-L(24)  & CIFAR-10 	&	99.60\% \\
+\hline
+RoBERTa-S(3)    & CIFAR-100 	&	99.66\% \\
+RoBERTa-L(3)  & CIFAR-100   & 	99.10\% \\
+RoBERTa-L(24) & CIFAR-100  &	99.76\% \\
 \hline\hline
@@
 \end{center}
-\caption{Comparision of accuracy of the pre-trained language models and iGPT-L on the CIFAR-10 and CIFAR-100 datasets in the image classification task.
-RoBERTa-large is short for RoBERTa-wwm-ext-large. (a) iGPT-L model was trained far more than 18 epochs, it was trained by 1,000,000 iterations of pre-training and a few epochs for fine-tuning.}
+\caption{Comparision of accuracy of the pre-trained language models and iGPT-L on the COVID19, CIFAR-10 and CIFAR-100 datasets in the image classification task.
+    (a) iGPT-L model was trained far more than 18 epochs, it was trained by 1,000,000 iterations of pre-training and a few epochs for fine-tuning.}
 \end{table}
@@
 
+\section{Reproducibility}
+
+The convolutional neural networks for image classification experiment notebook can be found at https://colab.research.google.com/drive/\\
+167uMdDGmXSr1xwdM4GFwfiuBpz0bCbeA?usp=sharing. Related code are placed on https://github.com/ShenDezhou/CAIL2021/tree/master/dogflb.
+
+The image classification model with transformer encoder experiment notebook can be found at https://colab.research.google.com/drive/\\
+1saMYaaR3ih1eo9ttYy0Ncb5V003uVyEV?usp=sharing. Related code are placed on https://github.com/ShenDezhou/CAIL/tree/master/CAIL2020/rlfl.
+
 \section{Conclusion}
@@
  as an example to prove its performance for Computer Vision tasks, such as image classification.
- The finding might benefit various subjects, namely  for their specific research.
+ The finding might benefit various subjects.
 Tests showed that the proposed model outperforms the iGPT-L model without augmentation on the image dataset,
 the model achieved accuracy of $99.60\%\sim99.74\%$ on the CIFAR-10 image set,
-and accuracy of $99.10\%\sim99.76\%$ on the CIFAR-100 image set.
+accuracy of $99.10\%\sim99.76\%$ on the CIFAR-100 image set, and achieved accuracy of $99.51\%\sim100.00\%$ on the COVID-19 tomography image test set.
 

### 2021-04-17 A-BasicCommom/CICAI2021/image_classification.tex
1.might be the last final version.

@@
 
-  Image classification and categorization are essential to the capability of telling the difference between images for a machine vision task.
-  As the \underline{B}idirectional \underline{E}ncoder \underline{R}epresentations from \underline{T}ransformers became popular in many tasks of natural language processing recent years,
-  it is intuitive to use these pre-trained language models for enhancing the computer vision tasks.
-  In this paper, by encoding image pixels using pre-trained transformers models, then connect to a fully connected layer,
-  the classification model outperforms the iGPT-L model, and achieved accuracy of $99.60\%\sim99.74\%$ on the CIFAR-10 image set,
-  accuracy of $99.10\%\sim99.76\%$ on the CIFAR-100 image set, and achieved accuracy of $99.51\%\sim100.00\%$ on the COVID-19 tomography image test set.
+  The \underline{B}idirectional \underline{E}ncoder \underline{R}epresentations from \underline{T}ransformers represents the recent popularity of many tasks in natural language processing.
+  These pre-trained language models have been used to enhance computer vision tasks for many years.
+  This paper uses a pre-trained transformer model to encode image pixels, and then connects to the fully connection layer, dropout layer and Softmax layer.
+  The performance of the classification model is better than the current best iGPT-L model.
+  It surpasses the current best accuracy in the CIFAR-10/100 image set and the COVID-19 tomographic image classification set.
 
@@
 
- This paper proposed a novel idea by using the pre-trained language models for image representation and take image classification
- as an example to prove its performance for Computer Vision tasks, such as image classification.
- The finding might benefit various subjects.
-Tests showed that the proposed model outperforms the iGPT-L model without augmentation on the image dataset,
-the model achieved accuracy of $99.60\%\sim99.74\%$ on the CIFAR-10 image set,
-accuracy of $99.10\%\sim99.76\%$ on the CIFAR-100 image set, and achieved accuracy of $99.51\%\sim100.00\%$ on the COVID-19 tomography image test set.
+This article proposes a new idea of using pre-trained language models for image characterization and image classification.
+Through empirical analysis, the negative impact of the transformer on the CNN model is discussed, and it is proved that the pre-trained language model can improve the performance in image classification.
+This finding may benefit various topics of computer vision tasks.
+The test shows that the proposed model is better than the classification effect of the iGPT-L model without enhancing the image data set.
+The accuracy is $99.60\%\sim99.74\%$ on the CIFAR-10 image set, $99.10\%\sim99.76\%$ on the CIFAR-100 image set, and $99.51\%\sim100.00\%$ on the COVID-19 tomographic image test set.
 

### 2021-04-18 A-BasicCommom/CICAI2021/image_classification.tex
1. fix some writeup.

@@
 
-  Unsupervised pre-training is important to modern research of deep learning.
+  \par Unsupervised pre-training is important to modern research of deep learning.
   Lee et al.~\cite{lee2009convolutional} used the pre-training approaches in Computer Vision tasks in 2009,
@@
   Thus, the pre-training step becomes important in CV and NLP.
+
+  \par The presentation of the Transformer~\cite{vaswani2017attention} model has profoundly changed the field of NLP,
+especially the subsequent series of Transformer-based large-scale pre-training language models,
+which opened a new model training paradigm in NLP: first in large-scale unlabeled Pre-train the model on the text,
+and then use task-specific small data to fine-tune the model.
+
+  \par Transformer's first show in CV is Vision Transformer~\cite{dosovitskiy2020image}.
+The specific method is to divide a picture into multiple non-overlapping patches.
+The patch here can be considered as a token in NLP, and the patches are arranged to form a sequence, get patches embedding after a Linear Embedding.
+In order to do the image classification task, it is still imitating the BERT method of adding $[CLS]$, adding a special mark $[class]$ at the beginning of the patch sequence, and then add the position code to the Transformer to do the encoding.
+
+  \par Liu et al.~\cite{liu2021swin} uses a patch merge mechanism between the Transformer layers to integrate adjacent patch features to achieve an effect similar to the downsampling in CNN.
+In ViT, self-attention is calculated for all input patches, and the shifted window mechanism designed by Liu et al.
+allows self-attention to be calculated only for patches in a certain local window for the complexity problem of Transformer.
+The window should be shifted to the lower right corner, this achieves cross-window feature interaction, which makes up for the limitation that only a single window can be seen.
+To a certain extent the receptive field is expanded on the upper side. The design is to have two successive Transformer layers, one using regular windows, and the other using sliding windows.
 
@@
 And it is difficult in handling the dichotomy between pixels and natural language texts in a single model.
-For per-pixel approach, non-parametric classifiers, e.g.
-neural networks, support vector machines, and decision trees,
+For per-pixel approach, non-parametric classifiers, e.g. neural networks, support vector machines, and decision trees,
 are the most well-known algorithms for their performance and generalization advantages in the late 1990s and 2000s.
-  Cui et al.~\cite{cui2020revisiting} proposed several whole-word-masking pre-trained Chinese language models,
-which are improved versions of BERT~\cite{devlin2019bert} pre-trained language models, namely RoBERTa(3), RoBERTa-L(3), and RoBERTa-L(24).
-The training of the RoBERTa(3) language model was based on Devlin et.
-al.'s BERT model,
-moreover, the pre-trained Chinese language models use extra 5 billion training tokens comparing to 0.4 billion tokens in the BERT model.
-These models achieved better performance in Chinese machine reading comprehension, Chinese document classification, and other downstream natural language tasks.
+ \par Cui et al.~\cite{cui2020revisiting} proposed several whole-word-masking pre-trained Chinese language models, which are improved versions of BERT~\cite{devlin2019bert} pre-trained language models.
+The pre-trained Chinese language models use extra 5 billion training tokens comparing to 0.4 billion tokens in the BERT model.
+BERT and RoBERTa-L(24) models both achieved an f1-score of 97.8\% in the THUCNews dataset.
   He and Peng~\cite{he2017fine} combined the vision stream and language stream as two parallel channels for extracting multi-source information in the image classification task,
@@
 e.g. support vector machines and conditional random field, in many datasets such as movie reviews, Stanford sentiment treebank, and TREC question.
-Cui et al.'s pre-trained language model, namely RoBERTa(3), RoBERTa-L(3), and RoBERTa-L(24), had improved performances over many other machine learning algorithms.
-BERT and RoBERTa-L(24) models both achieved an f1-score of 97.8\% in the THUCNews dataset, which contains 65,000 news reports in 10 domains.
 
@@
 
-We use the Jittor\cite{hu2020jittor} library as the modeling tool, and the TsinghuaDogs\cite{Zou2020TsinghuaDogs} dataset to compare the performance with competitors.The experiment was performed on an Nvidia V100, with 16GB of RAM,
-which can provide 100 tera-flops of computation capability.
+We use the Jittor\cite{hu2020jittor} library as a modeling tool to compare with competitors on the TsinghuaDogs\cite{Zou2020ThuDogs} dataset.
+The experiment was conducted on the Nvidia V100 with a memory of 16GB which provides 100 Tera-Flops computing power.
 
@@
 
-\par Three of the most popular approaches for image classification tasks are per-pixel, subpixel, and heterogeneous.
-CNN models are fundamental and often used as baselines to compare the classification performance.
+\par CNN models are fundamental and often used as baselines to compare the classification performance.
 The vision system of human has a mechanism that focuses limited attention on the key information to save resources and to get the most efficient information quickly.
@@
 From the Table (1) ResNet152 and SE-ResNet152 in the middle part and the bottom part, we can see that there is imbalance on the dataset for different classes, the top class has 7449 instances,
-and the bottom class has 200 instances. As a result, using 80\% of the TsinghuaDogs data might beat the 100\% under Stochastic Gradient Descent optimizer.
+and the bottom class has 200 instances.
+As a result, using 80\% of the TsinghuaDogs data might beat the 100\% under Stochastic Gradient Descent optimizer.
 In later discussion, we use 80\% of the TsinghuaDogs data to train the model for best performance and accuracy.
@@
 
-Generality speaking, the performance of the pre-trained language models achieved in the document classification tasks.
-
 We used the RoBERTa-L with 3 and 24 layers as encoder, and tested on two Chinese Judicial datasets, which has two and four classes.
@@
 
-For the per-pixel image classification approach, for every RGB channel of pixels in an image,
+\par For the per-pixel image classification approach, for every RGB channel of pixels in an image,
 each pixel had its pixel-channel code, ranging from 0x00 to 0xff for different colors.
@@
 \begin{center}
-  \fbox{\rule{0pt}{2in} \includegraphics[width=0.9\linewidth]{classification.pdf}}
+  \fbox{\rule{0pt}{0in} \includegraphics[width=0.95\linewidth]{classification.pdf}}
 \end{center}
@@
 
-We design simple classification models without too many layers, as Figure (1) shows,
+\par We design simple classification models without too many layers, as Figure (1) shows,
 and use the CIFAR-10 and CIFAR-100 dataset as an example to show the architecture of the model.
-The model architecture has seven functional layers:
-
-\begin{itemize}
-\item {\bf Input layer}
-\item {\bf Concatenation layer}
-\item {\bf Trim layer}
-\item {\bf Encoder layer}
-\item {\bf Embedding layer}
-\item {\bf Feature Extraction layer}
-\item {\bf Output layer}
-\end{itemize}
+The model architecture has seven functional layers: Input layer,
+Concatenation layer,
+Trim layer,
+Encoder layer,
+Embedding layer,
+Feature Extraction layer,
+Output layer.
 
@@
 \end{center}
-   \caption{Accuracy of the image classification models with the pre-trained language encoder on the CIFAR-10 and CIFAR-100 dataset in the training epochs.}
+   \caption{Accuracy of the image classification models with the pre-trained language encoder on the CIFAR-10/10 and COVID-19 dataset in the training epochs.}
 \label{fig:short}
